Suicide mention

My journey through medication has been long and storied.

\begin{quote}
Tell me.
\end{quote}

In time.

All meds come with side effects, of course. If you take too much lithium, I found, you cycle rapidly through moods, start vomiting, and the right side of your body goes weak. When you go off fluoxetine, you get what are called brain zaps, which is rather like the feeling of missing a step on a staircase and slipping safely down to the one below it; that sense of unbalance and terror and near miss, followed by relief and surety repeated once every few seconds.

\begin{quote}
When you take anxiolytics and your life is a mess beyond simple anxiety disorders, you dissociate so hard that you try to kill yourself.
\end{quote}

I said later.

\begin{quote}
Continue.
\end{quote}

Thank you.

Well, when you take antipsychotics for long enough, you run the risk of movement disorders. That was something that had originally crossed my mind when the tic first started, except I wasn't on any of the relevant meds at the time.

\begin{quote}
And you didn't think to bring it up when you started on olanzapine.
\end{quote}

No.

\begin{quote}
Nor when you switched to quetiepine, or from there to lurasidone.
\end{quote}

No.

\begin{quote}
Why?
\end{quote}

March 10, 2018:

I stayed away from reading too much about my own mental health problems for a long time because I'm not a doctor, and have seen what trying to be smarter than one's doctor can do. In fact, I stayed away from reading most anything about these things for a long time, until I realized I needed SOME language to describe what was going on to my docs.

\begin{quote}
And how did that work?
\end{quote}

With a recent physical health problem cropping up, I decided that my embargo wasn't worth keeping up in that instance. Of course, almost immediately after, I suffered a crash and decided to do a bunch of reading on bipolar, and you know, it's a real shitmess.

I had thought I'd have a chance at normalcy, that I'd get better over time, that - and here I should've been tipped off to the impossibility of the scenario - I'd be able to return to some previous golden era of Madison.

\begin{quote}
And the physical health problem?
\end{quote}

A movement disorder.
