From the point of view of the universe, Max's death wasn't a big deal, it was just my big deal.

On March 21st, 2012, I tried to kill myself.

It's amazing how such a simple statement of fact reflects, months of strange tension, slow recovery, and a whole lot of trying to understand what really happened. It's not a comfortable thing for anyone to discuss, but it's one of those things I need to discuss, need to get off my chest. A little too much of what makes life meaningful for me now is wrapped up in that one night.

\begin{quote}
Even now?
\end{quote}

Even now.

\begin{quote}
You wrote that disclaimer four months after the attempt itself. You copied it from some notes from back then. You even kept the Steve Eisman quote.
\end{quote}

Yes. Nostalgia, remember?

\begin{quote}
Are you nostalgic for those weighty months after you tried to kill yourself?
\end{quote}

If Matthew died on September of that year, then he was sick long before. This was part of his long, slow death rattle.

Perhaps it's not totally accurate to say that I'm nostalgic for that time in particular, but I suppose I am nostalgic for the sense of change that permeated the air around me then. Something big was happening. Something terrible and wonderful.

\begin{quote}
And you got to witness it from the inside.
\end{quote}

Yes. I got to watch the agonal breathing that went on for far too long. I got to see his eyes widen in terror. I got up to fetch the cold compress and came back to a quiet room.

I'm not nostalgic for that pain, no. I'm nostalgic for the fact that I am who I am because I went through that. I'm nostalgic for what it came to symbolize. I'm nostalgic for its part in Madison's birth.
