The problem of working with clients on a task with a specified end-goal, one that is finished and about which you can say, ``ah, it does \emph{this} now'', is that when the project is done, there is nothing left.

\begin{quote}
This is a problem with any task. This is a grander problem.
\end{quote}

Yes, even with self-appointed tasks, even with tasks at a non job-shop. It happened just recently, too. I finished my time at IA. I got home from visiting Barac. I got the contract signed at NV.

If you hit a deadline and succeed, or if you have some work travel, or if you get home from a vacation, suddenly there's this empty bit of your future where there used to be this thing. There's just a void there. A sudden lack of weight.

\begin{quote}
And so, back then, you finished the release at work and also finished the office move in one fell swoop, and went home.
\end{quote}

I went home and took my meds like a good girl, and then proceeded to dissociate right through the evening.

Dissociation is a hell of a drug.

\begin{quote}
It's a dreamy thing. It's a soft thing. It's a cottony thing. It's a muffled thing. It's watching your hands move. It's watching yourself breathe. It's feeling the air move in and out of you with a distant, slightly confused detachment. It's ``ah, it does \textbf{this} now'', except saying that about some strange machine which is not yourself.
\end{quote}

I watched myself sit down in my chair. I watched myself turn on \emph{Babylon 5}. I watched myself mow through two glasses of gin.

\begin{quote}
You watched yourself with a metaphysical quirk of the eyebrow as you reached forward, grabbed the box of X-acto wood-carving tools --- purchased, doubtless, for some long forgotten project --- and flipped it open. You watched numbly as you slashed open the inside of your arm. There was a moment where you marveled at how long it took for the blood to well up, where you could see the white of subcutaneous fat.
\end{quote}

And then the pain snapped me to.
