Okay, I lied. Just a little bit.

\begin{quote}
Yes. You didn't dissociate through the entire thing. There was no small part of that scene that was horribly, terrfyingly intentional.
\end{quote}

What really woke me up was watching this person-who-was-me somehow go into `fuck it' mode and tear the shit out of his right arm from one end to the other with a very sharp, very new razor blade.

It was like the rush of coming to your senses after a nightmare, the pulling forward and the re-anchoring, the flood of adrenaline in preparation for flight.

It wasn't necessarily the cut that woke me. It was the second or so before when I entered that `fuck it' mode, and I was too slow, too confused and frightened to stop this person-who-was-me from pulling the ultimate embarrassing act: trying to commit suicide while watching a dumb '90s science fiction show.

\begin{quote}
It was a slow awakening. You weren't just too slow, you were not fully awake yet. The dream of dissociation was still clinging, gauzy, to you.
\end{quote}

V I do not know which to prefer, The beauty of inflections Or the beauty of innuendoes, The blackbird whistling Or just after.

I can remember it so clearly.

\begin{quote}
You can remember it because you still live it.
\end{quote}

Yes. I still feel that slide into someone-else-ness, and then the snap back when drawn back into self-ness. Back into here and now.

\begin{quote}
You felt that last night.
\end{quote}

Yes.

\begin{quote}
You felt that slide into dissociation, felt the folding blade click into place with a vague sense of surprise, then jolted as it drew across your leg.
\end{quote}

Yes.

\begin{quote}
You felt that same jolt of humiliation and pain and anger and fear.
\end{quote}

Yes.

\begin{quote}
Especially this time. You cut too deep. Your usual superficial-yet-still-painful scratch had turned into something of a flay.
\end{quote}

Yes.

\begin{quote}
You needed twelve stitches. You lied and said you dropped your knife while cleaning it.
\end{quote}

Yes.

\begin{quote}
Are you writing about this now because you were, on some subconscious level, working up to this most recent little climax?
\end{quote}

I really don't know.

\begin{quote}
Tell me what happened after.
\end{quote}

I started whispering James' name--

\begin{quote}
Both times?
\end{quote}

Both times. I started whispering his name, then eventually swallowed the miniscule bit of pride I had left and called out loud enough to wake him up. ``Can you come help me?'' I asked. It took asking two more times before he got up. I found out later that he thought I had made a mess and just wanted help cleaning up, thinking that I should just clean up my own messes. A good point, that.

Though the rest of the night in March is still sort of a blur --- I hadn't totally gotten out of the state that I was in, just woken up enough to engage with the mechanics --- I do remember James helping me to clean and bandage my arm as we sat on the floor of the bathroom, the dog occasionally wandering in and out. The whole time, I was still sobbing, blubbering out, ``I don't want to leave you, I don't want to leave Zephyr, I don't know why I did that, I'm sorry'' over and over again.
