I'm so tired.

\begin{quote}
I know.
\end{quote}

Can I let Matthew tell the story? Can I put his words here, and can I catch up on the sleep I missed while in the ER? Can I feel better before I write again?

\begin{quote}
Yes, but don't make a habit of it.
\end{quote}

Okay.

The last thing I did before going to bed that night was to send an email to work saying that I would be in later in the day due to an ``emergency appointment'' in the morning. I certainly couldn't tell them what had actually happened, but I had so thoroughly exhausted myself and still felt so bad that I decided sleeping in would help me out quite a bit.

I wound up at the office around eleven in the morning, and sat down, feeling tired, worn thin, and still traumatized from the fact that I had apparently acted out something I had thought was just one of those persistent negative thoughts that won't go away, one with no grounding in reality. Within minutes, I received a message from my boss informing me that my attitude in the last few weeks was not acceptable. I had been irritable and angry, to the point where my supervisors felt as though they had to word things so that I wouldn't get upset.

I was stuck in a weird situation, here. On the one hand, my boss was totally right and I really did need to take a look at how I was interacting with others at work, but on the other hand, I wasn't in a place to do anything about it at the time, and I certainly didn't feel as though I could talk to my boss about what had happened in order to save the conversation for another time.

I did my best to accept it and trudge through the rest of the day. The plan that was in place before was to follow a friend up to Blackhawk for a free night at a casino hotel that he had available. It seemed like getting out of town might actually help, and it also meant that my workday was significantly shorter than it would've been otherwise.

The drive after work was calming, and I actually got to the point where I felt as though the night out would be a good change of pace to keep me from going too crazy.

And you know? The evening really did help. It was a lot of fun spending \$20 on roulette and walking away with \$60, it was fun eating a ridiculous amount of crab legs, and it was\ldots{}well, it was mortifying, watching some of saddest people I've ever seen in my life sit, lost, in front of their slot machines.

We had planned on going hot-tubbing, but, as became clear when I took off my shirt back at the room and exposed the rather bulky bandage along the underside of my arm, that was pretty much out of the question, so we mostly just sat around talking, and, in my case, trying to feel better about the whole thing.

I was fine until it was time for bed. As is usually the case, the stillness is when I get the worst, in terms of anxiety. That's when it's easiest for my mind to wander, fixate on a subject, and loop over it in all the worst ways for the longest time. The problems started when sleep didn't come.

And didn't come.

And still didn't come.

After a time, I suppose I just lost it. I got up and started pacing the room, walking from the bathroom to the window and back again, clenching and unclenching my hands before I let loose a ``Jesus fucking Christ!''

I locked myself in the bathroom and broke down again.

Both James and Karl checked in on me throughout the next few hours, but it was mostly spent huddled up on the cold tile of the floor feeling awful about both myself and what I'd done --- that it had any effect on those around me was just starting to hit home. I will not lie that, several times throughout the night, I wished that I had succeeded in order to not be going through what I was going through at the time. I simply couldn't stand what I'd done.
