Let's talk about something else. Please.

\begin{quote}
One more question, and then we can.
\end{quote}

Okay.

\begin{quote}
How far have you come since then?
\end{quote}

I think a long ways.

\begin{quote}
You think?
\end{quote}

Well, every time I think I've come a long ways, I do something horribly stupid again. Every time I think I'm over all this, I tear at myself. Every time I think I'm getting good at talking about my mental health, I wind up in this pit where I have to destroy myself, to make it physically evident that I'm unwell in some invisible way. I always have. I tried to blind myself when I was ten, remember? I tried to lose a finger, a leg. I cut. I burned.

\begin{quote}
Is it about proving that you're unwell?
\end{quote}

How could I possibly prove that I'm too depressed to be around others? How could I possibly prove that I'm too anxious and sad and upset and numb to look at a chat lest the read-receipts show that I am okay enough to exist? How could I possibly prove such a thing when you look at me and see me hale and intact?

\begin{quote}
You are talking about self harm. I asked about suicide. How far have you come since your first suicide attempt.
\end{quote}

I still think about it on the daily. I still obsess over it. Now I'm more likely to just go to bed, though.

\begin{quote}
Is it so simple?
\end{quote}

No, of course not, but look, I'm thirty-three. I'm too old for it to be tragic, too young for it to be a midlife crisis, too healthy for it to be understandable, too sick for it to be a surprise. It would just be sad and weird, not to mention mean to those in my life. I've got that perspective now. I'm thirty-three, I've made it this far, I've worked this hard, and I can at least understand that.

It's easier to just go to bed and wait it out, or maybe just get out the soldering iron for a bit, because yeah, it still blows, but at least now I know it'll pass, and five months down the line, I can do the same dance all over again.

\begin{quote}
That seems rather fatalistic.
\end{quote}

I'm tired. I don't even know what to do about this anymore, other than wait it out. My doctor got mad at me for saying I've come to terms with feeling like shit for a few weeks every five months or so, that that's just my life forever now.

I've just never seen any evidence to the contrary.
