\label{ally:3}
\begin{paracol}{2}
  \begin{leftcolumn}

\begin{ally}
Do you remember when you met me?
\end{ally}
When I met you? I don't remember it so much as a meeting as you were just already there.

\begin{ally}
I was, yes.
\end{ally}
After high school, then. That's when you showed up. That's when life began. That's when I started thinking of myself as a person. That's when I started thinking of others as people, with their own motivations, their own desires, their own incentives and failings.

\begin{ally}
And you made it through.
\end{ally}
After a fashion.

\begin{ally}
You're here, now. You made it through.
\end{ally}
\begin{verse}
\emph{She never wanted to be\\
\vin What she became;\\
\vin \vin The irony of which\\
\vin \vin \vin Is not lost on her.}
\end{verse}

\begin{ally}
Touching.
\end{ally}
Hey now, don't be rude. Aren't you supposed to be my ally?

\begin{ally}
I \textbf{am} your ally. I'm just not your friend.
\end{ally}
Fair enough.

So you showed up after high school. You showed up after life slid sideways through puberty. I went digging, you know. To find this out.

\begin{ally}
Oh?
\end{ally}
Yeah. June 2004. There you are. I say,

\begin{quotation}
The navy blue I've been seeing at waist level in front of me and to my left is contentment. I'm not entirely sure that it being omnipresent is a good thing, however, considering the colors it's mixed with. Am I really content with longing and hopelessness? It's not out of the question, I suppose that it could just be another aspect of my personality. But that just brings up the question of whether or not it's something I ingrained into myself through habit, something where I just kinda accepted that feeling such things is normal, okay, and what I want; or is it something I was born with, or that we're all born with? Is it a side effect of love, expecting impossible desires and the blind hopelessness that follows the end of a four year undertaking?
\end{quotation}

And you replied\ldots{}?

\begin{ally}
You're rambling.
\end{ally}
So pleased you remember.

\begin{ally}
You're rambling.
\end{ally}
I suppose I am. But there you were. You said \emph{You're rambling} to which I replied ``Guilty, conspirator.'' And that was that. That was us. We never greeted each other. Why would we?

I kept digging, too. You stuck around for a year. I saw you off and on until June 2005. In October, 2004, I said that empathy is cooler in person. \emph{Why?} you asked. \emph{So you can verify? Don't you trust your feelings?} I said I didn't know, and then I begged you not to go.

\begin{ally}
Everyone always leaves, don't they?
\end{ally}
Perhaps. It's good to hear from you again. Even after fourteen years, I've missed you.

\begin{ally}
And what was the last thing I said to you?
\end{ally}
\emph{I was going to call you emo, or suicidal, but no, not goth.} It was when Ash and Shannon and I found a house to move into.

\begin{ally}
I believe I also called you a prick.
\end{ally}
Was I?

\begin{ally}
Yes.
\end{ally}
Am I still?

\begin{ally}
Yes, but a different kind.
\end{ally}
You're as chipper now as you were then.

\begin{ally}
Yes, but a different kind.
\end{ally}
\newpage

\end{leftcolumn}
\end{paracol}
