\begin{quote}
Why am I here?
\end{quote}

Aren't you always?

\begin{quote}
With you, sure. Why am I bound to words, though? It's been fourteen years.
\end{quote}

Surely that's not all on me. You must play some role in it. I was talking with my partner about doing something autobiographical for my next project, after all.

\begin{quote}
I'm the observer and the mirror. All I can do is reflect your choices back at you. Choice itself is not my department.
\end{quote}

After getting \href{https://makyo.ink/publications/restless-town/}{\emph{Restless Town}} finished, I needed something to do. Some other project that would make me feel like I was being productive.

\begin{quote}
Feel, or seem?
\end{quote}

Both. If I sat still, I'd burn up. If I was seen sitting still, clearly I'd be worth less in the eyes of those around me, right?

\begin{quote}
Not my department.
\end{quote}

Right.

So I started digging through stuff I'd already done, seeing if any of it could be cleaned up and turned into a new project. I stumbled across \href{https://makyo.ink/publications/rum-and-coke/}{\emph{Rum and Coke}} and found it mostly clean as it was, so I decided to publish it as a book. Paperback and ebook, I mean, not just the stories online.

\begin{quote}
Were you proud of them?
\end{quote}

To an extent. A different me wrote them. A lesser me, in some ways. I was younger, I hadn't quite found my voice and tone. No \href{https://makyo.ink/publications/arcana}{\emph{Arcana}}, no \emph{Disappearance}, no \href{https://writing.drab-makyo.com/fiction/getting-lost/}{\emph{Getting Lost}} or \href{http://post-self.io}{\emph{Post-Self}}. All I had was a few scattered tidbits and my mom's words ringing in my ears: ``You wrote your own wedding vows, right? I could tell.''

A me with a different identity, too. A me that was working on gender through small steps. I hadn't yet picked up the word `trans' for myself. I was non-binary, presenting male, writing to justify myself. Or maybe to hype myself up. I was writing works about gender and poly problems being worked through to convince myself it was possible.

\begin{quote}
They read like parables.
\end{quote}

They were, to me. Each one came with an internal discussion after the last line, \emph{now, what can we take from this?} Something in a circle. Socratic. A talking stick.

\begin{quote}
I know, I was there.
\end{quote}

Of course.

\begin{quote}
Why didn't I show up then?
\end{quote}

I was too\ldots{}something. Too busy, too preoccupied. I was focused too much on identity, too much on The Work, as it were, to reflect. Maybe I was moving too quickly to notice my choices being shown to me.

\begin{quote}
You'd mostly stopped \href{https://adjectivespecies.com}{{[}adjective{]}{[}species{]}} by then, too.
\end{quote}

Life got weird. I was transitioning--

\begin{quote}
A choice.
\end{quote}

--I was solidifying my relationship with Judith--

\begin{quote}
A choice.
\end{quote}

--I was starting to burn out at work--

\begin{quote}
Was that a choice?
\end{quote}

The result of choices, maybe. The result of the choice to start drinking. It \emph{is} called \emph{Rum and Coke}, after all. The result of the choice to get into computers. The result of the choice to work from home, which itself was the result of a choice to take the previous job so far from home.

\begin{quote}
You burned out in part because you burned so hard at the start.
\end{quote}

Was I not supposed to? I had to prove myself.

\begin{quote}
To whom?
\end{quote}

You?

\begin{quote}
Not my department.
\end{quote}

One of your neighbors, perhaps. A cubicle over, a floor above, something like that.

\begin{quote}
Do you anthropomorphize me that much?
\end{quote}

No, I suppose, I don't. You're not my therapist, sitting in a chair across from me and talking me through my problems. You're not person shaped. You're the shape of my hands displaced half an inch behind my own, navy blue and trimmed with sea-foam green.

\begin{quote}
You haven't used colors in fourteen years, either.
\end{quote}

What I'm trying to say is that maybe you're back because of nostalgia. \emph{Restless Town} was done and couldn't be published yet, and a prideful part of me didn't want it to be my first book, so I pulled \emph{Rum and Coke} into shape.

It rubbed my nose in the past. I published it a few weeks ago, and I wasn't done with the past, so I started archiving more data. I dug up my old hard drives. I grabbed stuff from Dreamhost, both files and database backups. I finally unlocked my LJ account and archived that.

\begin{quote}
And you work at an archive.
\end{quote}

I go through phases, looking back at the past. I'll spend a few days trying to backdate some log files, or dig through my old scores and publish them --- I did that too, alongside \emph{Rum and Coke}, publish a bunch of my old music --- or resurrect my notes on \href{http://nanon.lang.drab-makyo.com}{\emph{Nanon}}, or the like.

\begin{quote}
You are quite mercurial.
\end{quote}

A failing. That may play a role in my burnout. I'm only good at something for seven years before it becomes so intolerable that I have to leave. Happened with school.

\begin{quote}
So here I am, your ally, twice seven years later.
\end{quote}

I hadn't thought of it that way.

\begin{quote}
Portentous. The only way it would've been more so is if it were thrice seven years.
\end{quote}

I ran away thrice seven years ago. In seventh grade, in 1997, no less.

\begin{quote}
Ill omens. What will happen to me in seven years?
\end{quote}

Will you leave me for good?

\begin{quote}
Can an ally disinhabit a mind so easily?
\end{quote}

I'm not comfortable with that question. I'm not comfortable with its implications. Either way, the past is important to me because maybe it can help me figure out the present. Those who don't know history are doomed to blah blah blah.

\begin{quote}
And have you figured out your present?
\end{quote}

For me to pull out that trite quote about my own personal history speaks pretty well to my fears of doing things accidentally. I've certainly figured out my present better than twice-seven-years-ago me had figured out his.
