\label{ally:5}
\begin{paracol}{2}
  \begin{leftcolumn}

\noindent When 2007 rolled around, I turned 21. \emph{What if,} I thought to myself. \emph{What if I decided to see what it feels like to be addicted to something?}

By that point, alcohol was this nebulous thing. I'd roped a few people into getting me alcohol now and then, and it was fine. I'd started brewing and it was whatever. I had beer and it was alright. I went through a mead phase--

\begin{ally}
You went through several.
\end{ally}
--I went through a wine phase, and an absinthe phase--

\begin{ally}
Don't sell yourself short. You wrote an essay on absinthe.
\end{ally}
--and a gin phase. That's the one that got me. I had a bottle of Beefeater's, what was to become my gin of choice, and I had an inch of it poured over ice and I was standing in the kitchen. Such a wide open space. The kitchen at that apartment was larger than my bedroom now, and it opened onto a living room the size of what we have now. I was standing tall in that vast plain of a room, staring down into my glass and watching the way the ice melting into the gin created swirls of two different kinds of transparent. I was thinking how it was probably due to the different ways the two liquids refracted light, and then I was laughing, because I was staring down into my drink like something out of a bar.

\emph{What if I decided to see what it feels like to be addicted to something?} I thought. I drank every night that week.

\begin{ally}
Why ruin your life on accident when you can do it on purpose?
\end{ally}
I don't think I was thinking in those terms at that point.

\begin{ally}
Are you now?
\end{ally}
Perhaps.

\begin{ally}
Maybe you're just afraid of doing anything by accident.
\end{ally}
Perhaps.

\begin{ally}
You're sounding like me more by the day.
\end{ally}
Learn from the best.

\begin{ally}
And so you set about with a will.
\end{ally}
Like magic. I set forth my will with a stated goal and made it happen. My spell was spoken and washed down with liquor. I drank nearly every day from then on out. I spent thousands of dollars on alcohol over the next ten years. I went through more mead phases and more beer phases. I went through a distillation phase. Magic is empowerment through attention to detail.

\begin{ally}
The MEAD principle. Cute.
\end{ally}
I drank hard with the choir, and then I left school and drank hard with the programmers. If there's one thing that most programmers do better than computers, it's drinking, after all.

I did some work at a bar, even. Just making their menu and website for them in exchange for free drinks.

\begin{ally}
You mastered \LaTeX that way. A very you thing to do.
\end{ally}
I did well at it. I still have one of the menus and some of the paper laying around somewhere. I did that until the bartender left and, when I asked for my next payment from the owner, he flipped out at me and threatened to sue me for impersonating him. I don't think I realized Raffi, the bar manager who hired me, was already on his way out.

I drank my way out of one job and through a good chunk of another. I drank until I got better at it than I was at software. I drank myself into burnout. I drank until I collapsed.

\begin{ally}
You used up your spell slots. You ran out of will. You had to quit by accident.
\end{ally}
I worked to quit, I'll have you know. It wasn't easy. It took meds and some rough nights.

\begin{ally}
You were less of a person then than you were when you started drinking. The you who started drinking by focusing on \textbf{starting drinking} was more real than the you who collapsed in the kitchen from a PNES and stopped drinking because she was completely empty of intention.
\end{ally}
Should I start the daily drinking again, then?

\begin{ally}
You're more of a person now than you were when you started drinking.
\end{ally}
That, coming from you, is a glowing endorsement.

\begin{ally}
You may have been more of a person when you started than when you stopped, but you weren't much of one, even then.
\end{ally}
\newpage
\end{leftcolumn}
\end{paracol}
