Some explicit stuff about suicide in this one.

I think of myself as a trans woman, not a woman. I think of past me as male, not female. To an extent, I think of past me as cisgender. I was a guy. I was that gay guy who tumbled out the other side of puberty and was left to figure out what the fuck. I am not who I was.

\begin{quote}
You have ship-of-Theseus'd yourself into what you are.
\end{quote}

I was not Madison. I am not Matthew. I can't deny his existence, though. He was him, and to erase that, to toe the party line and say I've always known that I was Madison, would do a disservice him.

He got in all those relationships. He loved so hard it hurt. He dreamed of being held. He struggled with the words.

He fought. He enacted his cruelty in countless subtle ways. He promised himself he'd be better than his dad and failed more often than not.

He rode the same crests of hypomania and crashed just as hard after. Once, he tried to schedule his hobbies into his day so thoroughly that he forgot to schedule meals, then, having failed two weeks later, considered shooting himself in the head. Anxiety rode him just as thoroughly. Once, dead convinced that he had meningitis, he wrote a note apologizing to loved ones and left it on the bedstand.

He was just as mercurial, too. The brewing phase--

\begin{quote}
Phases. Plural.
\end{quote}

--the gun phase, the photography phase and all its subphases: digital, film, cross-processing, rangefinders.

\begin{quote}
Yeah, he was a prick.
\end{quote}

You said I still am, but a different kind.

\begin{quote}
In all fondness.
\end{quote}

How kind.

All this to say, I have not always known I was trans. To pretend such would be to erase a real, actual person who tried his best more often than not.

\begin{quote}
Have you answered Theseus' question?
\end{quote}

I don't know.
