\label{ally:21}
\begin{paracol}{2}
  \begin{leftcolumn}

\begin{ally}
When you started this project, several people asked if you were okay.
\end{ally}
Yes.

\begin{ally}
Were you?
\end{ally}
I think so. I was swinging up toward hypomania, and plowing heedlessly through nostalgia. Some of it was good, some of it was bad, but I don't think that had much bearing on me starting the project.

\begin{ally}
Robin asked if you were okay. ``I just want to make sure,'' she said once. ``You asked me to check in on you if you ever started talking about geese.''
\end{ally}
Perhaps this has a similar feel to it. A similar scent of ritual, a similar flavor of mysticism, a similar sense of some other reality vignetting my vision.

\begin{ally}
lorxus asked if you were okay. ``People normally write memoirs at the ends of their lives.''
\end{ally}
Life is a series of beginnings and endings dovetailed messily together.

\begin{ally}
There is a final ending, though.
\end{ally}
I don't think I'm near that, despite what passive ideation might tell me. I'm not writing some drawn out farewell.

\begin{ally}
So, why are we talking, you and I? Where is this going?
\end{ally}
We're talking because this project, self indulgent as it is, is leading me to confront and process a lot of different things, which I'd call a net positive. We're talking because how can I know what I think until I say --- or write --- it? We're talking because I've got a lot on my mind.

This is going nowhere.

\begin{ally}
I don't know whether to be proud or insulted by that.
\end{ally}
Can you feel either?

\begin{ally}
Not my department. The metaphor is still useful.
\end{ally}
Well, fair enough. I didn't mean that idiom, anyway. This is going nowhere because it's a project that needn't have a direction.

It's not a directed thing.

It is a river.

It is the movement of the tides.

It's guided only by gravity and the lay of the land.

It is its own \emph{musica universalis}.

It's a conversation.

\begin{ally}
Conversations have direction.
\end{ally}
Not all of them.

It's one of those late-night conversations that go where they will, in which sometimes very little is said.

It is not a minded thing. It has no autonomy and yet has no guiding force. No sapient guiding force, at least.

It is a way. It is a path, and yet the path is not the walker.

\begin{ally}
This is going nowhere.
\end{ally}
Maybe, but maybe that's the point.
\newpage

\end{leftcolumn}
\end{paracol}
