\begin{paracol}{2}
  \begin{leftcolumn}

\noindent My turn.

\begin{ally}
Shoot.
\end{ally}
Why ask this now? Why ask about the core instead of a side quest?

\begin{ally}
I did. I asked about TS.
\end{ally}
Don't deflect.

\begin{ally}
Okay.
\end{ally}
Why ask about the project? Why ask about yourself?

\begin{ally}
You had job interviews. You had the convention. You're visiting Barac. You stopped writing for a bit.
\end{ally}
I started again, didn't I?

\begin{ally}
Yes. Hypomania is fading into the comfortable static of a ground state, though. You're \textbf{still} writing. That's why I'm asking. Why are you writing this if you're not hypomanic?
\end{ally}
I wrote a bunch of \emph{Restless Town} when I wasn't hypomanic.

\begin{ally}
Yes.
\end{ally}
I wrote some of \emph{Rum and Coke} when I wasn't hypomanic.

\begin{ally}
It shows, in the last one.
\end{ally}
I've grown as a writer. I've grown as a person. I can continue projects whose inception lay in hypomania.

\begin{ally}
And yet you say that you know a thing is right if you feel the same when depressed as when hypomanic. You can tell a decision is worth making if something other than strange energies birthed it.
\end{ally}
Yes.

\begin{ally}
Did strange energies not birth me?
\end{ally}
I don't know. Maybe. I don't think they birthed this project, though. I think this project is\ldots{}hmm.

\begin{ally}
An honest one? A true one? A worthwhile one?
\end{ally}
Sort of.

Maybe I think it's an earnest one. One that was borne out of a real desire, birthed by a need beyond what might be imbued by hypomania. A more grounded need, not one based in those non-Newtonian laws that govern that other space, where mechanics break down and strange energies spring, palladial, into being.
\newpage
\end{leftcolumn}
\end{paracol}
