\label{ally:25}
\begin{paracol}{2}
  \begin{leftcolumn}

\begin{ally}
You were gone.
\end{ally}
I was out of town, yes. Out of town and cramming in as much work as I can during these last few weeks at the Archive.

\begin{ally}
You were gone. Not just from writing, but from home, from ritual, from reality. You were someone else. Your head was elsewhere.
\end{ally}
That's a bit dramatic, isn't it?

\begin{ally}
Are you not a different person at conventions? Are you not a different person when living in a different home with someone else?
\end{ally}
Maybe. I like to think of it as postprocessing. The picture you take is fixed and largely unchanging, but you can process it into different things with different filters. The person I am is fixed and largely unchanging, but some people and some places bring out, say, artsy black-and-whites, while others bring out glossy, oversaturated colors

\begin{ally}
And yet when you were out, you weren't engaging with some parts of your life. Ones you might otherwise consider integral. No for-fun software, no music, no chat, no writing.
\end{ally}
Were you lonely?

\begin{ally}
Not my department.
\end{ally}
I suppose I was. Even at the convention, even seeing two different partners, I was lonely. Or, if it could be said of things rather than people, I was lonely for not having those fulfilling aspects about. I missed writing, I missed you.

\begin{ally}
I wasn't gone.
\end{ally}
I know. It's not even like when we don't talk. You were there. I just wasn't able to engage, and that's an integral part of our relationship. It happens from moment to moment. It is not something that exists in any sense of permanence or stasis. It is defined by movement and momentum.
\newpage
\end{leftcolumn}
\end{paracol}
