\label{ally:19}
\begin{paracol}{2}
  \begin{leftcolumn}
\index{ally|(}
\noindent The tragic core to all this, to this whole project, is that I am not an interesting person. Or maybe interesting, but unremarkable.

\begin{ally}
You're in a mood.
\end{ally}
\emph{Coming to terms with being a terrible person}, I wrote, but I'm not even that. I'm just a person.

I'll be the first to admit that I'm largely just a boring person. I know that. There's nothing remarkable about my life. Middle class, middling intelligence, average looks --- at least for a trans girl --- okay sense of humor, no unusual challenges, unless the movement disorders count.

\begin{ally}
So?
\end{ally}
What's this, then? A memoir? What would that accomplish?

\begin{ally}
Validation? I've already mentioned that.
\end{ally}
What would the written account of an ordinary life validate?

\begin{ally}
Sometimes it's worthwhile just hearing that ordinary people living ordinary lives can get by in the world. That despite being trans, despite feeling like garbage sometimes, you can still function. That even the drabbest of makyō still have stories to tell.
\end{ally}
I suppose that's fair. Literary fiction exists separately from genre fiction, as silly a distinction that is to make, because of the validation we find in the unfantastic.

\begin{ally}
Where is this heading? What is the future? What are we leading to?
\end{ally}
In the context of this project, or just life in general?
\end{leftcolumn}
\end{paracol}

\renewfontfamily\pagenumfont{Gentium Book Basic}[Color=CCCCDCFF]
\backgroundcolor{c[1]}[rgb]{0,0,0.2}
\backgroundcolor{C[1](0.6\columnsep,10000pt)(10000pt,10000pt)}[rgb]{0,0,0.2}
\begin{paracol}{2}
  \begin{rightcolumn*}
    \input{content/dad-as-a-person.tex}
  \end{rightcolumn*}
  \begin{leftcolumn}

\begin{ally}
Is there an end? A goal?
\end{ally}
I'm not sure.

\begin{ally}
What will the last page say?
\end{ally}
{[}\ldots{}{]} Endings were writ on your face, your hands, and your steps --- your very pace spoke of completion.

\begin{ally}
Are you thinking of ending this project?\index{ally!meta}
\end{ally}
Not at all. I've got a list of side quests I need to complete in order to make you happy, and their very nature makes it easy to complete. One or two thousand words, an hour or two's conversation with you, and then they're done and I don't have to pick up where I left off.

I'm just tired.

\label{ally:20}

\begin{ally}
Let me ask this another way, perhaps. Why are we doing this? Why are we talking? Why did you start?
\end{ally}
Let's put a pin in just why exactly you're asking these questions. I'd like to know what the origin after I give you the whys and wherefores.

\begin{ally}
Okay.
\end{ally}
To the question at hand, though, I think I covered that before, right? I started this project in a fit of nostalgia\index{Nostalgia} and one of the end results of an unstoppable wave of nostalgia\index{Nostalgia} plus a sort of graphomania is the need to write about the past, and to do so in such a way as to invoke the past in the process.

\begin{ally}
I guess I'm trying to decide whether or not to believe you.
\end{ally}
What's not to believe here? I spend page after page digging through old LJ entries, old poetry, old pictures and art and logs--

\begin{ally}
Let's talk about TS.
\end{ally}
Don't derail me. These are your questions.

\begin{ally}
Point.
\end{ally}
What's not to believe about a project filled to overflowing with nostalgia\index{Nostalgia} being borne from nostalgia\index{Nostalgia}?

\begin{ally}
I don't doubt the roots in nostalgia\index{Nostalgia}, I doubt the intentionality.
\end{ally}
You doubt that I started this on purpose?

\begin{ally}
Did you summon me? Answer truly.
\end{ally}
I don't know.

\begin{ally}
I say that I've always been here, but that's only a part-way truth. That's only half-meaning drizzled over too many words. It's easy enough for someone to say that an abstract concept, a loose portion of someone's personality has always been there. Of course that's the case. Why did you summon \textbf{me}, though? Are you in need of an ally?
\end{ally}
I'm surrounded by friends and chosen family, these days. Most of them are my allies.

\begin{ally}
Well, maybe we should disentangle what exactly an ally is before we continue down the path of why you summoned me.
\end{ally}
Okay. I was going to call you my shadow, but that's not exactly right, is it?

\begin{ally}
No.
\end{ally}
You share some similarities, I guess. You have these aspects of myself that are submerged beneath the surface, usually. You see me from a distance. You know everything about me.

\begin{ally}
I do. But by its very definition, I'm not your shadow. Like I told you, I'm not your id.
\end{ally}
And like I told \emph{you}, it was a joke.

\begin{ally}
You'll have to imagine me laughing.
\end{ally}
Right.

\begin{ally}
I'm not your shadow or your id because those are not necessarily things you can see. They are the things that are, by definition, unknown and unknowable by the ego.
\end{ally}
Or at least heavily obscured. Dr Jekyll knew of Mr Hyde. Perhaps you're not my shadow, but maybe the personification of enantiodromia. Perhaps this is my process of assimilation. Perhaps this is me airing my dirty laundry.

\begin{ally}
It's not \textbf{not} that. There are enough parts of me that are opposite of you for the similarities to be more than superficial. Enantiodromia carries too many implications of balance and equilibrium, however. That there are parts of me that are opposite of you does not make me the opposite of you. You could not press us together, merge us completely, and wind up with some more complete self.
\end{ally}
Right. You'd have to be the same size as me, and you're not.

\begin{ally}
I don't have a size.
\end{ally}
You'd have to be in the same place as me, and you're not.

\begin{ally}
I don't have a place.
\end{ally}
Right. \emph{You're not person shaped,} I said. \emph{You're the shape of my hands displaced half an inch behind my own, navy blue and trimmed with sea-foam green.}\index{Numinous!colors}

\begin{ally}
I don't have physicality. I don't have boundaries.
\end{ally}
You are bounded by me. I am your boundaries.

\begin{ally}
Are you?
\end{ally}
Can an ally move beyond a mind? Can allyship --- true, individual allyship --- move beyond the allegiance?

\begin{ally}
You tell me.
\end{ally}
I don't know that I can.

\begin{ally}
I am a liminal creature. I told you that. I'm almost a shadow but miss the mark. I'm near to the concept of a back-stage persona but miss the mark. I get close to being you, but never quite come into focus enough for the outlines to match up.\index{Liminal}
\end{ally}
Are you not just me? Just a part of me?

\begin{ally}
There is no me without you.
\end{ally}
Is there a me without you?

\begin{ally}
Can you imagine so dull a life?
\end{ally}
You're not that exciting.

\begin{ally}
Not my department.\index{ally!Not my department}
\end{ally}
Right.

So an allegiance in the orthocosmic sense\footnote{wiki.postfurry.net/wiki/Metacosmology} is a relationship two entities where they help each other. Or at least trust that they can rely on the help of the other at need. It's not contingent upon friendship, as you are so fond of saying, but that's not to say that they're mutually exclusive.

\begin{ally}
I am an endocosmic ally.
\end{ally}
Are you helping me, then?

\begin{ally}
Do you not feel my aid?
\end{ally}
I suppose I do. Sometimes it feels like you're just here to kick my ass.

\begin{ally}
Ass-kicking is well within the bailiwick of an ally. To not kick your ass when you need it would be to fail at being a good ally.
\end{ally}
I've heard that said about friends. A fair-weather friend may leave you to create your own demise, while a true friend will knock some sense into you.

\begin{ally}
True friends are almost always also strong allies.
\end{ally}
But not vice versa. I see that now. You are not my friend.

\begin{ally}
I am not your friend.\index{ally!I am not your friend}
\end{ally}
But you are my ally.

\begin{ally}
I am your ally.
\end{ally}
\newpage

\label{ally:21}

\begin{ally}
When you started this project, several people asked if you were okay.
\end{ally}
Yes.

\begin{ally}
Were you?
\end{ally}
I think so. I was swinging up toward hypomania, and plowing heedlessly through nostalgia\index{Nostalgia}. Some of it was good, some of it was bad, but I don't think that had much bearing on me starting the project.\index{Mental health!bipolar!mania|(}

\begin{ally}
Robin\index{Relationships!Robin} asked if you were okay. ``I just want to make sure,'' she said once. ``You asked me to check in on you if you ever started talking about geese.''\index{Numinous!birds}
\end{ally}
Perhaps this has a similar feel to it. A similar scent of ritual, a similar flavor of mysticism\index{Numinous}, a similar sense of some other reality vignetting my vision.

\begin{ally}
lorxus\index{Relationships!lorxus} asked if you were okay. ``People normally write memoirs at the ends of their lives.''
\end{ally}
Life is a series of beginnings and endings dovetailed messily together.

\begin{ally}
There is a final ending, though.
\end{ally}
I don't think I'm near that, despite what passive ideation might tell me. I'm not writing some drawn out farewell.

\begin{ally}
So, why are we talking, you and I? Where is this going?
\end{ally}
We're talking because this project, self indulgent as it is, is leading me to confront and process a lot of different things, which I'd call a net positive. We're talking because how can I know what I think until I say --- or write --- it? We're talking because I've got a lot on my mind.

This is going nowhere.

\begin{ally}
I don't know whether to be proud or insulted by that.
\end{ally}
Can you feel either?

\begin{ally}
Not my department. The metaphor is still useful.
\end{ally}
Well, fair enough. I didn't mean that idiom, anyway. This is going nowhere because it's a project that needn't have a direction.

It's not a directed thing.

It is a river.

It is the movement of the tides.

It's guided only by gravity and the lay of the land.

It is its own \emph{musica universalis}.

It's a conversation.

\begin{ally}
Conversations have direction.
\end{ally}
Not all of them.

It's one of those late-night conversations that go where they will, in which sometimes very little is said.

It is not a minded thing. It has no autonomy and yet has no guiding force. No sapient guiding force, at least.

It is a way. It is a path, and yet the path is not the walker.

\begin{ally}
This is going nowhere.
\end{ally}
Maybe, but maybe that's the point.
\newpage
\label{ally:22}

\noindent My turn.

\begin{ally}
Shoot.
\end{ally}
Why ask this now? Why ask about the core instead of a side quest?

\begin{ally}
I did. I asked about TS.
\end{ally}
Don't deflect.

\begin{ally}
Okay.
\end{ally}
Why ask about the project? Why ask about yourself?

\begin{ally}
You had job interviews. You had the convention. You're visiting Barac. You stopped writing for a bit.\index{Relationships!Barac}
\end{ally}
I started again, didn't I?

\begin{ally}
Yes. Hypomania is fading into the comfortable static of a ground state, though. You're \textbf{still} writing. That's why I'm asking. Why are you writing this if you're not hypomanic?\index{Mental health!bipolar!mania|)}
\end{ally}
I wrote a bunch of \emph{Restless Town} when I wasn't hypomanic.

\begin{ally}
Yes.
\end{ally}
I wrote some of \emph{Rum and Coke} when I wasn't hypomanic.

\begin{ally}
It shows, in the last one.
\end{ally}
I've grown as a writer. I've grown as a person. I can continue projects whose inception lay in hypomania.

\begin{ally}
And yet you say that you know a thing is right if you feel the same when depressed as when hypomanic. You can tell a decision is worth making if something other than strange energies birthed it.
\end{ally}
Yes.

\begin{ally}
Did strange energies not birth me?
\end{ally}
I don't know. Maybe. I don't think they birthed this project, though. I think this project is\ldots{}hmm.

\begin{ally}
An honest one? A true one? A worthwhile one?
\end{ally}
Sort of.

Maybe I think it's an earnest one. One that was borne out of a real desire, birthed by a need beyond what might be imbued by hypomania. A more grounded need, not one based in those non-Newtonian laws that govern that other space, where mechanics break down and strange energies spring, palladial, into being.
\newpage
\label{ally:30}

\noindent Does death take more than one form? Can it be anything other than it is? Can it sneak up on you while you aren't looking, and then when next you take a breath, you realize that you are in some afterlife?

\begin{ally}
I suppose it must, given this lead in.
\end{ally}
Have I died? Has some part of me already rotted and sloughed off? Is this, in some very literal way, an afterlife?

\begin{ally}
Do you feel as though, another seven\index{Numinous!seven} years having passed, you are moving on from the life that you built up?
\end{ally}
Yes.

\begin{ally}
Then I see no reason not to label it as such.
\end{ally}
Perhaps lorxus was right. Perhaps I am writing this at the end of a life.\index{Relationships!lorxus}

\begin{ally}
What are you leaving behind?
\end{ally}
I think I'm leaving behind that bit of me who was struggling to live earnestly.

\begin{ally}
Are you not, now?
\end{ally}
No, I think I am. Or, well, I think I am living fairly earnestly. I think what has happened over the last few years is that the struggle changed its shape.

The Madison who was struggling to come to terms with a post-Matthew life is not me any longer. She spent the last seven years mourning him, in a way. She spent the last seven years figuring out how to live without him, throwing away his stuff, leaving behind family and homes and states.\index{The Death of Matthew}

\begin{ally}
Is this her memoir? Or yours?
\end{ally}
I don't know, honestly.

All I can say is that, for some reason, at some point while working on this project, I might have died. I have entered a liminal space once again. It's a different one, to be sure, but it's somewhere in between who I was and some undefinable potential self.

Perhaps some early whiff of this liminality is what got to start this project in the first place, to summon you. Perhaps it was burnout reaching a head that signaled the death of that version of me.

Perhaps I have simply, like Theseus' well-worn ship, become something completely new while I wasn't looking.\index{Ship of Theseus}
\newpage

\label{ally:31}
\noindent I've been pulling this all into a book. Like, a physical one. A paperback.\index{ally!meta}

\begin{ally}
I know.
\end{ally}
How do you feel about that?

\begin{ally}
Not my department.\index{ally!Not my department}
\end{ally}
That feels like an evasion to me. You had opinions on me streaming the process of writing. You had opinions on the process itself: you called me out on writing stuff in commit messages, on having our conversations in comments in the source code. You had opinions on me buying the domain name. Do you have no opinions about our words on something to be bought and sold?

\begin{ally}
A friend once asked Maddy, ``Why do you shout into the void?''\index{Koan}
\end{ally}
I write all of this down because the very act of putting it into words brings a sense of clarity that I lack without. By taking these moments of my life and articulating them, I almost automatically get another viewpoint on them.

\begin{ally}
And by articulating them as a conversation, you get two. That is not the friend's question.
\end{ally}
No, I suppose it isn't.

I write for the clarity, but I share out of some perverse need. \emph{The chances that ally will pick up any sizeable audience are slim, so I almost feel like I'm publishing it as an extension of my compulsive need to overshare,} I prophesied. I share because I have to.

\begin{ally}
Does Maddy shout into the void because she must shout into the void?
\end{ally}
Perhaps. Sometimes.

Sometimes I have to speak so that someone will hear me out of some desire for feeling justified. I need to be heard, to be seen, so that even if I'm going through something alone, others will know that I am doing so. I need to be witnessed.

\begin{ally}
There is power in the word, as you say, but there is also power in the act of speaking it. There is no value-judgment for me or anyone else to make in that. Words have power, speaking has power.
\end{ally}
There is value-judgment in the content, though.

\begin{ally}
Yes. There is value-judgment in intent, as well. That you are publishing these words is not something that I \textbf{can} have an opinion about.
\end{ally}
Okay. What about my intent?

\begin{ally}
Your compulsive need to do overshare is an implicit part of our relationship.
\end{ally}
Shall I throw your words in your face?\index{ally!throwing stones}

\begin{ally}
By all means.
\end{ally}
\emph{Am I something to be bought and sold? Am I something to be traded and marketed?}\footnote{ally.id/aside/2}

\begin{ally}
Have you answered the question? \textbf{Am} I something to be bought and sold? Me, here, being a part of yourself.
\end{ally}
Since having that conversation, I've released two books, and yes, I suppose you are. \emph{I} am. We are a brand to be built up and marketed, parceled up and sold to any comer.

``The tragic core to all this,'' I wrote, ``is that I'm not an interesting person.'' I \emph{am} a writer, though. This will be my fourth book, something I never thought I'd say back in seventh grade, when I discovered I actually rather enjoyed writing those silly five paragraph essays. I never thought that I'd be the type of person to sit down and actually write things.

Hell, I never thought I'd be the type of person to sit down and actually finish\ldots{}well, anything. It's the type of thing that continually feels out of reach for me, someone who is up to her neck in stalled projects and who justifies them with phrases like ``the process is the art''.

That said, I can't stop. I can't not make more things. I can't not write. If I have to write, and if, implicit in that need to write is a need for my writing to be read, then yes, you are something to be bought and sold. I am. We are.

\begin{ally}
See? Not my department.
\end{ally}
\newpage

\label{ally:32}
\begin{ally}
My turn.
\end{ally}
Shoot.

\begin{ally}
You said: ``you are not the project, but there is no project without you.''\footnote{Ibid.}\index{ally!throwing stones}
\end{ally}
Yes, that applies to us both.

\begin{ally}
You have spoken to your compulsive need to overshare, and you have spoken to the fact that the act of writing and selling a book is, in its own way, the act of selling yourself. \textbf{Restless Town} and \textbf{Eigengrau} are not so firmly tied to you as this, however. \textbf{Rum and Coke} certainly is not. I don't think you could say the same about this. Speak to your ties to this project.
\end{ally}
Do you suspect that it is too personal to sell?

\begin{ally}
You asked my feelings on the matter.
\end{ally}
I'm of two minds on the matter.

\begin{ally}
Har har.
\end{ally}
Thank you. Seriously, though, I can see two different sides of this.

I feel like I'm putting my maddest edges\index{Mental health}, as Jon Ronson puts it, on display. In the process of working on this project, I was forced to confront some of the most difficult aspects of my life by its very nature.

In the process of pulling the book together, I was forced to reread much of what I had written, and there are parts of it where my words burn too hot, or get too slippery to hold. There's a feverish quality to them. It's something that felt good to write purely for the sensation of it bursting forth from me in uncontrollable torrents.

These maddest edges are something that are integral to the project. You, after all, are one of the, and this project is named after you.

\begin{ally}
Is it mad to have a six month long therapy session with an imaginary interlocutor?
\end{ally}
This is both more and less than that, and you know it.

\begin{ally}
Yes.
\end{ally}
It would be `mad', I suppose, were I to believe that you were an \emph{actual} interlocutor. It would be `mad' were I to present these things as a universal worldview. It would be `mad', awful as that word is, were I anything but deliberate with this project.

As it is, I summoned you. I started pulling down bits of nostalgia\index{Nostalgia} when my I was shutting down my Dreamhost account, when I went to lock my ancient LiveJournal. I got the idea to write, so I did. It was a deliberate effort.

\begin{ally}
Is that mad?
\end{ally}
\ldots{}huh.

\begin{ally}
A question for another time. Tell me of your two minds.
\end{ally}
Right.

On the one hand, I read back through all of this and I find myself tasting blood. Who is this Madison? Is she okay? She seems to be having a rough time of things sometimes, and at others she doesn't seem wholly sane, or at least not wholly healthy. That's a scary thing for someone to put on display. What could possibly lead someone to do that? Some strange form of self-flagellation?

And on the other, while I'm most certainly not wholly healthy, I am, at my core, a storyteller. A young one, and certainly one of uneven quality, but I'm learning and improving by doing. There are stories to be told here, with my life, and that's what I'm doing. I'm making them interesting. I'm embellishing some of them. Hell, I'm making some stuff up wholesale. And I'm doing all of this for the specific purpose of it being read as a story.

In the end, it's the storyteller that wins out over the concerned, private individual. If I can't \emph{not} overshare, if I must compulsively tell stories, then I'm going to tell the stories I have and I'm going to make them worth reading.

\begin{ally}
A friend once asked Maddy, ``Why do you shout carefully constructed, thoroughly edited, well rehearsed speeches into the void?''\index{Koan}
\end{ally}
Maddy replied, ``It pays the bills.''
\index{ally|)}
\newpage
  \end{leftcolumn}
\end{paracol}
\resetbackgroundcolor
\renewfontfamily\pagenumfont{Gentium Book Basic}[Color=000000FF]
