\begin{verbatim}
<div class="col-md-4 text-right">
<h3>I</h3>
<p><em>Geese Level:</em><br />
Unnerving</p>
<p><em>Expect:</em><br />
Anxiety</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

A hundred geese overhead --- A thousand --- A million ---

Heady scent of premonition. Acrid tang of ill omens. Portents. Too much meaning In too small a space.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>II</h3>
<p><em>Geese Level:</em><br />
Noise-Cancelling Headphones</p>
<p><em>Expect:</em><br />
auditory aberrations</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

Geese are a byproduct of laminar shear stress Of two layers of phantasmagorical Newtonian fluids, Which is why they're often seen on a plane. A thin, sort-of Truth From a sort of thin layer geese chromatography.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>III</h3>
<p><em>Geese Level:</em><br />
Eldrich</p>
<p><em>Expect:</em><br />
red tint to vision; hot flashes</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

As the dove bears the olive branch, so too the goose bears the wand that withers all it touches. A wand of nightshade, Core of tainted silver. A wand of obscure origin, The goose surely stole it. Malice begets malice.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>IV</h3>
<p><em>Geese Level:</em><br />
Beyond Comprehension</p>
<p><em>Expect:</em><br />
confusion; nausea; sweating; racing pulse</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

We know not the transgression, the origin - We know not the punishment, only the terror.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>V</h3>
<p><em>Geese Level:</em><br />
Excruciating</p>
<p><em>Expect:</em><br />
pounding heart; tunnel vision; racing thoughts; black outs;
\end{verbatim}

blood pouring from ears

\begin{verbatim}
</div>
<div class="col-md-8 verse">
\end{verbatim}

Geas Wing Dark Horizon

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>VI</h3>
<p><em>Geese Level:</em><br />
Terrifying</p>
<p><em>Expect:</em><br />
tinnitus; piloerection; shortness of breath; uneven gait</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

I'd rather owls. Owls, as though geese were turned inside out, made less evil. Still portentous, Still momentous, Just less terrifying. Owls are okay. I can think about owls.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>VII</h3>
<p><em>Geese Level:</em><br />
Uncomfortable</p>
<p><em>Expect:</em><br />
subdermal itching; formication</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

Life within a comfortable grid. Parallel lines Interrupting narrowing circles Of birds in flight. Travel in straight lines. Turn at right angles. Trace the roof of your mouth With wet tongue.

I'm not afraid of geese anymore Because I can step on them now. I'm big enough.

\begin{verbatim}
<div class="col-md-4 text-right">
<h3>VIII</h3>
<p><em>Geese Level:</em><br />
Birds</p>
<p><em>Expect:</em><br />
birds</p>
</div>
<div class="col-md-8 verse">
\end{verbatim}

Ritual thinking Driven by geese --- By lines, by grids, by food --- By numbers and neat delineation. And I'm left with questions: Why the portents? Why the anxiety? Or maybe: Did I take my meds this morning?

Failing that, Can I just have the comfort of prayer Or the ecstasy of signs Without bleak paranoia Over circling birds?
