\emph{History of the matter --- One step closer to Ein Sof --- Shock and Awe --- Coming to terms with being a terrible person}

I am not writing this for it to be believed, or even seen as a creed --- how could I hold that power over anyone? --- but simply to explain myself. Read this and take it into account, as only one man's manifesto.

When someone recently asked me about my religious beliefs because they were genuinely interested to know, I was at a loss. I think I answered a muttered excuse of being agnostic because God was none of my business.

Thinking back on it now, this answer is inadequate for a few reasons. For one, my reply was based off the set and setting: this was during a choir tour in South Korea, and not only was most of the choir Christian, but most of the stops on the tour were to Christian churches. Secondly, and due in part to the above, I'm sure our concepts of God differ in many ways. Lastly, born of my haste, I was not completely explicit when I said ``none of my business.''

Now that we are back home and I have time in the evenings to do as I please and study what I will, I will strive to come up with a more complete answer to this rather complex question. A bit of history is certainly in order for this to be complete. I was born in the mid eighties to baby-boomer parents. Both my mother and father were raised by devoutly religious parents --- my father was in the Lutheran church, I'm fairly sure, but I don't know about my mom --- though both dropped their religion sometime during their high school or college years and neither have shown much if any inclination towards it since. Rather, both became very strict atheists later in life, my mother in particular. While my dad may have made a comment every now and then about the irrational nature of organized religion, my mom would often go into diatribes about how useless even personal religion was, or how absurd the concept of God is.

This was my spiritual diet for most of my early years, and it took hold fairly well. I remember visiting my paternal grandmother once when I was nine or so, and following her to church one Sunday. She said that it was a secret, that my dad didn't want her to bring me along. I was excited for the prospect until a few minutes into the sermon, when it all just became a dull blur to me --- I didn't even get to go up to the front of the hall for communion, and I really, really wanted to try the crackers.

This was not a positive experience for me, to be sure, and so I wound my way through elementary school proudly calling myself an atheist, after my parents, just as I'm sure many others proudly proclaimed their Christianity or Judaism. It wasn't until middle school, really, that, with the development of my super-ego, I began to even contemplate anything of a spiritual nature. Of course, at that age and with that background, I lacked the vocabulary necessary to flesh out these contemplations, much less to voice them. Needless to say, my developing moral code was at odds with what I had been taught and had practiced up until that point.

That's not to say that I had been taught that murder is alright, or that I had been thieving from an early age. More subtle than that, I began to see my actions at the time and before that in elementary school in a new light. I began to see that my actions and words affected those around me, sometimes in profound ways. The most profound by far was when I ran away from my father.

Hoping to produce another engineer just like himself and my mother (and we see how far that got), he put a very large emphasis on doing well in school, particularly in math and science. In sixth grade, I moved down to live with him instead of my mom, making the hour's drive to stay with her every other weekend in a reversal of the previous schedule. In the first quarter of my seventh grade year, however, when I receieved my first `F' on a midterm report card, I panicked and left home before he got back from work, leaving a shattered cosmetics mirror on the table along with the report card, took the quarters in the change jar, and rode my bike to the Wal-Mart nearby. It was October. I was eleven.

While I shivered and waited for the ideas to come to me behind the dumpsters and A/C units of the Wal-Mart, I reasoned with the screaming of my fledgling conscience: The broken mirror stood for my broken trust in my dad --- I did not think that he would not get irrationally angry with me because of my grades. Further, my running away was to be an escape from all of those things and a return to the safety of my own mind and plans. I would ride the bus up to Boulder, where my mom lived, and plan the next step of my escape to safety.

In reality, the broken mirror and flight from home were both symbolic more of my slowly shattering world-view as center of my own universe than some trust related issue. Or, if they were related to trust, than it was the trust I had previously placed in my own childlike infallibility. This was subconsciously hammered in on that cold night at the bus station and the following several days.

My mom found me the next morning outside Waldenbooks --- she knew me so well --- and the rest of the day was filled with tears on everyone's behalf. Hours were spent on the phone with my dad as he went through my room and tried to sort out what had gone wrong in the situation. The answers I gave were half-truths and evasive comments skirting the issues really at hand, and even some outright lies. The problem I had was a conflict in myself and no words to describe it. I fell, of course, to blame, and claimed that my dad spent too much time at the bar with my step-mom (the bartender). This was a legitimate concern to my parents, though I cherished the time alone, so I used it to escape from the consequences of my actions.

This all led to me moving back in with my mom to complete my public schooling. This helped, perhaps in ways other than intended: not only was my mom a little more free with me than my dad had been, but Boulder was much more constructive to spiritual growth than Lakewood by far. It was the first step in a long and ongoing journey to figure out my place in the world and finding meaning with this life I've found in my possession.
