\begin{quote}
If Matthew died on September 6th, 2012, was Madison born then?
\end{quote}

No, I don't think so. Madison was born some years later. Maybe at some point in 2014. The years in between were a sort of liminal time.

\begin{quote}
You found yourself in a place between.
\end{quote}

I did. There was this time in my life when I was figuring out gender. I was figuring out poly. I was figuring out working. I was figuring out not being at school and moving away from music and learning to write and all the interstices of alcoholism. Those little nooks and crannies you never know about until you start drinking in earnest.

It was like a second period of growing up. Something more refined than a rebirth. Something less grand. Something subtler.

\begin{quote}
You also learned the term `hendiatris'.
\end{quote}

I have a style, alright?

\begin{quote}
Right.
\end{quote}

It's the time when I started {[}a{]}{[}s{]}, the time when I started to look at my life in earnest, to give thought to the fact that one might actually enjoy things, have opinions. It was the time I started to let go of irony, bit by bit.

\begin{quote}
It was the time you started to own yourself.
\end{quote}

Maybe. Maybe not. I'm still working on that one. It feels like an ongoing struggle.

\begin{quote}
What's the old saw? You'll finally perfect it six months after death?
\end{quote}

I think that was about when men leave puberty.

\begin{quote}
Let's talk about TIASAP.
\end{quote}

No more, please.

\begin{quote}
Let's talk about puberty.
\end{quote}

That first exploration? I don't know if I'm ready for that, yet.

\begin{quote}
So what \textbf{are} you talking about?
\end{quote}

Well, I was going to talk about that liminal phase, but you seem to have other ideas.

\begin{quote}
That just means you're unfocused.
\end{quote}

Well, yes.

\begin{quote}
Tell me about that place in between, then.
\end{quote}
