\begin{quote}
Was it really so bad to be in this liminal space?
\end{quote}

Of course not. I just got done saying how much I learned during that time.

\begin{quote}
You don't make it sound pleasant.
\end{quote}

It wasn't, I suppose. I mean, obviously there was a lot of good going on in my life. I started a few relationships that are still going strong to this day. I solidified my place in the industry. {[}a{]}{[}s{]} took off. Good stuff came of it. A better me came of it.

\begin{quote}
At what cost?
\end{quote}

Well.

Okay. A lot of that time was bound up in recovery. There was the suicide attempt in March that ate up a lot of my emotional bandwidth on a daily basis for quite a while.

There are a lot of cute metaphors for how pain and grief work on a daily basis. Spoon theory is great and all, but it's starting to lose its luster for me. I like the idea of spell slots. It was like the number of spell slots I had to work with before needing a long rest was reduced by half after that, and it took me two years at least to bring it back up.

\begin{quote}
You remain a parody of yourself.
\end{quote}

It's only been a few days since you reminded me of that.

\begin{quote}
I will never cease to do so.
\end{quote}

Fine.

Another metaphor is that you have a box with a ball in it. On the wall of the box is a button that causes pain, exhaustion, anxiety, your choice. When it starts out, the ball is big and with basically every movement, it bumps up against the button and activates it. Over time, the ball gets smaller and bumps up against the switch less often.

Or maybe you could think of it as endurance. You can hold a glass of water for a few minutes, but after a bit, it becomes painful, and after along time, your arm can start to feel paralyzed. Over time and with training, you might be able to endure that longer and longer.

The last two, in particular, are used often with the idea of grief in mind, which, I suppose, is fitting given how much I still bear over Margaras.

\begin{quote}
Do you feel any for Matthew?
\end{quote}

Less, perhaps.

\begin{quote}
Was it that easy to let go?
\end{quote}

I don't know. Maybe.
