Coming out to myself and JD was more gradual. A sea-change.

\begin{quote}
Maybe that's what those two years were between Matthew and Madison were.
\end{quote}

Nothing of him that doth fade, but doth suffer a sea-change into something rich and strange.

I suppose so. I explored around the edges of it. I touched it tentatively. I lived my life in widening circles.

\begin{quote}
Surely you mean narrowing.
\end{quote}

Okay, yes. It was too good a line to pass up, though. Shakespeare \emph{and} Rilke in one go?

\begin{quote}
There is nothing new under the sun.
\end{quote}

Ooh, and Ecclasiastes, you spoil me.

\begin{quote}
Treat, as they say, yourself. Carry on.
\end{quote}

There were little fits and starts between James and I. I remember laying on the couch --- that awful, awful yellow couch --- and him getting playful, and then some little movement of his touched a nerve and I started crying because of the way that brushed up against that me that wasn't in focus. It brought it to the forefront the fact that I didn't align with myself, that there was a lag in my proprioception, that I was falling behind myself.

Is there some word for ecstasy that doesn't imply it being positive? Something that captures the feeling of being outside oneself, beside oneself, behind oneself without implying the sense of greatness, of awe that goes along with spiritual \emph{ekstasis}?

\begin{quote}
Dissociation?
\end{quote}

Yeah.

That.

That little bit of panic-colored dissociation that I would later name dysphoria would come in waves. Sometimes it'd be triggered, as it was then. Sometimes it would fade slowly into view and I'd go on a tear making skirts and then it would fade back into the low background static of the anxiety that goes along with being a member of a minority identity group.

\begin{quote}
There \textbf{was} ecstasy, though. There was euphoria as well as dysphoria.
\end{quote}

Yes.

The moment when my hair got long enough to put up in a ponytail.

The utter terror of shaving my legs for the first time, weird as it sounds. Outrageously stupid, and yet the feeling of \emph{having} shaved legs was incredibly validating.

The first time I looked in the mirror and saw the trace of femininity.

The softening of skin.

The first ``she'' on the street.

The first ``ma'am'' on the phone.

Hell, the first time dressing feminine.

\begin{quote}
What, back when you were nine? When you snuck into the spare room and tried on one of Julie's dresses?
\end{quote}

Holy \emph{shit} could you just \emph{shut up}.

\begin{quote}
Wow, touched a nerve, there.
\end{quote}

We will talk about that later.
