Today, my therapist asked what the plot was to this new writing project.

\begin{quote}
Me!
\end{quote}

Pretty sure you're just the antagonist.

\begin{quote}
Come now, don't say that about yourself.
\end{quote}

Right.

I stammered something about how it was more about overriding themes. I wrote about alcoholism. I wrote about dad. I wrote about all those little side-quests. ``It's about the way creativity affects and is affected by all these different things in my life,'' I said.

``Were you not creative when you drank?''

``Certainly not as much as I am now that I've stopped.''

``This sounds exhausting,'' she said.

``Well, it is, in a way. It's very easy to write. It flows onto the screen far easier than any fiction or article I've written before, but it leaves me totally beat afterward.''

\begin{quote}
You're really good at wearing yourself out. You spin in circles around the smallest things. You wind up exhausting yourself on the daily.
\end{quote}

I suppose I do, at that.

\begin{quote}
Well? You sound unsure of how you answered her.
\end{quote}

This project is sort of ill-defined.

\begin{quote}
You are ill-defined.
\end{quote}

Not going to deny that.

I'd say a lot of this project is accidental, unintentional. I stumble about at the end of your lead and, as you say, spin circles around the smallest of things. It's hard to come at this with some sort of idea of a plot. I can't even work chronologically, because if we work from the beginning of Matthew's life back in 2000, we keep having to double back and look at proto-Matthew's life before that, and to understand that, we keep having to look at all these other people.

\begin{quote}
There are too many of you.
\end{quote}

Says my ally.

\begin{quote}
Point well taken.
\end{quote}

All the same, I'm not sure that I answered her incorrectly. The core conceit of this project is one of creativity. Not anything so guided and structured as \emph{writing} or \emph{composing} or \emph{programming}, but that raw, primal thing from which the others spring.

\begin{quote}
Or seep, depending on the day.
\end{quote}

It's about the ways in which this idea, this entity impinges itself upon various things in my life. It's about the ways I shape and am shaped by it. It's about turning it back in on itself, as much as I can, and applying creativity to the idea of creativity itself.

\begin{quote}
Using words.
\end{quote}

Well, mostly words so far, yes, though I'm slowly incorporating bits of other things in there, too.

\begin{quote}
There's another metaphor to be made here. Remade, actually. You keep winding up stuck on these very abstract concepts. You keep talking about your complex feelings on your dad or on the way Margaras' death affected you or on mysticism, and then you circle them again and again, now narrowing, now widening, in an attempt to triangulate some imagined center.
\end{quote}

Writing, composing, programming, those are all inexact tools to apply toward inexact goals, though. Is that so wrong? Is it wrong to try and focus through words? Is it wrong to try and figure out more of how you think through something creative?

\begin{quote}
No, but it \textbf{is} important that you be cognizant of that fact.
\end{quote}
