All of writing, all of creativity is selfish. To take some idea or some concept and to set it down on paper and say, ``I made this'' is selfish, of course, but to then take that thing and show it to others with the expectation that they might get something out of it as well is taking that several steps further.

To sit down in front of the keyboard and to say, ``I am going to write a story about a person who runs away from home to escape her fundamentally unhappy life'' and to then take that story, post it on the internet, submit it to anthologies, publish it in a collection and attempt to get others to read it, is selfish. It's an act of improvement for the writer, sometimes on a very real basis, if there is money to be made in the process.

To sit down in front of the keyboard, however, and say, ``I am going to write a story about me when I ran away to escape my fundamentally unhappy life'', well, now we're up to three levels of selfishness. I try and nail down an idea to paper or screen and say, somehow, that it is \emph{right} and \emph{good}, I make that idea about \emph{myself}, and then I try to show that idea to \emph{others}\ldots{}

\begin{quote}
Is there no good to be had from memoirs, then? From any autobiographical content?
\end{quote}

There's certainly good to be had for the writer, for the creator. On my end, I'm making something that I both feel proud about and am learning from. I'm learning more about this art, I'm learning more about all of these problems I'm tackling --- I didn't know, for instance, just how conflicted I was about my dad until I started writing that section of the site. I though, \emph{oh, I'll write about my past and make the final point that I've had to accept that there's a certain amount of my dad that I'm comfortable having in my life, a certain level of relationship that's acceptable}. I was not expecting to learn, through writing, just how conflicted I am about him still.

\begin{quote}
And for others? Is there not enjoyment to be gained from that which you create?
\end{quote}

\emph{Disappearance} was good, I thought. I got a lot of good words sent my way from some folks that mean a lot to me for it. The story left an impact on them, they came away from it with some sort of enjoyment, or at least some level of emotional resonance.

This project, though? I don't know. there are bits that I've tried to make enjoyable. I had fun with the koans and birds. I put a lot of emotional investment into the bits about Margaras and my dad. I tried to do some fun mixed-media stuff with the fursoña animations and the mysticism stuff. I can see those being enjoyable.

\begin{quote}
And the rest?
\end{quote}

I don't know. Honestly.

\begin{quote}
What about applicability?
\end{quote}

I\ldots{}hmm.

\begin{quote}
You came into this page thinking, ``Ah yes, time to dunk on myself again'', didn't you?
\end{quote}

I guess I did. Self-deprecation runs deep in queer lives. Self-doubt plagues artists. Self-deception runs in the family.

\begin{quote}
Selfishness is defensible when it leads to entertainment, applicability, or self-improvement.
\end{quote}

To an extent. At some point, it's just narcissism. At some point gets so ``treat yourself'' that one loses sight of collective improvement.

\begin{quote}
Of course. Are you really in danger of such?
\end{quote}

Constantly, feels like.
