The first poetry I remember writing was back before high school. At some point I picked up the poetry bug and decided I was going to try my hand at it. Finding it hard, I quit after the first poem I wrote. It was something really, \emph{really} bad, too. Something where all I knew about poetry was that it should rhyme, so I sacrificed\ldots{}well, everything in search of a rhyme. Readability. Sense. It was horrifying.

\begin{quote}
You find a lot of your old stuff horrifying. Play can be creative.
\end{quote}

Sure. Play teaches us how to be creative. A lot of creativity is playful.

This went a step back from that. Play is important, sure, but it didn't make anything I'd actually call a poem. It was an innocent mockery in the same way as a boy trying on his dad's shoes and blazer.

I suppose it's a good thing that a lot of my early works are lost to time.

\begin{quote}
You filled reams of paper and countless blank books with drawings and doodles and words. You drew maze after maze on copy paper. You grew exceptionally fond of creating parabolic curves with straight lines. You went through a phase of drawing elaborate worlds of ramps and springs and houses for tiny spherical creatures with horns for mouths. Do you miss none of that?
\end{quote}

In a cute sort of way, I suppose. It was fun. I would laugh at it now, but I wouldn't find anything new to build off of it. After all, this project is built off writings after I was born. All that is from proto-Matthew.

\begin{quote}
You drew an entire comic set in the world of Garth Nix's Abhorsen trilogy, except the main characters were foxes. You filled a few notebooks with furry art, too. You kept a diary well after your dad destroyed the first one, intended originally as letters to send to your friend. You called it Julene. You later feared that would be creepy, and changed it to Kai. Do you miss none of that?
\end{quote}

I kept some, of course. Some of it is irrevocably online. I couldn't remove it if I wanted to.

I burned the journal, though. It was a remnant of proto-Matthew. It was from before I was born.

\begin{quote}
At what point did play cease being just play, then? At what point did creativity assert itself?
\end{quote}

When I started singing. When I first heard Madrigals sing during my first choir concert. When I stopped drawing and started writing. When I realized that there was more to art than playing at art.
