\begin{quote}
I assume you went looking for one of these execrable poems of yours?
\end{quote}

I did. I wasn't really able to find much from The Before Times, but I found a few from shortly after while prowling through my LiveJournal and archives of my old site in high school.

\begin{quote}
\href{https://web.archive.org/web/2005*/http://ranna.babylonia.flatirons.org/}{RedFox! Productions}, right?
\end{quote}

Gah, yeah. I was a kid, alright?

\begin{quote}
If you say so.
\end{quote}

September 26, 2003:

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\tightlist
\item
  Borne through air, Close my eyes. Wind ruffles hair Soul sighs, Heart flies; I'm the wind.
\end{enumerate}

I flow east: Over the plains, Over land creased. Current refrains, Cloud stains As I build.

Trees bow at my Will To move drives me Onward I push through Mountains Do nothing but Divert The rain as I Flow.

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Borne through air - Rise up high - Driven there, Earth nigh, I sigh; I'm the wind.
\end{enumerate}

I flow west: Past the lakes, Water my guest; Thunder makes Noise, wakes, As I storm.

Sand flies at my Force Builds as I Push Across the Land Flows beneath my Self Means nothing to Wind.

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Borne through air, Through the night And dawn fair. No fight, Only flight; I'm the wind.
\end{enumerate}

I flow south On the ocean, On delta's mouth My motion Just notion As I breathe.

Waves break as I Drive Past the thin Sands Lift themselves to my Body Waxes as I Press Through the stillness of Night.

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Borne through air, Around the world And forests I tear; Ferns furled, Trees burled; I am the wind.
\end{enumerate}

I flow north, Across the ice; I roll forth Past spice -- So nice -- As I change.

Men bask as I Warm Drops of rain Fall Colored leaves Shiver Because of the Chill Wind blows on Past.

\begin{quote}
It's not without its own sense of charm.
\end{quote}

I suppose. It's crude. It's a bit heavy-handed.

\begin{quote}
Your others are not?
\end{quote}

Well, okay, fair. I like to think that I've improved nonetheless.

\begin{quote}
Are these old ones not creative? Are they still just play?
\end{quote}

The more I think of it, the more I think it's that they're just too\ldots{}work. They're not creative, because they're too mechanical. I had realized that writing wasn't just play, so I stopped playing altogether.

\begin{quote}
Wrong answer.
\end{quote}

Tell me about it.

January 11, 2003:

What hath man wrought! When faced with the question of love Or seeking peace with the answer thereof, Or faced with life peril-fraught, Created a god, or several, to satisfy Some need to fulfill or deny A lacking - A slacking On someone else's behalf, Or his own behalf - And on the world a question of faith brought.

And when a man, endowed With the ability to make his own God, Does so with nary a nod, And finds the god shan't be cowed, What does he then? And when a group of men Make their God With nary a nod, And cow him easily, rightly To them, and find him tightly bound, what then, with a god bowed?

What then, indeed, should a God, Now lesser than his creators, do When his creators move to gods new? Is he then still a God? Or is that when God dies, Not bloated with swarms of flies, But forgotten? Not rotten, Forgotten and immortal, what then? Does he hope to come again, Rising a second time, perhaps again to be God?

One would hope that the God, being omniscient Would realize he was no longer, otherwise Might he become destructive? Likewise, A god, waiting patient Could become restless, Try to leave his creators breathless, Again, But then, Be pronounced a heretic By all but the hermetic And others of the new God ignorant.

So hence a people divided Those of Whispers and those of Nanon, Fight to the tooth and fight to the bone, Until over Whispers Nanon presided; And when those of Nanon took Speech from the Whispers so as to look And not hear, They here Those of Whispers with Supposed powers of myth Of creation with speech's remnants provided.

So it was before the fall of Whispers that Faith of most all lay in technology, Remnants of religion lay in astrology And superstitious fears like the black cat. Only after the fall did the faiths Of only the Whisperers turn to mysterious wraiths And gods, But the odds That one of the gods was taken more seriously Than the rest was small, and not mysteriously, The small bit of Faith quickly passed as society's scat

Now, it's come that those of Nanon have all but forgotten Those of Whispers except perhaps in myth Maybe portrayed as consorting with Black cats or something equally rotten. But for the Whisperers, the city Of Nanon is very real, also denial of pity Of sunlight, For sunlight Is blocked by the city directly overhead And the Whisperers know of only shadow instead; Only death out from beneath the city to be gotten.

The magic that's spoken of those Of the Whispers, is often made Out to be more, but because of their stayed Speech, only whispers remain in quite prose. So through the long stretches of time, The Whisperers, through long stretches of rhyme Can make - Only make - What they wish, with words divine, Benign, or malign, And in their creations complete trust repose.

So begins a story, often told but never yet writ Of a divided people still the same And the rise and fall of a god played like a game. While not true itself, it is truth lit: As men continue to create and live under gods, What would happen if the gods, at odds, Warred and fell, Raising hell In the process? What would happen In a society misshapen If a wrathful god fell and no one cared a whit?

\begin{quote}
Ah yes, your Keats phase.
\end{quote}

It was a mixture of Keats and Larry Niven, I think.

\begin{quote}
That is intensely Madison.
\end{quote}

Thanks.

I had recently read \emph{The Ringworld Throne}, so I was thinking about vertically stratified cities, and had also been on a Keats kick ever since reading \emph{The Hyperion Cantos}, so I decided I would write a sci-fi epic poem to support my conlang.

It's a mess.

\begin{quote}
Could be worse.
\end{quote}

Could be better.
