\begin{quote}
If you went from a mockery of creativity to a mockery of play, when did you settle down and just write a damn story?
\end{quote}

I think it wasn't too long after, actually. I wrote \href{https://writing.drab-makyo.com/fiction/all-of-time-at-once/}{\emph{All of Time at Once}} in April of 2004, and that was the first time I started to think, \emph{ah-hah, okay, there's a rhythm to this, a pace, a set of mechanics as well as an art.}

And from then on, I basically dropped writing in favor of music for months. Sure, there were a few others scattered around there. \href{https://writing.drab-makyo.com/fiction/tu-pater-et-mater/}{\emph{Tu pater et mater}} in May of 2003, and \href{https://writing.drab-makyo.com/fiction/light/}{\emph{Light}} in June of 2004, but other than that, I kind of just dropped it.

\begin{quote}
Why?
\end{quote}

I graduated. I left language arts classes behind. I went to school for an engineering major.

\begin{quote}
One you were supremely unhappy in.
\end{quote}

Right. And then when I started writing again, it was music.

I wrote a few essays I was reasonably proud of, but it took another four years before I decided to actually sit down and give writing a go in a more structured setting, and then only because of NaNoWriMo.

\begin{quote}
Ah yes, your ``boy meets girl with a twist'' story.
\end{quote}

Yeah, \href{https://writing.drab-makyo.com/fiction/consequences-of-dissonance/}{\emph{The Consequences of Dissonance}}.

\begin{quote}
You originally named it \textbf{Coming to Terms with Being a Terrible Person}.
\end{quote}

I did, yeah. I was fresh off my relationship with Kayla and well into a relationship with Kanja, and had a head full of hatred for who I used to be.

\begin{quote}
And who you were becoming.
\end{quote}

Well, it wasn't \emph{Coming to Terms with Having Been a Terrible Person}, was it?

\begin{quote}
Fair enough.
\end{quote}

It wasn't a bad story, really, nor even that poorly written. I've even thought of revisiting it sometime. It was sort of a coming out story, but a coming-out-for-the-second-time sort of thing. Gay boy starts dating a girl and has to go through the social process of coming out as bi.

\begin{quote}
As Madison?
\end{quote}

I suppose. I went through my own series of comings-out, so maybe I have more insight into that now.

\begin{quote}
And you're less of a terrible person.
\end{quote}

Doubt.

\begin{quote}
There are perfectly cromulent reasons for you to think of yourself as a terrible person in the past, and even as a terrible person in 2008. Or even one now, really. You're just less of one.
\end{quote}

Always improving, I guess.

\begin{quote}
How did it feel to come up with a schedule, a goal, and a plan, and then to stick to it?
\end{quote}

I never finished the story.

\begin{quote}
But you won NaNoWriMo that year. You went over by eight thousand lines.
\end{quote}

I guess.

\begin{quote}
And you're dodging the question.
\end{quote}

That's why, though. It felt good while it lasted. It felt good during that hypomanic rush to actually complete something, to come up with an outline and actually work through it.

Then I finished NaNo with several hours to spare and tried to keep going, but there was something missing. I felt rudderless. I kept trying to poke at it, but I think I was working as well as I was because of the deadlines. I was still trying to balance the work with the fun that go into a creative endeavor.

\begin{quote}
Did you stop having fun, or did you stop doing the work?
\end{quote}

I think it's more complex than that. There was fun to be had in the race to the finish line. I think that's why NaNo is so popular. And doubtless it was work, of course.

But with the fun of having already won gone, I was faced with the fact that I had less outline than I had originally thought. Pantsing, as the community so eloquently puts it, may work well for some folks, but I was mostly left feeling uninspired and unmotivated once December hit. The same thing happened with \emph{Getting Lost} and \emph{Inner Demons}. I started strong enough with the basic idea as I tried to write by the seat of my pants, but without a direction or even any goal, I lost steam and wound up disheartened.

\begin{quote}
Do you not do well without goals, then? You don't seem to have one for this project.
\end{quote}

It's not necessarily that. More that, the shorter the project, the less planning that's required. I do much better with articles and short stories than I do with novels. At least so far, given the amount of planning that goes into each.

This project is working as well as it is because of my heavy reliance on these side-quests. I can break a story down into manageable chunks so that, by the time I might start losing direction, they're about overwith anyway.

Besides, I have you to help.

\begin{quote}
Me? Little old me?
\end{quote}

Yeah. It's much easier to have a conversation than it is to plan out a story. You keep taking me in directions I don't mean to go.
