\begin{quote}
I suppose you also searched your archives for poly.
\end{quote}

You know me so well.

\begin{quote}
Of course.
\end{quote}

The first mention on LiveJournal was April 6th, 2004.

\begin{verbatim}
Of the interesting topics that popped up, that of polygamy stuck with me the most.  Michael has a date with another on Thursday and, while this brought up issues with Merlin and Atrius, all I can say right now to Michael is that I wish him the best of luck.  It just feels like it would actually /work/ in his case.  As to how it pertains to me, I'm not sure if my mind could handle having two mates.  Granted I still have a thing for Kory (hah, good luck with that) and a few others, I just don't think I could find another who a) would be willing to have that sort of relationship with me and b) I could have that sort of relationship with.  Ah well.  Something to think about.
\end{verbatim}

\begin{quote}
Never one to have a high opinion of yourself.
\end{quote}

That's hindsight talking.

\begin{quote}
You literally just got out of a therapy session where you talked about how you don't believe you deserve a better job.
\end{quote}

Touché.

Michael and I's relationship was rocky, tumultuous. We met through a queer group and from there wound up in a weird, heated romance that danced around sex, gender, mental health, everything. We fought, we made up. We got annoying. We made out a lot, we had sex, though with each of our individual hangups around sex, it was rarely penetrative.

\begin{quote}
It was penetrative once.
\end{quote}

That's rare, isn't it?

\begin{quote}
Vanishingly.
\end{quote}

Listen, we were both trans. The subject was complex.

\begin{quote}
You were a cis gay guy. You told me that. You were unsure of vaginas.
\end{quote}

It started that way, I suppose. I learned.

\begin{quote}
Then you bought one for yourself.
\end{quote}

Listen.

\begin{quote}
Yes?
\end{quote}

There were bits of sexuality that didn't work for me when I was bepenised. A lot of those make sense in a transgender context. Matthew was still a gay guy, but the Ship-of-Theseusizing was already beginning.

\begin{quote}
`Bepenised'? `Ship-of-Theseusizing'?
\end{quote}

You verbed it first.

\begin{quote}
We've gotten off track.
\end{quote}

Right.

In two previous relationships, poly had come up, and neither time, it had worked. With Merlin and Atrius, I had immediately jumped to jealousy. I felt as though I was being set aside.

\begin{quote}
Never one to have a high opinion of yourself.
\end{quote}

It didn't last. That was part of the breaking point. Similarly with Andrew and Ryn. I've heard it said that jealousy is a sign that one's needs are not being met.

\begin{quote}
What did you need that you weren't getting?
\end{quote}

I thought it was someone to myself.

\begin{quote}
You couldn't own yourself, maybe you could own someone else.
\end{quote}

That hurts to hear.

\begin{quote}
Is it wrong?
\end{quote}

I don't know. Maybe it isn't. Maybe I wanted to keep someone. To possess them. Maybe it was a reaction to being owned.

\begin{quote}
Let's talk about kink.
\end{quote}

Let's fucking not.
