I won't repost them, because they're direct logs, shortly after the conversation mentioned before, the issue of Michael bringing another partner to the queer group we were a part of came up. How would we work a situation where I, coming from a monogamous point of view, would be in the same room with my partner and metamour? Would we split our time? Would one of us get ignored while the other got attention? Would we both get attention? Would we just plain avoid it?

\begin{quote}
It's surreal, even for me, to hear you talk about this today, given your current situation.
\end{quote}

Suppose that the young man, Matthew, is in a monogamous relationship with someone. As the years go by the relationship begins to change, fades, and is replaced by a new one, more open than the last. After a decade or so, all of the parts have been replaced and Matthew, now Madison, is in a polycule the size of Rhode Island. Is Madison still the same person as Matthew?

\begin{quote}
That's a bit heavy-handed.
\end{quote}

You can't start the metaphor train a-rollin' and then expect it to stop on a dime.

\begin{quote}
I'll own that.
\end{quote}

I met JD in 2005, and met Robin in 2012. By 2013, I was in a relationship with both, and we were sharing dinner, along with Robin's partner, at a convention. It was natural. Comfortable. It was fun.

And now, I'm in relationships of various sorts with a half dozen people. The changes between then were so incremental, and discussed so thoroughly, that it really does feel Ship of Theseish.

\begin{quote}
Stop.
\end{quote}

Never.

The other consequence of that is that, along the way, I sufficiently distanced myself from the mechanics of my parents' relationships that I finally felt comfortable in calling that dream fulfilled. The turning point was my mom, during one of her visits back to Colorado, mentioned my relationship with Robin as something she could never do.

\begin{quote}
Are you sure it wasn't writing a Python/Javascript/SVG web app to map polycules using force-directed layouts?
\end{quote}

Okay, maybe it was before then.

\begin{quote}
And score a point to the ally.
\end{quote}

I didn't feel better than my mom when she said that, of course. Her relationships matured well over time, I think. She and Bob got better at communicating and expressing their needs. And even if they hadn't, the love she had for all of her partners was no less valid for being monogamous.

\begin{quote}
Could you say the same of your dad, had he said that to you?
\end{quote}

I don't know.

\begin{quote}
Probably not.
\end{quote}

Yeah, probably not.
