If poly is queer, in that it's not relationship-normative, then I'm queer. If being trans is queer because it's not gender-normative, then I'm queer. If my identity blurs lines, then I'm queer.

If I'm in a relationship with someone, then, is that a queer relationship? Is my partner queer?

\begin{quote}
What would they say?
\end{quote}

I don't know. I haven't gotten to the point of talking to myself about this yet, much less talking with them. That's what this process is, isn't it?

\begin{quote}
So what would you say, then?
\end{quote}

My gut instinct says that, since I'm trans, I've transgressed the lines of gender-normative relationships; since I'm poly, I've transgressed the lines of relationship-normative relationships. That, since I am queer, the relationship must be as well.

\begin{quote}
But?
\end{quote}

But it doesn't really feel like it. I feel like a girlfriend. Barac feels like a boyfriend. I feel like I've stepped onto an escalator, here.

\begin{quote}
There is an error in your gut instinct: it does not take into account that, in a relationship between two people, there are more than just two actors. There is you, there is your past, there is Barac and his, and there is society, influencing all four of you. That you are queer and that Barac does not consider himself to be is beside the point. Society, Barac, and Barac's past all think of this as a straight relationship --- or a take on one, at least --- and that's overwhelming your gut instinct, which only has access to you, and limited access to your past.
\end{quote}

Is that why I feel contention, then? Is that why there are an odd number of actors in this situation?

\begin{quote}
Perhaps. Perhaps you are feeling contention because you are having to work, for once, rather than slot smoothly into a relationship.
\end{quote}

My other relationships have taken work, though.

\begin{quote}
Your other partners have spoken the same language as you. It was easier to coordinate that work. You and Barac are having to learn each other's language as you go along.
\end{quote}

Robin and I had to learn the language of poly when we were starting out together. Judith and I and Colton and I both had our own things to learn as our relationships grew.

\begin{quote}
Yes, but you all spoke queer. None of you really spoke normative, a skill you're having to learn late in life.
\end{quote}
