\begin{verbatim}
% Trying to connect to furry: 74.207.243.108 8889.
% Connected to furry.
#$#mcp version: "2.1" to: "2.1"
Welcome to
              _____                 _ _ _   _    _ __   _   ,  SM
               /  '                ' ) ) ) ' )  / /  ) ' ) /
            ,-/-, . . __  __  __  , / / /   /  / /      /-<
           (_/   (_/_/ (_/ (_/ (_/ / ' (_  (__/ (__/   /   )
                                /
                               '
          The first 99 & 44/100% anthropomorphic/Furry TinyMu*

(The SM means that FurryMuck is a Service Mark of the FurryMuck Wizards)
To connect to your existing character, type "connect <name> <password>".
To receive a new character, send mail to join@furrymuck.com
To see the latest news, type "news" after connecting to a character.
To disconnect from a character, type "QUIT".
Use the WHO command to find out who is currently online.
Use the 'whereare' command to find places with active people.
Use the 'wizzes' command to see what Wizards are on line, or the 'helpstaff'
 command to see who of the help staff is on.
Use "connect guest guest" to visit FurryMUCK as a guest.
All users of FurryMuck are bound by our AUP. "NEWS AUP" to read this document.
----

Sadly, FurryMuck has lost one of its own.

S'A'Alis, May 29, 1963 -- September 5, 2012, the Large Furry Marsupial, and a
member of the L'Drey, a space-faring, fox-like species. He was never without his
'Eternally Filled Highly Caffeinated Coffee Mug of Doom'. From 1993 - 1999,
S'A'Alis hosted the servers that FurryMUCK ran on, and was a character creation
wizard 1993-2001. Condolences can be sent to his beloved wife, IceWolf:

M. Vogt, W5910 Genske Road, Black Creek, WI 54106

Life is eternal, and love is immortal,
and death is only a horizon;
and a horizon is nothing save the limit of our sight.
 -Rossiter Worthington Raymond

----
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
Makyo stretches out and yawns toothily, shaking Makyo's fur out.
Players online for whom you are watching:
Danish            Makyo             Taxus             
Done.
The next scheduled database save will be in 24 mins, 14 secs.
You place a strategic call to one deity or another.
Makyo disappears in a puff of complacency.
Purple Nurple Foyer(#52464RLJ)
You step in through the door and into a cramped foyer.  Advertising
posters plaster the walls and there's another door right in front
of you (east).  The door is padded purple vinyl, studded in a diamond
pattern.  This is the Purple Nurple, Furrymuck's gay/les/bi nightclub
and meeting place.  Feel free to come on in if you are straight too.. we
don't bite (unless you ask nicely ;)  There is a sign on the wall next to
the door and a notice where the computer used to be, saying that it's now
in the main room.
Players inside the Nurple:
 TealFox            Floid              MegaWolf           Srass
 White_Fox          Cain               JanusFox           Singe
[Exits: <IN> to the Purple Nurple   <OUT> to Sable Street]
Contents:
Polo
PN RULES : READ THIS TO BE ABLE TO ENTER
You enter the PN
Makyo disappears in a puff of complacency.
The Purple Nurple
You are in the Purple Nurple, furry's premier gay/les/bi spot.  
The room is large, a converted warehouse - the ceiling's
about fifty feet above the crowded floor.  An entire suspended
lighting grid swivels back and forth in the middle of the room,
rigged with a complex array of lights, lasers and mirrors.  
The overall effect is of an alien spacecraft hovering about twenty
feet over the dance floor.  Huge projection wall-screens flicker
images of furries dancing, clips from anime movies, computer
graphics reels and old cartoons.  The music is loud, thumping
techno and house, bass thundering through the gyrating furries
on the dance floor.
To one side is a lounge area, acoustically out of the main thrust
of the speaker stacks allowing normal conversation.  A bar with
every drink known is along the wall of the lounge, and
the floor is scattered with heavy-duty beanbag chairs, funky couches,
and other assorted furnishings, all roomy enough for at least two furs.
A small staircase leads up to the Nurple Apartments.
Contents:
TealFox
Floid
MegaWolf
Srass
White_Fox
Cain
JanusFox
Fiend Plushie
Singe
All complaints --> Rigel
NURPLE ADULT/PG POLICIES ****** PLEASE READ
Bulletin Board
You whisper, "Makyo hugs on fox." to TealFox.
Miko arrives from the foyer.
Makyo nuzz on SQRL.
Miko fluffs the foxyfluff.
TealFox whispers, "TealFox  hugs tightly. :(" to you.
You whisper, "Makyo leans in against, squeeze.  Rrf." to TealFox.
White_Fox has connected.
White_Fox has disconnected.
Singe hugs Miko!
Miko squeezes Singe!
Singe growls, "poor margaras :("
TealFox whispers, "TealFox  just got the news a little bit ago... still shaken," to you.
JanusFox sighs, "Yah poor guy :(
Cain curls up tight on xane again
Miko chatters, "What, huh?"
Miko o.o
TealFox knew him before either of us were in the fandom. I ... yeah. no words right now. Just tears,
You whisper, "Makyo nods and nuzz at.  Little torn upabout it." to TealFox.
1) Duelist  2 days ago -- Fallout IRL!
2) Makyo  Today -- Margaras
Use 'read <mesgnum>'to list a message.  Use 'read <keyword>' to list
messages with a keyword.  Use 'read -' to read the next message.
Done.
You yerf, "Miko: read 2"
Cain holds Teal close
Miko cries.
TealFox whispers, "TealFox  nods. yeah, me too." to you.
TealFox snugs Miko too
Miko hugs TealFox!
Srass says, "That was a nice post, by the way, Makyo."
Singe nods.
You yerf, "Spelled fallibility wrong twice :o)"
White_Fox erfs.  :/
You yerf, "Oh well."
Srass says, "We know what'cha mean."
You yerf, "I started coming around here when I was 14.  You all mean quite a bit to me."
TealFox snugs Makyo. "Intent comes through. "
Singe growls, "I think I was 16 when I first showed up here."
Singe growls, "Maybe 17"
FoxLord arrives from the foyer.
FoxLord waves
Srass waves
FoxLord snugsa Tealfoxie
Singe mmhs.
Srass says, "I wish I could've grown up here like that.  I think I would've ended up less screwed up."
MegaWolf growls softly, "I think I'm still in denial."
Cain nods and noses at Xane ears
MegaWolf muzzlerubs Cain, squeezes more.
TealFox didnt really start discovering my self until late...i didnt come out until like 23... and didnt find the fandom till almost 30. i knew Margaras pre fandom on some of the IRC chat channels. :/
White_Fox murrs, "I met margsy right after meeting Malky. "
White_Fox murrs, "Whl happened to be local :)  Good peoples"
White_Fox murrs, "Miss him. :/"
Pyat arrives from the foyer.
Pyat squeaks
JanusFox yips, "It's just so sudden.  And he's usually around so often."
Somewhere on the muck, Taxus has disconnected.
Singe growls, "yeah"
Pyat squeaks unhappily. Margaras?
Cain woofs, "Margs gave me a good bit of selfconfidence in areas I really didn't have. It'll always be a good memory for me"
Somewhere on the muck, Vikki_Fox has connected.
FoxLord barks, "what happened to marg?"
Singe growls, "car crash"
FoxLord barks, "No."
Pyat thinks Margaras' family would be glad to know people are coming together to remember him in odd places
"Physics," Floid summarizes.
FoxLord snorts
Pyat has left.
Polo arrives from the foyer.
Singe growls, "jackal"
JanusFox yips, "I wonder if they'll ever figure out what happened."
Miko watches yesterday's QI on Margy's behalf.
Singe likes QI.
Floid says, "So, uh, did anyone tell Paf?"
Srass dunno Paf.
KurtMRufa arrives from the foyer.
Singe hasn't talked to Esel in ages.
Srass hugs Kurt.
KurtMRufa nosenoses on Srass.
Somewhere on the muck, Herefox has connected.
White_Fox has disconnected.
Rommel arrives from the foyer.
Rommel yips, "Good Morning."
Srass says, "Morning."
Duelist arrives from the foyer.
Dachande. arrives from the foyer.
Duelist chrp.
Dachande. enters! for a chane.
Dachande. g
Srass earscritches Duelist.
Duelist licks Srass!
TealFox mrf
MegaWolf noses D&D
Polo yaaaawns and picks up Rommel to flop on Dachande.
Rommel yips? "Oh! Good morning Polo."
Dachande. wheeze squeaks from all the weight on him.
Polo is very light, though the fennec's a bit tubby ;)
MegaWolf fluffs Rommel
Polo says, "Wrecked today, had a bilobial migraine. x.x"
Rommel Sticks an ice pick into Polos ear to make it feel better?
Rommel has been fortunate. I once had an "Ocular Migraine". the Funny lights without the pain.
Polo says, "Oh, it's gone, but left me exhausted."
Rommel Ahs and removes the Ice pick then. :)
TealFox has disconnected.
Cain is gonna run
Cain hugs around
Cain teleports away.
Cain has left.
Polo says, "Oh, I get those fairly often, or other single-focus ones.  This, alas, was my entire brain spazzing out.  Like an electric storm...  random memories, talking nonsense to myself, sounds, lights and much much much pain."
Polo says, "I get them very rarely."
TealFox has connected.
TealFox winks out of sight in the sparkling glow of a space/time rift.
TealFox has left.
Puc arrives from the foyer.
Puc mewfs.  Morning
Srass says, "Morning."
Makyo swish.
Duelist licks you!
Miko picks Puc up and applies pettings.
You lick Duelist!
Himmel arrives from the foyer.
Himmel flops.
You yerf, "Cats."
Puc mrarfs, droops, soaks up squirrel lovins.  "Hey :)"
Miko pets Himmel with Puc.
Rommel yips, "I am sorry to hear that. I have known several people RL that get shut down by them completely."
Himmel curls up to Miko.
Miko puts an arm around Himmel and sits Puc on his other shoulder.
Puc chuckles and leans against whosever neck is closest.
Somewhere on the muck, Tigerwolf has connected.
MegaWolf has disconnected.
Polo snuggles up with Rommel the eardog, and gently noms his ears, "How are you keeping, trouble? :)"
Rommel is doing well. Has been slow week. Which is good I suppose.
Polo says, "Opposite of me then."
Polo says, "I would like a slow week soon :)"
Srass has disconnected.
Makyo wrf, disc golf time.
Puc wanna go disc golfing!
Duelist growls quietly, "Fox on a golf course!"
Duelist has seen that somewhere before....
KurtMRufa has disconnected.
KurtMRufa has connected.
KurtMRufa makyonose.
Kia arrives from the foyer.
Himmel says, "Morning, Kia."
JanusFox has had foxes following him during golf, but that's a different matter.
Himmel says, "Or, well."
Himmel says, "Afternoon, for you."
Duelist whips out his hockey stick. He 'skates' up to a sleeper, winds up and lets a slapshot go!
MegaWolf is sent home.
MegaWolf has left.
Srass is sent home.
Srass has left.
White_Fox is sent home.
White_Fox has left.
Kia says, "..."
Himmel says, "Oh, don't start this."
Floid makes IT housecall now.  Whee.
Floid has disconnected.
Mundy arrives from the foyer.
Malkoten arrives from the foyer.
Malkoten yawns
FoxLord mmms Disc Golf
Mundy gooses Duelist!
Duelist O.O
Mundy :O
Puc headbutts FoxLord!
JanusFox yips, "Sounds like something I'd play on a C64."
Somewhere on the muck, TealFox has connected.
Rei_Ayanami arrives from the foyer.
Mundy pets TIGRSKNK belly.
Rommel nods hello to Rei
Mundy says, "What. http://imgur.com/gallery/fPjAx "
KurtMRufa metalyawns.
Rei_Ayanami waves in greetings.
Himmel has such a headache.
KurtMRufa puts on some Hearts of Space.
Wildcard arrives from the foyer.
Wildcard waves.
Duelist stretches!
Miko chatters, "Well, that didn't take long. Obsidian Entertainment put up a Kickstarter for a new RPG in the style of Baldur's Gate, Planescape: Torment, Icewind Dale, et al, asking for a whopping $1.1M, less than 24 hours ago, and looks like they'll hit the target within the hour."
Miko chatters, "Two people (including Notch) have gone for the $10,000 pledge."
KurtMRufa remarks, "So how does this thing work?  Do you get your money back at some point?"
Miko chatters, "You get backer rewards depending on how much you kicked in. The typical one being "you get a copy of whatever we're making" for $10-20."
Miko chatters, "In that instance it basically works as a preorder.. except with no actual guarantee that the project's going to be finished and the thing is going to exist. So sort of halfway between a charity and and a preorder."
KurtMRufa remarks, "Oh, okay.  And if they don't make it, well, it's what it is."
Miko chatters, "A lot of people do seem to be very keen to pitch in to try and get that thing they want that nobody makes any more made. There's usually lower options as well, throw in a couple of bucks and get the mp3 soundtrack and an exclusive 1920x1080 wallpaper image, buy the thing when it comes out."
Miko chatters, "I wish there was a "shut up and take my money now" option, though, the "we'll pull the money from your account when the pledge target is hit" system has caused a big wodge to come out of my daily-use account two months later when I've just gotten bills in the mail a few times so far."
Somewhere on the muck, Azure has connected.
Azure arrives from the foyer.
Azure prowls in.
Azure picks each sleeper up-- it must be some trick of perspective-- to slip into his pocket.  That can't be right, can it?
Floid is sent home.
Floid has left.
Rommel winks out of sight in the sparkling glow of a space/time rift.
Rommel has left.
Duelist pets a tinytinyfox!
Azure noses up against Duelists's hand.
Azure yips, "Good morning."
Duelist growls quietly, "Hello foxy!"
Samanthia arrives from the foyer.
Samanthia slinks in.  Rar.
Samanthia pets Azure and SKNK.
Azure yips, "Hello, Black 'n WHite."
Mundy gets a present from digikey in the mail.
Azure hugs Samanthia, "Hello, Kirin."
Malkoten winks out of sight in the sparkling glow of a space/time rift.
Malkoten has left.
Somewhere on the muck, MegaWolf has connected.
Ryan arrives from the foyer.
Samanthia says, "How is small blue fox?"
Azure yips, "I'm doing fairly well, thank you."
Azure yips, "I think I'm going to go to Meijer's."
MegaWolf arrives from the foyer.
MegaWolf strokes Azure's ears
Samanthia okays.
KurtMRufa mmfs.  Interesting stuff.
Azure slinkso ver and noses MegaWolf, "Guten Tag."
Duelist growls quietly, "So how is folks doing today? Coping?"
Samanthia yawns and is engaged in server migration.
Puc has disconnected.
Mundy rubs TIGRSKNK.
MegaWolf growls softly, "Still kind of numb"
Kia has disconnected.
Malken arrives from the foyer.
Malken lies down on a couch
Azure yips, "KI'm alright."
Duelist kinda numb too. Unsure of how to deal....
Duelist growls quietly, "Plus didn't sleep good last night."
JanusFox hears that.
JanusFox yips, "It has pretty good closure though I wish it had more, somehow."
Mundy licks Duelist!
Mundy ponders ordering a switch machine..
Malken waves to Mundy
Mundy licks Malken!
MegaWolf always has nightmares so he can't really judge his mental state by his dreams.
Duelist growls quietly, "I was pondering if we shouldn't schedule smething, ya know, in here, just a sort of....I dunno, chance to say something and listen and all that."
Wildcard winks out of sight in the sparkling glow of a space/time rift.
Wildcard has left.
Darkness suddenly appears by Rei.
Rei_Ayanami meeps a little, then touches shoulders with the Darkness.
Darkness smiles.
Samanthia watches progress bars.  Grump.
Milehighyena arrives from the foyer.
Milehighyena seeks the techies.
Somewhere on the muck, TealFox has disconnected.
Darkness says, "What kind of tech.."
Milehighyena cackles, "I need a new MP3 player. my RCA has been great, but it has taken some bad abuse in my pocket at work. the case is cracked and held together with tape. "
Darkness says, "Allright."
Darkness says, "Price Range?"
Duelist growls quietly, "Duh, an iPod, of course"
Milehighyena cackles, "I need a new one with a decent color screen so I can look at my pr0n. for under fity dollars."
Duelist growls quietly, "Might as well buy from the company that invented the mp3 and music."
Mundy starts prototyping MSMVs
Azure yips, "Franhaufer?"
Milehighyena cackles, "looking around at places, i see a lot of cheap by some brand named Coby. Anyone ever heard of them? Sandisk?"
Milehighyena cackles, "i'd love to replace this little RCA, but thety discontinued this model. maybe because it was too thin and flimsy."
Miko listenin' to The Eels - "Last Stop: This Town." o/~ You're dead, but the world keeps spinning.. o/~ Take a spin through the world you left o/~ It's getting dark a little too early o/~ Are you missing the dearly bereft? o/~
MegaWolf yawns softly, and curls up in his beanbag.
Darkness says, "Id say Sony, but they are a little more expensive. "
Reveille arrives from the foyer.
Samanthia pets Reveille.
Reveille noses Samanthia.
Malken waves to the long lung dragon
Reveille nods at Malken.
Malken hasn't seen that dragon in a while
Samanthia says, "How is noodle dragon?"
Darkness rummages through her bag and grabs a bag of o-, stabs a straw into it and drains it.
Reveille is doing well.
Scruff arrives from the foyer.
Scruff sneaks in, an up into Duelist's lap
Malken waves to little Scruff!
Milehighyena summons a recognizer, who pickes up the sleepers. "It's the Games for you, Programs!"
Kia is sent home.
Kia has left.
Puc heads to the sweeper's home to bang their mother.
Puc has left.
Scruff miaows hi to the sofalion
Azure bows, "Mr. Scruff.
Duelist pets CHTA
Malken hasn't seen Scruff for a while, either.
Scruff nosetouches the littlebluefoxy, lightly
Samanthia pets Reveille more.
Scruff curls around bigstrongskunkpaw
Reveille rrrhs and arches under Samanthia's petting.  She blinks at Duelist.  Skunk? O_o
Duelist is!
MegaWolf kisses Scruffnose
Malken thinks skunk Duelist is handsome
Duelist grins! Well skunks do, ya know, have that whole black/white formal thing goin' on
MegaWolf growls softly, "Studmephit."
Malken nods "indeed.  and such a muscular one"
Duelist grins.
Duelist growls quietly, "Genetics! >;)"
MegaWolf nips Duelist just a lil'
Scruff chirps, "And luxuriously fluffy tail!"
Duelist growls quietly, "Well that's genetics too"
Darkness looks over her shouler. Absent tail.. Hmm.
Miko listens to Grandaddy and has a bit of a cry.
Milehighyena has disconnected.
Azure has been mildly in love with The Fiery Furnaces for the last few days.
Rei_Ayanami has left.
Scruff wriggles a bit, settling
Duelist stretches out!
Scruff snuffles into skunkbellyfur
Mundy chews on wires.
Samanthia oops.
Azure goes off to Meijer's.
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Somewhere on the muck, Azure has disconnected.
Polo wakes up from passing out again. x.x
Samanthia has disconnected.
Samanthia has connected.
Samanthia beats on networking stuffs.  OKay.  Time to scoot.  Shouldn't be connected while re-arrangign the tuuuuubes.
Samanthia pets a noodle dragon and absconds.
Samanthia teleports away.
Samanthia has left.
Reveille leans against where Samanthia was, and falls over.
Dachande. Woo house clean at 11am.
Polo sniffs Reveille.
Scruff sits in the middle of D&D's livingroom, looks untidy ^-^
Reveille smells dragonny.
Kia arrives from the foyer.
Dachande. Rarrrrg, damn cats!
Polo earperks and looks around.
Scruff chirps, "A bit like this - http://farm8.staticflickr.com/7238/7344470384_47570f82cb_z.jpg"
Reveille growls, "Fluffy!"
Mundy licks Dachande.!
Dachande. licks Mundy!
Himmel | http://www.afterelton.com/poll/2012/09/ultimate-slash-madness-tourney-round-four
Himmel says, "Vote Destiel, guys. C'mon. You know you want to."
MegaWolf omgchta
Mundy studies his prototype vs. schematic.. Grrr..
Somewhere on the muck, Vikki_Fox has disconnected.
Dachande. thinking time for shower.
Mundy rebuilds.. >.<
Scruff shower later! New Doctor Who in 18min!
Dachande. says, "For you. I haven't even seen the ones prior to it, need to get on the torrents."
Danish arrives from the foyer.
Scruff miaows hi to the pastry-in-disguise
Danish tousles Scrufff and fluff and squirrel and cats.
Dachande. says, "Don't have HD BBC not going to watch a LD 9x6 on 4x3 with boarders."
Scruff nodnods, internets be useful there
Dachande. nodnods.
Dachande. Sweaty n stink of house dirt, shower now. :)
Makyo mrrrp.
Scruff awwfox. Hugsfox.
Duelist licks you!
Makyo snoooof at Danish and Scruff and Duelist.
Duelist growls quietly, "Makyo, that was a beautiful write-up on the board."
You yerf, "Mrrf.  Thanks."
Makyo likes so many of you so much :|
Kia has disconnected.
Danish winces.
Danish lows, "Fuck."
Danish teleports away.
Danish has left.
You page-pose, "Makyo nuzz.  Alright?" to Danish
Duelist pets upon foxish.
(p) In a page-pose to you, Danish hugs.
Makyo nuzz upon skunk.
MegaWolf kisses Makyo's nose 'gain.
Makyo snf, smooch at woof.
Somewhere on the muck, Danish has disconnected.
Scruff clambers up, stretches out on the bar
Danish arrives from the foyer.
Polo didn't know the person, but bereavement sucks, so condolences to the bereaved that are present.
Miko hugs Danish!   Whitcomb jumps into Miko's arms and murrs loudly.
You hug Danish!   He jumps into your arms and murrs loudly.
Scruff nuzzles Danish!
Danish snugs back.
FoxLord barks, "that...just fucking sucks/"
Danish whispers, "I don't wanna be all dramatic and shit but I am crying my goddamned eyes out.  >.< *hugs*" to you.
Scruff nods. It does indeed, a great deal.
You whisper, "Makyo squeezes around, "S'okay.  That was me last night and this morning."" to Danish.
Scruff chirps!
Kia is sent home.
Kia has left.
Milehighyena mutters as he is forced to leave. "...time is up, the song  is over. Thought I'd something more to say."
Milehighyena has left.
Miko murmurs, "So it goes."
MegaWolf gruffs. Reality calls.
MegaWolf has disconnected.
Miko snuggles up with Makyo and Danish and all. -.-
Makyo nestles all in, snooof.
Danish cuddles on squirrel and fox and cheetah and all present.
Danish never thought it would happen, but you never do.
Kia arrives from the foyer.
Danish waves.
Scruff hugskiatail
Danish whispers, "How'd you find out?  Mutual friend?" to you.
Kia nods and pats Scruff.
You whisper, "Someone came in last night and told us all, a friend of Pyat.  I kinda lost it for a while c.c  All cried out now, feeling sort of...lost in memory, I guess." to Danish.
Danish whispers, "Danish headshakes.  Buries nose in your fur and still can't stop crying.  I dunno." to you.
You whisper, "Makyo hugs around and holds close, meanwhile.  Rrwf." to Danish.
Danish gets fox fluff and squirrelpoof all damp and idles for a little while.
Somewhere on the muck, Tony_Cheval has connected.
Kia has disconnected.
KurtMRufa resprawl.
Scruff trots over, noses at robodog. Hello!
ZeitOtter arrives from the foyer.
Kuttas arrives from the foyer.
Makyo nose Kuttas.
Danish hugs on Kuttas.
Kuttas hugs Danish.
Mundy gets a working prototype of a MSMV.
Kuttas sadhyenas.
Mundy nibbles Duelist!
Miko chatters, "We all has a sad."
Danish nods and draws Kuttas into the hugpile.
Scruff sneaks out for a little while
Scruff teleports away.
Scruff has left.
KurtMRufa beeps and noses on Kuttas and arfs too.
Somewhere on the muck, Scruff has disconnected.
Mundy eyeballs http://www.amazon.com/Amico-Position-Toggle-Switch-Terminals/dp/B005GI851C/
Djirin arrives from the foyer.
Djirin headperches on Rev.
Reveille oofs, sat on.
Djirin is light as a bodi!
Djirin boid
Reveille is just a tiny thing!
Djirin gets out a magnifying glass? "Hmmm.  Somebody shrink you?"
Reveille has been shrunken for a while.  It lets her actually fit in the door.
Ryan winks out of sight in the sparkling glow of a space/time rift.
Ryan has left.
Mundy hmms..
Djirin headglomfs Rev
Reveille flails!
Djirin mmfs.  wiggly
Zeph arrives from the foyer.
Zeph rowr.
Reveille paws at Djirin and huffs.
Djirin drools helpfully on Rev. c.c
Reveille gahs, covered in cat spit!
Djirin bahs. "Cleanspit"
Reveille growls, "Still cat spit!"
Djirin hmms?
Djirin changes form.
Djirin drools dragonishly then
Reveille eeps and squirms all the more, scruffed by the now-dragon.
Zhorah arrives from the foyer.
Zhorah waves.
KurtMRufa arfatta Rev.
Djirin sheds helpfully on on Rev. furry dwagin
Makyo nuzzat Zhorah, Zeph.  Zs.
Zeph snugga on Makyo.
Zeph whispers, "Zeph full of sad re: Margs. :<" to you.
Zhorah lean on Makyo
Draconis arrives from the foyer.
Draconis rr!
Reveille growlfs atta Kurt!  And then gets covered in Djirin's fluff.
Makyo purrprr, swish on Zeph and Zhorah.
Draconis nuzzles Zhorah!
Draconis nuzzles Zeph!
Zhorah nuzz at Draco
Reveille yays, more dragons.
Draconis licks Danish!  Whitcomb wonders exactly why they did that.
Draconis cuddles Reveille!
You whisper, "Makyo nod, noses.  Very sad fox. Grew up around him." to Zeph.
Reveille purrs and snugs Draconis. ^_^
Draconis hrrrr. "Revsmevs."
Zeph whispers, "Zeph cuddles much. "Did not know him for as long myself, but even so. Want to do something but have no idea what."" to you.
Reveille growls, "Dat's me."
Draconis growfs, "How be's?"
Djirin grumps as Rev gets stolen away. c.c
Draconis cuddle Djiin too!
Djirin hurrahs
Djirin !
Draconis adds more r's. Rrrrrr.
Djirin headglomfs Draconis
Zeph whispers, "Zeph sorry to go on about." to you.
Draconis snrtl.
Draconis growfs, "Teehee, Undine is engrossed in Bastion."
You whisper, "Makyo leans in against and nods, "Not sure what, either.  Could maybe set up something to make one donation for everyone to that thing mentioned in the obit."" to Zeph.
Djirin hms? "Whats that?"
You whisper, "S'okie.  Been torn up since last night, feels good to talk about." to Zeph.
Draconis growfs, "http://supergiantgames.com/?page_id=242"
Polo says, "I found it a bit...  well, reliant on a narrator.  And for something using a beautiful narrator, the Stanley Parable was better done (and being turned into a game!)."
Reveille growls, "It's a really well done, if somewhat short, run around and hit things fantasy game."
Polo says, "I bought it and found it rather dull and Diablo-esque."
Zeph whispers, "Yarr, had thought about donationy thing myself. Am rubbish at organising things though. At first part of me wanted to think it was an elaborate stunt, that he'd turn up laughing to have tricked us." to you.
Duelist licks Draconis!
Danish nuzzles Draconis!
Draconis enjoyed it.
You whisper, "Makyo nodnods, "The thought occured to me, too, but I think only because I didn't really want to believe it.  Setting up a fake obituary and news stories doesn't seem like Margs.  Anyhow, I dunno.  Do you think people would want to do that?  Or would there be something better suited?"" to Zeph.
Draconis growfs, "Diablo-esque is a compliment :)"
Polo says, "Trailer for the new Stanley Parable: http://www.youtube.com/watch?v=bB4AR5Crb54"
Polo says, "That narrator is _amazing_."
Zeph whispers, "It does sound like a good enough idea, to me. Some kind of charitable donation I think would be good regardless, even if not that specific place. Personally, I was thinking of maybe making some kind of music tribute or something." to you.
Miko chatters, "It's quite wonderful."
You whisper, "Yeah.  I can't even figure out what these guys are, other than a motorcycle funeral guard, much less how to donate.  And yeah, was trying to think of any sort of tribute I could make, beyond financial :/" to Zeph.
Miko chatters, "And a million miles away from clicketyclickety grindgrindgrind."
Zeph whispers, "Yeah, I dropped an email their way to see what was going on but haven't heard back yet. Maybe could get interested folks to work together on something, I dunno." to you.
Miko chatters, "Also not fantasy in the "elves and orcs" way but in the "weird ghost things that live on crumbling platforms in the sky" way."
Polo says, "Alas, at the time Bastion was released for Mac the Trine games were on sale and gave me waaay much more fun :)"
Polo says, "Another trailer for Stanley Parable HD remix: http://www.youtube.com/watch?v=AZ-IcS7mRSk :)"
Draconis elects to investigate the Stanley Parable, for he has not before.
Zeph yarr, downloaded that himself but has been distracted by Black Mesa Source.
Polo says, "It's...  like Dear Esther.  Very short and quirky, but exceptionally poignant :)"
ZeitOtter has disconnected.
Somewhere on the muck, Sarusa has connected.
Draconis rararar.
Djirin zipbz2targz
Somewhere on the muck, TealFox has connected.
Draconis smrk.
Djirin nibbles on Draconis while looking innocent.
Polo lost 80 hours to Civ V. x.x
You whisper, "Typed and retyped something to ask people, but just can't quite bring myself to do it right now.  Still kinda raw, I guess :S" to Zeph.
You whisper, "Makyo can ask later, if things go alright at work next week." to Zeph.
Draconis whoah. 30k seeds for black mesa o.o
Djirin purrs quietly, "hurrah thievery! c.c"
Malken liked Bastion
Draconis growfs, "thievery?"
Zeph whispers, "Zeph noddles, makes sense. :3" to you.
Djirin shrugs. "Is this Black Mesa a free game?"
Draconis growfs, "Yes."
Zeph mews, "Free mod, yeah."
Djirin purrs quietly, "Hurrah free then! c.c   Whenever I hear someone talk of bit torrent and the like I only think of one thing"
Draconis growfs, "I only tend to thieve TV programs, and then only for time-convinience rather than having not paid for them ('cause I have.)"
Somewhere on the muck, TealFox has disconnected.
JanusFox le pant.
Zeph mews, "Foxpants."
Djirin depants Janus
JanusFox yips, "Pantaloons you."
You yerf, "Fox++"
JanusFox increments non-atomically.
Djirin noses at the nonatomic fox
JanusFox rubs those noses.
Djirin glomfs foxhand
JanusFox eeps and pulls away, "I guess that makes me steam powered.
JanusFox is steampunkfox?
Zeph < fox.steampowered.com >
Zeph mews, "Note: not actual address."
JanusFox yips, "D'aww."
Polo is at 'We've Got Hostiles'.  It's an exceptional mod.  Pretty much an AAA game except for animation quality.
Djirin has left.
Dachande. says, "So AAB then?"
Dachande. bark.
ZeitOtter is sent home.
ZeitOtter has left.
Kia is sent home.
Kia has left.
MegaWolf is sent home.
MegaWolf has left.
Makyo cuuuurrrl forever.  So out of it this afternoon.
JanusFox perk, "Black mesa source is out?!
Dachande. says, "Yup"
Dachande. says, "I downloaded it, and installed it, but i can't seem to find the program launcher."
JanusFox dances about!
JanusFox yips, "Finally aome bloody good news."
Makyo :o)
Makyo packs for Canada.  So nerrrrvous.
Polo says, "It's in the Steam menu, Dachande."
JanusFox yips, "Don't be.  Canadians are far from the dangerous monsters they're made out to be on the Red Green show."
Zeph mews, "You've gotta stick it in the /steamapps/sourcemods folder, then quit and restart steam and it should show up."
You yerf, "I automatically assume Canadians are awesome.  It's the travel that has me nervous :S"
Danish lows, "What's in Canada, Feral?"
Mundy says, "Feral's done. :x"
Polo is Canadian.
You yerf, "Work.  Week-long sprint."
Polo says, "I just ran the installer that came with it and it showed up in Steam."
Danish lows, "Oh, neat."
You yerf, "Should be awkward meeting all these people in person for the first time, despite having worked with them for a few weeks now."
JanusFox yips, "Did you let them know about your affliction"
Danish lows, "I'm sure they'll just try to glomp you or w/e.  Goes with the territory."
JanusFox pokes that torrent with a stick, "Goooo faster!
Zeph mews, "Being an adorable fox is a blessing, not an affliction."
You yerf, "We have daily video conferences.  They've seen :o)"
JanusFox may beg to differ on that.
Mav arrives from the foyer.
Polo torrented it on his root server in the netherlands, downloaded it from there.
Somewhere on the muck, Tony_Cheval has disconnected.
Polo says, "Well, it's a blessing in looks, but the smell requires getting used to. :)"
Dachande. says, "yeah not in my steam only b game i have is bastion, which i need to tyr one of these days."
Danish lows, "It's good."
Zeph mews, "Might not have the Source SDK, you need to click the dropdown in 'Library' (should say All Games) and select Tools, then grab Source SDK."
Zeph mews, "Right click and pick Install and you should be good."
Dachande. says, "Yeah steam opened and said i needed that, so did that."
Zeph hmm
Dachande. says, "Then i had the source thing, but that went away."
Zeph dunno then!
Dachande. says, "Ehh not a big deal, shouldn't try it on the laptop anyay."
Dachande. says, "not sure what i was thinking getting it on here. :)"
JanusFox yips, "That it's essentially a game from 1998 :D"
JanusFox yips, "It should run on an iphone at this point ;)"
Zeph mews, "True, it's the same base game, but Black Mesa has given it a level of advanced shininess and awesomeitude."
Polo says, "The installer downloaded the Source SDK for me..."
JanusFox yips, "On the other hand, Morrowind cripples me now so."
Zeph mews, "So it ain't gonna run on a Pentium II."
KurtMRufa unidles.
KurtMRufa beep beep then.
Zeph pet on Kurtbot some!
Polo says, "It is not in any way the same base game.  Everything has been re-done using Source 2007."
KurtMRufa houndleans on Zeph.
Polo says, "The plot and set-pieces have been used, but it's all original content (or content from Half Life 2)."
Himmel climbs onto Danish.
Himmel curls up.
Danish scriffles Himmel and hugs on him.
Mundy flumps.
KurtMRufa wants the compute for the damn games to be in the cloud.
Himmel is gonna go eat dinner then come back and be distressed s'more.
Kuttas, too, he thinks.
Zeph mews, "OnLive did that, and they nearly went bust."
KurtMRufa will use this kind of thing as a snappy answer to people who ask about doing supercomputing in the cloud.
Draconis has disconnected.
Zeph mews, "Admittedly, it might be for reasons other than nobody subscribing. Didn't look into it too much."
Zeph mews, "On the basis of having a) a pretty decent computer, b) a mediocre internet connection."
Makyo nuzz at Himmel, Kuttas.
Kuttas pets Makyo.
Polo says, "Supercomputing is already done in the cloud.  I worked on the CERN Grid back in 2005 (I was doing security research) and that was used to find the Higgs very successfully.  I believe that the incoming beam data was 10TiB/sec."
Himmel petpets Makyo. Dashes, a bit.
Polo says, "I would imagine it's more to do with commodity graphic processing hardware being unvirtualisable."
Dachande. go to try and buy some jeans.
Kuttas sneakyhyenas into the shadows. c.c
KurtMRufa metalyawns.
Himmel returns.
Zeph sneaks to bed, full of tired and bleh.
Zeph goes home.
Zeph has left.
Somewhere on the muck, Zeph has disconnected.
Singe has disconnected.
JanusFox rubs that...aww.
MegaWolf arrives from the foyer.
Danish hugs MegaWolf!
TealFox arrives from the foyer.
[public] Sarusa says, "Chinese pet jerky kills at least 360 dogs, one cat in the US. Surprise."
Miko titters a little. Sewageburst in downtown Helsinki. Cars sliding around, people falling over, a stench for blocks and blocks and blocks.
Danish lows, "Like a summer block party where they open the hydrants."
Scruff arrives from the foyer.
Scruff sneaksbackin
Scruff perches somewhere up in Danish's antlers
Zhorah returns
Scruff chirps!
Draconis is sent home.
Draconis has left.
Singe eeks!
Singe has left.
Fiend Plushie bounds after Singe.
Danish pets Scruffy protectively.
KurtMRufa beeps.
Danish scoots closer to Kurt to buff him a little, as well.
KurtMRufa wag wags and does some gleaming too.
Danish smiles.
Scruff takes the opportunity to nose down between perky metallic ears
Himmel is only slightly disappointed that the girl who plays Mary-Kate in Very Mary-Kate isn't actually Mary-Kate.
Miko almost listens to Do You Realize?, but stops himself.
Miko is reminded of Footpad by a loose mental association. :/
Danish urk.
Scruff chirps, "Why is Footpad a :/ ?""
Miko chatters, "Footpad and Margs."
Danish lows, "Still can't believe he got me onto all that music."
Himmel says, "What about Footpad?"
Miko chatters, "With the delighted piling onto and face-washing and all that."
Himmel says, "Oh."
Himmel says, "Right."
Danish :(
Miko chatters, "Does he know?"
Himmel says, "Oh, god."
Scruff mrf. "He's going to be crushed."
Miko has a bit of a cry again.
Himmel says, "Does anyone here have his contact info?"
Miko puts the Field Mice on, like a fluffy blanket.
Himmel says, "Draco might, but he's not on, at the moment."
Danish hugs Miko!
Miko nuzzles Danish!
Miko sees an update from Orin on his Facebook timeline, innocently bollocking on about something or other. Argh.
Scruff chirps, "I see Draco was here, which means Unds'll know now. He'll be very, very upset."
Miko didn't have the gumption to mention but presumably someone did.
Danish puts on "Straight to Hell", the song he got me into the Clash with.
Reveille'splodes.  *poof*
Scruff still trying to work out if he'll be able to make it to Pebble's funeral on Friday. Awesome people should stop dying.
Miko chatters, "I-"
Miko chatters, "Pebble's dead?"
Himmel gives Miko a squeeze.
Scruff nods, "Last Friday."
Miko :(
Harth arrives from the foyer.
Harth says, "Hello."
Miko chatters, "A day later."
Miko chatters, "I only met him once or twice and didn't know him very well, but I loved reading his LJ. I hadn't thought about him for a long time."
Scruff chirps, "Absolutely beautiful person. He'd known it was coming, and had time to prepare, say his goodbyes, which is something, I guess."
Zhorah rumbles, "I dunno pebble"
Miko chatters, "There's not a lot more you could ask, really."
Somewhere on the muck, Azure has connected.
MegaWolf growls softly, "The lion?"
Himmel doesn't know why he knows the name Pebble.
Himmel doesn't know why he knew he was a Lion.
MegaWolf growls softly, "Himmel: Taps"
Himmel says, "... That Pebble is online currently. Which is rather morbid."
Miko chatters, "Pebblepup."
MegaWolf growls softly, "I don't know either of them"
Miko tries to find an LJ dumper.
Scruff chirps, "No, he hadn't been on FM for years, and wasn't ever on Taps"
Danish lows, "Fuck, his one interest on LJ..."
Scruff chirps, "He'd had the name Pebble here when he was"
MegaWolf curls.
Azure arrives from the foyer.
Danish snouts into Megapup.
MegaWolf snugs Danish
Scruff chirps, "He actually had that about eight years ago, Danish"
Acy arrives from the foyer.
Danish ahh.
Acy woof.
Polo noses Azure.
Mav climbs up and perches on Acy.
Danish continues nosing Mega and waves to Acy.
Polo scritches Mav.
Acy topples.
Makyo noses at folks.
Polo goes home.
Polo has left.
Danish lows, "All packed?"
Mav falls over, paws in the air.
Acy puppy says, 'whine whine whine.'
You yerf, "Kind of half-heartedly packing.  Mostly watching here."
Mav wruffs gruffly, "My dog is mute."
Himmel's dog was mute unless she saw another dog or he was teasing her.
MegaWolf's dog only barks if people or dogs approach the house. Of course "approach" can mean 3 houses away or more.
Himmel says, "I think it's horrible that people will surgically disable dogs' vocal chords."
Himmel says, "... Cords."
MegaWolf growls softly, "She "talks" a lot though, not a whine or a bark, more like little squeaks and other odd noises."
MegaWolf growls softly, "Tryin' to talk!"
You yerf, "Dogs <3"
Scruff blinks. People do that? o.O
MegaWolf better run some errands before it gets too late.
TealFox curls
Himmel says, "Devocalization, yes."
MegaWolf growls softly, "Debarking"
Scruff hugs MegaWolf!
Himmel pets Megs.
Scruff chirps, "That's hideous! Like declawing a cat."
Zhorah:<
TealFox has disconnected.
Miko chatters, "Emergency Back-up Greek Alphabet: adolf, beta, gamma, leia, delta, echo, foxtrot, theta, peter, smegma, mocca, corbett, khaki, kyber, mira, hindley, phooey, abercrombie, abba, pasta, hasta, lavista, zeta, jones."
Zhorah blinks
Makyo gonna go get comfortfood sushi.  Back in a bit.
Danish waves.
Scruff hugfox. Fooox. <3
Makyo smoochat folks :3  Be excellent!
Makyo idlehere.
Danish lows, "Fox cuddling services available all day.  Revolutionary."
TealFox has connected.
TealFox sighs at his connection today
Danish pets Teal and his connection both.
TealFox mmm. Pets
Acy says, "Makyerf is going away?"
Acy says, "My puppy bark sounds like the alarm bark of a squirrel."
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Danish lows, "He's going to Canada to catch fish with his paws, I think he said."
MegaWolf has disconnected.
Acy says, "Weird."
Danish shrugs, fopses.
Scruff noses around, sneaks off to bed. Nini!
Scruff teleports away.
Scruff has left.
Acy says, "Darnit puppy quit eating everything that is not nailed down. "
Miko chatters, "It's a PUPPY."
Miko chatters, "What were you expecting?"
Mav chews on Acy.
Acy says, "Ow ow my feet."
Acy says, "I have started calling her piglet."
Duelist stretch out!
Danish lows, "What breed is she?"
Mav wruffs gruffly, "Stink shep."
Acy says, "She is a german shepherd dog."
Acy http://acy.livejournal.com/360495.html
Duelist growls quietly, "Oh my god, look at her."
Duelist - http://i10.photobucket.com/albums/a115/AcyKat2069/Dogs/IMAG0441.jpg
Acy says, "Hahah."
Duelist growls quietly, "Pure awesome."
Acy says, "I gave her a bath and she was soft and fluffy for exactly one day."
Miko looks at the puppy and cries a bit. :4)
JanusFox rolls acy's puppy in things that smell... wonderful.
Acy says, "She does not need help with that."
Duelist growls quietly, "She will be giant dog soon!"
Acy nodnods.
Danish :3
Acy says, "I do not like the food the breeder had her on.  Trying to figure out what to put her on now."
Duelist growls quietly, "I uhh, well food is a weird subject"
Acy says, "She started eating her poop yesterday and i was all D:"
Duelist growls quietly, "Everyone swears by theirs."
Mav wruffs gruffly, "Sheppies are just gross."
TealFox has disconnected.
Acy says, "I read that they do that because of undigested protein leftover in the poo."
Danish punches Mav in the nipples.
KurtMRufa hrfm
Mav nipple squirts.
Danish mm.
Duelist - http://d4fxuz90idxmu.cloudfront.net/images/default/products/large/12069-1.jpg
Duelist growls quietly, "That is what Kostya eats."
TealFox has connected.
Acy says, "The breeder suggested I give her pig ears to chew on but they make her breath smell like feets."
Kia arrives from the foyer.
Mav wruffs gruffly, "Pig ears are yum because they stink."
Kia frinks.
Duelist growls quietly, "Nylabones!"
Duelist growls quietly, "Better than pig ears."
Mav feeds this stuff to his dogs http://www.diamondpet.com/products/diamond_naturals/dogs/
Acy says, "She prefers the ears to nylabones."
Duelist growls quietly, "Wait wait, you're giving your shep a choice?"
Acy says, "Sure, why not?"
Mav wruffs gruffly, "Mine get pig ears and various other animal body parts."
Duelist growls quietly, "Never give a shep a choice"
Acy says, "How else will I know what a high value reward is?"
Himmel says, "Sheps require harsh regimentalization. Strict orders."
Duelist growls quietly, "And make shep work for everything!"
Acy says, "She is only 8 weeks."
Duelist growls quietly, "Hee hee hee. She's gonna own you."
Acy is still teaching her to make eye contact with her name.
Danish lows, "Mrs. Cassidy.  Mrs. Eliza Cassidy.  You stop eating that this *instant*."
Acy says, "I am relatively firm with her.. I guess.  I kennel her and stuff."
Floid arrives from the foyer.
Mav wruffs gruffly, "Remember that dogs don't feel guilt."
Danish waves to Floid.
Floid says, "Arf."
Danish lows, "Dogs only feel it when you tenderly rub their malamute nipples."
Mav squirt.
Danish lows, "It's the only way he'll learn."
Kia says, "All dogs have malamute nipples? "
Duelist recommends the dog beating stick!
Danish lows, "Mav does."
Danish notes that Floid is kind of an anagram of El Fido.
Floid says, "Mav is director general of the USSMNR."
Acy says, "You milk malamute, you have friend for life."
Danish lows, "Whereas chows just want to cuddle afterwards."
Acy cuddles up to Danish.
Acy says, "Going to try walking her for a minute."
Danish shares a glass of milk with Acy before he goes.
Duelist growls quietly, "There is much sitting when first walking a shep."
TealFox winks out of sight in the sparkling glow of a space/time rift.
TealFox has left.
Acy has disconnected.
KurtMRufa arf arf arf.
Somewhere on the muck, TealFox has disconnected.
Acy has connected.
Danish lows, "I told a really good joke while you were gone and everyone laughed and it made me popular."
Acy says, "Yes there was sitting.  We made it halfway down the block then a barking pitbull caused resistance."
Dachande. says, "Tell it again Danish."
Zhorah rumbles, "looked back at this screen and first thing I saw was malamute nipples....]"
Danish isn't in the mood right now.  Gotta pace it.
Himmel rubs Danish. "You -are- Popular."
Danish hugs Himmel!
Zhorah rubs his unpopular on Danish
Danish hugs Zhorah!
Acy says, "Ah, my nipples explode with delight."
Miko loves Danish!  Whitcomb isn't sure he's ready for that level of commitment yet.
Mav gets a towel.
Danish kisses Miko!
Danish goes to smoke.
Floid says, "http://wonkette.com/484178/the-lord-jesus-hates-dr-pepper-and-you-should-too"
Danish has been smoking every time he wanted to cry today, so it's on to pack 2.
Himmel hugs Danish's head.
Miko gets linked to http://creeper.naurunappula.com/org/e9/36/e9362063fc8378ad/0/967709.gif elsewhere. Serendippitydoodah.
Acy o.O
Miko has just been having a cry whenever he feels like it. It's good for you.
Acy says, "Miko did my puppy really make you cry?"
Miko chatters, "I, um. Are you perhaps missing the context?"
Himmel says, "Margs, Ace."
Floid is very taking a nap.
Danish quietly saves that as Danish.gif.
KurtMRufa rrf.
Acy says, "Oh."
Acy says, "Yeah, heh.. when I look at her I think, 'In 8-10 years you'll be gone too.'"
Harth has disconnected.
Mav wruffs gruffly, "Sheppies only live 8 to 10 years?"
Danish stares at fatweaseldog in the hallway, more of a force of nature than an actual thing.
Danish lows, "According to the vet he's 17, but the vet is stupid."
Acy says, "According to wikipedia sheps live 8-10 years."
Mav punishes his sheppie for living too long.
Acy says, "Aww."
Acy says, "She's half husky."
Mav wruffs gruffly, "So she gets to live longer."
Himmel says, "SHepsky?"
Himmel says, "Sheps live longer than 8-10 years, I'm sure of it."
Himmel says, "-Danes- live 8-10 years because of their size problems."
Mav wruffs gruffly, "Generally larger dogs have shorter lives."
Mundy  whistles for a bouncer, and a huge gorilla steps out of nowhere, and hauls out the sleeping furries. "Time ta go, boyz.." he growls..
Harth is sent home.
Harth has left.
MegaWolf is sent home.
MegaWolf has left.
Mundy gooses Dachande.!
Himmel actually thinks Danes are 10-12.
Kia's cat is planning on never dying.
Acy says, "Well hopefully my shep will live longer.  She is supposed to have good genes and stuff."
Somewhere on the muck, Scruff has disconnected.
Miko used to know a cat that was eighteen years old.
JanusFox yips, "And she's black!"
Mav wruffs gruffly, "I had two cats, lived 19 and 21 years."
Acy has an 18 year old cat.  She is gray and has a scratchy meow that sounds like Macy Gray.
Kia's cat is... lessee. Got her in 1997, fall. So, 15.
Danish lows, "According to Wikipedia you are King of Togo, Acy."
Acy says, "Neat."
Miko chatters, "World record is 38 years and a bit."
Acy was also born on the same day Robespierre got the guillotine.
Danish lows, "http://en.wikipedia.org/wiki/Togo"
Danish lows, "Ah, fuck, fucking robots."
Danish lows, "You were King of Togo for roughly 15ish seconds."
Srass appears in a glowing pentagram, with an ominous rumble. He thunders, "WHO DARES DISTURB--", then looks around.  "Oh, um... hiya."  The pentagram fizzles out, anticlimactically.
Srass has arrived.
Danish hugs Srass!
Srass hugs Danish!   Whitcomb jumps into Srass's arms and murrs loudly.
Srass leans on Kurt.
Danish hands http://imgur.com/FNzKY to HRH.
Srass says, "Lame."
Acy uhr...
Srass says, "That's not a photoshop, that appears to have been an actual edit to the page."
Srass says, "By a comcast customer in south carolina somewhere."
Danish lows, "Knology wanted to drill a bunch of holes."
Kuttas arrives from the foyer.
KurtMRufa beep beeps.
Srass says, "Who?"
Himmel says, "South Carolina?"
Himmel says, "Whoever do I know from there?"
Srass snugs Kurt.
Paladin pads in and barks!
Paladin has arrived.
Srass licks Kuttas' muzzle.
Srass also rubs Paladin's ears.
Kuttas licks Srass' whiskers.
Paladin flicks one ear: ~_^ and then the other: ^_~
Miko chatters, "Those are eyes, dear."
Paladin barks, "I am not some Asian emoticon!"
Paladin has always, always used them as ears.
Mav ^..^
Paladin rubs Mav!
Mav gets fur all over.
Danish &._.&
Paladin gets dingo all over.
Mav gets a napkin.
Kuttas pokes at waffles.
KurtMRufa .
Danish pets Kurt and Kuttas.
FoxLord has disconnected.
Kuttas leans.
Miko chatters, "Danish is a former boxer?"
Paladin barks, "I thought he was more like a labrador."
Himmel boxes Danish.
Himmel ships him to Murray.
[ Kuttas looked at you ]
KurtMRufa taps its fingertips together.
Danish eyes Miko.
Danish also dies, no airholes.
Danish headshakes.
Srass pets Kurt's fingertips.
Mundy licks Paladin!
Miko chatters, "& looks like a boxer's ear."
Paladin licks Mundy!
Danish ahhh.  Hard to render antlers on one line in ASCII.
Himmel lean on Kuttas.
Mundy licks Paladin's dingo tongue
Paladin pants, like a dingo! This makes him twice as cute! Even babies are no longer afraid of him!
Kia hungers a bit.
+++++Leanin' 'yena just smelled you!
Danish ruffles Kuttas between the ears.
Kuttas smells hollow.
Himmel disagrees.
Kuttas oopses. ruffle, not snuffle.
Danish hugs Kuttas!
Paladin barks, "Ruffle snuffle. I think I shall put that in my actions."
Paladin ruffle-snuffles Danish!
Danish licks Paladin!
Miko chatters, "Do the ruffle snuffle!"
Srass, come to think of it, gets rid of all the extra accoutrements, and just goes quadrupedal for a while.
Paladin ruffle-snuffles Miko!
Kuttas curls up against him.
Srass nuzzles Kuttas.
Kuttas squeezes.
KurtMRufa tilts its head to the side.
Mundy grunty.
Zhorah pets Kuttas.
Makyo wakesup.  Nuzz folks.
Kuttas is an anthro spotted hyena.  He's slightly taller than average, despite having the characteristic slight-hunchback typical of hyenas, probably due to the long neck which is also typical of the species.  His torso is slightly long, and his legs are slightly short; he's built stoutly, a remnant of his youth spent on the Serengeti, where life makes you hard or leaves you hungry.  He walks di'grade, but erect; even so, he's quick, nimble, and flexible.  He is easily capable of dropping to all fours when needed. On his right thigh, about two hands-breadth below his hip, is a fine, vertical scar, a straight line about three inches long and visible through his fur, which grows gray alongside it. He is leaning very closely on Srass, and appears to be quite comfortable.
[ Leanin' 'yena noticed you looking at him ]
Carrying:
BUTTON: Arcturus 2012! Cause '[Redacted] Happens.'
BUTTON: Arcturus 2012! 'FRONT TOWARD ENEMY'
tribal lance
An Invitation
Zhorah tug at Makyo
Makyo nosenose at Zhorah.
% Connection to furry closed: recv: Connection reset by peer
\end{verbatim}
