\begin{verbatim}
% Trying to connect to furry: 74.207.243.108 8889.
% Connected to furry.
#$#mcp version: "2.1" to: "2.1"
Welcome to
              _____                 _ _ _   _    _ __   _   ,  SM
               /  '                ' ) ) ) ' )  / /  ) ' ) /
            ,-/-, . . __  __  __  , / / /   /  / /      /-<
           (_/   (_/_/ (_/ (_/ (_/ / ' (_  (__/ (__/   /   )
                                /
                               '
          The first 99 & 44/100% anthropomorphic/Furry TinyMu*

(The SM means that FurryMuck is a Service Mark of the FurryMuck Wizards)
To connect to your existing character, type "connect <name> <password>".
To receive a new character, send mail to join@furrymuck.com
To see the latest news, type "news" after connecting to a character.
To disconnect from a character, type "QUIT".
Use the WHO command to find out who is currently online.
Use the 'whereare' command to find places with active people.
Use the 'wizzes' command to see what Wizards are on line, or the 'helpstaff'
 command to see who of the help staff is on.
Use "connect guest guest" to visit FurryMUCK as a guest.
All users of FurryMuck are bound by our AUP. "NEWS AUP" to read this document.
----

Sadly, FurryMuck has lost one of its own.

S'A'Alis, May 29, 1963 -- September 5, 2012, the Large Furry Marsupial, and a
member of the L'Drey, a space-faring, fox-like species. He was never without his
'Eternally Filled Highly Caffeinated Coffee Mug of Doom'. From 1993 - 1999,
S'A'Alis hosted the servers that FurryMUCK ran on, and was a character creation
wizard 1993-2001. Condolences can be sent to his beloved wife, IceWolf:

M. Vogt, W5910 Genske Road, Black Creek, WI 54106

Life is eternal, and love is immortal,
and death is only a horizon;
and a horizon is nothing save the limit of our sight.
 -Rossiter Worthington Raymond

----
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
Makyo stretches out and yawns toothily, shaking Makyo's fur out.
Players online for whom you are watching:
Acy               Azure             Danish            Floid             
KurtMRufa         Makyo             MegaWolf          Miko              
Sarusa            Tigerwolf         Triggur           
Done.
The next scheduled database save will be in 8 mins, 19 secs.
You place a strategic call to one deity or another.
Makyo disappears in a puff of complacency.
Purple Nurple Foyer(#52464RLJ)
You step in through the door and into a cramped foyer.  Advertising
posters plaster the walls and there's another door right in front
of you (east).  The door is padded purple vinyl, studded in a diamond
pattern.  This is the Purple Nurple, Furrymuck's gay/les/bi nightclub
and meeting place.  Feel free to come on in if you are straight too.. we
don't bite (unless you ask nicely ;)  There is a sign on the wall next to
the door and a notice where the computer used to be, saying that it's now
in the main room.
Players inside the Nurple:
 MegaWolf           Turkzyn            Kia                Kyhwana
 Paladin            Kuttas             Srass              Floid
 Acy                Danish             Malken             Mundy
 Himmel             Dachande.          Duelist            KurtMRufa
 Miko               JanusFox          
[Exits: <IN> to the Purple Nurple   <OUT> to Sable Street]
Contents:
PN RULES : READ THIS TO BE ABLE TO ENTER
You enter the PN
Makyo disappears in a puff of complacency.
The Purple Nurple
You are in the Purple Nurple, furry's premier gay/les/bi spot.  
The room is large, a converted warehouse - the ceiling's
about fifty feet above the crowded floor.  An entire suspended
lighting grid swivels back and forth in the middle of the room,
rigged with a complex array of lights, lasers and mirrors.  
The overall effect is of an alien spacecraft hovering about twenty
feet over the dance floor.  Huge projection wall-screens flicker
images of furries dancing, clips from anime movies, computer
graphics reels and old cartoons.  The music is loud, thumping
techno and house, bass thundering through the gyrating furries
on the dance floor.
To one side is a lounge area, acoustically out of the main thrust
of the speaker stacks allowing normal conversation.  A bar with
every drink known is along the wall of the lounge, and
the floor is scattered with heavy-duty beanbag chairs, funky couches,
and other assorted furnishings, all roomy enough for at least two furs.
A small staircase leads up to the Nurple Apartments.
Contents:
MegaWolf
Turkzyn
Kia
Kyhwana
Paladin
Kuttas
Srass
Floid
Acy
Danish
Malken
Mundy
Himmel
Dachande.
Duelist
KurtMRufa
Miko
JanusFox
All complaints --> Rigel
NURPLE ADULT/PG POLICIES ****** PLEASE READ
Bulletin Board
[foodgeeks] Genn says, "Ah ha, and yes, i see why"
Duelist licks you!
Makyo rrf.
You lick Duelist!
Duelist growls quietly, "Hello foxy"
Name                   Sex        Species     ('whospe #help' for help)
Makyo                  N/A        Anthro Arctic Foxy
MegaWolf               male       White Wolf 'Morph
Turkzyn                Male       Wolf
Kia[idle 5m]           male       ringtailed lemur (lemur catta)
Kyhwana[idle 2m]       male       Young morphic'leopard
Paladin                Male       Big Blond Dingo
Kuttas[idle 21m]       male       spotted hyena
Srass[idle 6m]         male       polymorphic black panther (quadruped)
Floid[idle 1h]         male       Dingo
Acy                    mALE       Chow chow (chow)
Danish[idle 2m]        Manmoose   Manmoose
Malken[idle 1h]        male        bipedal immortal lion
Mundy[idle 29m]        -unknown-  -unknown-
Himmel[idle 12m]       Male       Cat
Dachande.[idle 3m]     Male.      Wolf.
Duelist                Male       Skunk!
KurtMRufa[idle 32m]    robot      greyhound
Miko[idle 3m]          o->        Nut muncher
JanusFox               male       Cross Fox
You yerf, "Hi skunk."
Duelist growls quietly, "How's you doing?"
Srass says, "ttytter sounds like a utility that helps find and download pictures of ttytts."
Kia says, "ttytties"
Srass nods.
You yerf, "Not...well.  Up and down.  Whatever, though :o)  How're you?"
KurtMRufa snrks.
Duelist growls quietly, "Technical illustration and train layouts to keep my mind busy."
Makyo nod.  Packingfox.
Turkzyn sits down.
Duelist growls quietly, "Ah yeah, Canuckyfox, eh?"
Duelist growls quietly, "Where in Canuckville ya headed?"
Turkzyn heads up the stairs.
Turkzyn has left.
You yerf, "Soon enough, yeah :3  Montreal."
Duelist growls quietly, "Montreal? Oh my god."
You yerf, "Hahah, why?"
Zhorah arrives from the foyer.
Zhorah back
Duelist growls quietly, "They're all Habs fans! O.O"
Duelist growls quietly, "You HAVE To wear an Avalanche sweater up there!"
Duelist growls quietly, "That's the old QC team!"
Kyhwana hmms at Srass "Sure! Just on twitter too!
Srass grins.
You yerf, "Awr, haha.  Dunno that I'll even be getting out much, honestly.  We'll see!"
MegaWolf should booze tonight.
You yerf, "Dunno if we'll be working at the Canonical office or a hotel meeting room, really."
MegaWolf growls softly, "Does spiced rum go with root beer?"
Kyhwana purrrs, "http://www.floodgap.com/software/ttytter/"
Duelist growls quietly, "That might be intense, MegaWoof"
Makyo was going to have a rob roy, but it didn't have any sweet vermouth, so it used lillet instead.  Worked out well.
Duelist....rum-n-juice
Duelist growls quietly, "Capt Morgan - Black. Man, that is good rum."
Srass did play with ttytter a while back.
Duelist played with tits awhile back.
MegaWolf growls softly, "I have oakheart."
MegaWolf growls softly, "It's not bad, prefer the Captain"
Duelist growls quietly, "Oakheart and root beer. Hmmm!"
Zhorah noses Duelist.
Duelist growls quietly, "I can't say, man. I wanna say 'sure' but I dunno."
Duelist licks Zhorah!
MegaWolf hrr. Let's see. Oakheart, Bombay Sapphire, Crown Black and butter shots.
MegaWolf growls softly, "I don't think I have any coke."
Duelist growls quietly, "No juice?"
You yerf, "Sapphire straight from the bottle."
MegaWolf growls softly, "I have a lot of that Walgreens glass bottle soda because apparently it's discontinued"
MegaWolf growls softly, "Cranberry, oh and I do have tonic water, forgot about that"
Duelist growls quietly, "Makyo!"
You yerf, "Gin and cranberry is good!"
You yerf, "Duelist!"
MegaWolf growls softly, "Root beer, cream, black cherry, orange creme, and strawberry creme."
Duelist growls quietly, "Never pull from the bottle....well, in extreme circumstances its ok"
Miko chatters, "You have Kina Lillet?!"
MegaWolf growls softly, "Cranberry and... gin? I don't think I'd like that. n.n"
MegaWolf doesn't like gin except in G&T
You yerf, "Ah well.."
Duelist totally wanna go drinking, in Vegas, with Makyo. Bring your boy!
Duelist will bring his!
Makyo oooh, nodnod ^^
MegaWolf growls softly, "I need to stop buying other booze and just buy vodka"
Miko kinda wants a drink. Hasn't had one in ages.
Makyo has... this, Miks: http://en.wikipedia.org/wiki/File:Lillet.jpg
Duelist growls quietly, "Vodka and Rum is all you need."
MegaWolf never has amaretto left over after a con because people drink 8 oz glasses of it when he's not looking.
Duelist growls quietly, "Tho the mixers are nice"
Duelist growls quietly, "Mostly anything made by Dekuyper\"
Kyhwana nod at Srass "It's neat.
Duelist growls quietly, "Hot Damn! Is pretty awesome."
Duelist growls quietly, "Cinnamon schnapps."
Miko chatters, "Ah, it sez "currently goes simply by Lillet or Lillet Blanc" on the Wikipedia page."
MegaWolf growls softly, "Buttershots and cream soda? (instant diabeetus!)"
Miko brought a bottle of Hot Damn! from the States once and never figured out anything reasonable to do with it other than pass the bottle around as a sort of prank. c.c
MegaWolf growls softly, "I saw an ad for cinnamon whisky at the liquor store next to the Chinese place tonight"
MegaWolf growls softly, "Sounded kinda good, actually."
Miko chatters, "No, wait!"
Miko chatters, "Is Hot Damn! the one I like?"
Duelist growls quietly, "It's good on a cold evening, Miko, for just that, yes."
MegaWolf growls softly, "Fireball, I think."
Khyber arrives from the foyer.
Miko bought a bottle of something violently pink that was pretty horrible, but he's had this stuff with a..
Miko chatters, "Ah, Fireball's the one I like. Shots. :3"
Duelist growls quietly, "Hot Damn! is not pink."
Miko chatters, "What's the one I don't like, then?"
MegaWolf growls softly, "Need Stoli"
Miko shakes Duelist. "Tell me!"
You yerf, "1 part Bailey's, 1 part Kahlua, dash of hot damn, and you've got an oatmeal cookie."
Miko falls over.
You yerf, "Usually a shot."
Duelist growls quietly, "What what what?"
Duelist growls quietly, "Wait"
KurtMRufa just pours some johnnie walker blue.
Somewhere on the muck, Herefox has connected.
MegaWolf growls softly, "I never buy Stoli for a con because it's just barely on the edge of "too expensive for you ungrateful schmucks""
Khyber walks in, thinks Miko means Aftershock.
Duelist - http://tinyurl.com/26j9tfu
Makyo has scotch, but knows all of the boy's drinks.
Duelist growls quietly, "Taht is Hot Damn!"
MegaWolf growls softly, "I did buy Cointreau a few years ago though"
Acy had to stop and sing to his puppy.
Khyber wonders if he sgill has that bottle of tres generaciones...
Duelist growls quietly, "What is THIS?"
Duelist growls quietly, "A 'Hot Apple Pie Shot'"
Acy says, "And she whined."
Makyo's shep will sing along with choral music :3
Zhorah noses Khyber.
MegaWolf still thinks a chocolate cake shot is bizarre.
Duelist growls quietly, "1 part apple rum, 1/2 part Hot Damn!, graham cracker garnish."
Kuttas licks Duelist!
Duelist licks Kuttas!
Mundy ta-dahs http://bit.ly/U8uTiF
Duelist growls quietly, "Hi, Y3NA!"
Khyber pets Zhorah
Kuttas says, "hey."
MegaWolf should just do shots of Crown, really. Also wishes he'd gotten to try the JB Devil's Cut.
Duelist growls quietly, "Is that what I think it is, Mundy?"
Mundy says, "Probably."
Duelist squeeeeeeeze Kuttas!
Duelist growls quietly, "How ya doin', Y3NA?"
Mundy's missing the O-F-O, SPDT switch.
MegaWolf growls softly, "Cinnamon schnapps, vanilla vodka, and spiced rum would be a Chai Tea."
Makyo not really a shot fox :/  More a neat-rocks-on-the-side or a tall drink fox.
Duelist uses O-F-O DPDT switches
Duelist has a stupid amount of flavored vodkas.
Duelist growls quietly, "Including CHOCOLATE cake vodka."
Srass says, "I take it O-F-O doesn't mean 'Out Fucking Off' in this context?"
Duelist growls quietly, "On Off On!"
Srass hmms doubtfully.
Duelist growls quietly, "Don't you doubt me!"
Duelist growls quietly, "It can't be an Ooooooooo! switch!"
Srass says, "That's true, if it were an OOO switch, it would be made by the Omniscient Overlords of the Omniverse, and they're all Out Of the Office."
MegaWolf growls softly, "On and off are small enough words that I don't normally see them abbreviated like that n.n"
Khyber whips out some foxnip that smells and tastes of root beer
Mundy says, "O-F-O is easier to type than On-Off-On."
Kuttas is okay, probably.
Srass nods.
Vetiver arrives from the foyer.
Mundy says, "And those circuits actually work as desired too."
Duelist growls quietly, "Yeah, me too"
Duelist growls quietly, "Build me 32 of those, Mundy!"
Duelist cracks the whip!
Kia has disconnected.
Mundy says, "You said you only had 16 switching machines. :)"
Duelist growls quietly, "Oh, ok!"
Duelist growls quietly, "Build me 32 of those, Mundy!"
Duelist growls quietly, "Err"
Mundy says, "Fail. :P"
Duelist growls quietly, "Build me 16 of those, Mundy!"
Duelist cracks the whip!
Duelist has been drinking! He is prone to fail and horny.
Mundy actually ordered one of the switching machines.
Duelist growls quietly, "Hopefully not at the same time!"
Miko is not a shot sqrl by himself.
Acy says, "Yeeagh!  Puppy's first fart! D:"
Mundy says, "Porno Disaster."
Duelist would have sent you a switching machine.
You yerf, "Get used to those, Acy :|"
Acy horrified.
Mundy says, "It's very likely that I'll burn it out in testing."
Khyber laughs at Acy
Miko chatters, "I put away quite a lot of Fireball as shots at Oswaldo's once when there was a bunch of people around and I was being pestered to ditch the diet for the evening and get drunk."
Duelist growls quietly, "I dunno, these fuckers are tough."
Dralen arrives from the foyer.
Srass says, "You don't need to get used to those.  You just need a cork."
Acy says, "She looks all guilty."
Dralen meeeeeeeeeeeeeeeeps.
Srass says, "Or possibly a cork with a double reed in the middle."
MegaWolf's dog doesn't do that unless her tummy doesn't agree with her food, which is why she's on Evo Herring and not Beef now.
Kuttas pets Dralen.
Duelist growls quietly, "Ya know....we should all meet in the middle"
Duelist growls quietly, "And drink"
Srass licks Dralen.
Khyber arfs at Dralen
Duelist growls quietly, "What is the middle?"
Mundy says, " http://www.youtube.com/watch?v=z1n3JBQdN84 "
Duelist looks at Vetiver.
Zhorah want hugs
Kia has connected.
Dralen smooches at Srass and leans on Khyber.
Kia frinks.
Khyber wraps dragonfox in tails
Dralen wiggles!
Kuttas reads his 1st ed ad&d books.
Vetiver hmms at Duelist?
Danish hugs Kuttas!
Somewhere on the muck, Tony_Cheval has connected.
Acy hahaha, he still has some of those.
MegaWolf's dog is too damned smart.
Danish rubs, waves, so on, out.
MegaWolf growls softly, "Is ridiculous!"
Duelist growls quietly, "we got a Y3NA in AK, a droxy in ON and a jaquar in MX. What is 'the middle'"
Duelist growls quietly, " ??"
Srass smooches Dralen.
Danish has disconnected.
Khyber softly says, "the middle is here in California!!!!"
Acy puppy does not like being petted very much. .(
Kia excludes the middle.
Acy :(
Duelist growls quietly, "Apologies, of course, to the Aussie and NZ furs who would put 'the middle' out in the middle of the ocean."
MegaWolf growls softly, "I made a little tether tennis ball on a rope thing to play with her this afternoon. Didn't take her long to figure out to go for the rope and not the ball if she actually wanted to catch it, but she mostly chased the ball anyway."
Vetiver quorks, "Alaska throws off that middle a lot, so it'd be like Montana or Wyoming."
MegaWolf growls softly, "When she got tired of playing, she finally managed to tug it away from me... and wrapped the rope around her paw with it before she lay down to chew on the ball, so I couldn't pull it away anymore."
Duelist growls quietly, "Oh, Acy....the puppy will not like to be touched til, like, week 16."
KurtMRufa licks its nose calmly.
Duelist growls quietly, "Kostya would not let me touch him until about 4 months old."
Duelist growls quietly, "I hear that is a shep thing."
Acy says, "Really?  What's up with that?"
MegaWolf growls softly, "Mine only likes to be pet when -she- wants to be pet, but that's most of the time. Too much petting and she'll wiggle away though."
Duelist growls quietly, "I couldn't touch Kostya for a couple months and now I can totally snug with him."
Duelist growls quietly, "Very affectionate doggie"
Duelist growls quietly, "But it just takes time."
Srass noses folks, wanders back to the store for a bit.
MegaWolf growls softly, "Don't remember any specific no-touchie age though, she slept on my mom's head her first few nights home."
Srass recoils as a team of carpenters arrive.  Brandishing belt sanders, they smooth him down until he's all gone.
Srass has left.
Duelist growls quietly, "Kostya, when he was a pup, would actually move away from me when I came near. Heh."
Mundy *touches* TIGRSKNK.
Acy says, "You forgot to keep bacon in your pocket."
You yerf, "Zephyr did that too, really, took him being sleepy for petting."
Acy says, "She just fusses a lot when she's sleepy and moves to a different spot to sleep."
KurtMRufa remarks, "Animals are funny."
Acy says, "She tilts her head adoreably when I whistle."
Acy daaaawh.
Duelist licks Mundy!
MegaWolf growls softly, "Mine was a little carpet shark for awhile though, nip nip nip."
Miko chatters, "Did Seapunk ever become a thing?"
Duelist growls quietly, "Do not forget"
Duelist growls quietly, "You are new alpha"
Duelist growls quietly, "She is still getting used to you"
Himmel says, "Piratepunk count, Miko?"
Himmel says, "Because that's pretty popular."
Acy says, "Yeah I know."
Duelist growls quietly, "Soon she will luv you more than anything!"
Duelist growls quietly, "And be the most bestest and loyal friend you have"
Acy could use one of those!
Miko wishes he could have a dawg.
Himmel friends Acy. On FaceBook.
JanusFox is loyal like a fox.
Duelist growls quietly, "Kostya is my most loyal and bestest friend!"
Duelist growls quietly, "The Noble Dog."
MegaWolf luff teh sheppy puppy.
Acy eek?
MegaWolf growls softly, "Of course they love their treats more than you ;)"
Duelist growls quietly, "Not mine"
Acy says, "She especially likes the bacons flavored treat bits."
Miko chatters, "They're not *cats*."
Acy says, "And she likes turkey and hot dogs."
MegaWolf growls softly, "Mine's favorite is liverwurst"
MegaWolf growls softly, "Also she likes coconut."
JanusFox likes those things to, but not combined.
Acy says, "I haven't tried liver."
Duelist
MegaWolf growls softly, "We can tell when she absolutely loves something because she practically floats towards you like a cartoon"
Duelist's dog like steak
Duelist growls quietly, "And chicken"
Miko chatters, "Dogs are nuts for liver, as a rule."
Duelist growls quietly, "And hamburgers"
Paladin is nuts!
Miko chatters, "You feed your dog steak? You're spoilin' that pup. :3"
Acy says, "I made some liver bits by boiling and chopping liver and drying it out in the oven but I froze it all when otherdog didn't like it."
Miko gives Pal liver.
Duelist growls quietly, "Of course I feed him steak!"
MegaWolf growls softly, "I made a coconut lamb for Easter and she ran into the kitchen and stared at me the entire time I was making it."
Duelist growls quietly, "he watches, guards and defends my house!"
MegaWolf growls softly, "The instant I took the top off the coconut flavor"
MegaWolf growls softly, "Dog appears out of nowhere!"
Acy says, "Hehe."
MegaWolf growls softly, "So we got coconut flakes for treats."
Kia thought vultures were the ones who loved liver. every night.
Miko's sister likes raw bloody liver.
Himmel says, "Ew."
MegaWolf's likes steak but it didn't get a "huge eyes floaty dog drooling all over" reaction like the liverwurst.
[public] Frnkzk says, "Come on, everything's better with dinosaurs. Weren't you ever kids?"
Duelist growls quietly, "Remember the rule. If you wouldn't eat it, don't feed it to your dog."
Himmel says, "'Wouldn't'?"
MegaWolf growls softly, "I wouldn't eat herring but that's more due to my general loathing of seafood :P"
MegaWolf growls softly, "She luvs her herring Evo"
Himmel says, "I wouldn't eat meat, but I'm not going to kill my potential dog."
MegaWolf growls softly, "She has a sweet tooth too, we finally gave in and got her some carob chip treats."
Makyo nits Himmel.  There.  Stuff to pick :o)
Duelist petpetpet MakyoFOX
Himmel knits Makyo. Perfect for fluffs.
Makyo's shedding could easily make quite a cozy coat!  So luxurious..
Makyo nosenosenose Duelistskunk.  Prf.
Himmel wears Makyo. "I can feel you all around me."
Kia has disconnected.
MegaWolf growls softly, "Now I want two sheppies."
You yerf, "Close.  Against your skin.  Rrrr."
Duelist wants 11 sheps
Himmel purr.
Acy says, "You cannot have mine!"
Duelist growls quietly, "But that was Kostya's idea."
Duelist growls quietly, "I do not necessarily agree."
Acy squeezes his little piglet pup!
You yerf, "Zephyr wants 1 more dog.  A mutt."
Zhorah hug so much Makyo
MegaWolf growls softly, "One of our dog trainer's friends has 7 Australian Shepherds."
Makyo hughuuuuuug around Zhorah.
Kuttas wipes his nose.
Duelist growls quietly, "I asked Kostya....3 dogs, 7 dogs, 11 dogs....and he got all excited when I said 11 dogs!"
MegaWolf growls softly, "I know they're not quite as nutty as border collies are but that's still a lot of neurotic dog in one house!"
Acy says, "3+ of any animal is crazy cat lady territory."
Acy says, "Except maybe fish."
MegaWolf growls softly, "We may get a second one when she's 5-ish"
MegaWolf growls softly, "I'd love to get a golden but the breed is a huge cancer magnet :|"
Himmel o-o Mega.
Duelist growls quietly, "Is dumb!"
Duelist growls quietly, "Blonde dog."
Himmel says, "Very dumb."
MegaWolf growls softly, "Nu-uh. Only the goofy show dogs!"
MegaWolf growls softly, "Gun dog is smart!"
Himmel pff!
Himmel says, "Get a 'Mute."
Duelist growls quietly, "That is a yellow lab"
Duelist growls quietly, "Not a golden"
MegaWolf growls softly, "Goldens are gun dogs too!"
You yerf, "Zephyr's half gsd, half border collie.  There's a neurosis or eight in there."
Miko chatters, "Poodle is arguably the smartest dog, which seems nuts."
Acy says, "If you get a yellow lab you have to name it Butter."
MegaWolf growls softly, "Eh, mostly the border collie half"
Miko chatters, "GSD's up there too though."
MegaWolf growls softly, "Borders are -nutty-"
MegaWolf growls softly, "Cute tho'"
Miko chatters, "Our husky/landseer cross was clever enough to be a smartass."
Acy says, "If I get another dog it'll be a giant schnauzer."
You yerf, "He's a nut."
Duelist - http://www.petmedsonline.org/top-10-smartest-dogs-in-the-world.html
Duelist growls quietly, "Taht list fails at #4"
Zhorah rumbles, "We have a sheep dog and a basset, and my kitten"
Duelist growls quietly, "Golden retriever is dumb"
MegaWolf bites Duelist!
Duelist has defense mechanism!Be careful!
MegaWolf tranqs Duelist for That Operation[tm]
Duelist tranqs MegaWoof for an operation!
Duelist growls quietly, "You don't need those things dangling about"
MegaWolf growls softly, "Descenting isn't nearly as bad as that!"
Duelist growls quietly, "You take something from me, I take something from you."
Himmel takes Duelist's stereo.
MegaWolf takes Duelist's wallet so he can't pay the vet. :D
Duelist growls quietly, "Sorry, I can just dip into the casino stash"
Duelist growls quietly, "And that's in a safe!"
MegaWolf uses the wallet to hire Ocean's 14.
Duelist growls quietly, "Nah nah, just face it"
Dachande. falls over, defeated by a very delicious dinner.
Duelist growls quietly, "You cut on me, you get deballed"
Himmel snrks at D.
Duelist growls quietly, "Snip them fuckers right off."
Himmel says, "Is Kostya fixed?"
MegaWolf growls softly, "Skunks need that operation to be outstanding members of society!"
Duelist growls quietly, "So do wolves"
Dachande. says, "Outstanding, or upstanding?"
MegaWolf growls softly, "Both!"
Dachande. prevers to be instanding.
Himmel prefers to be downstanding.
MegaWolf hmphs and just gently nips Duelist's nose
Himmel, beta as fuck.
MegaWolf growls softly, "Bad mephit"
Acy would guess that Kostya has his balls.
Duelist growls quietly, "Kostya is not fixed, correct."
Himmel nods at Duelist.
Acy says, "That does not seem like the sort of thing Duelist would do."
Dachande. pushes Himmel to the ground so he feels happy.
Himmel whimpers.
Dachande. sits on him.
Himmel's muzzle finds its way into places.
Duelist growls quietly, "Ain't no one convinced me that fixing my dog is good for him."
Kia has connected.
Kia finishes watching an old ep of Lost Girl. Then, the Doc.
Himmel points out that good for him is rarely the concern.
Kia calls up Comrade Stalin, who shows up in his orange vest with a broom to sweep the sleepers off to their homes.
Danish nips the arm of whoever's trying to wake him up and scurries back to his den.
Danish has left.
Srass arrives via giant ladle, landing in a quivering blob.  In the distance, Satan's lunchlady shouts, "Snaaaaack!"
Srass has arrived.
Duelist growls quietly, "Some butch fucking dyke stood up in front of the county commissioners and told a story about how cutting off my dogs balls will stop the irresponsible owner across town from having his dog breed....but I didn't follow that logic."
Himmel says, "There is no logic."
Himmel sighs. People.
Kuttas hugs Srass.
Srass hugs Kuttas.
Makyo sheds on Himmel: http://makyo.drab-makyo.com/pretties/arctics/10985897.jpg
Duelist growls quietly, "Then I called that bitch on it and she got all offended."
Kyhwana beeps at Srass "What did you get from the store?
Duelist growls quietly, "Just cuz some dyke don't wanna see male genetalia don't mean I should cut my dogs nuts off."
Duelist growls quietly, "STOP LOOKING, bitch."
Himmel brushes Makyo in a tub.
You yerf, "Christ, drop it."
Duelist growls quietly, "That fox had a fur-splosion!"
Srass licks Kyhwana's nose.  "Whole grain tortillas, for the cranberry almond chicken salad I got earlier."
Kyhwana oohhs
Srass got some Framboise Lambics on the earlier trip.
Kia chuckles a bit. His mother is in favor of neutering all dogs 'cause dog balls are icky.
Acy says, "The penis is a weapon.   A tool of opression!"
Khyber pats a fullwuff
Acy says, "The gun, however, is good."
KurtMRufa taps its fingertips together.
Kia says, "All the bullets and bombs and missles are shaped like dicks. "
Khyber has disconnected.
Makyo gonna bath.  Probably also take half a muscle relaxant.  Will sleep well tonight.
Himmel pets Makyo.
Makyo nuzznuzz at Himmel.
Acy noses Makyerf.
Srass leans over and nibbles interferingly at Kurt's fingertips.
Makyo pett on Acymuzz.
Acy says, "Makyo I'ma visit you at the store somedaya"
Acy!
You yerf, "Please dooooo :D"
Makyo okay really bath.
-- You have left channel 'public'
Kia secretly loves Doctor Who.
Acy says, "Now we all know."
Kia says, "Shh. "
Himmel wants to watch Doctor Who, but he isn't allowed, 'cause he really only wants to watch from season 5 on, and he's been forbidden from doing so until he watches the first four.
Himmel has psychotic Whovian friends.
Miko chatters, "Oh shit, that's what I was gonna watch but forgot."
Kia thinks it's best to start with Eccleston.
Dachande. says, "Watch a couple bakers, then the dude after him, then watch eccleston, then proceed."
Kia says, "It's made for people who know fuck-all about Doctor Who, like most of us who haven't been watching it since 1960. "
Himmel says, "THe First New Doctor, Kia?"
Kia nods.
Himmel says, "I saw some episodes."
Himmel says, "He's cool."
Himmel says, "But."
Himmel says, "I want Matt Smith."
Miko chatters, "I recommend coming down with a wicked stomach flu and lying on a couch watching the first few seasons straight through on a laptop, with a bucket by your side."
Kia says, "Also, don't fall in love with him.  He only does one season, and that next guy is even better. "
Himmel knows.
Duelist growls quietly, "ShutthefuckupDachthereisnoTomBaker!!!!!"
MegaWolf needs to find an atorrential way to download everything since The End Of Time.
Himmel chuckles at Duelist.
Himmel says, "But seirously."
Duelist growls quietly, "It NEVER happened!"
Himmel says, "Matt Smith."
Himmel says, "DO Want."
Kia has a lovely Tom Baker scarf.
Dachande. says, "Oh and you have to see all the episodes with Harriet Jones, and Sarah Jane Smith."
Himmel says, "My First Who Fan Friend made the mistake of showing me a clip from the premiere of season five."
Himmel says, "And then forbidding me from watching more than the first episode."
Dachande. says, "Ahh."
Himmel says, "That dick."
Miko chatters, "Is that the one that starts with them on the run?"
Kia's never watched a Tom Baker, but it's not like anyone else has a convenient visual identifier.
Himmel says, "Fishy custard, Miko."
Dachande. nods, "The reluctant regeneration."
Miko chatters, "Ohhh. Nowhere near as good as the opening of season six."
Himmel Wants to see the opening of season six, he supposes.
Miko chatters, "But watch 'em all, anyway. You don't wanna miss The Empty Child/The Doctor Dances."
Miko chatters, "Or Blink."
Kia prrrrs at that one.
Himmel says, "I can go back and watch them. I'd be fine with that."
Himmel says, "But."
Miko chatters, "You may wanna miss the ones with the farting aliens."
Kia says, "Blink is like the first Alien. They introduced an amazing thing, which they later ruined. "
Himmel says, "Weeping Angels/"
Himmel says, "?"
Kia nods.
Miko did not care for the return of the Angels. Apparently they're coming by for a third go 'round soon. <.>
Himmel says, "Yeah."
Dachande. says, "And the warewolf, have to see the warewolf."
Kia nods. They're like the new fucking Daleks.
Himmel says, "They might take Amy, Meekz."
Dachande. says, "Oh and Turn Left."
Kia says, "That one has cat people. "
Dachande. says, "The Library."
Dachande. says, "Okay just all of the Catherine Tate season."
Miko chatters, "Silence In The Library."
Miko chatters, "Gridlock!"
Dachande. says, "Yes that"
Dachande. says, "And Gridlock, it has kittens."
Miko chatters, "Gridlock has a cat dude and a human lady who've had KITTENS."
Kia prrrs. Catherine Tate was the shiz.
Kia says, "That black lady, not so much. "
Himmel downloads an album that features a girl yelling at him that he's a bad person because he's male.
Dachande. says, "Donna made Rose look like a waste. Martha is just badass."
Kia says, "Martha was boring. "
Dachande. says, "Later martha, not early martha"
Miko chatters, "She was a bit of a non-entity in comparison to Donna or Amy, yeah."
Duelist growls quietly, "You are the people who walk up to a Dr Who Pinball machine and ask 'who are those guys on the glass?'"
Kia says, "Rose was chavvy, but she grew on you. "
Dachande. says, "Best part of Rose was her mom. And i watched the classics on netflix too."
Kuttas taps the butt of the spear he is carrying on the ground. Thump, thump-thump.... A dark mist spills out across the ground from that point, flowing outward, chilling the feet of those nearby.
Himmel says, "Nah, nah, I've had the classic doctors beaten into me, Duelist."
Himmel says, "That one what with the coat and stuff."
Duelist growls quietly, "I'm just kidding, really, except I had someone ask me that."
Kia rubs his thumbs. Is it normal for piano to give calluses? Also, he's sort of excited that he's now understanding why people play way up on the keys sometimes.
Himmel says, "... Really?"
Himmel says, "That's sad, D."
Himmel says, "THough."
Himmel says, "I live in Kentucky."
Himmel says, "I didn't even -hear- about Doctor Who until senior year of High School."
Duelist growls quietly, "They think Dr Who started in 2005."
Himmel nods.
Kia laughs his ass off at a certain line.
Acy remembers watching it on PBS as a little kid. o.O
Himmel says, "Well, I'd seen flashes of it on..."
Himmel says, "Uh..."
Himmel says, "Random antenna tv channels."
Himmel says, "Cannot remember for certain. But I only know what it was now."
Duelist as well, Acy. Used to sneak out of bed to watch it on PBS!
Dachande. says, "It was often shown late night pbs."
Dachande. says, "The only station with the balls to play brittish tv."
Himmel puts big, square, plastic glasses on Duelist. "Nard."
Dachande. says, "But really even if ya want to start with Smith, you'll clear through that swiftly, go back and see the rest."
Himmel will!
Himmel is certain he'll be hooked, by then.
Kia says, "More like: We couldn't come up with anything worthwhile to put on our smarty tv channel, so we had to take it from the Brits. "
Duelist growls quietly, "Oh no no, MomTiger was a huge Dr Who fan. USed to go to all the conventions and everything."
Kia says, "Or at any rate, we couldn't appropriate funds for anything to put on our smarty tv channel. "
Himmel says, "... Maybe I'll start watching it, Naruto: Shippuden, and Red vs. Blue at the same time."
Himmel says, "I've made deals with friends."
Dachande. says, "Dude, naruto doesn't end."
Himmel says, "I'll watch their TV Shows, if they watch mine."
Himmel says, "Well, I know."
Himmel says, "But."
Dachande. says, "Just warning ya, you think you're close to the end, you're not."
Himmel says, "And a bunch of it is Filler."
Kia thinks Himmel should watch House of Cards.
Dachande. says, "Good though, very good."
Himmel says, "House of Cards?"
Dachande. says, "Also watch The Killing."
Himmel yeegh.
Kia says, "Brilliant Brit political thriller TV show. "
Himmel says, "I had to find someway to convince friends to watch Supernatural."
Himmel says, "So, I agreed to trade."
Kia says, "Has Ian Richardson, who is so fucking awesome. "
Himmel says, "My one friend who watches Supernatural has seen all of it. Except the two best seasons, 4 and 5."
Kia says, "And his character's intitials are FU. "
Himmel teehees at Kia.
Himmel says, "I dunno. I'm not big on Political thrillers."
Kia says, "It's really, really fucking good. "
Himmel will give it a testdrive.
Kia says, "Francis Urquhart is a monster, and yet delightfully charming. "
Dachande. Fuckit torrents latest who.
Dachande. says, "There's only 3 out so far right? Asylum, spaceship and town yeah?"
Paladin barks, "Yups."
Kia says, "Yesh. "
Himmel says, "If anyone likes modernized, edgy fantasy staples and/or grim takes on judeo-christian mythology, Supernatural is an awesome fuckin' show."
Kia suggests Lost Girl if you like urban fantasy. And hot people. And really short bartenders.
Himmel nudges Dach. "Though, I dunno how you took to it. Didn't ask, afterward."
Himmel says, "I'm okay with urban fantasy."
Himmel googles Lost Girl.
Dachande. says, "Supernatural is a very nice show. It's got a good feel to it, the characters are serious with humor mingled in so it's not too daunting. The writing is witty an the characters are belivable. Also unlike most new scifi shows there's noone from a previous show I recognize so it's not like watching Farscape go through the Stargate."
Dachande. says, "While I've not got around to watching more of it, I would reccomend Supernatural and will most likely watch it myself."
Himmel snickers at Dach.
Himmel says, "Well, the actors are from other things, but they're wildly different."
Vetiver hears 'urban fantasy' and thinks of Lord of the Rings, but set in South-Central.
Himmel says, "Jared Padalecki, who places Sam, was on Gilmore Girls before SPN."
Himmel says, "Er... Who plays."
Dachande. Boooos fucking 500 seeders and 2000 leachers.
Kia says, "Starting at the beginning isn't strictly necessary with Lost Girl, but I wouldn't start with watching, say, the current episode on Sci Fi. It's the end of the season and shit's getting real. "
Dachande. says, "Yeah but I never watched Gilmore Girls as I am not vagina."
Himmel says, "Jensen Ackles, who plays Dean, was on The Young and the Restless. And... something else."
Dachande. says, "Again, penis."
Himmel says, "Oh, yeah!"
Himmel says, "Dark Angel!"
Makyo mrrp, mrrp.
Kia says, "Urban Fantasy is, say, Buffy. Or Charles de Lint's ten thousand books that are all the same. "
Himmel says, "Oooh, I loved Angel."
Himmel says, "And Buffy, except for a lot of the main characters."
Dachande. says, "Buffy was good until the weremonkey then it got a bit silly."
Himmel liked buffy for Willow and Seth Green's character and Angel and Spike, kind of.
Himmel says, "But Spike is totally better with Angel than Buffy."
Himmel says, "I mean that in every way possible."
Kia needs to finish watching Buffy sometime.
Dachande. says, "Boo ep2 finished before ep1"
Dachande. says, "Damnit! I keep forgeting to not download everything into the porn folder =P"
Kia says, "It's all porn. Just some of the people are wearing more clothes and fucking less. "
Kuttas says, "What is this 'Buffer' and 'Spike' of which you speak?"
Dachande. says, "Late 90"
Kia says, "Buffy: She was a vampire slayer. "
Kia says, "Spike: He was a vampire. He also briefly showed up in a Ninth Doctor episode, I think. "
Dachande. says, "Er late 90's tv urban fantasy dramas revolving around vampires, witches, lesbians, and david boreanas. who i think is spelled his name right, but hes the guy on bones."
Himmel says, "Yeah, that's his name."
Kuttas snerks. "Bones."
Kia says, "Looking, by the way, like shit warmed over. "
Himmel says, "David Boreanas is a studmuffin."
Himmel says, "I'd give him Bones."
Kia tsks at the Doctor. Never realized he wore fucking CLIP-ON suspenders.
Acy hahah.
Dachande. says, "Well yeah he's a normal guy, not going to have tailored buttons."
Kia says, "Proper suspenders are the Height of Fashion. Clip-on suspenders are trashy. "
Kia, sort of baffled by this new firm he may move to.  They're casualer. But lemur has a certain personal brand-style that involves his suspenders.
Azure arrives from the foyer.
Azure yips, "BHello, creatures.""
You yerf, "Hello, fox."
Himmel says, "Casual and vintage formal are easily conbined, Kia."
Duelist growls quietly, "Hello miniscule foxy!"
Himmel... combined*
Dachande. says, "the last guy wore chucks with suits, they tend to have a little something common among the fashion, it helps them blend in."
Dachande. says, "Except for the question mark doctor, but we don't talk about him much."
Kia --hat, suspenders, french cuffs and button collars.
Himmel says, "Eccleston was hugely cas."
Dralen flops.
Duelist pets upon diminutive vulpine!
Azure does not really care for sneakers with suits.
Azure noses Duelist, "Hello, giant skunk."
Himmel says, "Black jeans, boots, teeshirt, leather jacket."
Kia regularly wears sneakers with his suit, until he gets to work.
Dachande. says, "Eccleston looked like he worked at the docs, but as a gangster more so than a fish monger."
Duelist is economy sized!
Himmel nods.
Kuttas hugs Azure.
Miko chatters, "How do normal suspenders attach?"
Miko chatters, "Are there buttons on the pants?"
Kia says, "Yes. "
Dachande. says, "Some come with buttons installed, otherwise ya get a tailor to stick em on."
Dachande. says, "Like Larry King and his jeans."
Kia says, "Brits tend to put the buttons on the outside; US puts them on the inside, because that's where they belong. "
Dachande. says, "Outside looks better though, otherwise it's like you're hitchin em to your britches."
Azure hugs Kuttas.
Kia disagrees.
Kia is slowly drifting towards removing the belt loops from his suit trousers.
Dachande. says, "Personaly I like the style that attach to belt loops."
Azure yips, "You aren't even supposed to see the suspenders."
Himmel says, "You aren't."
Kia says, "Azure is espousing the super-trad opinion, under which suspenders are rather like underwear. "
Miko chatters, "Bleah."
Himmel says, "It's very plebeian, very pedestrian, to show one's suspenders."
Azure yips, "That's why I only wear suspenders under a jacket mostly."
Himmel says, "Only a working man need take off his jacket."
Azure yips, "Though I do have a pear of clip-ons I wear with jeans if I'm doing moving."
Srass hugs Azure with a foreleg, carefully.
Azure yips, "Since I find if I'm bending and wiggling around suspenders are better than a belt."
Kia'd feel rather silly wearing his angels-and-devils suspenders if no one could see them.
Azure yips, "Ornamentation belongs on your tie :)"
Dralen meeeeeeps.
Dachande. says, "I think they're like undies, i wear fancy nice looking underwear that matches the main color of my clothes for my own pleasure, not the showing of others."
Kia does not wear a tie if he can possibly avoid it.
Azure doesn't really like 'cutesy' ties.
Srass says, "That's like wearing spiderman underoos, Kia.  Some things are better left hidden."
Azure yips, "Though someone did get me a really nice royal blue one with a random pattern of lightning bolts I'm quite fond of."
Kia disagrees! but then he's the one who's made this a thing of his.  
Kia says, "WOrthy of note: Ladies love the suspenders. "
Himmel says, "Kia: do suspenders go over or under a waistcoat?"
Dachande. says, "Laides love them because they can line them over thier nipples and show all of the fun bags with out getting arrested."
Kia doesn't generally wear a three-piece, but they'd go under. This is fairly obvious, since the waistcoat extends below the waist of the pants.
Duelist growls quietly, "ClassyFox."
Azure has one three-piece and one two-piece.  Tends to wear the three piece more at night and the two piece in the day.
Kia doesn't *ever* wear a three-piece, actually. Not that it's not pretty awesome, but jesus h. He sweats enough as is.
Azure yips, "Plus the two piece is a nice light grey and I think it goes better with the bright violet and electric blue shirts."
Makyo has 3-piece from wedding.  Wears it very rarely, because yeah, sweating >:/
Himmel says, "YOu would hate my typical style, Kia, maybe."
Azure yips, "The three-piece is a dark charcoal and I generally wear a white shirt, mother of pearl cuff links, and a more conservative tie with it.,"
Kia also may or may not have Millenium Falcon cufflinks.
Azure has three pears of cuff links, one lapis, one mother of pearl, and one just stainless steel.
Kuttas says, "What are the pieces?"
Duelist naturally, when talking about suits, recommends double breasted.
Himmel says, "Though I must thank you. I've just realized a need for Braces."
You yerf, "Slacks, jacket, vest, Kuttas."
Kuttas wears jeans pretty much all the time. The only suit he owns is a military uniform.
Kia has his Millenium Falcons, his 1950s subway tokens, his 3 kopek pieces, the art deco ones he can't actually put on, and the ones made from .45 Long Colts.
Himmel combines waistcoats and dress shirt with flared jeans with frayed hems and maybe holes at the knees or under the ass.
Kuttas says, "Ah. So, in the two piece, is it slack and jacket? Or jacket and vest?"
Kuttas knows a number of people who wear jacket, vest, and jeans.
KurtMRufa's player got a suit in high school and still has that same one.
Kia isn't paying nearly enough attention to this Dr. Who.
Duelist has many suits because, well, he likes wearing 'em
Himmel does have this glorious brown suit.
Azure used to have a three piece double breasted coal black suit he adored, but it ended up being Severely Damaged due to him wearing it all the time.
Himmel says, "I hate brown clothing, I should note."
Himmel says, "Doesn't work well with my complexion."
Kia likes his suits. And... fuckity fuck.
Azure says to Himmel, "But, really, I wear way too much colour on a daily basis to be properly 'trad'."
Himmel says, "But this suit is -beautiful-. And manages to work."
Himmel chuckles at Azure.
Kia'd meant to swing by CitiShoes and pick up some stuff to apply to his horse's-ass shoes. :(
MegaWolf totally fails at fending off RL
Kia, having spent a stupid amount of money on these shoes, wants to treat them really, really well.
You yerf, "Slacks and jacket for 2-piece, yeah :o)"
Kuttas wears what he normally wears. Blue Jeans, carhartt shirt, plaid Woolrich overshirt, boots and belt.
Azure tends to go for something like, say, dark grey slacks, light grey jacket, bright violet shirt, and a nice geometric or striped tie.
Duelist should get a new suit. Hmm!
Azure yips, "And a silk square, of course."
Kia recommends MyTailor.com.
Kia says, "Best if Mr. Whatzisnuts, the owner, comes to your town, but always good. "
Kia says, "Hemrajani, that's his name. "
Duelist just goes to Caesar's Palace and buys a Dolce and Gabbana and has it fit to him.
Kia says, "Better to have a suit made-to-measure for you from scratch.  Your fabric, your choices for everything. "
Azure admits he really wants to get a proper linen suit made for summer time.
Duelist growls quietly, "Not when you change sizes like I do."
Dralen can't afford pretty clothes. "Mexx and Buffalo. Can't afford D&G or Zegna.
Kia would like a linen suit, but dunno how it'd go over. Maybe if he switches to the not fox firm.
Azure yips, "And species."
Duelist growls quietly, "Ahh, I used to go Armani,but that's so played....and then I found D&G and just really liked 'em."
Dachande. wears $15 jeans and $20 shirts, looks like a fat fuck.
Kia says, "And a... thingy. "
Kia brainfarts.
Miko chatters, "Hello, me."
Kia says, "The other summer fabric. Not madras; I don't want to look like a degenerate gambler. "
Kia says, "Seersucker. "
Duelist has linen and seersucker suits. Required out here.
Dralen says deeply, "Versace fits me to a T, but no way I can afford Versace."
Azure yips, "Seersucker?"
Kia really wants to roll into work in a seersucker, straw fedora, and spectators.
Azure yips, "I like madras."
Duelist growls quietly, "Nothing fits me. The standard drop for a US suit is 6 inches. My drop is 14."
Azure yips, "Actually my favourite thing to wear in the summer is a linnen jacket, madras shirt, and a pair of darkish brown slacks."
Kia points at MyTailor!
Darkness arrives from the foyer.
Azure yips, "White shoes and a panama."
Darkness waves.
Makyo rrf, so much for early bed.  Gulps down half a muscle-relaxant and sprawls, about bedtime.
Srass wavesw.
Kuttas waves.
Duelist has a panama hat :)
Duelist wave too
Azure has been accused of drifting straight out of 'business casual' and into 'business technicolor', though.
Kia likes madras too. His standard summer wear involves madras shorts. But he'd never do slacks or a sportcoat in it, because... again, he'd look like a degenerate railbird.
Himmel wishes he was a chick, when thinking on Fashion.
Azure yips, "Chicks don't get pockets."
Azure yips, "I just wish I were in the 19th century."
Himmel says, "Steampunk is so much easier when you're a girl, though."
Azure yips, "It is?"
Himmel nods at Azure.
Dachande. says, "So true"
Azure yips, "They have to do corsets and crap."
Azure yips, "Men get all the good clothes in steampunk."
Azure would so love to be able to get away with going to work in a frock suit.
Makyo hands out cheek-kisses, because you all are wonderful.  Will idle here, again, until disconnected for exactly the same reason.
Himmel says, "Yes, but those are far more readily available than, say, a functionally single-piece waistcoat."
Duelist growls quietly, "You are a gentleman, Azure"
Duelist growls quietly, "And, as such, you should dress appropriately."
Himmel says, "Or perhaps it's just my locale."
Azure yips, "That is true, it always annoys me how much old design clothing is made like costumeware instead of something you'd actually wear."
Himmel nods.
Duelist - http://www.gentlemansemporium.com/gentlemans.php
Himmel thanks Duelist a lot.
Azure does seriously want an opera cloak now, though, ever since he had a dream in which he was fighting a duel in one.
Kuttas hmms. He hasn't been to that site in a while.
Miko likes suits on under-25s and over-60s.
Himmel throws three weeks' worth of checks at the 'Vest' section.
Skylos arrives from the foyer.
Skylos softly barks, "woof!\"
Skylos sits.
Azure listens to some Ambient Metal.
Miko also has an outfit that he lately just wears and wears and wears and then washes and then wears again.
Azure grins at Duelist, "Well, I believe in the Nikola Tesla school of fashion.  Nothing says "I spend my days working on fantastic technical problems and trying to revolutionize the world" like a really nice suit.
Kia says, "Azure: Become Solicitor General of the United States. "
MegaWolf puppy sleeping in her box.
Azure asks Kia, "Why?"
Duelist growls quietly, "I agree, Mr TinyFox."
Kia says, "On the rare occasion that the SG goes to court, they wear morning dress. "
Kia says, "Stripey pants, frock coat and all. "
Miko chatters, "Dark gray worn and frayed bootcut jeans, black zippered and twin-breast-pocketed knit thing with shoulder thingies and horizontal grey stripes in pairs, snug short black leather jacket with hood. Black slip-on tennis shoes. They all just go super well."
Azure ooohs.
Miko doesn't have any other ensembles that fit so well so he just doesn't wear anything else any more. c.c
Darkness sits quietly on one of the couches.
Azure suspects having his background in mathematics rather than law would somewhat impede this goal.
KurtMRufa remarks, "Pants."
Azure asks Darkness, "How do you do?"
Duelist growls quietly, "Men should dress finely."
Dralen dresses like a hipster.
Kia says, "Law schools exist. "
Miko thinks really young guys in suits &c look cute, and old men in the full getup look charmingly dapper.
Kia knows this from personal experience.
Miko chatters, "Anyone in between.. eh.. look like they're in accountancy."
Miko chatters, "Unless they're going nuts with the waxed moustache and cane."
Duelist growls quietly, "Then they ain't wearing the right suit, Miko"
Kia says, "Depending on your specific educational background, you could wind up in patent prosecution, which is a really lucrative niche.  On the other hand, it won't make you SG of the US. "
Azure yips, "Yes, but I'm pissed off at patent law."
Kia says, "Well, it is sort of rubbish. "
Azure did have fun chatting with the Patent Attorney, though.
JanusFox has disconnected.
JanusFox @batbats his ISP, but, to no avail.  He wimpers as he fades out.
Miko chatters, "Couldn't you fight the other side as a patent lawyer?"
MegaWolf growls softly, "Calvin's dad was a patent attorney"
Azure yips, "he even gave us the "You don't have to like it.  You have to accept the law as it is and act rationally." speech."
Azure yips, "Which I respected quite a lot."
Darkness looks up to Azure. "I am well. How are you?"
Miko chatters, "OK, not all guys under 25 look good in the full kit. Zac Efron just looks like a giant douche when he wears a suit."
Miko image googling, aimlessly.
Azure smiles at Darkness, "I'm doing qutie well, thank you."
Dralen says deeply, "Adrien Brody looks pretty fucking hot in a sharp suit."
Kia says, "Patent prosecution is specifically the practice of applying for and getting patents with the USPTO. "
Miko chatters, "I think it's because he always looks so rumpled."
Miko chatters, "I mean, not the suit. The guy inside it."
Kia says, "It requires, because of what you have to do to practice before the USPTO, a specific educational background. "
Miko chatters, "It's the contrast."
Kia says, "Patent litigation is a different specialty, which is basically just a litigator who litigates patent cases. "
Azure aaahs.
Kia says, "Helps to have a technical background, but isn't required. "
Darkness smiles.
Miko titters at http://cs1.fashionising.com/media/suit-trends/three-piece-suit-2011.jpg
Azure can't wait until his danged patents get approves so he can point to them and say, "See?  SEE?" when he applies for jobs.
Himmel says, "Those gloves are -perfect- with that, Miko."
Duelist growls quietly, "You will lose, Azure."
Miko chatters, "I didn't even notice the gloves."
Miko chatters, "But they are indeed very rapey gloves."
Azure yips, "Lose?"
Skylos heard a series of gunshots nearby after police went buy with lots of sirens vrooming and horns.  Then there was a helicopter.  Then the helicopter went away.
Azure yips, "Lose what?"
Miko chatters, "And so go very well with the rest of the "date rapist" Halloween costume."
Duelist growls quietly, "Yep, someone with a much huger patent litigation budget will just steal your patent."
Miko scratches his head. Is this a bad suit? http://www.ahfashion.com/products_pictures/Sharcoal.jpgM.jpg
Himmel says, "I think, instead of sunglasses, he ought to have gone with a hat, either also-solid-black or also-pinstriped."
Himmel says, "I would say, yes, Miok."
Miko chatters, "Because that looks just terrible. That's like a nasty cheap supermarket suit, right?"
Duelist growls quietly, "It'd be a nicer suit if it fit him properly, Miko."
MegaWolf patents the method of soothing small blue foxes with a FoxBox
Himmel says, "Miko."
Azure yips, "Oh, I wouldn't litigate it."
Azure yips, "I'd be very put off with my employer if they tried it."
Himmel says, ":nods."
Azure yips, "And offer to testify for the defense."
Miko chatters, "It looks like it's too tight at the shoulders and too loose at the waist, yeah."
Kia isn't so sure about his fall hat. May be time to visit Pork Pie again.
Duelist growls quietly, "Bottom line, Patent is all about money. If you got the budget, you win the idea."
Azure yips, "I just like it since it's a matter of public record and I can actually show off the technical details of something I've worked on."
Miko chatters, "Right, yes, it's a $189 suit."
Darkness is enveloped in a sparkling glow as a space/time rift envelops her and she winks out of sight.
Darkness has left.
MegaWolf growls softly, "Or some European guy named Einstein steals it and loses your application."
Miko chatters, "Or Thomas Edison crosses your name out and writes his in."
Azure doesn't even think it should have been patentable.
Azure hisses at THomas Edison.
Azure yips, "The Steve Jobs of the electrical world."
Duelist growls quietly, "May 9, 2008, Tech Crunch reports MIT students demonstrating their Android apps. Winner is an app called Locale which allows a user to dynamically change their phone settings based on location. June 26, 2008 Apple files a patent app to patent 'allowing a user to dynamically change their phone settings based on location'."
Kia shakes his fist at Thomas Edison and pets his pigeons. Whom he loves. Like women.
Duelist -  http://techcrunch.com/2008/05/09/mit-students-demonstrate-their-android-applications/
Miko chatters, "I didn't realize the "size 00" trend in fashion models extended to men. All these dudes modeling for Dolce & Gabbana's suits look like they've got corsets on under there."
Himmel whiiiiiiiines: http://tinyurl.com/8jrwjqm
Duelist growls quietly, "Apple has a HUGE patent litigation budget. THat's how they innovate."
MegaWolf growls softly, "I'm going to laugh so hard when the Apple bubble finally pops"
Azure yips, "The iPhone 5 is a fairly good sign it's starting to."
Kia says, "This will make you feel better, Miko. http://worldwideinterweb.com/component/k2/item/1444-the-ultimate-runway-model-fails-compilation.html"
Mundy shows http://www.digikey.com/product-detail/en/CD14538BE/296-14074-5-ND/525847 to TIGRSKNK.
Himmel says, "Social apps are really popular."
Miko chatters, "Poor girls."
Duelist O.O
Kuttas idles.
Mundy says, "I think I'm gonna order some of these on Monday."
Duelist growls quietly, "What is that?"
Himmel says, "Multivibrater?"
Himmel says, "Vibrator, rather."
Mundy says, "Imagine the breadboard pic I showed you, shriveled up into a single IC chip, with power and LEDs connected to it."
Kia's favorites, in order, are: the one who walks off the stage, the one who falls into the pool, and the one who gets hit by the giant pendulum.
Duelist huhs.
MegaWolf gets a headache looking at digikey's website
Kia idles briefly.
Mundy says, "Cheaper and easier."
Kuttas has been saying multivibrator all along. Monostable, bistable, and astable.
Duelist growls quietly, "How is this useful to me?"
Kuttas now idles
Himmel rub Yenaears.
Duelist growls quietly, "Is true! Y3NA has been saying that!"
Mundy says, "More useful to me, because it'll be easier to work with.  But produces the same results."
Mundy says, "And you didn't go to Y3NA to make these? :)"
Duelist growls quietly, "I did! But Y3NA is a hard workin' yena and is busy!"
KurtMRufa licks its nose.
Mundy says, "Also.. You gonna be using N-Scale switch lights?"
Miko nuzzles and goes to bed. He was intending to get up five hours from now, but guesses he'll sleep in.
Miko winks out of sight in the sparkling glow of a space/time rift.
Miko has left.
Somewhere on the muck, Miko has disconnected.
Srass helps Kurt lick its nose.
Srass compares and contrasts the taste with that of Kuttas' nose.
Duelist growls quietly, "I was just gonna use LEds"
Mundy says, "Little tiny LEDs with wires running to the controller?"
Duelist growls quietly, "Sure!"
Acy sees his piglet looking at him!
Acy daaaawh!
Acy wrassles with little piglet!
Mundy needs to know stuff before building anything. ^.^;
MegaWolf hrms. Video won't run for him despite telling Noscript to "allow all" five times in a row.
Duelist growls quietly, "Let me see here"
Mundy says, "Like.. Where are these controller modules gonna be located?  At the switches, or at a central control spot."
Duelist growls quietly, "Man, wiring a train is a bitch!"
Duelist growls quietly, "CEntral control spot"
Kuttas wriggles his nose. His nose tastes like hyena and [redacted].
MegaWolf growls softly, "I should probably upgrade firefox"
Srass tastes hyena repeatedly.
MegaWolf growls softly, "I'm still on 3.latest"
Kuttas tastes more and more like hyena. He noses along Srass' gigantic panthernoggin.
Srass rumbles, and paws gently at Kuttas.
Kuttas wraps his arms around Srass' neck and clings close.
MegaWolf's still annoyed with Firefox suddenly jumping 10 numbers in a year or so
Srass hugs Kuttas close.
Mundy says, "Hmm.. Also.. How many blinken lights per switch track are we looking at?"
Duelist growls quietly, "Blink?!"
Azure yips, "Well, yeah, that was a stupid decision."
Duelist growls quietly, "They don't blink!"
Azure yips, "I blame Google."
Mundy biteys TIGRSKNK.
Mundy says, "One pair per switch?"
Kia prrs at Otello. So dramatic.
Duelist growls quietly, "I don't understand!"
Duelist growls quietly, "Hang on...."
Kia looks forward to seeing one of the Three Tenors conduct it.
Kia, pleased to have seen Placido sing in The Mysterious Island, too.
Duelist - http://tinyurl.com/8et2ff6
Mundy says, "You have two LEDs.. One indicates left-side, the other right-side."
Duelist growls quietly, "The LED determines which side is open"
Mundy says, "So these LEDs are gonna be on the 'main control'."
Mundy says, "Nothing out there in the model?"
Mundy says, "Also.. This begets another question.. Are you gonna have a control panel for the switches like that pic?"
Skylos has disconnected.
Skylos has connected.
Duelist growls quietly, "Yes"
Mundy says, "Okay."
Mundy says, "This is a critical bit of info for the enclosure of the controller. ^.^"
Somewhere on the muck, Tigerwolf has disconnected.
Himmel orgasms in his ears.
Somewhere on the muck, Tilton has connected.
Somewhere on the muck, Rollo has connected.
Dachande. says, "Ugh i hate getting that out of my ear, harder than up the nose"
Makyo hands out cheek-kisses, because you all are wonderful.  Will idle here, again, until disconnected for exactly the same reason.p #away Snoozin'
Mundy says, "Or inbetween the keys."
Kyhwana mrrp
You say, "fuck phones"
Kuttas climbs up on top of Srass and sprawls.
Mundy ponders tiny little black boxen with screw terminals all over.
Himmel snugs Makyo.
Away message and away flag are now set.
Srass reaches up and pets Kuttas, lazily.
You say, "just trying to set away :S nighty for real"
Duelist smooch Makyo!
Kuttas pets Srass back, sprawling lazily.
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Rollo arrives from the foyer.
Rollo waves gently
Skylos softly barks, "Rollo!"
Skylos hugs otter
MegaWolf licks the not-asleep-Makyo :>
Rollo churrrs, and hugs the nice doggie
Skylos smiles and petpets the nice otter.
Kia checks on the shipping status of his lifetime supply of lube.
Kuttas kinda craves Chinese food again
Skylos softly barks, "a 55 gallon barrel of j-lube powder?"
Makyo just a paranoid fox.  Very.  REally bed now, though y'all can keep the resmooching.
Kia says, "An 8+1 pack of bad-dragon cumlube clear. "
Himmel would enjoy a bad dragon product.
Kia checks on the shipping status of his outrageous order of large silicone appliances.
Acy says, "Night kids."
Duelist o.o
Acy has disconnected.
Kia has a bad dragon product. Likes it, more or less. Not a huge fan of the knot, though.
Kuttas wonders which one.
Himmel probably wouldn't require a knot.
Kuttas pets Himmel. "Silly cat."
Himmel says, "The Dragon Toys are particularly appealing."
Himmel says, "As is the Gryphon."
Kia hmms and thinks he's going to get a fucking huge delivery of a) lube, b) huge fucking silicone toys and c) snuff on Monday.
Himmel is soft.
Skylos softly barks, "tell me of the silicon toyes"
Kia has the Faerie Dragon. http://bad-dragon.com/products/elden
Skylos but you getting new ones?
Dralen wants to get a new Bad Dragon toy, but can't afford it.
Himmel oooooooohs.
Himmel says, "The Earth Dragon looks veeeeery nice."
Kuttas shakes his head. "Ridged are not cool...
Himmel | http://bad-dragon.com/products/clayton
Kia whispers about things to Skylos. None of the rest of you need to know about his perversions.
Duelist is keen on Bad Dragon. Great business model.
Rollo has disconnected.
Kuttas says, "Oh? What's their business model?"
Kia says, "Sell perverted sex toys to perverts. "
Himmel oooooh: http://bad-dragon.com/products/cole
Duelist growls quietly, "Well, the artist draws lewd porn to get his fans all hot-n-horny"
Duelist growls quietly, "Then, all of a sudden,you can buy the dick featured in the lewd porn!"
Kuttas cackles.
Kia thinks that the lewd porn looks like everyone is made of rubber.
Duelist growls quietly, "It's a great idea."
Duelist growls quietly, "And, clearly, it works."
Duelist growls quietly, "Then you 'buy' a popular porn site and get free advertising."
Dachande. says, "Oi none of them dragon toys look like they'd be good up the ass."
Kuttas says, "They own a porn site?"
Himmel says, "For vids of people testing toys."
Himmel says, "Well. Using, not just testing."
Kuttas says, "Oh. Hmm."
Skylos softly barks, "I LOVE my dragon toy 'bruiser fusion' up the ass.  And my drippy dragon.  And my david the werewolf."
MegaWolf growls softly, "Whowhuh?"
Kia quite likes his Eldon, but again... lemur seems not to work well with knots.  Apparently he has the "made to be fucked by horses rather than dogs" gene.
Himmel is also rather enamored with that one, Skylos. And also, the liger.
Himmel says, "Bruiser and David, I mean."
MegaWolf @.@
MegaWolf stays outta this one. n.n
Kuttas says, "So, anyway."
Kuttas says, "How 'bout them Royals?"
Duelist growls quietly, "They're no good, man"
Kia supposes he needs to get himself a Reds hat.
Himmel says, "They suck."
Kia, sort of hoping for the Yanks to flame out so that he doesn't get stuck with a Reds-Yanks world series.
Skylos softly barks, "I think I can see the pattern though Kia."
Duelist growls quietly, "Oakland A's. That's the team!"
Skylos softly barks, "the less emphasized the knot the more fun it is."
Kia frinks?
Skylos softly barks, "Like I have a bad dragon 'ridgeback' original design"
Skylos softly barks, "that's FRICKING AWESOME to be fucked by"
Skylos softly barks, "Its just really hard to find somebody who will fuck me with it."
Kia says, "No, it's not that. The knot is pleasant enough, but once it's in you just feel really full... and then ou have to get it out again. And that is less fun. "
Skylos softly barks, "I even wrote a fan fiction about it."
Skylos likes to play with sliding knot in and out.
Skylos softly barks, "http://dogpawz.com/skylos/indexes/title-dragoncock.html"
Duelist sits by Kuttas. He got no idea about these toys. He just uhh....has sex. Heh.
Kia likes a bit of that feeling of pulling inside, but the knot thing is too much. Also, we are totally going to get bitched out fby someone for breaking the rating in here, right? Didn't that happen a few nights ago?
Skylos softly barks, "duelist has a partner that will have sex with him."
Kuttas says, "So, yeah. How about we spare the graphic descriptions of what you do with your toys, eh? PG-13 and all."
Skylos softly barks, "that's a nice thing to have."
Kia, psychic.
Himmel decides to save up for Clayton. Nods.
MegaWolf blinks.
Kia doesn't like Clayton. Ugly.
Kuttas says, "I'm not bitching anyone off, Kia. You can get off your horse now."
Kia was on a horse?
Kuttas nudges Duelist.
Kia thought he was on a boat.
Floid suggests the Zeta tiger, anyhey.
Kuttas says, "I kinda want chinese food."
Skylos softly barks, "clayton looks nice and ripply."
Himmel disagrees, Kia!
Duelist hms! "Do they have Chinese food up there?"
Himmel says, "No, D. It's all Whale Blubber."
Kuttas says, "Of course! As much as anywhere, anyway."
Kia says, "De gustibus, Himmel. "
Floid says, "Also, wait, wait."
Floid says, "Kia, you just ... you're into SNUFF PORN?"
Dralen says deeply, "I thought you enjoyed riding your horse, Kia :D"
Kia says, "No, no. "
Dralen says deeply, "Nono, Floid. Snuff the tobacco format."
Floid says, "That was the pun kids."
MegaWolf growls softly, "Man, anime with half serious realistically drawn characters and half cartoony emoticon/Snarf characters is just annoying to watch."
Himmel snickers.
Kia says, "https://mistersnuff.com/"
MegaWolf growls softly, "Visually annoying."
Floid says, "It was basically the worst pun ever, hence the warning shot."
Kia may or may not have a small collection of HorseMage pics, but that's beside the point.
Duelist peers at Kuttas! "I am surprised by that. Are there any places open right now? Delivery?"
Kuttas says, "Yeah, but they won't deliver out here in the sticks. I'll have to go in. The Buffet is open until 10:30"
Duelist hmms! Buffet!
Floid also scrolls up.  Do not underestimate the popularity of the iPhone 5.  Everyone at the office wants one even though they do not know why.  Fashion symbol + this year's Buick.
MegaWolf nips Floid's dingo-y parts
Duelist do like buffet!
Dralen lives in Chinatown in Toronto. Can get Chinese food until about 3am.
MegaWolf growls softly, "Dingos!"
Kuttas does, too. He eats like a hyena. c.c
Floid says, "I cannot totally bitch about the 'we ran out of other things to do so we started figuring out how to improve the voice quality' part, though."
Kia shows up at Dralen's for dim sum.
Floid says, "That'll be nice when it trickles down into cheapphones."
Kia does not like NY chinatown. It's filthy, smells bad, and is crowded. Plus, it's full of Chinamen.
Floid says, "It does have That Smell to it, whatever that is."
Kia says, "Plus, it keeps expanding. "
Kia doesn't even understand it. Chinamen shouldn't be able to afford Manhattan.
MegaWolf growls softly, "Little Italy is now Little Tokyo"
Floid says, "Culturally I think the haggling thing runs deep there."
Floid does not recall much Tokyo there, Mega.
Kia says, "Nah, Little Italy is still there, but it's basically Disneyland. "
Floid says, "LI is down to one street, like, though.  Is Puglia's still there?"
Kuttas says, "They have those little sugar-stuffed doughballs rolled in sesame seeds. They're delicious."
Kia says, "A couple blocks of red sauce restaurants. "
Dralen says deeply, "We'll go for dumplings next time, Kia."
Kuttas says, "Plus the steamed pork dumplings that remind me of mandu."
Kuttas says, "Hmm... perhaps I should go to the Korean restaurant, instead. I haven't had kimbap in forever."
Kia has occasionally wound up in Chinatown when running southwest. He's never happy about it. He's actually given up on running that direction--has realized that, while hitting USq sucks, it's like two blocks of pedestrian congestion. SoHo is block after block after block of hell.
Himmel purrpurrpurr, Kimbap.
Kia once wound up in TriBeCa when running southeast, which he almost never does. Lemur was lucky to make it back home.  The streets down there make no sense.
Kia says, "And it's not like the Village, where at least you can occasionally sight off of the Freedom Tower. "
Kia says, "No landmarks at all. Just lots of little streets going off in no direction at all. "
Kia finally found the FDR and walked home.
Dralen had good Ethiopian the other day. "I'm lucky... I live in a neighborhood with just about any kind of major cuisine you could name.
Dralen says deeply, "In under 10 minute walk."
Dralen says deeply, "Under 5 for most."
Kia has that here too.
MegaWolf growls softly, "We have chinese and seriously overpriced thai"
Kia tried to take the ex for Ethiopean once. The walk was five minutes. The wait at the restaurant was more like 30
MegaWolf growls softly, "And chain restaurants"
Kia still needs to get someone to go provide moral support for his battle with phaal.
Himmel says, "Pride goes before the Phaal."
Kuttas points at the lazing sleepers and goes all tribal, shouting, "Ki'i ki-rharg, ki'i etya stye ngyet-ngye!"
Rollo is sent home.
Rollo has left.
Khyber growls and lets the broom sweep him into a portal, but not before snapping it's handle.
Khyber has left.
Acy is sent home.
Acy has left.
JanusFox takes the hint and heads off someplace more quiet.
JanusFox has left.
MegaWolf squeek-meep Dralen
Kia wants to get on the Phaal of Fame.
MegaWolf noms on Floid, because dingo.
Somewhere on the muck, Triggur has reconnected.
Kia says, "Dingos nom on others. Mostly babbies. "
Kia says, "How are they formed, anyway? Babbies, I mean. Not dingoes. "
Himmel says, "How -is- babby formed?"
Kia wants to know how girl get pragnent.
MegaWolf pokes at Floidingo, who doesn't really seem to do much of anything at all.
Dralen smooches on Mega.
MegaWolf growls softly, "I think I should exchange him"
Kia gives Floid a pinch of snuff. Porn.
KurtMRufa teleports away.
KurtMRufa has left.
Somewhere on the muck, KurtMRufa has disconnected.
Kia says, "Benoit."
Dralen says deeply, "Balls."
Dralen says deeply, "See? It's automatic."
Kia kisses Dralen. :)
Dralen grins.
Mundy says, "Babby ate my balls."
Kia is going to introduce a coworker to Archer tomorrow.
Kia has already given her The Big Lebowski. Not to be confused with the Dude, or His Dudeness, or Duder, or El Duderino if you're not into that whole brevity thing.
Kuttas drapes over Srass.
Srass curls around and nuzzles along Kuttas.
Kia manages a 3/5 on the Composers edition of Truth or Fail.
Floid awws, his scrollback doesn't extend all the way to 'before he connected and immediately went to sleep.'
Kia hates that the vlogbrothers do not do all of the Truth or Fails. >:(
MegaWolf's fortune cookie is "The suspense is exciting. I hope it last."
Floid also had the experience of WTF Tribeca, come to think of it.
MegaWolf growls softly, "Does anyone make fortune cookies that actually tell fortunes anymore?"
Srass says, "Yeah, I see them all the time at the place I go to."
Duelist always gets cookies that say 'some damn woof will need biteys today'!
MegaWolf bop Duelist!
Kuttas idles to see why his alarm clock is going off.
Duelist growls quietly, "Pretty accurate!"
Duelist bitey MegaWoof!
Floid says, "Duelist the Poodle."
MegaWolf doesn't do anything bad but tigers and skunks bitey anyway!
MegaWolf growls softly, "Duoodle?"
Srass says, "Doodle!"
Kia pffs. 2/5 on Cats.
Duelist oh yeah!
Duelist feelin' FOXY!
MegaWolf kisses Duelist instead!
Duelist bitey MegaWoof!
Duelist growls quietly, "Now you got bitey from a fox too"
MegaWolf *smewch!*
MegaWolf growls softly, "Foxes are hot too :>"
MegaWolf nibbles all over fox ears!
Mundy says, "Maybe you should eat him, FOX."
Duelist ew!
Mundy says, "Hah"
MegaWolf flicks Mundy woof's nose
Mundy says, "Season him with dragon spoo first? ;)"
Duelist hms!
Duelist growls quietly, "Says the guy with the drum."
Kia grrrs. 3/5 on Muppets.
Mundy drops Mundy's Spooge Drum of One Hundred Gallons.
Kuttas climbs into the spooge filled drum with a thick *SCHPLUT!*
Kuttas has left.
Mundy <.<
Mundy says, "Kuttas says, "I found a penny!""
Kuttas arrives from the foyer.
Kuttas c.c
Kuttas found a penny in there. TOTALLY worth it.
Srass says, "Be sure and wash it off."
Srass says, "Or go back in and spend it. c.c"
Kuttas says, "Spend it? On what?"
Kuttas rubs on Mundy.
Duelist muhahaha!
Floid says, "You just put it in that slot at the tip of his dick and see what comes out."
Srass says, "'Spend a penny' is a British idiom for taking a piss."
Skylos softly barks, "Kind of like seeing a man about a horse"
Kuttas hmms. That sounds vaguely familiar.
Floid finds http://www.furaffinity.net/view/8840919/ for Mega.
Somewhere on the muck, Tony_Cheval has disconnected.
Duelist hah!
Dachande. tilts his head... "That buldge is off."
Dachande. says, "It's like he has a sock in there."
Paladin barks, "He needs heelpads."
Dachande. says, "That too"
Dachande. says, "Everything is good except the crotch, the extra ass cheeks, and the heels"
Srass squints.  "Extra ass cheeks?"
Kuttas says, "Probably best not to ask..."
Srass says, "Someone paid for that. o.o"
Kia'd see a man about a horse.
Kia'd also buy that for a dollar, but not *that.*
Dachande. says, "This is why you pay after you find out they look like they have a sock stuffed in their testicles."
Kia notes that if his mother was a sculptor, equestrian statues would looks slightly different.
Dachande. says, "More vag?"
Mundy says, "Here's a commission horror: http://www.furaffinity.net/view/7019725/ :)"
Dachande. says, "I swear I can read the sarcasam in post 4"
Himmel says, "Eh, there are people who would slobber over that."
Kia says, "Mom hates dogballs, so I assume she'd hate horseballs too. "
Dachande. says, "I blame my current inner monologue."
Kia says, "And equestrian statues always have horseballs. "
Srass says, "Your mom has tried dogballs?"
Dachande. says, "Of course they would have horseballs, they're a classic symbol of fertility."
Kia says, "In Russia, near St. Isaac's, there was this building... it didn't just have horseballs. It had horse sheath with plainly visible horsecock inside, complete with horse urethral process. "
Srass o.O
Dachande. says, "And lemur fingerprints? :D"
Kia wanted to take a picture, but was shy. <:)
Kia says, "Always it's a bit awkward with horse genitals. "
Dachande. says, "Ehh they are probably used to tourists from a prude country being surprised at the casual nature at which their country acceps the items that exist in reality on bodies."
Floid needs to upload merhorse dong that was down the street from the office for city art-horse-event-thing still.
Paladin ponders urethral process.
Mundy kisses Paladin!
Kia says, "Russia doesn't really have tourists, because they make it really fucking difficult. "
Kia would've also liked to have taken a picture of the Belgian mares, but... well, he took a picture of one's face. Not the other end. <:)
Kia says, "She did have a pretty face.  But one does not just take a picture of a Belgian police mare's ass. "
Kuttas has left.
Kuttas arrives from the foyer.
Dachande. licks Kuttas!
Floid frowns at being 'home' which results in being handed drafts to read at 1:35AM on a Sunday and told what he'll be doing tomorrow.
Kia thinks Floid is continuing to exemplify why families should never have businesses.
Kia says, "Perhaps somewhat less than crazy bitch I have to deal with, but. "
Dralen says deeply, "There's a good result for a commission: http://www.furaffinity.net/view/8845139/"
Kia wishes that crazy bitch was as crazy in person as she is in email. IN person, she's charming. In email, she leads to me drinking myself stupid and cutting myself.
Srass says, "That's definitely an improvement."
Kia worries that, if he gets job at not fox, crazy bitch will become a friend's responsibility. No one should have to deal with crazy bitch.
Srass is rather fond of this particular commission, too, but he forgot who tipped him off to it: http://www.furaffinity.net/view/7118610/
Kia thinks this commission is awesome. http://www.furaffinity.net/view/4172160
Duelist bedtime!
Duelist licks Kuttas!
Duelist licks Srass!
Himmel says, "Dem balls."
Srass licks Duelist!
Himmel pet Duelist.
Duelist growls quietly, "You two be 'good'! >;)"
Duelist growls quietly, "Nite all!"
Srass says, "Aw, man!"
Kuttas hugs Duelist.
Kia asks you all to remind him to take his contacts out before bed.
Kuttas says, "Who us? O.o"
Duelist nods! 'good'! Note the quotes >;)
Kuttas c.c
Duelist grins.
Duelist goes home.
Duelist has left.
Himmel will, Kia.
Srass tries to imagine lemur contacts.  They must be the size of dinner plates. o.o
Dachande. says, "It is nice seeing nuts in a size 15."
Srass says, "That's a nifty looking one, Kia, but... Man, those feet look nearly gollumesque somehow. o.o"
Somewhere on the muck, Triggur has disconnected.  (But they're still online.)
Kia felt bad for Bryn Teufel watching the Ring. That blackout contact on his eye looked really uncomfy.
Kia gives Srass two big toes up.
Srass giggles.
Kia continues to love his favorite Warren Zevon song.
Kia says, "Even as it gets ever closer to my life. "
Kuttas should probably go get food. Probably too late for Chinese.
Dachande. likes this commision, http://bit.ly/RTYhu1
Skylos winks out of sight in the sparkling glow of a space/time rift.
Skylos has left.
Dralen says deeply, "Never too late for Chinese... in my neighbourhood, at least."
Kuttas would totally encourage someone commission him if he didn't suck at drawing
Kia looks away down Second Avenue.
Kuttas says, "It closes early here. Well, not terribly early."
Kuttas says, "But too soon for me to haul ass in and eat."
Dachande. digs it because friend randomly did it for him, and added the cyan, which i kinda like.
Dachande. needs a real scan of it.
Kia peers at this and wonders if he'll have a scar.
Dachande. says, "You can rub sand in it if you want one."
Dachande. says, "Kitty sand works best, the infection helps the skin panic andd grow faster which results in the scar tissue formation."
Dachande. says, "Also the weeping puss will prolong the seperation of skin which agian, scar tissue."
Kuttas says, "Dach, you've got issues. o.o"
Floid says, "So that's how you got that nevus in the shape of Bob Dobbs."
Kia doesn't, really.
Dachande.:D
Kia says, "Just... well. Never mind. I'll spare you the crazy talk. "
Floid offers some Bactine, anyway.
Kesareya arrives from the foyer.
Kesareya pads in and flops.
Floid snugs on a Kes, tiredly.
Malkoten arrives from the foyer.
Malkoten flops.
Vetiver pats Malkoten.
Kesareya licks over Floid softly.
Floid says, "Vrrf."
Kesareya smiles and licks one of Floid's ears.
Srass strokes Malkoten.
Dralen okays. Falling asleep means bed time.
Kesareya says, "Aww, nini, draggy."
Srass hugs Dralen!
Srass says, "'Night!"
Kuttas noses Dralen. "Rest well."
Dralen smooches on Srass and Kuttas, and fuzzles all the length of Kia's tail.
Malkoten curls up around Srass trap like.
Dralen swishes his tail, and is gone.
Dralen has left.
Dachande. says, "AH well off to bed guys, ya'll take it easy."
Paladin cuddles Dachande.!
Srass says, "Same here on both counts."
Srass earscritches the lot of you.
Srass is set upon by amorphous, eyeless chartreuse anthropods of no distinct species, and vaguely tribal-looking garb.  He is quickly bound and gagged, and dragged off by his ankles, struggling and trying to curse through the gag.
Srass has left.
Himmel says, "g'nigth."
Kesareya has left.
Malken has disconnected.
Floid hrh.  Apparently he's been doing the protein-shake thing long enough that his body doesn't know what the fuck to do with a huge wad of pasta.
Lion_Cub arrives from the foyer.
Lion_Cub mehs.
Floid hm.  Or he could've easily picked up some crud from dealing with visiting (and vacuuming portions of) dog-dust house and so on today.
Floid says, "So much loose DNA flopping around."
Kuttas mehs, also.
Floid applies some Purel, then pets L_C.
Lion_Cub craps, reading about Margaras.  "That's awful."
Kuttas nods.
(p) In a page-pose to you, Lion_Cub hugs. "Ugh.  Thanks for posting the obit."
Kyhwana nods at LC x.x
Floid then pets more.
Kuttas mehs again, abruptly fighting off tears once more.
Kuttas sighs.
Lion_Cub sorries. "I didn't mean to bring it up again."
Kuttas says, "No, no worries."
Kuttas says, "I've been doing this all day. I've still got his picture open on my desktop."
Himmel squeezes Kuttas.
Malkoten snugga LC!
Malkoten rumbles, "Just so you know LC, yer not allowed to die."
Lion_Cub noses a panther.
Lion_Cub purrs, "I hope you hold me to that."
Malkoten waggles his eyebrows
Lion_Cub curls up beside panthers. "Folsom is next weekend."
MegaWolf has disconnected.
Malkoten has never been.  Far too Canadian.
Lion_Cub frowns. "I went with Andreal, once." x.x
Malkoten rearranges that so it makes more sense.  Too far, Canadian :D
Malkoten rumbles, "what's it all about?"
Lion_Cub purrs, "The leather and what not."
Kia whistles for a taxi...
Kia leaves via the quiet Taxi service.
Kia has left.
Zhorah stirs
Himmel bed.
Himmel winks out of sight in the sparkling glow of a space/time rift.
Himmel has left.
Vetiver goes home.
Vetiver has left.
Floid also would've accepted "Far.  Canadian, too."
Somewhere on the muck, Azure has disconnected.
Kuttas slips out
Kuttas has left.
Somewhere on the muck, Herefox has disconnected.
Lion_Cub winks out of sight in the sparkling glow of a space/time rift.
Lion_Cub has left.
Somewhere on the muck, Lion_Cub has disconnected.
Floid tries something sleep-related again.
Floid has disconnected.
Zeph arrives from the foyer.
Zeph rowr.
Kyhwana meow
Paladin barrrrk.
Zhorah has disconnected.
Somewhere on the muck, Tilton has disconnected.
Kareb arrives from the foyer.
Scruff arrives from the foyer.
Scruff chirps!
Zhorah is sent home.
Zhorah has left.
MegaWolf is sent home.
MegaWolf has left.
Floid is sent home.
Floid has left.
Malken raises a warding finger, and says serenly,"Do not bother, I can provide my own transportation."  He then disappears in a swirl of darkness.
Malken has left.
Scruff leeeans in against Malks
Kyhwana chirp atta Scruff
Scruff hugsaleopardtail
Paladin barks, "Spots and dots."
Scruff has those! Although some of them are more like smudges o.o
Paladin has fluff and ruff.
Paladin barks, "Though I do have a spotty dawg laying around."
Zeph mews, "Mornin' Scruffles!"
Kareb has disconnected.
Scruff chirps, "You're a snowleopard again! <3"
Zeph is! He rekatted.
Malkoten unidles
Malkoten hugsa Scruffs, could use cuddles ^.^
Malkoten thinks he's gonna head to bed now.  2 am is bed time *nods*
Malkoten winks out of sight in the sparkling glow of a space/time rift.
Malkoten has left.
Scruff sneaksouttoo
Scruff teleports away.
Scruff has left.
Somewhere on the muck, Scruff has disconnected.
Himmel arrives from the foyer.
Himmel says, "The sandman and I have had a disagreement."
Himmel whistles for a bouncer, and when it comes near, the nametag says, "Fresh," and it has dice in one ear.
Kareb is sent home.
Kareb has left.
Somewhere on the muck, Triggur has disconnected.
Zeph has disconnected.
Kyhwana lifts up the rug and pushes all the sleepers under it.. he jumps on it a few times and the rug goes flat
Zeph is sent home.
Zeph has left.
Kyhwana durp
Undine arrives from the foyer.
Himmel says, "Hey, Unds."
Himmel says, "Did you hear?"
Undine says, "What?"
Himmel says, "About Margs."
Himmel gestures toward the message board.
Kyhwana mrps at Undines
Draconis arrives from the foyer.
Draconis mwrf.
Undine says, "Thanks Himmel."
Draconis sad :(
Himmel rubs Undine.
Himmel and Draco.
Draconis nuz.
Himmel rubs Dracosnout.
Undine has connected.
Undine has disconnected.

You have been logged out due to inactivity.

% Connection to furry closed by foreign host.
\end{verbatim}
