The one thing we did together that we both seemed to earnestly enjoy was skiing.

\begin{quote}
There were other things you enjoyed.
\end{quote}

Together?

\begin{quote}
Reading, perhaps?
\end{quote}

He tried to get me to read \emph{Flowers for Algernon}, but I wound up skimming parts, enough to keep him happy when he asked me about them, all while reading the copy of \emph{Mossflower} I'd hidden down the back of the couch. The closest we got was reading \emph{The Dark Tower}.

\begin{quote}
Catch?
\end{quote}

One-sided and short-lived. We played a few times. Then, after telling me to ``get under'' a fly ball, it hit me square on the forehead and he laughed, telling me I was supposed to get my glove up, too. We never played again.

\begin{quote}
The dogs?
\end{quote}

Dad used to punish the dogs by locking then in the basement. If he was really mad, he'd toss then down the stairs by the scruff.

\begin{quote}
School? Math? Computers? Being smart?
\end{quote}

Listen.

You have to understand that there were only two valid emotions for my dad: pride and anger. Being good at computers and math was not something that was enjoyable in its own right. Not for the both of us. The part that we shared there was that we had to have something we could declaim about. Something we could pull out and show that we might be proud of it.

\begin{quote}
So you went skiing, because you both were about the same level at that.
\end{quote}

I bounced, he didn't.

\begin{quote}
That's a factor of your age and size. I don't think you actually bounce all that well.
\end{quote}

Fair.

You're right, though. We went skiing together because that was just sort of the thing we enjoyed --- for different reasons, I'm sure --- and it just so happened that we enjoyed doing it around each other, too.

There would be mishaps, of course. Forgetting boots or poles was a big one. I forgot my poles once and thought I'd be found, dead, in the woods later that day. We wound up renting a pair. From then on, I was determined to learn how to ski without them.

\begin{quote}
It turned out to be fun, at least.
\end{quote}

Yes.

We fell into a habit. Go skiing every other weekend, since that was my time staying with him, from late fall to mid spring. We'd make the drive from the suburbs west of Denver up into the mountains. We'd hit Winter Park, our favorite, or we'd maybe run over to Arapahoe Basin or Loveland Pass.

We'd ski from nine in the morning until about three in the afternoon. We'd grab lunch. Dad would grab `beer-thirty' a little bit after that and let me do a few runs on my own while he chatted up a bartender.

\begin{quote}
You would get the buffalo green chili every lunch, when you wound up at Winter Park. At Loveland, it would be the build-your-own pizzas. It was all so routine.
\end{quote}

It was the most comfortably routine thing that we did together. Not even school could top that.

\begin{quote}
It was, above all, pleasant.
\end{quote}

At times.

\begin{quote}
Yes.
\end{quote}

At times it was stressful. At times it felt like we were going skiing so that my dad could take some time away from home, away from Julie. At times, when Julie came with us, it would be more stressful on the slopes than it was at home.

And then it fell apart.

\begin{quote}
Yes,
\end{quote}

There's no one time I could point to and say, ``Ah-hah, \emph{this} is when things fell apart.'' There were a few indicators, to be sure, but no one single instance.

There was only that last ski trip to Steamboat.

\begin{quote}
When?
\end{quote}

My birthday.

\begin{quote}
Which?
\end{quote}

I don't even remember. Middle school? Freshman year of high school?

\begin{quote}
Had life started yet?
\end{quote}

It must have. It must have been high school, then. It must have been spring break. It must have been, because I could drive, then. Dad made me take my turn driving his new truck while he sat in the passenger seat and drank glumly. Tecate after Tecate. Julie sat in the back and stayed quiet. Even then the cracks were showing in their relationship.

\begin{quote}
It started snowing on the drive.
\end{quote}

Yes.

\begin{quote}
You drove a fraction of an inch too close to the shoulder, your right wheel veered from the dark tracks plowed through the thin layer of snow by the car in front of you. He shouted, ``Pull over at the next exit, if you're going to drive like that. Snow could cause too much drag on the tires and drag us off the road.''
\end{quote}

Yes.

\begin{quote}
He was drunk and in pain. His shoulder again. He yelled at Julie. Told you both to let him drive in silence.
\end{quote}

Yes.

\begin{quote}
When you got to the condo that you'd rented. He took four or five advil with a Corona, apologized sullenly, and went to go lay down.
\end{quote}

I don't remember any of the rest of the trip. All I remember is that we watched \emph{Fellowship of the Ring} and that, at one point on the drive back, I asked a question about angular momentum.

\begin{quote}
You wanted to promise him, visibly, that you were still smart. You wanted to appeal to him in a way that you knew he'd take well.
\end{quote}

I wanted him to be okay with me.

\begin{quote}
Dig deeper.
\end{quote}
