When I was getting ready to leave bConnected, I started struggling with movements. It started as a twitchiness in the hands. It started with a wringing of the fingers. It started with a slight nod of the head. It started in so many tiny ways that I didn't really put together.

Twitching, twitching. Screw lorazepam. Gonna walk the dog instead :D

--- Maddy, whose tail is behind her (@drab\_makyo) August 19, 2012

\begin{quote}
Twitch twitch.
\end{quote}

Yeah.

\begin{quote}
And how does this tie in with your dad, again?
\end{quote}

Getting there.

\begin{quote}
I'll be patient.
\end{quote}

Good.

The twitchiness grew worse. It grew to a jerk of the head to the side. It went from the occasional thing to something that hit every second and a half or so. It started impeding my speech. I started stuttering. I lost my balance and had to use a cane for a while.

\begin{quote}
It came and went. Not all of that happened at once.
\end{quote}

When I think back on that time, it's just a smear of time from when I got the offer at Canonical and Further Confusion 2013 a few months later. There are bits of time that stick out as being particularly tic-filled, of course, and bits of time I know I was free of it.

\begin{quote}
You were free of it in Montreal, at your intro sprint.
\end{quote}

Yes, and it came back during UDS in Copenhagen. It came back and it stayed.

\begin{quote}
Did it?
\end{quote}

For our purposes here, yes, it did.

\begin{quote}
`Our'?
\end{quote}

Listen. When your body rebels and tries to shake your brain out through your ears and dislodge your eyes, when your friend dies in a car crash and you only find out about it a week later, when you start a brand new job and fly all the way across the country, getting stuck in London along the way, time stops making a whole lot of sense. At some point, I had the tic, and it stayed.

\begin{quote}
Touchy tonight, aren't we?
\end{quote}

You're being as helpful as ever.

\begin{quote}
Not my department.
\end{quote}

At some point during this whole process, Thanksgiving rolled around and I went to visit dad.

\begin{quote}
Oh.
\end{quote}

See?

I emailed him ahead of time, warning him that I was struggling with a transient tic disorder caused --- or at least exacerbated --- by one of my medications. I felt so embarrassed, to be seen by him like that.

\begin{quote}
Like what? Vulnerable?
\end{quote}

Yes. To be seen as week by someone who placed so high a premium on strength.

\begin{quote}
He was hardly a body-builder.
\end{quote}

Well, no. Not physical strength. Moral, perhaps? He certainly prided himself on his composure, and this was me in a state where I was literally unable to maintain my composure.

\begin{quote}
At least you had an excuse for avoiding eye contact.
\end{quote}

It was, oddly, a fairly calm and cozy evening. JD came with. We had some turkey breast. I brought a bottle of bourbon and some homemade cranberry sauce. We talked.

\begin{quote}
It was nice.
\end{quote}

It was. This was at the time in my life where I was learning what the proper amount of `dad' was that I could handle. About three hours. Maybe a little more. Any more than that and we'd both fall back into our old habits. We had much better reunions than we did an ongoing friendship.

\begin{quote}
And you drank, then.
\end{quote}

Yes.

\begin{quote}
You laughed when you knocked the bottle of bourbon off the counter and immediately caught it before it fell to the ground. ``The tic has led to my reflexes getting better,'' you said.
\end{quote}

Dad didn't quite know how to accept me acknowledging my vulnerability.

\begin{quote}
It was nice.
\end{quote}

In a smirking sort of way, I guess. In a \emph{oh wow I'm different now} way. In a \emph{I guess I'm finally starting to grow out of being your son} way.

\begin{quote}
Matthew had died.
\end{quote}

Yes. Matthew had died, and we were doing Thanksgiving together.

\begin{quote}
It was nice.
\end{quote}

It was. He had come to the wedding, so the truth was out, as it were, about JD and I, though he surely had known already. During one of his prior visits to Fort Collins, he had invited me down to grab dinner with him in Lakewood sometime, saying, ``You can bring your\ldots{}ah, you can bring James with you, too.''

\begin{quote}
Tell me about `man'.
\end{quote}

Matthew was dead. Madison was conceived. She would be born soon.

\begin{quote}
Dig deeper.
\end{quote}
