I talk up my style as frumpcore. \emph{It's the synthesis of momcore and downtempo librarian,} I say. In reality, It's an intentionally garbage-y, thrown-together look designed to, I hope, lead onlookers' eyes to slide right off of me as unremarkable.

\begin{quote}
Ah yes, the invisible six-foot-one trans woman with purple hair. That tired old trope.
\end{quote}

While I've had fursoñas that were intended to be something better than myself --- Makyo, for a while, was dressed in a nice suit --- more often than not, they've played along similar lines.

Ranna was a gay fox, a bit pudgy, with two tails he readily admitted were an early affectation to differentiate himself from countless other foxes.

Makyo was intentionally a transfeminine vixen who didn't pass.

Maddy's a dumpy, nerdy cis girl who dresses to hide her weight.

\begin{quote}
And Madison's a dumpy, nerdy transfeminine girl who doesn't pass and dresses to hide her weight?
\end{quote}

I suppose.

\begin{quote}
You don't give yourself enough credit.
\end{quote}

Is that your department, now? Cheering me on?

\begin{quote}
I'm your ally.
\end{quote}

But not my friend.

\begin{quote}
No, but I am your ally.
\end{quote}

Fine. How do I not give myself enough credit?

\begin{quote}
Firstly, you're not as invisible as you seem and frumpcore isn't seen as that cohesive from the outside. Secondly, you pass better than you imagine. Everyone tells you that, you just can't yet hear it. Finally, you just got done writing some heavy shit after a day of worrying about work, so of course you're down on yourself. You don't want to pass, remember? You want to be visibly trans. You want to be seen as the trans psychopomp you strive to be.
\end{quote}

\ldots{}Wow.

\begin{quote}
Your very words set lie to your insecurities. Your fursoñas are yourself expressed more earnestly than you can manage in person.
\end{quote}

Thank you.

\begin{quote}
If you could become Maddy, would you?
\end{quote}

Yeah, in a heartbeat.

\begin{quote}
Why?
\end{quote}

You said it as well as I could. She's the front-stage persona I wish were also my back-stage persona.

\begin{quote}
And she's pretty.
\end{quote}

I mean, she's still a dumpy fat nerd.

\begin{quote}
Let's talk about kink.
\end{quote}

Oh for Christ's sake.
