So, I think the order of my entry to furry was as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Find a furcode in someone's forum sig.

  \begin{quote}
  Oh my aching bones.
  \end{quote}

  Shut up, you're not that old, the internet just moves \emph{really} fast. Besides, you don't have bones.
\item
  Find a furcode decoder.
\item
  Find Captain Packrat's page on furry.
\item
  Find Yerf!.
\item
  Make a dragon character.
\item
  This lasts three days. No one pays attention to me. Make a fox character.
\item
  Meet some furries on GovTeen (née Puberty101).
\item
  Start talking with furries on AIM.
\item
  Join FluffMUCK.
\end{enumerate}

\begin{quote}
Ah yes, Fluff. May she rest in eternal solitude.
\end{quote}

She's not totally gone. I don't think. I actually haven't checked in a while.

\begin{quote}
I'm starting to doubt your commitment to nostalgia, here.
\end{quote}

What would I gain from such?

\begin{quote}
You could go look in the park. You could go ride around in the Universe-in-a-Box. You could \texttt{laston} some folks, maybe.
\end{quote}

Weirdly enough, of the people I would \texttt{laston}, I was finally reintroduced to a few not too long ago by, of all people, Zorin, head wiz of Fluff. Rela and GC. I was glad to see them doing well.

\begin{quote}
You were glad to see they were alive.
\end{quote}

I was glad to see they were alive, yes. That was around the time I had found the obituary for Danny.

\begin{quote}
You could \texttt{laston} Marek.
\end{quote}

I'm not sure I could take that.

\begin{quote}
Is that why you don't want to connect?
\end{quote}

It's one reason. Nostalgia is only so much fun. It's fun up until a certain extent, and then it becomes painful.

\begin{quote}
It's fun up until you're confronted with mortality and uncertainty. Danny died, and you don't know if Marek's alive.
\end{quote}

Yeah.

It's no longer fun, but it's no less important.

\begin{quote}
Let's talk about Margaras.
\end{quote}

Not yet.

\begin{quote}
Danny's passing was an abstract thing. Maragaras' was much more immediate. Much more concrete and real.
\end{quote}

Please.

\begin{quote}
Take your time.
\end{quote}
