A time to kill, and a time to heal; a time to break down, and a time to build up.

My interest in furry wound down a bit in university. I'd burned myself a bit too hard, hurt too many people, grew too jaded to take part. I still prowled around the usual haunts on the MUCKs, still poked my head in FFF, still looked at all the art, \href{https://adjectivespecies.com/2012/03/21/makyos-kaddish/}{but my heart wasn't in it anymore}.

\begin{quote}
There was a reason behind this. There were people behind this.
\end{quote}

Well, true. I don't know how to square that with\ldots{}well, a lot of things.

\begin{quote}
You don't know how to square that with how you felt about those people at the time.
\end{quote}

That's one aspect, yes. I also don't know how to square that with the fact that I was growing too jaded in a lot more than just furry. I grew jaded at school. I grew jaded at work. I struggled with my relationships. I struggled.

\begin{quote}
You struggled with gender.
\end{quote}

Well, yes, but I wasn't quite ready to admit that, yet.

\begin{quote}
You struggled with self harm.
\end{quote}

Yes.

\begin{quote}
You struggled with the intersections, the interstices, and the liminal spaces.
\end{quote}

I was going to write about {[}a{]}{[}s{]}. Where are you taking me?

\begin{quote}
Straight homeward to your symbol-essences.
\end{quote}

Shall I not die, then?

\begin{quote}
Isn't that the point of writing?
\end{quote}

I'm pretty sure all our names are writ on water at this point.

\begin{quote}
Come now. You wanted to be Keats when you grew up.
\end{quote}

You're in a mood.

\begin{quote}
You're in a mood.
\end{quote}

Fine.

Where are you taking me?

\begin{quote}
Let {[}a{]}{[}s{]} speak for {[}a{]}{[}s{]}. Let yourself speak for yourself.
\end{quote}

Okay.
