Matthew didn't end when I changed my name. Matthew ended September 14th, 2012.

\begin{ally}
He died on the 6th. He just didn't know he was dead yet.
\end{ally}
May I post a log?

\begin{ally}
You ask your ally for permission?
\end{ally}
Alright.

Watch the process of moving on.
\newpage

\begin{verbatim}
Koray arrives from the foyer.
Koray murmurs, "Margaras would come here, yes?"
Kuttas says, "Possible. Who's asking?"
Koray murmurs, "A bearer of bad news"
Kuttas doesn't like the sound of that.
Kuttas says, "What happened?"
Koray murmurs, "http://www.obitmichigan.com/Obituary/13660/Ryan-Abbott"
Koray murmurs, "Which is him, I believe"
Kuttas says, "Fuck."
MegaWolf blinks.
Paladin barks, "It does look like him, without the glasses."
Koray murmurs, "Sorry... I didn't mean to bring ya down"
Koray murmurs, "I just thought you should all know"
Kuttas says, "Thank you."
Vetiver blinks.
Vetiver quorks, "Gotta be kidding me."
Koray nods. "Also, http://www.furaffinity.net/user/margaras/ if you wanna say anything."
Srass says, "HOw did it happen?"
Koray waves.
MegaWolf -.- http://www.fox17online.com/news/fox17-ryan-abbott-soldier-from-grand-rapids-dies-in-washington-20120911,0,6686609.story
Koray teleports away.
Koray has left.
Paladin barks, "Well, that first web page does identify him by name. Wow, that sucks."
Himmel._.
Himmel says, "GOddammit."
Vetiver sighs. That's unbelievable.
Vetiver quorks, "Dammit."
Himmel says, "That... fucking sucks. ._."
Cain frowns so fucking hard
Kuttas says, "I'd noticed he hadn't been around in a while..."
Srass says, "Well, he was a little more scarce of late, but..."
Zhorah rumbles, "Wait, what happened?]\"
Srass says, "He was on as recently as 9/3."
Srass says, "Margaras died."
Himmel says, "It doesn't specify."
Kuttas says, "Car wreck."
MegaWolf growls softly, "He'd only started being active again in the past few years. -.-"
Zhorah rumbles, "o.o"
Himmel says, "A car wreck?"
Himmel says, "Seriously?"
Vetiver never met him in person, but he's been a friend here for over a decade. :(
Kuttas says, "Yeah"
Cain curls up, is no ofuckingkaywith this
MegaWolf growls softly, "I"ve pretty much known him ever since I've been here"
Kuttas says, "That's what the second link said."
MegaWolf squeezes Cain tightly.
Paladin is surprised that whoever wrote the first obituary knew his online name to include it.
Duelist growls quietly, "Oh fuck."
Kuttas misses that the first time through.
Dachande. Fuck :( That's just awful.
Himmel nods.
Zhorah hmmm
Cain hides in xane
Zhorah curls around Kuttas.
MegaWolf yips
Duelist rubs the back of his head.
Dralen acks, "That's awful. Wut..."
Cain doesn't know what to think. Margs was awesome. missing doesn't even begin to describe...
Vetiver is just kind of in shock.
Srass says, "I looked up the Michigan Patriot Guard.  They sound pretty damn awesome."
Dachande. not really sure what to say about it, really lost someone good.
Vetiver hugs Dachande. :(
MegaWolf growls softly, "This is actually the first time someone close to me online has died, so I'm just... I don't know."
Dachande. hugs and holds.
Paladin barks, "We've had other furry deaths. Cyno, Furp ..."
MegaWolf growls softly, "I do wonder how many of the ones who quietly faded away are dead."
Paladin barks, "I would wager a few, Megs."
Cain nods to Xane and noses in as well.
MegaWolf growls softly, "Yeah, I'd barely even heard of Furp until he died. I guess he was really popular but I'd seen him on IRC a few times and that's it."
Vetiver knew Furp, but Margaras was much more of a presence here, so it hits harder.
Duelist growls quietly, "Yeah, Margs was a regular here."
Himmel says, "You don't know how you are?"
Dachande. says, "Yeah never knew Furp, Margs i've kown for a damn long time."
Himmel nudges Mega.
MegaWolf nips Himmel.
Srass says, "I've lost one other friend my own age, someone I knew in person, but somehow this hit harder."
Cain woofs, "it just feels unreal..."
Srass says, "Yeah, it does."
Himmel leans on Mega.
Dralen dated Cyno. Knew Margaras for years. Knew Kedri really well,
Vetiver wonders if Margaras ever met anyone from FM in person. I don't think he did. :/
Kuttas says, "I keep thinking, I wish I'd gone to Seattle in January, like I'd planned."
You yerf, "Vetiver: Rustitobuck."
Kuttas says, "Equis."
Vetiver quorks, "Oh, good."
Cain woofs, "I'm trying to reach Equis right now"
Kuttas hehs. Left voicemail... c.c
Zhorah dun know anyone from here's number
Himmel says, "I texted him."
Himmel says, "And tweeted."
Kuttas says, "Well, hell. He's gonna have a lot of messages from us, apparently..."
JanusFox yips, "Wait... wtf..."
Kuttas pets Djirin, smiling a little.
JanusFox yips, "No :("
JanusFox yips, "fuck."
Vetiver quorks, "Always thought he was a really nice guy. He seemed to be a little directionless for a few years, when he was pretty scarce around here, but joining the army seemed to change things for him."
Srass says, "He always seemed so fascinatingly enigmatic to me..."
Kuttas nods.
Srass says, "And he had one of the cooler names I ever ran across.  Sanskrit for 'hunter.'"
Kuttas says, "Heh. I didn't know that."
Srass says, "He didn't either when he first picked it out -- I forget where he said he did find it."
Kuttas says, "He's one of the only people here I was immediately comfortable with."
MegaWolf chuckles softly. "And apparently he never updated his pinfo, since about 1999..."
MegaWolf growls softly, "I'd forgotten he wasn't always lynxy"
Srass says, "His prism cat form was pretty. :)"
Himmel says, "Srass: Rudyard Kipling."
Duelist growls quietly, "Oh I got something for that. Known Margs for years....right? Whitest guy in the world, I mean, ya know, look at the pic, right? Kept me in funk-drumming rhythms forever. I mean, funk drumming. Not kidding. He gave me, like 4 funk-drumming music books."
MegaWolf growls softly, "Yus. Now I remember it."
Kuttas says, "He mentioned a while back that he thought he should update it."
Vetiver quorks, "That's about when I first met him here."
JanusFox yips, "Is that really him?  That's for sure him right?"
Vetiver quorks, "Yeah."
Duelist growls quietly, "You say enigmatic and I do not disagree, but man, that lynx was dynamic."
MegaWolf growls softly, "The birthday in his pinfo matches, too."
Himmel says, "The Michigan Obituary mentions him by name. Online."
Kuttas says, "The obituatry names him as 'Margaras'/"
JanusFox is stunned.
Vetiver thinks we all are.
Acy arrives from the foyer.
Acy barkbark.
Himmel is just... sad.
Acy nose MegaRuff; SpookyFox.
JanusFox yips, "He was too fucking nice to die :(("
Kuttas says, "Acy: http://tinyurl.com/92fgx2d"
Floid says, "It's almost like someone in training said 'this is what you're going to do with the rest of your life.'"
MegaWolf squeezes Acy real tight.
Acy says, "Wow, that's pretty fucked up.. o.o"
Kuttas says, "I'm glad he'll be buried with honors."
Himmel nods.
Eibon has left.
You yerf, "Not doing well with this, gonna sneak.  Keep being excellent.  Will stay and listen 'til I time out."
Cain hugs Makyos
Srass squeezes Makyo's shoulder.
Kuttas ruffles Makyo.
Floid whispers, "Floid extremehugs." to you.
Mundy says, "Looks like Equis got the message(s)."
Dralen nodnods, "He tweeted."
Acy snickers a little. "He drove out to Chicago not long after I broke up with my ex.  We saw Mitch Hedberg."
Acy says, "Nothing about cause of death."
Srass says, "Car crash."
JanusFox yips, "Car accident with a guard shack at 5am."
Srass points to http://www.fox17online.com/news/fox17-ryan-abbott-soldier-from-grand-rapids-dies-in-washington-20120911,0,6686609.story
Acy says, "Oh."
JanusFox yips, "Whatever that means."
Srass says, "It could be anything.  Sudden loss of consciousness, problem with his vehicle, swerving to avoid hitting something..."
Kuttas says, "http://tinyurl.com/8tgj9y7"
Srass says, "There's something gauche about putting 'more faces of meth' and 'a century of sex symbols' in a sidebar next to that article."
Acy says, "If it bleeds it leads!"
Srass says, "Fucking media."
Dachande. says, "That's local news for ya."
Dralen says deeply, "At 5am, eh? Probably fell asleep at the wheel."
Duelist growls quietly, "There is other news....it's just....strange."
JanusFox yips, "I will really, really miss that lynx."
Acy says, "Other strange news?"
Duelist - http://www.kirotv.com/news/news/soldier-killed-fiery-unexplained-crash-jblm-guard-/nR4ys/
Duelist growls quietly, "It's...the first article before names were known and such"
Duelist growls quietly, "It's just bizarre."
Kuttas says, "10 Sep, they were still investigating."
Duelist growls quietly, "This is a 6 Sep article."
Floid says, "Maybe the NSA just decided to terminate their unnecessary furry-monitoring persona."
Malkoten blinkblinks?  Margs?
Srass says, "Yeah."
Vetiver really hopes that wasn't a...deliberate crash. :(
Srass says, "Me too. o.o"
Malkoten not happy. :(
Acy says, "It very well could have been."
MegaWolf growls softly, "I don't like the first comment on that article."
Acy fallsover.
MegaWolf growls softly, "But it does make it seem more accidental"
Dachande. says, "First comment says that guard tower is easy to hit and has been before due to being poorly lit."
Kuttas says, "Jesus."
JanusFox yips, "At 4am after being on base, all he was thinking of was going home."
Duelist growls quietly, "I think he lived on base"
JanusFox yips, "Ah."
JanusFox yips, "He had access to firearms anyway... why chance it."
JanusFox yips, "Had to be an accident."
Cain woofs, "what the hell are you people talking about"
Dralen says deeply, "Margaras was killed in a car accident."
Kuttas says, "He lived in the barracks."
Cain woofs, "no, I mean the conspiracy type bs"
Cain woofs, "not the time to spin yarns"
Dachande. says, "From the video it looks to be a pretty shitty location for that building."
Kuttas says, "Most guard shacks are in bad places for a building."
Dachande. nods, "They are designed to be in the way. Bleh."
Floid says, "I just figure he would've enjoyed me keeping it weird."
Cain woofs, "yeah, well, I guess you're right... :/"
JanusFox sigh, "Fuck."
JanusFox changes a few array pointers around and ends up someplace else.
JanusFox has left.
Duelist growls quietly, "Well, we got, like 25 people here who come here regularly and each one is gonna handle something like this differently, so lets be respectful and not jump on one another."
Duelist growls quietly, "We're all gonna have a bit of a hair trigger for awhile."
Malkoten goes straight to denial *nodnods*
Vetiver snugs Malkoten.
Cain is just reallyunhappyisall
Himmel puts an arm 'round Cain.
Srass says, "You're not alone."
Kuttas says, "Heh. He -was- my MOS series. 94Y."
KurtMRufa headshakes.
Kuttas sighs.
Dralen smooches on Kuttas and cuddles him and Srass together, stroking backs and shoulders.
Srass squeezes Dralen.
Kuttas hugs Dralen and Srass.
Dachande. Huh, sunofabitch woot has a good deal on a damascan steal santoku
Dralen is extra super sleepy after an incredibly elaborate Izakaya dinner tonight. "Time for sleep, folkses."
Srass says, "Sleep well."
Kuttas says, "Rest well."
Djirin slinks to bed as well.  gooses about
Djirin has left.
Dralen says deeply, "Also, if you ever get the chance for lobster sashimi. Take it."
Dralen meeps and flees.
Dralen swishes his tail, and is gone.
Dralen has left.
Kyhwana arrives from the foyer.
Kyhwana mrps and noses Srass "What happened? :(
Vetiver quorks, "Margaras died last week."
Duelist growls quietly, "I think its time for a drink."
Kia says, "..."
Kyhwana guessed as much, what happened? :(
Srass says, "He apparently drove into an abandoned guard shack.  They're still trying to figure out why."
Kyhwana ohs "Damn.
Kyhwana curls up on Srass and whipmers
MegaWolf nuzzles Kyhwana
Srass hugs Kyhwana.
Malkoten nods, pretty much the reaction everyone is having.
Kyhwana nuzzles back.
Vetiver quorks, "Just seems unreal somehow."
Duelist growls quietly, "It does!"
Duelist got no idea what to do or say or anything.
Srass nods.
Srass says, "Duelist's right.  This does call for a drink."
Himmel says, "There's nothing to do or say."
Mundy says, "Equis is probably a dozen drinks ahead of everyone"
Kuttas says, "I know what to say. He was a damned fine man, a damned good friend, and I'm going to miss him like hell."
Vetiver nods.
Srass says, "Equis is a dozen drinks ahead of everyone on a good day."
Srass nods to Kuttas.
Himmel says, "I feel the same way. But I can't imagine anyone here -doesn't-."
Duelist growls quietly, "Yeah, but this is sucky and tragic and un-called for."
Srass nods.
Duelist growls quietly, "That's kinda the problem with a crowd like this tho, ya know a 'relatively new' population...."
Duelist growls quietly, "I mean, it's gonna be 50-60 years before we say 'awww yeah, but he was 96 years old, it was his time' kinda thing."
Srass nods.  "This was wrong.  It was far too early."
Himmel says, "It's always too early."
Kyhwana bleh, shouldn't have just chekced his logs.
Srass says, "Your logs?"
Kyhwana purrrs, "MUCK logs."
Kyhwana purrrs, "Well, technically it's a single log."
Kuttas says, "Equis just said a few minutes ago that he needed a drink now."
Himmel is going to go to bed. He's sad. He'll feel sad for a while.
Kuttas hugs Himmel. "Rest well, cat."
Himmel says, "You, too, Yena, when you do."
Himmel winks out of sight in the sparkling glow of a space/time rift.
Himmel has left.
Mundy wants to see his toothycat now. :P
Zhorah doesn't know how to feel
Duelist growls quietly, "Well, a lot of us are probably rather numb at the moment."
Kuttas will probably be grepping logs before long. Remembering what good times got recorded.
Duelist growls quietly, "Hence the whole 'I dunno what to do, say, feel' thing...."
Kyhwana does, he's sad!
MegaWolf thinks he should go to bed.
Kyhwana snugs MW
Cain is going to go sleep too. Coughing worse the later he stays up
1) Duelist  2 days ago -- Fallout IRL!
2) Makyo  Today -- Margaras
Use 'read <mesgnum>'to list a message.  Use 'read <keyword>' to list
messages with a keyword.  Use 'read -' to read the next message.
Done.
MegaWolf squeezes Kyhwana extra tight
2) Makyo  Today -- Margaras
From: Makyo  22:26:18 09/14/12 PDT

For those who do not yet know, Margaras passed away in a car accident on Sept. 6, and folks in the PN were notified Sept 14.  Here is the obituary: http://www.obitmichigan.com/Obituary/13660/Ryan-Abbott
Personal bit, please feel free to skip ---
He's one of those people that helped raise me in a way.  Not intentionally, of course, but in the way of an older friend, sort of like how I imagine an older brother helps to raise younger siblings.  Just sort of accidentally leading the way without really knowing any better.  I never had older siblings, and circumstances of my childhood and adolecense led me to seek out those who could play that role.
I don't really know what that means about me, to be honest, that I sought out such a connection in such a place.  I think I've always craved someone in that role, of course, and having leadership more ready to admit fallabilty than my parents felt...refreshing, comforting, something.  Not that everyone's ready to admit fallability, but the ability to even talk about changes in life, even if they're for the negative, really adds a lot more human-ness, a lot more personality to someone in a guiding role than either of my parents offered when I was growing up.
Anyway, I'm so glad for the time I had with him.  I'm sad now, sure, but I'll always remember him happily.  Remember singing "K A L A M A Z O Oh what a gaaaal...in Kalamazoooo" at him in high school when my choir sang that song, remember talking about music and all the day to day things in life.  There are a lot of people who fit into this role for me, and I'll be sad to see every one of them leave, no matter how they do so, but for tonight, cheers, Margaras.
All my love.

Done.
Cain noses on Xane
MegaWolf kisses Cain's nose, snouts Makyo
Kuttas hugs Makyo.
Makyo snootles folk, ahem.  REALLY goes to bed now :o)
Cain teleports away.
Cain has left.
Zhorah feels bad about memories he does have
Rigel has connected.
Rigel oopses.
Rigel winks out of sight in the sparkling glow of a space/time rift.
Rigel has left.
Malken has disconnected.
MegaWolf has disconnected.
KurtMRufa teleports away.
KurtMRufa has left.
Somewhere on the muck, KurtMRufa has disconnected.
Sturgis arrives from the foyer.
Duelist whips out his hockey stick. He 'skates' up to a sleeper, winds up and lets a slapshot go!
MegaWolf is sent home.
MegaWolf has left.
Malken raises a warding finger, and says serenly,"Do not bother, I can provide my own transportation."  He then disappears in a swirl of darkness.
Malken has left.
Acy has disconnected.
Acy has connected.
Acy urph.
Kyhwana noses Acy
Acy rubs Kyhwana behind the ears.
Kyhwana mewls
Acy has disconnected.
Duelist bedtime! G'nite all
Duelist goes home.
Duelist has left.
Sturgis winks out of sight in the sparkling glow of a space/time rift.
Sturgis has left.
Kyhwana loafs all over Srass
Srass petpets catloaf.
Kyhwana purrup
Dachande. going to go to bed as well, good night ya'll.
Dachande. teleports away.
Dachande. has left.
Zhorah has disconnected.
Vetiver goes home.
Vetiver has left.
Zhorah has connected.
Zhorah back
Zhorah has connected.
Zhorah has connected.
Zhorah has disconnected.
Zhorah has disconnected.
Kuttas' beer is being most uncooperative.
Srass says, "How so?"
Kuttas says, "Well, to start with, it's not a twist top. Then, the it broke my bottle opener. Then, the bottle opener on my leatherman wouldn't fit."
Kuttas says, "In the end, though, it turns out there's a second bottle opener on the leatherman that -does- fit."
Srass says, "That's one stubborn beer."
Srass says, "A second bottle opener...?"
Kuttas says, "Yeah."
Kuttas says, "This is the SOG folding multitool they issued me at my last duty station in the Army. Apparently, they meant business when it came to beer. c.c"
Srass says, "Damn. o.o"
Kuttas drinks to Lynx.
Malkoten rumbles, "I think that I am off to bed.  G'night folks."
Srass says, "'Night."
Kuttas says, "Good night."
Kuttas says, "Rest well."
Malkoten will do.
Malkoten winks out of sight in the sparkling glow of a space/time rift.
Malkoten has left.
Kyhwana ponders cracking a beer even though he was hung over most of today
Srass emails Kyhwana a Negra Modelo.
Kuttas faxes an Alaskan Oatmeal Stout. The long distance charges are worth it. c.c
Srass mmms, oatmeal stout. -.-
Kyhwana mmms
Kuttas hand-delivers one to Srass.
Srass oohs! :3
Singe arrives from the foyer.
Fiend Plushie bounds in after Singe.
Singe slinks, sprawls.
Srass raises a glass to departed cats, and drinks.
Kuttas raises, taps on the table, and drinks deeply.
Zhorah has disconnected.
Srass says, "I've heard it said that everybody's tastes are different."
Kuttas gives exactly 0d0+0 fucks. He likes it.
> Kuttas rolls 0d0+0 and gets for a result of 0.
Kuttas points. "That many."
Srass says, "We really don't need any more deaths around here. :-P"
Kyhwana has some weird fruit sour beer thing in the fridge.
Srass says, "Like a lambic or something?"
Kyhwana purrrs, "Except brewed here.."
Srass aahs.
Singe growls, "Margaras died? :("
Srass says, "Yeah."
Kuttas says, "Singe:  http://tinyurl.com/92fgx2d"
Singe growls, "jeez"
Singe growls, "what happened? :("
Kuttas says, "Early morning single-vehicle wreck. Collided with a building."
Singe sighs.
Singe growls, "feeling more and more lucky by the da"
Singe growls, "day"
Kyhwana didn't follow him on twitter or vice versa, so can't see his tweets :(
Srass says, "His last post on LiveJournal has a really jawdroppingly gorgeous picture in it, though."
Somewhere on the muck, Tigerwolf has disconnected.
Paladin barks, "Of himself?"
Kuttas says, "Whose?"
Srass |http://i104.photobucket.com/albums/m170/margaras/Vacation-Jun2012/TwinFalls1.jpg
Srass says, "Of where he went on vacation, apparently."
Kuttas ahs.
Kuttas says, "Firefox is being retarded, trying to load it via HTTPS. This is pissing me off."
Kuttas says, "Yeah, that's a nice photo..."
Srass says, "Well.  What an unbelievably shitty way to start a weekend."
Kuttas hugs Srass and leans.
Srass hugs Kuttas.
Srass says, "Okay, I'm going to have to go to sleep, whether I like the idea or not.  Good night, gentlemen."
Kyhwana snugs Srass "Night
Srass hugs Kyhwana.
Srass steps behind a molecule.
Srass has left.
Kyhwana lifts up the rug and pushes all the sleepers under it.. he jumps on it a few times and the rug goes flat
Acy is sent home.
Acy has left.
Zhorah is sent home.
Zhorah has left.
Singe leans on Paladin.
Paladin cuddles Singe softly. "Have some pizza."
Singe growls, "saving it for tomorrow night"
Singe growls, "don't feel like sectioning olives right now"
Paladin just got some now! You can have some of his!
Singe eats.
Paladin barks, "Nom nom nom!"
Singe earperks. "someone made A Wrinkle In Time into a graphic novel. ._."
Scruff arrives from the foyer.
Scruff sneaks in
Kyhwana picks up Scruff and puts him in his lap and petpets
Scruff dangles, briefly, then nestles in against leopardtummy
Scruff halfcurls against one of Kyh's paws
Kyhwana petpets Scruff some more and sighs
Scruff mrow? What's up?
Kyhwana points at the board?
Scruff ;.;
Kuttas says, "I think I'm gonna go to bed."
Kuttas says, "Try to have a good night, friends."
Kyhwana snugs Kuttas too "Night
Kuttas hugs.
Kuttas sneakyhyenas into the shadows. c.c
Kyhwana ruffles scruff headfur
Scruff wriggles a bit closer against the leopardkitty. "It's really not fair, he was such a nice guy!"
Kyhwana nods..
Felder arrives from the foyer.
Felder whuffles to all
Kyhwana purrrs, "Hey Felder"
Felder mindsends, "Hi Kyh"
Felder flops onto a seat and sighs out
Scruff pads over to Felder, winds around his legs
Felder hugs on Scruff tight
Scruff has disconnected.
Scruff has connected.
Scruff bites his connection.
Scruff pads over to Feldy, winds around his legs
Felder hugs on Scruff again
Scruff nosebumps pn0y and leopardkitty, sneaks out for a bit. Gotta head into London for a few hours!
Scruff teleports away.
Scruff has left.
Felder winks out of sight in the sparkling glow of a space/time rift.
Felder has left.
Kyhwana erfs
Zeph arrives from the foyer.
Zeph rowr.
Kyhwana snugs Zephs
ZeitOtter arrives from the foyer.
ZeitOtter actually lives though he's been gone for nearly half a year
Kyhwana purrrs, "Hey Zeit"
ZeitOtter says, " so many new faces other than Singe. " snickers " and Mundy as well as Floid. " teases " Oldies. ""
Kyhwana noses Zeit at the board. And Zeph too.
Zeph hugs him some Kyhmew!
ZeitOtter says, " So what's been going on eh? "
Kyhwana clings to Zephs
ZeitOtter says, " Heh, lovely"
Singe rolls his eyes somehow.
Kyhwana eyes Singes eyes
Singe growls, "Margaras died. :("
Zeph mews, "Wait, what?"
Kyhwana nods
Singe growls, "I am told it was a car accident."
Kyhwana ers "Makyo's post on the board.
Zeph mrf. No more lynx.
JanusFox arrives from the foyer.
Zeph squeezes on SpookyFox.
JanusFox hugs Zeph.
ZeitOtter has disconnected.
Mundy has disconnected.

You have been logged out due to inactivity.
% Connection to furry closed by foreign host.
\end{verbatim}
\newpage

\begin{verbatim}
% Trying to connect to furry: 74.207.243.108 8889.
% Connected to furry.
#$#mcp version: "2.1" to: "2.1"
Welcome to
              _____                 _ _ _   _    _ __   _   ,  SM
               /  '                ' ) ) ) ' )  / /  ) ' ) /
            ,-/-, . . __  __  __  , / / /   /  / /      /-<
           (_/   (_/_/ (_/ (_/ (_/ / ' (_  (__/ (__/   /   )
                                /
                               '
          The first 99 & 44/100% anthropomorphic/Furry TinyMu*

(The SM means that FurryMuck is a Service Mark of the FurryMuck Wizards)
To connect to your existing character, type "connect <name> <password>".
To receive a new character, send mail to join@furrymuck.com
To see the latest news, type "news" after connecting to a character.
To disconnect from a character, type "QUIT".
Use the WHO command to find out who is currently online.
Use the 'whereare' command to find places with active people.
Use the 'wizzes' command to see what Wizards are on line, or the 'helpstaff'
 command to see who of the help staff is on.
Use "connect guest guest" to visit FurryMUCK as a guest.
All users of FurryMuck are bound by our AUP. "NEWS AUP" to read this document.
----

Sadly, FurryMuck has lost one of its own.

S'A'Alis, May 29, 1963 -- September 5, 2012, the Large Furry Marsupial, and a
member of the L'Drey, a space-faring, fox-like species. He was never without his
'Eternally Filled Highly Caffeinated Coffee Mug of Doom'. From 1993 - 1999,
S'A'Alis hosted the servers that FurryMUCK ran on, and was a character creation
wizard 1993-2001. Condolences can be sent to his beloved wife, IceWolf:

M. Vogt, W5910 Genske Road, Black Creek, WI 54106

Life is eternal, and love is immortal,
and death is only a horizon;
and a horizon is nothing save the limit of our sight.
 -Rossiter Worthington Raymond

----
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
Makyo stretches out and yawns toothily, shaking Makyo's fur out.
Players online for whom you are watching:
Danish            Makyo             Taxus
Done.
The next scheduled database save will be in 24 mins, 14 secs.
You place a strategic call to one deity or another.
Makyo disappears in a puff of complacency.
Purple Nurple Foyer(#52464RLJ)
You step in through the door and into a cramped foyer.  Advertising
posters plaster the walls and there's another door right in front
of you (east).  The door is padded purple vinyl, studded in a diamond
pattern.  This is the Purple Nurple, Furrymuck's gay/les/bi nightclub
and meeting place.  Feel free to come on in if you are straight too.. we
don't bite (unless you ask nicely ;)  There is a sign on the wall next to
the door and a notice where the computer used to be, saying that it's now
in the main room.
Players inside the Nurple:
 TealFox            Floid              MegaWolf           Srass
 White_Fox          Cain               JanusFox           Singe
[Exits: <IN> to the Purple Nurple   <OUT> to Sable Street]
Contents:
Polo
PN RULES : READ THIS TO BE ABLE TO ENTER
You enter the PN
Makyo disappears in a puff of complacency.
The Purple Nurple
You are in the Purple Nurple, furry's premier gay/les/bi spot.
The room is large, a converted warehouse - the ceiling's
about fifty feet above the crowded floor.  An entire suspended
lighting grid swivels back and forth in the middle of the room,
rigged with a complex array of lights, lasers and mirrors.
The overall effect is of an alien spacecraft hovering about twenty
feet over the dance floor.  Huge projection wall-screens flicker
images of furries dancing, clips from anime movies, computer
graphics reels and old cartoons.  The music is loud, thumping
techno and house, bass thundering through the gyrating furries
on the dance floor.
To one side is a lounge area, acoustically out of the main thrust
of the speaker stacks allowing normal conversation.  A bar with
every drink known is along the wall of the lounge, and
the floor is scattered with heavy-duty beanbag chairs, funky couches,
and other assorted furnishings, all roomy enough for at least two furs.
A small staircase leads up to the Nurple Apartments.
Contents:
TealFox
Floid
MegaWolf
Srass
White_Fox
Cain
JanusFox
Fiend Plushie
Singe
All complaints --> Rigel
NURPLE ADULT/PG POLICIES ****** PLEASE READ
Bulletin Board
You whisper, "Makyo hugs on fox." to TealFox.
Miko arrives from the foyer.
Makyo nuzz on SQRL.
Miko fluffs the foxyfluff.
TealFox whispers, "TealFox  hugs tightly. :(" to you.
You whisper, "Makyo leans in against, squeeze.  Rrf." to TealFox.
White_Fox has connected.
White_Fox has disconnected.
Singe hugs Miko!
Miko squeezes Singe!
Singe growls, "poor margaras :("
TealFox whispers, "TealFox  just got the news a little bit ago... still shaken," to you.
JanusFox sighs, "Yah poor guy :(
Cain curls up tight on xane again
Miko chatters, "What, huh?"
Miko o.o
TealFox knew him before either of us were in the fandom. I ... yeah. no words right now. Just tears,
You whisper, "Makyo nods and nuzz at.  Little torn upabout it." to TealFox.
1) Duelist  2 days ago -- Fallout IRL!
2) Makyo  Today -- Margaras
Use 'read <mesgnum>'to list a message.  Use 'read <keyword>' to list
messages with a keyword.  Use 'read -' to read the next message.
Done.
You yerf, "Miko: read 2"
Cain holds Teal close
Miko cries.
TealFox whispers, "TealFox  nods. yeah, me too." to you.
TealFox snugs Miko too
Miko hugs TealFox!
Srass says, "That was a nice post, by the way, Makyo."
Singe nods.
You yerf, "Spelled fallibility wrong twice :o)"
White_Fox erfs.  :/
You yerf, "Oh well."
Srass says, "We know what'cha mean."
You yerf, "I started coming around here when I was 14.  You all mean quite a bit to me."
TealFox snugs Makyo. "Intent comes through. "
Singe growls, "I think I was 16 when I first showed up here."
Singe growls, "Maybe 17"
FoxLord arrives from the foyer.
FoxLord waves
Srass waves
FoxLord snugsa Tealfoxie
Singe mmhs.
Srass says, "I wish I could've grown up here like that.  I think I would've ended up less screwed up."
MegaWolf growls softly, "I think I'm still in denial."
Cain nods and noses at Xane ears
MegaWolf muzzlerubs Cain, squeezes more.
TealFox didnt really start discovering my self until late...i didnt come out until like 23... and didnt find the fandom till almost 30. i knew Margaras pre fandom on some of the IRC chat channels. :/
White_Fox murrs, "I met margsy right after meeting Malky. "
White_Fox murrs, "Whl happened to be local :)  Good peoples"
White_Fox murrs, "Miss him. :/"
Pyat arrives from the foyer.
Pyat squeaks
JanusFox yips, "It's just so sudden.  And he's usually around so often."
Somewhere on the muck, Taxus has disconnected.
Singe growls, "yeah"
Pyat squeaks unhappily. Margaras?
Cain woofs, "Margs gave me a good bit of selfconfidence in areas I really didn't have. It'll always be a good memory for me"
Somewhere on the muck, Vikki_Fox has connected.
FoxLord barks, "what happened to marg?"
Singe growls, "car crash"
FoxLord barks, "No."
Pyat thinks Margaras' family would be glad to know people are coming together to remember him in odd places
"Physics," Floid summarizes.
FoxLord snorts
Pyat has left.
Polo arrives from the foyer.
Singe growls, "jackal"
JanusFox yips, "I wonder if they'll ever figure out what happened."
Miko watches yesterday's QI on Margy's behalf.
Singe likes QI.
Floid says, "So, uh, did anyone tell Paf?"
Srass dunno Paf.
KurtMRufa arrives from the foyer.
Singe hasn't talked to Esel in ages.
Srass hugs Kurt.
KurtMRufa nosenoses on Srass.
Somewhere on the muck, Herefox has connected.
White_Fox has disconnected.
Rommel arrives from the foyer.
Rommel yips, "Good Morning."
Srass says, "Morning."
Duelist arrives from the foyer.
Dachande. arrives from the foyer.
Duelist chrp.
Dachande. enters! for a chane.
Dachande. g
Srass earscritches Duelist.
Duelist licks Srass!
TealFox mrf
MegaWolf noses D&D
Polo yaaaawns and picks up Rommel to flop on Dachande.
Rommel yips? "Oh! Good morning Polo."
Dachande. wheeze squeaks from all the weight on him.
Polo is very light, though the fennec's a bit tubby ;)
MegaWolf fluffs Rommel
Polo says, "Wrecked today, had a bilobial migraine. x.x"
Rommel Sticks an ice pick into Polos ear to make it feel better?
Rommel has been fortunate. I once had an "Ocular Migraine". the Funny lights without the pain.
Polo says, "Oh, it's gone, but left me exhausted."
Rommel Ahs and removes the Ice pick then. :)
TealFox has disconnected.
Cain is gonna run
Cain hugs around
Cain teleports away.
Cain has left.
Polo says, "Oh, I get those fairly often, or other single-focus ones.  This, alas, was my entire brain spazzing out.  Like an electric storm...  random memories, talking nonsense to myself, sounds, lights and much much much pain."
Polo says, "I get them very rarely."
TealFox has connected.
TealFox winks out of sight in the sparkling glow of a space/time rift.
TealFox has left.
Puc arrives from the foyer.
Puc mewfs.  Morning
Srass says, "Morning."
Makyo swish.
Duelist licks you!
Miko picks Puc up and applies pettings.
You lick Duelist!
Himmel arrives from the foyer.
Himmel flops.
You yerf, "Cats."
Puc mrarfs, droops, soaks up squirrel lovins.  "Hey :)"
Miko pets Himmel with Puc.
Rommel yips, "I am sorry to hear that. I have known several people RL that get shut down by them completely."
Himmel curls up to Miko.
Miko puts an arm around Himmel and sits Puc on his other shoulder.
Puc chuckles and leans against whosever neck is closest.
Somewhere on the muck, Tigerwolf has connected.
MegaWolf has disconnected.
Polo snuggles up with Rommel the eardog, and gently noms his ears, "How are you keeping, trouble? :)"
Rommel is doing well. Has been slow week. Which is good I suppose.
Polo says, "Opposite of me then."
Polo says, "I would like a slow week soon :)"
Srass has disconnected.
Makyo wrf, disc golf time.
Puc wanna go disc golfing!
Duelist growls quietly, "Fox on a golf course!"
Duelist has seen that somewhere before....
KurtMRufa has disconnected.
KurtMRufa has connected.
KurtMRufa makyonose.
Kia arrives from the foyer.
Himmel says, "Morning, Kia."
JanusFox has had foxes following him during golf, but that's a different matter.
Himmel says, "Or, well."
Himmel says, "Afternoon, for you."
Duelist whips out his hockey stick. He 'skates' up to a sleeper, winds up and lets a slapshot go!
MegaWolf is sent home.
MegaWolf has left.
Srass is sent home.
Srass has left.
White_Fox is sent home.
White_Fox has left.
Kia says, "..."
Himmel says, "Oh, don't start this."
Floid makes IT housecall now.  Whee.
Floid has disconnected.
Mundy arrives from the foyer.
Malkoten arrives from the foyer.
Malkoten yawns
FoxLord mmms Disc Golf
Mundy gooses Duelist!
Duelist O.O
Mundy :O
Puc headbutts FoxLord!
JanusFox yips, "Sounds like something I'd play on a C64."
Somewhere on the muck, TealFox has connected.
Rei_Ayanami arrives from the foyer.
Mundy pets TIGRSKNK belly.
Rommel nods hello to Rei
Mundy says, "What. http://imgur.com/gallery/fPjAx "
KurtMRufa metalyawns.
Rei_Ayanami waves in greetings.
Himmel has such a headache.
KurtMRufa puts on some Hearts of Space.
Wildcard arrives from the foyer.
Wildcard waves.
Duelist stretches!
Miko chatters, "Well, that didn't take long. Obsidian Entertainment put up a Kickstarter for a new RPG in the style of Baldur's Gate, Planescape: Torment, Icewind Dale, et al, asking for a whopping $1.1M, less than 24 hours ago, and looks like they'll hit the target within the hour."
Miko chatters, "Two people (including Notch) have gone for the $10,000 pledge."
KurtMRufa remarks, "So how does this thing work?  Do you get your money back at some point?"
Miko chatters, "You get backer rewards depending on how much you kicked in. The typical one being "you get a copy of whatever we're making" for $10-20."
Miko chatters, "In that instance it basically works as a preorder.. except with no actual guarantee that the project's going to be finished and the thing is going to exist. So sort of halfway between a charity and and a preorder."
KurtMRufa remarks, "Oh, okay.  And if they don't make it, well, it's what it is."
Miko chatters, "A lot of people do seem to be very keen to pitch in to try and get that thing they want that nobody makes any more made. There's usually lower options as well, throw in a couple of bucks and get the mp3 soundtrack and an exclusive 1920x1080 wallpaper image, buy the thing when it comes out."
Miko chatters, "I wish there was a "shut up and take my money now" option, though, the "we'll pull the money from your account when the pledge target is hit" system has caused a big wodge to come out of my daily-use account two months later when I've just gotten bills in the mail a few times so far."
Somewhere on the muck, Azure has connected.
Azure arrives from the foyer.
Azure prowls in.
Azure picks each sleeper up-- it must be some trick of perspective-- to slip into his pocket.  That can't be right, can it?
Floid is sent home.
Floid has left.
Rommel winks out of sight in the sparkling glow of a space/time rift.
Rommel has left.
Duelist pets a tinytinyfox!
Azure noses up against Duelists's hand.
Azure yips, "Good morning."
Duelist growls quietly, "Hello foxy!"
Samanthia arrives from the foyer.
Samanthia slinks in.  Rar.
Samanthia pets Azure and SKNK.
Azure yips, "Hello, Black 'n WHite."
Mundy gets a present from digikey in the mail.
Azure hugs Samanthia, "Hello, Kirin."
Malkoten winks out of sight in the sparkling glow of a space/time rift.
Malkoten has left.
Somewhere on the muck, MegaWolf has connected.
Ryan arrives from the foyer.
Samanthia says, "How is small blue fox?"
Azure yips, "I'm doing fairly well, thank you."
Azure yips, "I think I'm going to go to Meijer's."
MegaWolf arrives from the foyer.
MegaWolf strokes Azure's ears
Samanthia okays.
KurtMRufa mmfs.  Interesting stuff.
Azure slinkso ver and noses MegaWolf, "Guten Tag."
Duelist growls quietly, "So how is folks doing today? Coping?"
Samanthia yawns and is engaged in server migration.
Puc has disconnected.
Mundy rubs TIGRSKNK.
MegaWolf growls softly, "Still kind of numb"
Kia has disconnected.
Malken arrives from the foyer.
Malken lies down on a couch
Azure yips, "KI'm alright."
Duelist kinda numb too. Unsure of how to deal....
Duelist growls quietly, "Plus didn't sleep good last night."
JanusFox hears that.
JanusFox yips, "It has pretty good closure though I wish it had more, somehow."
Mundy licks Duelist!
Mundy ponders ordering a switch machine..
Malken waves to Mundy
Mundy licks Malken!
MegaWolf always has nightmares so he can't really judge his mental state by his dreams.
Duelist growls quietly, "I was pondering if we shouldn't schedule smething, ya know, in here, just a sort of....I dunno, chance to say something and listen and all that."
Wildcard winks out of sight in the sparkling glow of a space/time rift.
Wildcard has left.
Darkness suddenly appears by Rei.
Rei_Ayanami meeps a little, then touches shoulders with the Darkness.
Darkness smiles.
Samanthia watches progress bars.  Grump.
Milehighyena arrives from the foyer.
Milehighyena seeks the techies.
Somewhere on the muck, TealFox has disconnected.
Darkness says, "What kind of tech.."
Milehighyena cackles, "I need a new MP3 player. my RCA has been great, but it has taken some bad abuse in my pocket at work. the case is cracked and held together with tape. "
Darkness says, "Allright."
Darkness says, "Price Range?"
Duelist growls quietly, "Duh, an iPod, of course"
Milehighyena cackles, "I need a new one with a decent color screen so I can look at my pr0n. for under fity dollars."
Duelist growls quietly, "Might as well buy from the company that invented the mp3 and music."
Mundy starts prototyping MSMVs
Azure yips, "Franhaufer?"
Milehighyena cackles, "looking around at places, i see a lot of cheap by some brand named Coby. Anyone ever heard of them? Sandisk?"
Milehighyena cackles, "i'd love to replace this little RCA, but thety discontinued this model. maybe because it was too thin and flimsy."
Miko listenin' to The Eels - "Last Stop: This Town." o/~ You're dead, but the world keeps spinning.. o/~ Take a spin through the world you left o/~ It's getting dark a little too early o/~ Are you missing the dearly bereft? o/~
MegaWolf yawns softly, and curls up in his beanbag.
Darkness says, "Id say Sony, but they are a little more expensive. "
Reveille arrives from the foyer.
Samanthia pets Reveille.
Reveille noses Samanthia.
Malken waves to the long lung dragon
Reveille nods at Malken.
Malken hasn't seen that dragon in a while
Samanthia says, "How is noodle dragon?"
Darkness rummages through her bag and grabs a bag of o-, stabs a straw into it and drains it.
Reveille is doing well.
Scruff arrives from the foyer.
Scruff sneaks in, an up into Duelist's lap
Malken waves to little Scruff!
Milehighyena summons a recognizer, who pickes up the sleepers. "It's the Games for you, Programs!"
Kia is sent home.
Kia has left.
Puc heads to the sweeper's home to bang their mother.
Puc has left.
Scruff miaows hi to the sofalion
Azure bows, "Mr. Scruff.
Duelist pets CHTA
Malken hasn't seen Scruff for a while, either.
Scruff nosetouches the littlebluefoxy, lightly
Samanthia pets Reveille more.
Scruff curls around bigstrongskunkpaw
Reveille rrrhs and arches under Samanthia's petting.  She blinks at Duelist.  Skunk? O_o
Duelist is!
MegaWolf kisses Scruffnose
Malken thinks skunk Duelist is handsome
Duelist grins! Well skunks do, ya know, have that whole black/white formal thing goin' on
MegaWolf growls softly, "Studmephit."
Malken nods "indeed.  and such a muscular one"
Duelist grins.
Duelist growls quietly, "Genetics! >;)"
MegaWolf nips Duelist just a lil'
Scruff chirps, "And luxuriously fluffy tail!"
Duelist growls quietly, "Well that's genetics too"
Darkness looks over her shouler. Absent tail.. Hmm.
Miko listens to Grandaddy and has a bit of a cry.
Milehighyena has disconnected.
Azure has been mildly in love with The Fiery Furnaces for the last few days.
Rei_Ayanami has left.
Scruff wriggles a bit, settling
Duelist stretches out!
Scruff snuffles into skunkbellyfur
Mundy chews on wires.
Samanthia oops.
Azure goes off to Meijer's.
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Somewhere on the muck, Azure has disconnected.
Polo wakes up from passing out again. x.x
Samanthia has disconnected.
Samanthia has connected.
Samanthia beats on networking stuffs.  OKay.  Time to scoot.  Shouldn't be connected while re-arrangign the tuuuuubes.
Samanthia pets a noodle dragon and absconds.
Samanthia teleports away.
Samanthia has left.
Reveille leans against where Samanthia was, and falls over.
Dachande. Woo house clean at 11am.
Polo sniffs Reveille.
Scruff sits in the middle of D&D's livingroom, looks untidy ^-^
Reveille smells dragonny.
Kia arrives from the foyer.
Dachande. Rarrrrg, damn cats!
Polo earperks and looks around.
Scruff chirps, "A bit like this - http://farm8.staticflickr.com/7238/7344470384_47570f82cb_z.jpg"
Reveille growls, "Fluffy!"
Mundy licks Dachande.!
Dachande. licks Mundy!
Himmel | http://www.afterelton.com/poll/2012/09/ultimate-slash-madness-tourney-round-four
Himmel says, "Vote Destiel, guys. C'mon. You know you want to."
MegaWolf omgchta
Mundy studies his prototype vs. schematic.. Grrr..
Somewhere on the muck, Vikki_Fox has disconnected.
Dachande. thinking time for shower.
Mundy rebuilds.. >.<
Scruff shower later! New Doctor Who in 18min!
Dachande. says, "For you. I haven't even seen the ones prior to it, need to get on the torrents."
Danish arrives from the foyer.
Scruff miaows hi to the pastry-in-disguise
Danish tousles Scrufff and fluff and squirrel and cats.
Dachande. says, "Don't have HD BBC not going to watch a LD 9x6 on 4x3 with boarders."
Scruff nodnods, internets be useful there
Dachande. nodnods.
Dachande. Sweaty n stink of house dirt, shower now. :)
Makyo mrrrp.
Scruff awwfox. Hugsfox.
Duelist licks you!
Makyo snoooof at Danish and Scruff and Duelist.
Duelist growls quietly, "Makyo, that was a beautiful write-up on the board."
You yerf, "Mrrf.  Thanks."
Makyo likes so many of you so much :|
Kia has disconnected.
Danish winces.
Danish lows, "Fuck."
Danish teleports away.
Danish has left.
You page-pose, "Makyo nuzz.  Alright?" to Danish
Duelist pets upon foxish.
(p) In a page-pose to you, Danish hugs.
Makyo nuzz upon skunk.
MegaWolf kisses Makyo's nose 'gain.
Makyo snf, smooch at woof.
Somewhere on the muck, Danish has disconnected.
Scruff clambers up, stretches out on the bar
Danish arrives from the foyer.
Polo didn't know the person, but bereavement sucks, so condolences to the bereaved that are present.
Miko hugs Danish!   Whitcomb jumps into Miko's arms and murrs loudly.
You hug Danish!   He jumps into your arms and murrs loudly.
Scruff nuzzles Danish!
Danish snugs back.
FoxLord barks, "that...just fucking sucks/"
Danish whispers, "I don't wanna be all dramatic and shit but I am crying my goddamned eyes out.  >.< *hugs*" to you.
Scruff nods. It does indeed, a great deal.
You whisper, "Makyo squeezes around, "S'okay.  That was me last night and this morning."" to Danish.
Scruff chirps!
Kia is sent home.
Kia has left.
Milehighyena mutters as he is forced to leave. "...time is up, the song  is over. Thought I'd something more to say."
Milehighyena has left.
Miko murmurs, "So it goes."
MegaWolf gruffs. Reality calls.
MegaWolf has disconnected.
Miko snuggles up with Makyo and Danish and all. -.-
Makyo nestles all in, snooof.
Danish cuddles on squirrel and fox and cheetah and all present.
Danish never thought it would happen, but you never do.
Kia arrives from the foyer.
Danish waves.
Scruff hugskiatail
Danish whispers, "How'd you find out?  Mutual friend?" to you.
Kia nods and pats Scruff.
You whisper, "Someone came in last night and told us all, a friend of Pyat.  I kinda lost it for a while c.c  All cried out now, feeling sort of...lost in memory, I guess." to Danish.
Danish whispers, "Danish headshakes.  Buries nose in your fur and still can't stop crying.  I dunno." to you.
You whisper, "Makyo hugs around and holds close, meanwhile.  Rrwf." to Danish.
Danish gets fox fluff and squirrelpoof all damp and idles for a little while.
Somewhere on the muck, Tony_Cheval has connected.
Kia has disconnected.
KurtMRufa resprawl.
Scruff trots over, noses at robodog. Hello!
ZeitOtter arrives from the foyer.
Kuttas arrives from the foyer.
Makyo nose Kuttas.
Danish hugs on Kuttas.
Kuttas hugs Danish.
Mundy gets a working prototype of a MSMV.
Kuttas sadhyenas.
Mundy nibbles Duelist!
Miko chatters, "We all has a sad."
Danish nods and draws Kuttas into the hugpile.
Scruff sneaks out for a little while
Scruff teleports away.
Scruff has left.
KurtMRufa beeps and noses on Kuttas and arfs too.
Somewhere on the muck, Scruff has disconnected.
Mundy eyeballs http://www.amazon.com/Amico-Position-Toggle-Switch-Terminals/dp/B005GI851C/
Djirin arrives from the foyer.
Djirin headperches on Rev.
Reveille oofs, sat on.
Djirin is light as a bodi!
Djirin boid
Reveille is just a tiny thing!
Djirin gets out a magnifying glass? "Hmmm.  Somebody shrink you?"
Reveille has been shrunken for a while.  It lets her actually fit in the door.
Ryan winks out of sight in the sparkling glow of a space/time rift.
Ryan has left.
Mundy hmms..
Djirin headglomfs Rev
Reveille flails!
Djirin mmfs.  wiggly
Zeph arrives from the foyer.
Zeph rowr.
Reveille paws at Djirin and huffs.
Djirin drools helpfully on Rev. c.c
Reveille gahs, covered in cat spit!
Djirin bahs. "Cleanspit"
Reveille growls, "Still cat spit!"
Djirin hmms?
Djirin changes form.
Djirin drools dragonishly then
Reveille eeps and squirms all the more, scruffed by the now-dragon.
Zhorah arrives from the foyer.
Zhorah waves.
KurtMRufa arfatta Rev.
Djirin sheds helpfully on on Rev. furry dwagin
Makyo nuzzat Zhorah, Zeph.  Zs.
Zeph snugga on Makyo.
Zeph whispers, "Zeph full of sad re: Margs. :<" to you.
Zhorah lean on Makyo
Draconis arrives from the foyer.
Draconis rr!
Reveille growlfs atta Kurt!  And then gets covered in Djirin's fluff.
Makyo purrprr, swish on Zeph and Zhorah.
Draconis nuzzles Zhorah!
Draconis nuzzles Zeph!
Zhorah nuzz at Draco
Reveille yays, more dragons.
Draconis licks Danish!  Whitcomb wonders exactly why they did that.
Draconis cuddles Reveille!
You whisper, "Makyo nod, noses.  Very sad fox. Grew up around him." to Zeph.
Reveille purrs and snugs Draconis. ^_^
Draconis hrrrr. "Revsmevs."
Zeph whispers, "Zeph cuddles much. "Did not know him for as long myself, but even so. Want to do something but have no idea what."" to you.
Reveille growls, "Dat's me."
Draconis growfs, "How be's?"
Djirin grumps as Rev gets stolen away. c.c
Draconis cuddle Djiin too!
Djirin hurrahs
Djirin !
Draconis adds more r's. Rrrrrr.
Djirin headglomfs Draconis
Zeph whispers, "Zeph sorry to go on about." to you.
Draconis snrtl.
Draconis growfs, "Teehee, Undine is engrossed in Bastion."
You whisper, "Makyo leans in against and nods, "Not sure what, either.  Could maybe set up something to make one donation for everyone to that thing mentioned in the obit."" to Zeph.
Djirin hms? "Whats that?"
You whisper, "S'okie.  Been torn up since last night, feels good to talk about." to Zeph.
Draconis growfs, "http://supergiantgames.com/?page_id=242"
Polo says, "I found it a bit...  well, reliant on a narrator.  And for something using a beautiful narrator, the Stanley Parable was better done (and being turned into a game!)."
Reveille growls, "It's a really well done, if somewhat short, run around and hit things fantasy game."
Polo says, "I bought it and found it rather dull and Diablo-esque."
Zeph whispers, "Yarr, had thought about donationy thing myself. Am rubbish at organising things though. At first part of me wanted to think it was an elaborate stunt, that he'd turn up laughing to have tricked us." to you.
Duelist licks Draconis!
Danish nuzzles Draconis!
Draconis enjoyed it.
You whisper, "Makyo nodnods, "The thought occured to me, too, but I think only because I didn't really want to believe it.  Setting up a fake obituary and news stories doesn't seem like Margs.  Anyhow, I dunno.  Do you think people would want to do that?  Or would there be something better suited?"" to Zeph.
Draconis growfs, "Diablo-esque is a compliment :)"
Polo says, "Trailer for the new Stanley Parable: http://www.youtube.com/watch?v=bB4AR5Crb54"
Polo says, "That narrator is _amazing_."
Zeph whispers, "It does sound like a good enough idea, to me. Some kind of charitable donation I think would be good regardless, even if not that specific place. Personally, I was thinking of maybe making some kind of music tribute or something." to you.
Miko chatters, "It's quite wonderful."
You whisper, "Yeah.  I can't even figure out what these guys are, other than a motorcycle funeral guard, much less how to donate.  And yeah, was trying to think of any sort of tribute I could make, beyond financial :/" to Zeph.
Miko chatters, "And a million miles away from clicketyclickety grindgrindgrind."
Zeph whispers, "Yeah, I dropped an email their way to see what was going on but haven't heard back yet. Maybe could get interested folks to work together on something, I dunno." to you.
Miko chatters, "Also not fantasy in the "elves and orcs" way but in the "weird ghost things that live on crumbling platforms in the sky" way."
Polo says, "Alas, at the time Bastion was released for Mac the Trine games were on sale and gave me waaay much more fun :)"
Polo says, "Another trailer for Stanley Parable HD remix: http://www.youtube.com/watch?v=AZ-IcS7mRSk :)"
Draconis elects to investigate the Stanley Parable, for he has not before.
Zeph yarr, downloaded that himself but has been distracted by Black Mesa Source.
Polo says, "It's...  like Dear Esther.  Very short and quirky, but exceptionally poignant :)"
ZeitOtter has disconnected.
Somewhere on the muck, Sarusa has connected.
Draconis rararar.
Djirin zipbz2targz
Somewhere on the muck, TealFox has connected.
Draconis smrk.
Djirin nibbles on Draconis while looking innocent.
Polo lost 80 hours to Civ V. x.x
You whisper, "Typed and retyped something to ask people, but just can't quite bring myself to do it right now.  Still kinda raw, I guess :S" to Zeph.
You whisper, "Makyo can ask later, if things go alright at work next week." to Zeph.
Draconis whoah. 30k seeds for black mesa o.o
Djirin purrs quietly, "hurrah thievery! c.c"
Malken liked Bastion
Draconis growfs, "thievery?"
Zeph whispers, "Zeph noddles, makes sense. :3" to you.
Djirin shrugs. "Is this Black Mesa a free game?"
Draconis growfs, "Yes."
Zeph mews, "Free mod, yeah."
Djirin purrs quietly, "Hurrah free then! c.c   Whenever I hear someone talk of bit torrent and the like I only think of one thing"
Draconis growfs, "I only tend to thieve TV programs, and then only for time-convinience rather than having not paid for them ('cause I have.)"
Somewhere on the muck, TealFox has disconnected.
JanusFox le pant.
Zeph mews, "Foxpants."
Djirin depants Janus
JanusFox yips, "Pantaloons you."
You yerf, "Fox++"
JanusFox increments non-atomically.
Djirin noses at the nonatomic fox
JanusFox rubs those noses.
Djirin glomfs foxhand
JanusFox eeps and pulls away, "I guess that makes me steam powered.
JanusFox is steampunkfox?
Zeph < fox.steampowered.com >
Zeph mews, "Note: not actual address."
JanusFox yips, "D'aww."
Polo is at 'We've Got Hostiles'.  It's an exceptional mod.  Pretty much an AAA game except for animation quality.
Djirin has left.
Dachande. says, "So AAB then?"
Dachande. bark.
ZeitOtter is sent home.
ZeitOtter has left.
Kia is sent home.
Kia has left.
MegaWolf is sent home.
MegaWolf has left.
Makyo cuuuurrrl forever.  So out of it this afternoon.
JanusFox perk, "Black mesa source is out?!
Dachande. says, "Yup"
Dachande. says, "I downloaded it, and installed it, but i can't seem to find the program launcher."
JanusFox dances about!
JanusFox yips, "Finally aome bloody good news."
Makyo :o)
Makyo packs for Canada.  So nerrrrvous.
Polo says, "It's in the Steam menu, Dachande."
JanusFox yips, "Don't be.  Canadians are far from the dangerous monsters they're made out to be on the Red Green show."
Zeph mews, "You've gotta stick it in the /steamapps/sourcemods folder, then quit and restart steam and it should show up."
You yerf, "I automatically assume Canadians are awesome.  It's the travel that has me nervous :S"
Danish lows, "What's in Canada, Feral?"
Mundy says, "Feral's done. :x"
Polo is Canadian.
You yerf, "Work.  Week-long sprint."
Polo says, "I just ran the installer that came with it and it showed up in Steam."
Danish lows, "Oh, neat."
You yerf, "Should be awkward meeting all these people in person for the first time, despite having worked with them for a few weeks now."
JanusFox yips, "Did you let them know about your affliction"
Danish lows, "I'm sure they'll just try to glomp you or w/e.  Goes with the territory."
JanusFox pokes that torrent with a stick, "Goooo faster!
Zeph mews, "Being an adorable fox is a blessing, not an affliction."
You yerf, "We have daily video conferences.  They've seen :o)"
JanusFox may beg to differ on that.
Mav arrives from the foyer.
Polo torrented it on his root server in the netherlands, downloaded it from there.
Somewhere on the muck, Tony_Cheval has disconnected.
Polo says, "Well, it's a blessing in looks, but the smell requires getting used to. :)"
Dachande. says, "yeah not in my steam only b game i have is bastion, which i need to tyr one of these days."
Danish lows, "It's good."
Zeph mews, "Might not have the Source SDK, you need to click the dropdown in 'Library' (should say All Games) and select Tools, then grab Source SDK."
Zeph mews, "Right click and pick Install and you should be good."
Dachande. says, "Yeah steam opened and said i needed that, so did that."
Zeph hmm
Dachande. says, "Then i had the source thing, but that went away."
Zeph dunno then!
Dachande. says, "Ehh not a big deal, shouldn't try it on the laptop anyay."
Dachande. says, "not sure what i was thinking getting it on here. :)"
JanusFox yips, "That it's essentially a game from 1998 :D"
JanusFox yips, "It should run on an iphone at this point ;)"
Zeph mews, "True, it's the same base game, but Black Mesa has given it a level of advanced shininess and awesomeitude."
Polo says, "The installer downloaded the Source SDK for me..."
JanusFox yips, "On the other hand, Morrowind cripples me now so."
Zeph mews, "So it ain't gonna run on a Pentium II."
KurtMRufa unidles.
KurtMRufa beep beep then.
Zeph pet on Kurtbot some!
Polo says, "It is not in any way the same base game.  Everything has been re-done using Source 2007."
KurtMRufa houndleans on Zeph.
Polo says, "The plot and set-pieces have been used, but it's all original content (or content from Half Life 2)."
Himmel climbs onto Danish.
Himmel curls up.
Danish scriffles Himmel and hugs on him.
Mundy flumps.
KurtMRufa wants the compute for the damn games to be in the cloud.
Himmel is gonna go eat dinner then come back and be distressed s'more.
Kuttas, too, he thinks.
Zeph mews, "OnLive did that, and they nearly went bust."
KurtMRufa will use this kind of thing as a snappy answer to people who ask about doing supercomputing in the cloud.
Draconis has disconnected.
Zeph mews, "Admittedly, it might be for reasons other than nobody subscribing. Didn't look into it too much."
Zeph mews, "On the basis of having a) a pretty decent computer, b) a mediocre internet connection."
Makyo nuzz at Himmel, Kuttas.
Kuttas pets Makyo.
Polo says, "Supercomputing is already done in the cloud.  I worked on the CERN Grid back in 2005 (I was doing security research) and that was used to find the Higgs very successfully.  I believe that the incoming beam data was 10TiB/sec."
Himmel petpets Makyo. Dashes, a bit.
Polo says, "I would imagine it's more to do with commodity graphic processing hardware being unvirtualisable."
Dachande. go to try and buy some jeans.
Kuttas sneakyhyenas into the shadows. c.c
KurtMRufa metalyawns.
Himmel returns.
Zeph sneaks to bed, full of tired and bleh.
Zeph goes home.
Zeph has left.
Somewhere on the muck, Zeph has disconnected.
Singe has disconnected.
JanusFox rubs that...aww.
MegaWolf arrives from the foyer.
Danish hugs MegaWolf!
TealFox arrives from the foyer.
[public] Sarusa says, "Chinese pet jerky kills at least 360 dogs, one cat in the US. Surprise."
Miko titters a little. Sewageburst in downtown Helsinki. Cars sliding around, people falling over, a stench for blocks and blocks and blocks.
Danish lows, "Like a summer block party where they open the hydrants."
Scruff arrives from the foyer.
Scruff sneaksbackin
Scruff perches somewhere up in Danish's antlers
Zhorah returns
Scruff chirps!
Draconis is sent home.
Draconis has left.
Singe eeks!
Singe has left.
Fiend Plushie bounds after Singe.
Danish pets Scruffy protectively.
KurtMRufa beeps.
Danish scoots closer to Kurt to buff him a little, as well.
KurtMRufa wag wags and does some gleaming too.
Danish smiles.
Scruff takes the opportunity to nose down between perky metallic ears
Himmel is only slightly disappointed that the girl who plays Mary-Kate in Very Mary-Kate isn't actually Mary-Kate.
Miko almost listens to Do You Realize?, but stops himself.
Miko is reminded of Footpad by a loose mental association. :/
Danish urk.
Scruff chirps, "Why is Footpad a :/ ?""
Miko chatters, "Footpad and Margs."
Danish lows, "Still can't believe he got me onto all that music."
Himmel says, "What about Footpad?"
Miko chatters, "With the delighted piling onto and face-washing and all that."
Himmel says, "Oh."
Himmel says, "Right."
Danish :(
Miko chatters, "Does he know?"
Himmel says, "Oh, god."
Scruff mrf. "He's going to be crushed."
Miko has a bit of a cry again.
Himmel says, "Does anyone here have his contact info?"
Miko puts the Field Mice on, like a fluffy blanket.
Himmel says, "Draco might, but he's not on, at the moment."
Danish hugs Miko!
Miko nuzzles Danish!
Miko sees an update from Orin on his Facebook timeline, innocently bollocking on about something or other. Argh.
Scruff chirps, "I see Draco was here, which means Unds'll know now. He'll be very, very upset."
Miko didn't have the gumption to mention but presumably someone did.
Danish puts on "Straight to Hell", the song he got me into the Clash with.
Reveille'splodes.  *poof*
Scruff still trying to work out if he'll be able to make it to Pebble's funeral on Friday. Awesome people should stop dying.
Miko chatters, "I-"
Miko chatters, "Pebble's dead?"
Himmel gives Miko a squeeze.
Scruff nods, "Last Friday."
Miko :(
Harth arrives from the foyer.
Harth says, "Hello."
Miko chatters, "A day later."
Miko chatters, "I only met him once or twice and didn't know him very well, but I loved reading his LJ. I hadn't thought about him for a long time."
Scruff chirps, "Absolutely beautiful person. He'd known it was coming, and had time to prepare, say his goodbyes, which is something, I guess."
Zhorah rumbles, "I dunno pebble"
Miko chatters, "There's not a lot more you could ask, really."
Somewhere on the muck, Azure has connected.
MegaWolf growls softly, "The lion?"
Himmel doesn't know why he knows the name Pebble.
Himmel doesn't know why he knew he was a Lion.
MegaWolf growls softly, "Himmel: Taps"
Himmel says, "... That Pebble is online currently. Which is rather morbid."
Miko chatters, "Pebblepup."
MegaWolf growls softly, "I don't know either of them"
Miko tries to find an LJ dumper.
Scruff chirps, "No, he hadn't been on FM for years, and wasn't ever on Taps"
Danish lows, "Fuck, his one interest on LJ..."
Scruff chirps, "He'd had the name Pebble here when he was"
MegaWolf curls.
Azure arrives from the foyer.
Danish snouts into Megapup.
MegaWolf snugs Danish
Scruff chirps, "He actually had that about eight years ago, Danish"
Acy arrives from the foyer.
Danish ahh.
Acy woof.
Polo noses Azure.
Mav climbs up and perches on Acy.
Danish continues nosing Mega and waves to Acy.
Polo scritches Mav.
Acy topples.
Makyo noses at folks.
Polo goes home.
Polo has left.
Danish lows, "All packed?"
Mav falls over, paws in the air.
Acy puppy says, 'whine whine whine.'
You yerf, "Kind of half-heartedly packing.  Mostly watching here."
Mav wruffs gruffly, "My dog is mute."
Himmel's dog was mute unless she saw another dog or he was teasing her.
MegaWolf's dog only barks if people or dogs approach the house. Of course "approach" can mean 3 houses away or more.
Himmel says, "I think it's horrible that people will surgically disable dogs' vocal chords."
Himmel says, "... Cords."
MegaWolf growls softly, "She "talks" a lot though, not a whine or a bark, more like little squeaks and other odd noises."
MegaWolf growls softly, "Tryin' to talk!"
You yerf, "Dogs <3"
Scruff blinks. People do that? o.O
MegaWolf better run some errands before it gets too late.
TealFox curls
Himmel says, "Devocalization, yes."
MegaWolf growls softly, "Debarking"
Scruff hugs MegaWolf!
Himmel pets Megs.
Scruff chirps, "That's hideous! Like declawing a cat."
Zhorah:<
TealFox has disconnected.
Miko chatters, "Emergency Back-up Greek Alphabet: adolf, beta, gamma, leia, delta, echo, foxtrot, theta, peter, smegma, mocca, corbett, khaki, kyber, mira, hindley, phooey, abercrombie, abba, pasta, hasta, lavista, zeta, jones."
Zhorah blinks
Makyo gonna go get comfortfood sushi.  Back in a bit.
Danish waves.
Scruff hugfox. Fooox. <3
Makyo smoochat folks :3  Be excellent!
Makyo idlehere.
Danish lows, "Fox cuddling services available all day.  Revolutionary."
TealFox has connected.
TealFox sighs at his connection today
Danish pets Teal and his connection both.
TealFox mmm. Pets
Acy says, "Makyerf is going away?"
Acy says, "My puppy bark sounds like the alarm bark of a squirrel."
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Danish lows, "He's going to Canada to catch fish with his paws, I think he said."
MegaWolf has disconnected.
Acy says, "Weird."
Danish shrugs, fopses.
Scruff noses around, sneaks off to bed. Nini!
Scruff teleports away.
Scruff has left.
Acy says, "Darnit puppy quit eating everything that is not nailed down. "
Miko chatters, "It's a PUPPY."
Miko chatters, "What were you expecting?"
Mav chews on Acy.
Acy says, "Ow ow my feet."
Acy says, "I have started calling her piglet."
Duelist stretch out!
Danish lows, "What breed is she?"
Mav wruffs gruffly, "Stink shep."
Acy says, "She is a german shepherd dog."
Acy http://acy.livejournal.com/360495.html
Duelist growls quietly, "Oh my god, look at her."
Duelist - http://i10.photobucket.com/albums/a115/AcyKat2069/Dogs/IMAG0441.jpg
Acy says, "Hahah."
Duelist growls quietly, "Pure awesome."
Acy says, "I gave her a bath and she was soft and fluffy for exactly one day."
Miko looks at the puppy and cries a bit. :4)
JanusFox rolls acy's puppy in things that smell... wonderful.
Acy says, "She does not need help with that."
Duelist growls quietly, "She will be giant dog soon!"
Acy nodnods.
Danish :3
Acy says, "I do not like the food the breeder had her on.  Trying to figure out what to put her on now."
Duelist growls quietly, "I uhh, well food is a weird subject"
Acy says, "She started eating her poop yesterday and i was all D:"
Duelist growls quietly, "Everyone swears by theirs."
Mav wruffs gruffly, "Sheppies are just gross."
TealFox has disconnected.
Acy says, "I read that they do that because of undigested protein leftover in the poo."
Danish punches Mav in the nipples.
KurtMRufa hrfm
Mav nipple squirts.
Danish mm.
Duelist - http://d4fxuz90idxmu.cloudfront.net/images/default/products/large/12069-1.jpg
Duelist growls quietly, "That is what Kostya eats."
TealFox has connected.
Acy says, "The breeder suggested I give her pig ears to chew on but they make her breath smell like feets."
Kia arrives from the foyer.
Mav wruffs gruffly, "Pig ears are yum because they stink."
Kia frinks.
Duelist growls quietly, "Nylabones!"
Duelist growls quietly, "Better than pig ears."
Mav feeds this stuff to his dogs http://www.diamondpet.com/products/diamond_naturals/dogs/
Acy says, "She prefers the ears to nylabones."
Duelist growls quietly, "Wait wait, you're giving your shep a choice?"
Acy says, "Sure, why not?"
Mav wruffs gruffly, "Mine get pig ears and various other animal body parts."
Duelist growls quietly, "Never give a shep a choice"
Acy says, "How else will I know what a high value reward is?"
Himmel says, "Sheps require harsh regimentalization. Strict orders."
Duelist growls quietly, "And make shep work for everything!"
Acy says, "She is only 8 weeks."
Duelist growls quietly, "Hee hee hee. She's gonna own you."
Acy is still teaching her to make eye contact with her name.
Danish lows, "Mrs. Cassidy.  Mrs. Eliza Cassidy.  You stop eating that this *instant*."
Acy says, "I am relatively firm with her.. I guess.  I kennel her and stuff."
Floid arrives from the foyer.
Mav wruffs gruffly, "Remember that dogs don't feel guilt."
Danish waves to Floid.
Floid says, "Arf."
Danish lows, "Dogs only feel it when you tenderly rub their malamute nipples."
Mav squirt.
Danish lows, "It's the only way he'll learn."
Kia says, "All dogs have malamute nipples? "
Duelist recommends the dog beating stick!
Danish lows, "Mav does."
Danish notes that Floid is kind of an anagram of El Fido.
Floid says, "Mav is director general of the USSMNR."
Acy says, "You milk malamute, you have friend for life."
Danish lows, "Whereas chows just want to cuddle afterwards."
Acy cuddles up to Danish.
Acy says, "Going to try walking her for a minute."
Danish shares a glass of milk with Acy before he goes.
Duelist growls quietly, "There is much sitting when first walking a shep."
TealFox winks out of sight in the sparkling glow of a space/time rift.
TealFox has left.
Acy has disconnected.
KurtMRufa arf arf arf.
Somewhere on the muck, TealFox has disconnected.
Acy has connected.
Danish lows, "I told a really good joke while you were gone and everyone laughed and it made me popular."
Acy says, "Yes there was sitting.  We made it halfway down the block then a barking pitbull caused resistance."
Dachande. says, "Tell it again Danish."
Zhorah rumbles, "looked back at this screen and first thing I saw was malamute nipples....]"
Danish isn't in the mood right now.  Gotta pace it.
Himmel rubs Danish. "You -are- Popular."
Danish hugs Himmel!
Zhorah rubs his unpopular on Danish
Danish hugs Zhorah!
Acy says, "Ah, my nipples explode with delight."
Miko loves Danish!  Whitcomb isn't sure he's ready for that level of commitment yet.
Mav gets a towel.
Danish kisses Miko!
Danish goes to smoke.
Floid says, "http://wonkette.com/484178/the-lord-jesus-hates-dr-pepper-and-you-should-too"
Danish has been smoking every time he wanted to cry today, so it's on to pack 2.
Himmel hugs Danish's head.
Miko gets linked to http://creeper.naurunappula.com/org/e9/36/e9362063fc8378ad/0/967709.gif elsewhere. Serendippitydoodah.
Acy o.O
Miko has just been having a cry whenever he feels like it. It's good for you.
Acy says, "Miko did my puppy really make you cry?"
Miko chatters, "I, um. Are you perhaps missing the context?"
Himmel says, "Margs, Ace."
Floid is very taking a nap.
Danish quietly saves that as Danish.gif.
KurtMRufa rrf.
Acy says, "Oh."
Acy says, "Yeah, heh.. when I look at her I think, 'In 8-10 years you'll be gone too.'"
Harth has disconnected.
Mav wruffs gruffly, "Sheppies only live 8 to 10 years?"
Danish stares at fatweaseldog in the hallway, more of a force of nature than an actual thing.
Danish lows, "According to the vet he's 17, but the vet is stupid."
Acy says, "According to wikipedia sheps live 8-10 years."
Mav punishes his sheppie for living too long.
Acy says, "Aww."
Acy says, "She's half husky."
Mav wruffs gruffly, "So she gets to live longer."
Himmel says, "SHepsky?"
Himmel says, "Sheps live longer than 8-10 years, I'm sure of it."
Himmel says, "-Danes- live 8-10 years because of their size problems."
Mav wruffs gruffly, "Generally larger dogs have shorter lives."
Mundy  whistles for a bouncer, and a huge gorilla steps out of nowhere, and hauls out the sleeping furries. "Time ta go, boyz.." he growls..
Harth is sent home.
Harth has left.
MegaWolf is sent home.
MegaWolf has left.
Mundy gooses Dachande.!
Himmel actually thinks Danes are 10-12.
Kia's cat is planning on never dying.
Acy says, "Well hopefully my shep will live longer.  She is supposed to have good genes and stuff."
Somewhere on the muck, Scruff has disconnected.
Miko used to know a cat that was eighteen years old.
JanusFox yips, "And she's black!"
Mav wruffs gruffly, "I had two cats, lived 19 and 21 years."
Acy has an 18 year old cat.  She is gray and has a scratchy meow that sounds like Macy Gray.
Kia's cat is... lessee. Got her in 1997, fall. So, 15.
Danish lows, "According to Wikipedia you are King of Togo, Acy."
Acy says, "Neat."
Miko chatters, "World record is 38 years and a bit."
Acy was also born on the same day Robespierre got the guillotine.
Danish lows, "http://en.wikipedia.org/wiki/Togo"
Danish lows, "Ah, fuck, fucking robots."
Danish lows, "You were King of Togo for roughly 15ish seconds."
Srass appears in a glowing pentagram, with an ominous rumble. He thunders, "WHO DARES DISTURB--", then looks around.  "Oh, um... hiya."  The pentagram fizzles out, anticlimactically.
Srass has arrived.
Danish hugs Srass!
Srass hugs Danish!   Whitcomb jumps into Srass's arms and murrs loudly.
Srass leans on Kurt.
Danish hands http://imgur.com/FNzKY to HRH.
Srass says, "Lame."
Acy uhr...
Srass says, "That's not a photoshop, that appears to have been an actual edit to the page."
Srass says, "By a comcast customer in south carolina somewhere."
Danish lows, "Knology wanted to drill a bunch of holes."
Kuttas arrives from the foyer.
KurtMRufa beep beeps.
Srass says, "Who?"
Himmel says, "South Carolina?"
Himmel says, "Whoever do I know from there?"
Srass snugs Kurt.
Paladin pads in and barks!
Paladin has arrived.
Srass licks Kuttas' muzzle.
Srass also rubs Paladin's ears.
Kuttas licks Srass' whiskers.
Paladin flicks one ear: ~_^ and then the other: ^_~
Miko chatters, "Those are eyes, dear."
Paladin barks, "I am not some Asian emoticon!"
Paladin has always, always used them as ears.
Mav ^..^
Paladin rubs Mav!
Mav gets fur all over.
Danish &._.&
Paladin gets dingo all over.
Mav gets a napkin.
Kuttas pokes at waffles.
KurtMRufa .
Danish pets Kurt and Kuttas.
FoxLord has disconnected.
Kuttas leans.
Miko chatters, "Danish is a former boxer?"
Paladin barks, "I thought he was more like a labrador."
Himmel boxes Danish.
Himmel ships him to Murray.
[ Kuttas looked at you ]
KurtMRufa taps its fingertips together.
Danish eyes Miko.
Danish also dies, no airholes.
Danish headshakes.
Srass pets Kurt's fingertips.
Mundy licks Paladin!
Miko chatters, "& looks like a boxer's ear."
Paladin licks Mundy!
Danish ahhh.  Hard to render antlers on one line in ASCII.
Himmel lean on Kuttas.
Mundy licks Paladin's dingo tongue
Paladin pants, like a dingo! This makes him twice as cute! Even babies are no longer afraid of him!
Kia hungers a bit.
+++++Leanin' 'yena just smelled you!
Danish ruffles Kuttas between the ears.
Kuttas smells hollow.
Himmel disagrees.
Kuttas oopses. ruffle, not snuffle.
Danish hugs Kuttas!
Paladin barks, "Ruffle snuffle. I think I shall put that in my actions."
Paladin ruffle-snuffles Danish!
Danish licks Paladin!
Miko chatters, "Do the ruffle snuffle!"
Srass, come to think of it, gets rid of all the extra accoutrements, and just goes quadrupedal for a while.
Paladin ruffle-snuffles Miko!
Kuttas curls up against him.
Srass nuzzles Kuttas.
Kuttas squeezes.
KurtMRufa tilts its head to the side.
Mundy grunty.
Zhorah pets Kuttas.
Makyo wakesup.  Nuzz folks.
Kuttas is an anthro spotted hyena.  He's slightly taller than average, despite having the characteristic slight-hunchback typical of hyenas, probably due to the long neck which is also typical of the species.  His torso is slightly long, and his legs are slightly short; he's built stoutly, a remnant of his youth spent on the Serengeti, where life makes you hard or leaves you hungry.  He walks di'grade, but erect; even so, he's quick, nimble, and flexible.  He is easily capable of dropping to all fours when needed. On his right thigh, about two hands-breadth below his hip, is a fine, vertical scar, a straight line about three inches long and visible through his fur, which grows gray alongside it. He is leaning very closely on Srass, and appears to be quite comfortable.
[ Leanin' 'yena noticed you looking at him ]
Carrying:
BUTTON: Arcturus 2012! Cause '[Redacted] Happens.'
BUTTON: Arcturus 2012! 'FRONT TOWARD ENEMY'
tribal lance
An Invitation
Zhorah tug at Makyo
Makyo nosenose at Zhorah.
% Connection to furry closed: recv: Connection reset by peer
\end{verbatim}
\newpage

\begin{verbatim}
% Trying to connect to furry: 74.207.243.108 8889.
% Connected to furry.
#$#mcp version: "2.1" to: "2.1"
Welcome to
              _____                 _ _ _   _    _ __   _   ,  SM
               /  '                ' ) ) ) ' )  / /  ) ' ) /
            ,-/-, . . __  __  __  , / / /   /  / /      /-<
           (_/   (_/_/ (_/ (_/ (_/ / ' (_  (__/ (__/   /   )
                                /
                               '
          The first 99 & 44/100% anthropomorphic/Furry TinyMu*

(The SM means that FurryMuck is a Service Mark of the FurryMuck Wizards)
To connect to your existing character, type "connect <name> <password>".
To receive a new character, send mail to join@furrymuck.com
To see the latest news, type "news" after connecting to a character.
To disconnect from a character, type "QUIT".
Use the WHO command to find out who is currently online.
Use the 'whereare' command to find places with active people.
Use the 'wizzes' command to see what Wizards are on line, or the 'helpstaff'
 command to see who of the help staff is on.
Use "connect guest guest" to visit FurryMUCK as a guest.
All users of FurryMuck are bound by our AUP. "NEWS AUP" to read this document.
----

Sadly, FurryMuck has lost one of its own.

S'A'Alis, May 29, 1963 -- September 5, 2012, the Large Furry Marsupial, and a
member of the L'Drey, a space-faring, fox-like species. He was never without his
'Eternally Filled Highly Caffeinated Coffee Mug of Doom'. From 1993 - 1999,
S'A'Alis hosted the servers that FurryMUCK ran on, and was a character creation
wizard 1993-2001. Condolences can be sent to his beloved wife, IceWolf:

M. Vogt, W5910 Genske Road, Black Creek, WI 54106

Life is eternal, and love is immortal,
and death is only a horizon;
and a horizon is nothing save the limit of our sight.
 -Rossiter Worthington Raymond

----
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
Makyo stretches out and yawns toothily, shaking Makyo's fur out.
Players online for whom you are watching:
Acy               Azure             Danish            Floid
KurtMRufa         Makyo             MegaWolf          Miko
Sarusa            Tigerwolf         Triggur
Done.
The next scheduled database save will be in 8 mins, 19 secs.
You place a strategic call to one deity or another.
Makyo disappears in a puff of complacency.
Purple Nurple Foyer(#52464RLJ)
You step in through the door and into a cramped foyer.  Advertising
posters plaster the walls and there's another door right in front
of you (east).  The door is padded purple vinyl, studded in a diamond
pattern.  This is the Purple Nurple, Furrymuck's gay/les/bi nightclub
and meeting place.  Feel free to come on in if you are straight too.. we
don't bite (unless you ask nicely ;)  There is a sign on the wall next to
the door and a notice where the computer used to be, saying that it's now
in the main room.
Players inside the Nurple:
 MegaWolf           Turkzyn            Kia                Kyhwana
 Paladin            Kuttas             Srass              Floid
 Acy                Danish             Malken             Mundy
 Himmel             Dachande.          Duelist            KurtMRufa
 Miko               JanusFox
[Exits: <IN> to the Purple Nurple   <OUT> to Sable Street]
Contents:
PN RULES : READ THIS TO BE ABLE TO ENTER
You enter the PN
Makyo disappears in a puff of complacency.
The Purple Nurple
You are in the Purple Nurple, furry's premier gay/les/bi spot.
The room is large, a converted warehouse - the ceiling's
about fifty feet above the crowded floor.  An entire suspended
lighting grid swivels back and forth in the middle of the room,
rigged with a complex array of lights, lasers and mirrors.
The overall effect is of an alien spacecraft hovering about twenty
feet over the dance floor.  Huge projection wall-screens flicker
images of furries dancing, clips from anime movies, computer
graphics reels and old cartoons.  The music is loud, thumping
techno and house, bass thundering through the gyrating furries
on the dance floor.
To one side is a lounge area, acoustically out of the main thrust
of the speaker stacks allowing normal conversation.  A bar with
every drink known is along the wall of the lounge, and
the floor is scattered with heavy-duty beanbag chairs, funky couches,
and other assorted furnishings, all roomy enough for at least two furs.
A small staircase leads up to the Nurple Apartments.
Contents:
MegaWolf
Turkzyn
Kia
Kyhwana
Paladin
Kuttas
Srass
Floid
Acy
Danish
Malken
Mundy
Himmel
Dachande.
Duelist
KurtMRufa
Miko
JanusFox
All complaints --> Rigel
NURPLE ADULT/PG POLICIES ****** PLEASE READ
Bulletin Board
[foodgeeks] Genn says, "Ah ha, and yes, i see why"
Duelist licks you!
Makyo rrf.
You lick Duelist!
Duelist growls quietly, "Hello foxy"
Name                   Sex        Species     ('whospe #help' for help)
Makyo                  N/A        Anthro Arctic Foxy
MegaWolf               male       White Wolf 'Morph
Turkzyn                Male       Wolf
Kia[idle 5m]           male       ringtailed lemur (lemur catta)
Kyhwana[idle 2m]       male       Young morphic'leopard
Paladin                Male       Big Blond Dingo
Kuttas[idle 21m]       male       spotted hyena
Srass[idle 6m]         male       polymorphic black panther (quadruped)
Floid[idle 1h]         male       Dingo
Acy                    mALE       Chow chow (chow)
Danish[idle 2m]        Manmoose   Manmoose
Malken[idle 1h]        male        bipedal immortal lion
Mundy[idle 29m]        -unknown-  -unknown-
Himmel[idle 12m]       Male       Cat
Dachande.[idle 3m]     Male.      Wolf.
Duelist                Male       Skunk!
KurtMRufa[idle 32m]    robot      greyhound
Miko[idle 3m]          o->        Nut muncher
JanusFox               male       Cross Fox
You yerf, "Hi skunk."
Duelist growls quietly, "How's you doing?"
Srass says, "ttytter sounds like a utility that helps find and download pictures of ttytts."
Kia says, "ttytties"
Srass nods.
You yerf, "Not...well.  Up and down.  Whatever, though :o)  How're you?"
KurtMRufa snrks.
Duelist growls quietly, "Technical illustration and train layouts to keep my mind busy."
Makyo nod.  Packingfox.
Turkzyn sits down.
Duelist growls quietly, "Ah yeah, Canuckyfox, eh?"
Duelist growls quietly, "Where in Canuckville ya headed?"
Turkzyn heads up the stairs.
Turkzyn has left.
You yerf, "Soon enough, yeah :3  Montreal."
Duelist growls quietly, "Montreal? Oh my god."
You yerf, "Hahah, why?"
Zhorah arrives from the foyer.
Zhorah back
Duelist growls quietly, "They're all Habs fans! O.O"
Duelist growls quietly, "You HAVE To wear an Avalanche sweater up there!"
Duelist growls quietly, "That's the old QC team!"
Kyhwana hmms at Srass "Sure! Just on twitter too!
Srass grins.
You yerf, "Awr, haha.  Dunno that I'll even be getting out much, honestly.  We'll see!"
MegaWolf should booze tonight.
You yerf, "Dunno if we'll be working at the Canonical office or a hotel meeting room, really."
MegaWolf growls softly, "Does spiced rum go with root beer?"
Kyhwana purrrs, "http://www.floodgap.com/software/ttytter/"
Duelist growls quietly, "That might be intense, MegaWoof"
Makyo was going to have a rob roy, but it didn't have any sweet vermouth, so it used lillet instead.  Worked out well.
Duelist....rum-n-juice
Duelist growls quietly, "Capt Morgan - Black. Man, that is good rum."
Srass did play with ttytter a while back.
Duelist played with tits awhile back.
MegaWolf growls softly, "I have oakheart."
MegaWolf growls softly, "It's not bad, prefer the Captain"
Duelist growls quietly, "Oakheart and root beer. Hmmm!"
Zhorah noses Duelist.
Duelist growls quietly, "I can't say, man. I wanna say 'sure' but I dunno."
Duelist licks Zhorah!
MegaWolf hrr. Let's see. Oakheart, Bombay Sapphire, Crown Black and butter shots.
MegaWolf growls softly, "I don't think I have any coke."
Duelist growls quietly, "No juice?"
You yerf, "Sapphire straight from the bottle."
MegaWolf growls softly, "I have a lot of that Walgreens glass bottle soda because apparently it's discontinued"
MegaWolf growls softly, "Cranberry, oh and I do have tonic water, forgot about that"
Duelist growls quietly, "Makyo!"
You yerf, "Gin and cranberry is good!"
You yerf, "Duelist!"
MegaWolf growls softly, "Root beer, cream, black cherry, orange creme, and strawberry creme."
Duelist growls quietly, "Never pull from the bottle....well, in extreme circumstances its ok"
Miko chatters, "You have Kina Lillet?!"
MegaWolf growls softly, "Cranberry and... gin? I don't think I'd like that. n.n"
MegaWolf doesn't like gin except in G&T
You yerf, "Ah well.."
Duelist totally wanna go drinking, in Vegas, with Makyo. Bring your boy!
Duelist will bring his!
Makyo oooh, nodnod ^^
MegaWolf growls softly, "I need to stop buying other booze and just buy vodka"
Miko kinda wants a drink. Hasn't had one in ages.
Makyo has... this, Miks: http://en.wikipedia.org/wiki/File:Lillet.jpg
Duelist growls quietly, "Vodka and Rum is all you need."
MegaWolf never has amaretto left over after a con because people drink 8 oz glasses of it when he's not looking.
Duelist growls quietly, "Tho the mixers are nice"
Duelist growls quietly, "Mostly anything made by Dekuyper\"
Kyhwana nod at Srass "It's neat.
Duelist growls quietly, "Hot Damn! Is pretty awesome."
Duelist growls quietly, "Cinnamon schnapps."
Miko chatters, "Ah, it sez "currently goes simply by Lillet or Lillet Blanc" on the Wikipedia page."
MegaWolf growls softly, "Buttershots and cream soda? (instant diabeetus!)"
Miko brought a bottle of Hot Damn! from the States once and never figured out anything reasonable to do with it other than pass the bottle around as a sort of prank. c.c
MegaWolf growls softly, "I saw an ad for cinnamon whisky at the liquor store next to the Chinese place tonight"
MegaWolf growls softly, "Sounded kinda good, actually."
Miko chatters, "No, wait!"
Miko chatters, "Is Hot Damn! the one I like?"
Duelist growls quietly, "It's good on a cold evening, Miko, for just that, yes."
MegaWolf growls softly, "Fireball, I think."
Khyber arrives from the foyer.
Miko bought a bottle of something violently pink that was pretty horrible, but he's had this stuff with a..
Miko chatters, "Ah, Fireball's the one I like. Shots. :3"
Duelist growls quietly, "Hot Damn! is not pink."
Miko chatters, "What's the one I don't like, then?"
MegaWolf growls softly, "Need Stoli"
Miko shakes Duelist. "Tell me!"
You yerf, "1 part Bailey's, 1 part Kahlua, dash of hot damn, and you've got an oatmeal cookie."
Miko falls over.
You yerf, "Usually a shot."
Duelist growls quietly, "What what what?"
Duelist growls quietly, "Wait"
KurtMRufa just pours some johnnie walker blue.
Somewhere on the muck, Herefox has connected.
MegaWolf growls softly, "I never buy Stoli for a con because it's just barely on the edge of "too expensive for you ungrateful schmucks""
Khyber walks in, thinks Miko means Aftershock.
Duelist - http://tinyurl.com/26j9tfu
Makyo has scotch, but knows all of the boy's drinks.
Duelist growls quietly, "Taht is Hot Damn!"
MegaWolf growls softly, "I did buy Cointreau a few years ago though"
Acy had to stop and sing to his puppy.
Khyber wonders if he sgill has that bottle of tres generaciones...
Duelist growls quietly, "What is THIS?"
Duelist growls quietly, "A 'Hot Apple Pie Shot'"
Acy says, "And she whined."
Makyo's shep will sing along with choral music :3
Zhorah noses Khyber.
MegaWolf still thinks a chocolate cake shot is bizarre.
Duelist growls quietly, "1 part apple rum, 1/2 part Hot Damn!, graham cracker garnish."
Kuttas licks Duelist!
Duelist licks Kuttas!
Mundy ta-dahs http://bit.ly/U8uTiF
Duelist growls quietly, "Hi, Y3NA!"
Khyber pets Zhorah
Kuttas says, "hey."
MegaWolf should just do shots of Crown, really. Also wishes he'd gotten to try the JB Devil's Cut.
Duelist growls quietly, "Is that what I think it is, Mundy?"
Mundy says, "Probably."
Duelist squeeeeeeeze Kuttas!
Duelist growls quietly, "How ya doin', Y3NA?"
Mundy's missing the O-F-O, SPDT switch.
MegaWolf growls softly, "Cinnamon schnapps, vanilla vodka, and spiced rum would be a Chai Tea."
Makyo not really a shot fox :/  More a neat-rocks-on-the-side or a tall drink fox.
Duelist uses O-F-O DPDT switches
Duelist has a stupid amount of flavored vodkas.
Duelist growls quietly, "Including CHOCOLATE cake vodka."
Srass says, "I take it O-F-O doesn't mean 'Out Fucking Off' in this context?"
Duelist growls quietly, "On Off On!"
Srass hmms doubtfully.
Duelist growls quietly, "Don't you doubt me!"
Duelist growls quietly, "It can't be an Ooooooooo! switch!"
Srass says, "That's true, if it were an OOO switch, it would be made by the Omniscient Overlords of the Omniverse, and they're all Out Of the Office."
MegaWolf growls softly, "On and off are small enough words that I don't normally see them abbreviated like that n.n"
Khyber whips out some foxnip that smells and tastes of root beer
Mundy says, "O-F-O is easier to type than On-Off-On."
Kuttas is okay, probably.
Srass nods.
Vetiver arrives from the foyer.
Mundy says, "And those circuits actually work as desired too."
Duelist growls quietly, "Yeah, me too"
Duelist growls quietly, "Build me 32 of those, Mundy!"
Duelist cracks the whip!
Kia has disconnected.
Mundy says, "You said you only had 16 switching machines. :)"
Duelist growls quietly, "Oh, ok!"
Duelist growls quietly, "Build me 32 of those, Mundy!"
Duelist growls quietly, "Err"
Mundy says, "Fail. :P"
Duelist growls quietly, "Build me 16 of those, Mundy!"
Duelist cracks the whip!
Duelist has been drinking! He is prone to fail and horny.
Mundy actually ordered one of the switching machines.
Duelist growls quietly, "Hopefully not at the same time!"
Miko is not a shot sqrl by himself.
Acy says, "Yeeagh!  Puppy's first fart! D:"
Mundy says, "Porno Disaster."
Duelist would have sent you a switching machine.
You yerf, "Get used to those, Acy :|"
Acy horrified.
Mundy says, "It's very likely that I'll burn it out in testing."
Khyber laughs at Acy
Miko chatters, "I put away quite a lot of Fireball as shots at Oswaldo's once when there was a bunch of people around and I was being pestered to ditch the diet for the evening and get drunk."
Duelist growls quietly, "I dunno, these fuckers are tough."
Dralen arrives from the foyer.
Srass says, "You don't need to get used to those.  You just need a cork."
Acy says, "She looks all guilty."
Dralen meeeeeeeeeeeeeeeeps.
Srass says, "Or possibly a cork with a double reed in the middle."
MegaWolf's dog doesn't do that unless her tummy doesn't agree with her food, which is why she's on Evo Herring and not Beef now.
Kuttas pets Dralen.
Duelist growls quietly, "Ya know....we should all meet in the middle"
Duelist growls quietly, "And drink"
Srass licks Dralen.
Khyber arfs at Dralen
Duelist growls quietly, "What is the middle?"
Mundy says, " http://www.youtube.com/watch?v=z1n3JBQdN84 "
Duelist looks at Vetiver.
Zhorah want hugs
Kia has connected.
Dralen smooches at Srass and leans on Khyber.
Kia frinks.
Khyber wraps dragonfox in tails
Dralen wiggles!
Kuttas reads his 1st ed ad&d books.
Vetiver hmms at Duelist?
Danish hugs Kuttas!
Somewhere on the muck, Tony_Cheval has connected.
Acy hahaha, he still has some of those.
MegaWolf's dog is too damned smart.
Danish rubs, waves, so on, out.
MegaWolf growls softly, "Is ridiculous!"
Duelist growls quietly, "we got a Y3NA in AK, a droxy in ON and a jaquar in MX. What is 'the middle'"
Duelist growls quietly, " ??"
Srass smooches Dralen.
Danish has disconnected.
Khyber softly says, "the middle is here in California!!!!"
Acy puppy does not like being petted very much. .(
Kia excludes the middle.
Acy :(
Duelist growls quietly, "Apologies, of course, to the Aussie and NZ furs who would put 'the middle' out in the middle of the ocean."
MegaWolf growls softly, "I made a little tether tennis ball on a rope thing to play with her this afternoon. Didn't take her long to figure out to go for the rope and not the ball if she actually wanted to catch it, but she mostly chased the ball anyway."
Vetiver quorks, "Alaska throws off that middle a lot, so it'd be like Montana or Wyoming."
MegaWolf growls softly, "When she got tired of playing, she finally managed to tug it away from me... and wrapped the rope around her paw with it before she lay down to chew on the ball, so I couldn't pull it away anymore."
Duelist growls quietly, "Oh, Acy....the puppy will not like to be touched til, like, week 16."
KurtMRufa licks its nose calmly.
Duelist growls quietly, "Kostya would not let me touch him until about 4 months old."
Duelist growls quietly, "I hear that is a shep thing."
Acy says, "Really?  What's up with that?"
MegaWolf growls softly, "Mine only likes to be pet when -she- wants to be pet, but that's most of the time. Too much petting and she'll wiggle away though."
Duelist growls quietly, "I couldn't touch Kostya for a couple months and now I can totally snug with him."
Duelist growls quietly, "Very affectionate doggie"
Duelist growls quietly, "But it just takes time."
Srass noses folks, wanders back to the store for a bit.
MegaWolf growls softly, "Don't remember any specific no-touchie age though, she slept on my mom's head her first few nights home."
Srass recoils as a team of carpenters arrive.  Brandishing belt sanders, they smooth him down until he's all gone.
Srass has left.
Duelist growls quietly, "Kostya, when he was a pup, would actually move away from me when I came near. Heh."
Mundy *touches* TIGRSKNK.
Acy says, "You forgot to keep bacon in your pocket."
You yerf, "Zephyr did that too, really, took him being sleepy for petting."
Acy says, "She just fusses a lot when she's sleepy and moves to a different spot to sleep."
KurtMRufa remarks, "Animals are funny."
Acy says, "She tilts her head adoreably when I whistle."
Acy daaaawh.
Duelist licks Mundy!
MegaWolf growls softly, "Mine was a little carpet shark for awhile though, nip nip nip."
Miko chatters, "Did Seapunk ever become a thing?"
Duelist growls quietly, "Do not forget"
Duelist growls quietly, "You are new alpha"
Duelist growls quietly, "She is still getting used to you"
Himmel says, "Piratepunk count, Miko?"
Himmel says, "Because that's pretty popular."
Acy says, "Yeah I know."
Duelist growls quietly, "Soon she will luv you more than anything!"
Duelist growls quietly, "And be the most bestest and loyal friend you have"
Acy could use one of those!
Miko wishes he could have a dawg.
Himmel friends Acy. On FaceBook.
JanusFox is loyal like a fox.
Duelist growls quietly, "Kostya is my most loyal and bestest friend!"
Duelist growls quietly, "The Noble Dog."
MegaWolf luff teh sheppy puppy.
Acy eek?
MegaWolf growls softly, "Of course they love their treats more than you ;)"
Duelist growls quietly, "Not mine"
Acy says, "She especially likes the bacons flavored treat bits."
Miko chatters, "They're not *cats*."
Acy says, "And she likes turkey and hot dogs."
MegaWolf growls softly, "Mine's favorite is liverwurst"
MegaWolf growls softly, "Also she likes coconut."
JanusFox likes those things to, but not combined.
Acy says, "I haven't tried liver."
Duelist
MegaWolf growls softly, "We can tell when she absolutely loves something because she practically floats towards you like a cartoon"
Duelist's dog like steak
Duelist growls quietly, "And chicken"
Miko chatters, "Dogs are nuts for liver, as a rule."
Duelist growls quietly, "And hamburgers"
Paladin is nuts!
Miko chatters, "You feed your dog steak? You're spoilin' that pup. :3"
Acy says, "I made some liver bits by boiling and chopping liver and drying it out in the oven but I froze it all when otherdog didn't like it."
Miko gives Pal liver.
Duelist growls quietly, "Of course I feed him steak!"
MegaWolf growls softly, "I made a coconut lamb for Easter and she ran into the kitchen and stared at me the entire time I was making it."
Duelist growls quietly, "he watches, guards and defends my house!"
MegaWolf growls softly, "The instant I took the top off the coconut flavor"
MegaWolf growls softly, "Dog appears out of nowhere!"
Acy says, "Hehe."
MegaWolf growls softly, "So we got coconut flakes for treats."
Kia thought vultures were the ones who loved liver. every night.
Miko's sister likes raw bloody liver.
Himmel says, "Ew."
MegaWolf's likes steak but it didn't get a "huge eyes floaty dog drooling all over" reaction like the liverwurst.
[public] Frnkzk says, "Come on, everything's better with dinosaurs. Weren't you ever kids?"
Duelist growls quietly, "Remember the rule. If you wouldn't eat it, don't feed it to your dog."
Himmel says, "'Wouldn't'?"
MegaWolf growls softly, "I wouldn't eat herring but that's more due to my general loathing of seafood :P"
MegaWolf growls softly, "She luvs her herring Evo"
Himmel says, "I wouldn't eat meat, but I'm not going to kill my potential dog."
MegaWolf growls softly, "She has a sweet tooth too, we finally gave in and got her some carob chip treats."
Makyo nits Himmel.  There.  Stuff to pick :o)
Duelist petpetpet MakyoFOX
Himmel knits Makyo. Perfect for fluffs.
Makyo's shedding could easily make quite a cozy coat!  So luxurious..
Makyo nosenosenose Duelistskunk.  Prf.
Himmel wears Makyo. "I can feel you all around me."
Kia has disconnected.
MegaWolf growls softly, "Now I want two sheppies."
You yerf, "Close.  Against your skin.  Rrrr."
Duelist wants 11 sheps
Himmel purr.
Acy says, "You cannot have mine!"
Duelist growls quietly, "But that was Kostya's idea."
Duelist growls quietly, "I do not necessarily agree."
Acy squeezes his little piglet pup!
You yerf, "Zephyr wants 1 more dog.  A mutt."
Zhorah hug so much Makyo
MegaWolf growls softly, "One of our dog trainer's friends has 7 Australian Shepherds."
Makyo hughuuuuuug around Zhorah.
Kuttas wipes his nose.
Duelist growls quietly, "I asked Kostya....3 dogs, 7 dogs, 11 dogs....and he got all excited when I said 11 dogs!"
MegaWolf growls softly, "I know they're not quite as nutty as border collies are but that's still a lot of neurotic dog in one house!"
Acy says, "3+ of any animal is crazy cat lady territory."
Acy says, "Except maybe fish."
MegaWolf growls softly, "We may get a second one when she's 5-ish"
MegaWolf growls softly, "I'd love to get a golden but the breed is a huge cancer magnet :|"
Himmel o-o Mega.
Duelist growls quietly, "Is dumb!"
Duelist growls quietly, "Blonde dog."
Himmel says, "Very dumb."
MegaWolf growls softly, "Nu-uh. Only the goofy show dogs!"
MegaWolf growls softly, "Gun dog is smart!"
Himmel pff!
Himmel says, "Get a 'Mute."
Duelist growls quietly, "That is a yellow lab"
Duelist growls quietly, "Not a golden"
MegaWolf growls softly, "Goldens are gun dogs too!"
You yerf, "Zephyr's half gsd, half border collie.  There's a neurosis or eight in there."
Miko chatters, "Poodle is arguably the smartest dog, which seems nuts."
Acy says, "If you get a yellow lab you have to name it Butter."
MegaWolf growls softly, "Eh, mostly the border collie half"
Miko chatters, "GSD's up there too though."
MegaWolf growls softly, "Borders are -nutty-"
MegaWolf growls softly, "Cute tho'"
Miko chatters, "Our husky/landseer cross was clever enough to be a smartass."
Acy says, "If I get another dog it'll be a giant schnauzer."
You yerf, "He's a nut."
Duelist - http://www.petmedsonline.org/top-10-smartest-dogs-in-the-world.html
Duelist growls quietly, "Taht list fails at #4"
Zhorah rumbles, "We have a sheep dog and a basset, and my kitten"
Duelist growls quietly, "Golden retriever is dumb"
MegaWolf bites Duelist!
Duelist has defense mechanism!Be careful!
MegaWolf tranqs Duelist for That Operation[tm]
Duelist tranqs MegaWoof for an operation!
Duelist growls quietly, "You don't need those things dangling about"
MegaWolf growls softly, "Descenting isn't nearly as bad as that!"
Duelist growls quietly, "You take something from me, I take something from you."
Himmel takes Duelist's stereo.
MegaWolf takes Duelist's wallet so he can't pay the vet. :D
Duelist growls quietly, "Sorry, I can just dip into the casino stash"
Duelist growls quietly, "And that's in a safe!"
MegaWolf uses the wallet to hire Ocean's 14.
Duelist growls quietly, "Nah nah, just face it"
Dachande. falls over, defeated by a very delicious dinner.
Duelist growls quietly, "You cut on me, you get deballed"
Himmel snrks at D.
Duelist growls quietly, "Snip them fuckers right off."
Himmel says, "Is Kostya fixed?"
MegaWolf growls softly, "Skunks need that operation to be outstanding members of society!"
Duelist growls quietly, "So do wolves"
Dachande. says, "Outstanding, or upstanding?"
MegaWolf growls softly, "Both!"
Dachande. prevers to be instanding.
Himmel prefers to be downstanding.
MegaWolf hmphs and just gently nips Duelist's nose
Himmel, beta as fuck.
MegaWolf growls softly, "Bad mephit"
Acy would guess that Kostya has his balls.
Duelist growls quietly, "Kostya is not fixed, correct."
Himmel nods at Duelist.
Acy says, "That does not seem like the sort of thing Duelist would do."
Dachande. pushes Himmel to the ground so he feels happy.
Himmel whimpers.
Dachande. sits on him.
Himmel's muzzle finds its way into places.
Duelist growls quietly, "Ain't no one convinced me that fixing my dog is good for him."
Kia has connected.
Kia finishes watching an old ep of Lost Girl. Then, the Doc.
Himmel points out that good for him is rarely the concern.
Kia calls up Comrade Stalin, who shows up in his orange vest with a broom to sweep the sleepers off to their homes.
Danish nips the arm of whoever's trying to wake him up and scurries back to his den.
Danish has left.
Srass arrives via giant ladle, landing in a quivering blob.  In the distance, Satan's lunchlady shouts, "Snaaaaack!"
Srass has arrived.
Duelist growls quietly, "Some butch fucking dyke stood up in front of the county commissioners and told a story about how cutting off my dogs balls will stop the irresponsible owner across town from having his dog breed....but I didn't follow that logic."
Himmel says, "There is no logic."
Himmel sighs. People.
Kuttas hugs Srass.
Srass hugs Kuttas.
Makyo sheds on Himmel: http://makyo.drab-makyo.com/pretties/arctics/10985897.jpg
Duelist growls quietly, "Then I called that bitch on it and she got all offended."
Kyhwana beeps at Srass "What did you get from the store?
Duelist growls quietly, "Just cuz some dyke don't wanna see male genetalia don't mean I should cut my dogs nuts off."
Duelist growls quietly, "STOP LOOKING, bitch."
Himmel brushes Makyo in a tub.
You yerf, "Christ, drop it."
Duelist growls quietly, "That fox had a fur-splosion!"
Srass licks Kyhwana's nose.  "Whole grain tortillas, for the cranberry almond chicken salad I got earlier."
Kyhwana oohhs
Srass got some Framboise Lambics on the earlier trip.
Kia chuckles a bit. His mother is in favor of neutering all dogs 'cause dog balls are icky.
Acy says, "The penis is a weapon.   A tool of opression!"
Khyber pats a fullwuff
Acy says, "The gun, however, is good."
KurtMRufa taps its fingertips together.
Kia says, "All the bullets and bombs and missles are shaped like dicks. "
Khyber has disconnected.
Makyo gonna bath.  Probably also take half a muscle relaxant.  Will sleep well tonight.
Himmel pets Makyo.
Makyo nuzznuzz at Himmel.
Acy noses Makyerf.
Srass leans over and nibbles interferingly at Kurt's fingertips.
Makyo pett on Acymuzz.
Acy says, "Makyo I'ma visit you at the store somedaya"
Acy!
You yerf, "Please dooooo :D"
Makyo okay really bath.
-- You have left channel 'public'
Kia secretly loves Doctor Who.
Acy says, "Now we all know."
Kia says, "Shh. "
Himmel wants to watch Doctor Who, but he isn't allowed, 'cause he really only wants to watch from season 5 on, and he's been forbidden from doing so until he watches the first four.
Himmel has psychotic Whovian friends.
Miko chatters, "Oh shit, that's what I was gonna watch but forgot."
Kia thinks it's best to start with Eccleston.
Dachande. says, "Watch a couple bakers, then the dude after him, then watch eccleston, then proceed."
Kia says, "It's made for people who know fuck-all about Doctor Who, like most of us who haven't been watching it since 1960. "
Himmel says, "THe First New Doctor, Kia?"
Kia nods.
Himmel says, "I saw some episodes."
Himmel says, "He's cool."
Himmel says, "But."
Himmel says, "I want Matt Smith."
Miko chatters, "I recommend coming down with a wicked stomach flu and lying on a couch watching the first few seasons straight through on a laptop, with a bucket by your side."
Kia says, "Also, don't fall in love with him.  He only does one season, and that next guy is even better. "
Himmel knows.
Duelist growls quietly, "ShutthefuckupDachthereisnoTomBaker!!!!!"
MegaWolf needs to find an atorrential way to download everything since The End Of Time.
Himmel chuckles at Duelist.
Himmel says, "But seirously."
Duelist growls quietly, "It NEVER happened!"
Himmel says, "Matt Smith."
Himmel says, "DO Want."
Kia has a lovely Tom Baker scarf.
Dachande. says, "Oh and you have to see all the episodes with Harriet Jones, and Sarah Jane Smith."
Himmel says, "My First Who Fan Friend made the mistake of showing me a clip from the premiere of season five."
Himmel says, "And then forbidding me from watching more than the first episode."
Dachande. says, "Ahh."
Himmel says, "That dick."
Miko chatters, "Is that the one that starts with them on the run?"
Kia's never watched a Tom Baker, but it's not like anyone else has a convenient visual identifier.
Himmel says, "Fishy custard, Miko."
Dachande. nods, "The reluctant regeneration."
Miko chatters, "Ohhh. Nowhere near as good as the opening of season six."
Himmel Wants to see the opening of season six, he supposes.
Miko chatters, "But watch 'em all, anyway. You don't wanna miss The Empty Child/The Doctor Dances."
Miko chatters, "Or Blink."
Kia prrrrs at that one.
Himmel says, "I can go back and watch them. I'd be fine with that."
Himmel says, "But."
Miko chatters, "You may wanna miss the ones with the farting aliens."
Kia says, "Blink is like the first Alien. They introduced an amazing thing, which they later ruined. "
Himmel says, "Weeping Angels/"
Himmel says, "?"
Kia nods.
Miko did not care for the return of the Angels. Apparently they're coming by for a third go 'round soon. <.>
Himmel says, "Yeah."
Dachande. says, "And the warewolf, have to see the warewolf."
Kia nods. They're like the new fucking Daleks.
Himmel says, "They might take Amy, Meekz."
Dachande. says, "Oh and Turn Left."
Kia says, "That one has cat people. "
Dachande. says, "The Library."
Dachande. says, "Okay just all of the Catherine Tate season."
Miko chatters, "Silence In The Library."
Miko chatters, "Gridlock!"
Dachande. says, "Yes that"
Dachande. says, "And Gridlock, it has kittens."
Miko chatters, "Gridlock has a cat dude and a human lady who've had KITTENS."
Kia prrrs. Catherine Tate was the shiz.
Kia says, "That black lady, not so much. "
Himmel downloads an album that features a girl yelling at him that he's a bad person because he's male.
Dachande. says, "Donna made Rose look like a waste. Martha is just badass."
Kia says, "Martha was boring. "
Dachande. says, "Later martha, not early martha"
Miko chatters, "She was a bit of a non-entity in comparison to Donna or Amy, yeah."
Duelist growls quietly, "You are the people who walk up to a Dr Who Pinball machine and ask 'who are those guys on the glass?'"
Kia says, "Rose was chavvy, but she grew on you. "
Dachande. says, "Best part of Rose was her mom. And i watched the classics on netflix too."
Kuttas taps the butt of the spear he is carrying on the ground. Thump, thump-thump.... A dark mist spills out across the ground from that point, flowing outward, chilling the feet of those nearby.
Himmel says, "Nah, nah, I've had the classic doctors beaten into me, Duelist."
Himmel says, "That one what with the coat and stuff."
Duelist growls quietly, "I'm just kidding, really, except I had someone ask me that."
Kia rubs his thumbs. Is it normal for piano to give calluses? Also, he's sort of excited that he's now understanding why people play way up on the keys sometimes.
Himmel says, "... Really?"
Himmel says, "That's sad, D."
Himmel says, "THough."
Himmel says, "I live in Kentucky."
Himmel says, "I didn't even -hear- about Doctor Who until senior year of High School."
Duelist growls quietly, "They think Dr Who started in 2005."
Himmel nods.
Kia laughs his ass off at a certain line.
Acy remembers watching it on PBS as a little kid. o.O
Himmel says, "Well, I'd seen flashes of it on..."
Himmel says, "Uh..."
Himmel says, "Random antenna tv channels."
Himmel says, "Cannot remember for certain. But I only know what it was now."
Duelist as well, Acy. Used to sneak out of bed to watch it on PBS!
Dachande. says, "It was often shown late night pbs."
Dachande. says, "The only station with the balls to play brittish tv."
Himmel puts big, square, plastic glasses on Duelist. "Nard."
Dachande. says, "But really even if ya want to start with Smith, you'll clear through that swiftly, go back and see the rest."
Himmel will!
Himmel is certain he'll be hooked, by then.
Kia says, "More like: We couldn't come up with anything worthwhile to put on our smarty tv channel, so we had to take it from the Brits. "
Duelist growls quietly, "Oh no no, MomTiger was a huge Dr Who fan. USed to go to all the conventions and everything."
Kia says, "Or at any rate, we couldn't appropriate funds for anything to put on our smarty tv channel. "
Himmel says, "... Maybe I'll start watching it, Naruto: Shippuden, and Red vs. Blue at the same time."
Himmel says, "I've made deals with friends."
Dachande. says, "Dude, naruto doesn't end."
Himmel says, "I'll watch their TV Shows, if they watch mine."
Himmel says, "Well, I know."
Himmel says, "But."
Dachande. says, "Just warning ya, you think you're close to the end, you're not."
Himmel says, "And a bunch of it is Filler."
Kia thinks Himmel should watch House of Cards.
Dachande. says, "Good though, very good."
Himmel says, "House of Cards?"
Dachande. says, "Also watch The Killing."
Himmel yeegh.
Kia says, "Brilliant Brit political thriller TV show. "
Himmel says, "I had to find someway to convince friends to watch Supernatural."
Himmel says, "So, I agreed to trade."
Kia says, "Has Ian Richardson, who is so fucking awesome. "
Himmel says, "My one friend who watches Supernatural has seen all of it. Except the two best seasons, 4 and 5."
Kia says, "And his character's intitials are FU. "
Himmel teehees at Kia.
Himmel says, "I dunno. I'm not big on Political thrillers."
Kia says, "It's really, really fucking good. "
Himmel will give it a testdrive.
Kia says, "Francis Urquhart is a monster, and yet delightfully charming. "
Dachande. Fuckit torrents latest who.
Dachande. says, "There's only 3 out so far right? Asylum, spaceship and town yeah?"
Paladin barks, "Yups."
Kia says, "Yesh. "
Himmel says, "If anyone likes modernized, edgy fantasy staples and/or grim takes on judeo-christian mythology, Supernatural is an awesome fuckin' show."
Kia suggests Lost Girl if you like urban fantasy. And hot people. And really short bartenders.
Himmel nudges Dach. "Though, I dunno how you took to it. Didn't ask, afterward."
Himmel says, "I'm okay with urban fantasy."
Himmel googles Lost Girl.
Dachande. says, "Supernatural is a very nice show. It's got a good feel to it, the characters are serious with humor mingled in so it's not too daunting. The writing is witty an the characters are belivable. Also unlike most new scifi shows there's noone from a previous show I recognize so it's not like watching Farscape go through the Stargate."
Dachande. says, "While I've not got around to watching more of it, I would reccomend Supernatural and will most likely watch it myself."
Himmel snickers at Dach.
Himmel says, "Well, the actors are from other things, but they're wildly different."
Vetiver hears 'urban fantasy' and thinks of Lord of the Rings, but set in South-Central.
Himmel says, "Jared Padalecki, who places Sam, was on Gilmore Girls before SPN."
Himmel says, "Er... Who plays."
Dachande. Boooos fucking 500 seeders and 2000 leachers.
Kia says, "Starting at the beginning isn't strictly necessary with Lost Girl, but I wouldn't start with watching, say, the current episode on Sci Fi. It's the end of the season and shit's getting real. "
Dachande. says, "Yeah but I never watched Gilmore Girls as I am not vagina."
Himmel says, "Jensen Ackles, who plays Dean, was on The Young and the Restless. And... something else."
Dachande. says, "Again, penis."
Himmel says, "Oh, yeah!"
Himmel says, "Dark Angel!"
Makyo mrrp, mrrp.
Kia says, "Urban Fantasy is, say, Buffy. Or Charles de Lint's ten thousand books that are all the same. "
Himmel says, "Oooh, I loved Angel."
Himmel says, "And Buffy, except for a lot of the main characters."
Dachande. says, "Buffy was good until the weremonkey then it got a bit silly."
Himmel liked buffy for Willow and Seth Green's character and Angel and Spike, kind of.
Himmel says, "But Spike is totally better with Angel than Buffy."
Himmel says, "I mean that in every way possible."
Kia needs to finish watching Buffy sometime.
Dachande. says, "Boo ep2 finished before ep1"
Dachande. says, "Damnit! I keep forgeting to not download everything into the porn folder =P"
Kia says, "It's all porn. Just some of the people are wearing more clothes and fucking less. "
Kuttas says, "What is this 'Buffer' and 'Spike' of which you speak?"
Dachande. says, "Late 90"
Kia says, "Buffy: She was a vampire slayer. "
Kia says, "Spike: He was a vampire. He also briefly showed up in a Ninth Doctor episode, I think. "
Dachande. says, "Er late 90's tv urban fantasy dramas revolving around vampires, witches, lesbians, and david boreanas. who i think is spelled his name right, but hes the guy on bones."
Himmel says, "Yeah, that's his name."
Kuttas snerks. "Bones."
Kia says, "Looking, by the way, like shit warmed over. "
Himmel says, "David Boreanas is a studmuffin."
Himmel says, "I'd give him Bones."
Kia tsks at the Doctor. Never realized he wore fucking CLIP-ON suspenders.
Acy hahah.
Dachande. says, "Well yeah he's a normal guy, not going to have tailored buttons."
Kia says, "Proper suspenders are the Height of Fashion. Clip-on suspenders are trashy. "
Kia, sort of baffled by this new firm he may move to.  They're casualer. But lemur has a certain personal brand-style that involves his suspenders.
Azure arrives from the foyer.
Azure yips, "BHello, creatures.""
You yerf, "Hello, fox."
Himmel says, "Casual and vintage formal are easily conbined, Kia."
Duelist growls quietly, "Hello miniscule foxy!"
Himmel... combined*
Dachande. says, "the last guy wore chucks with suits, they tend to have a little something common among the fashion, it helps them blend in."
Dachande. says, "Except for the question mark doctor, but we don't talk about him much."
Kia --hat, suspenders, french cuffs and button collars.
Himmel says, "Eccleston was hugely cas."
Dralen flops.
Duelist pets upon diminutive vulpine!
Azure does not really care for sneakers with suits.
Azure noses Duelist, "Hello, giant skunk."
Himmel says, "Black jeans, boots, teeshirt, leather jacket."
Kia regularly wears sneakers with his suit, until he gets to work.
Dachande. says, "Eccleston looked like he worked at the docs, but as a gangster more so than a fish monger."
Duelist is economy sized!
Himmel nods.
Kuttas hugs Azure.
Miko chatters, "How do normal suspenders attach?"
Miko chatters, "Are there buttons on the pants?"
Kia says, "Yes. "
Dachande. says, "Some come with buttons installed, otherwise ya get a tailor to stick em on."
Dachande. says, "Like Larry King and his jeans."
Kia says, "Brits tend to put the buttons on the outside; US puts them on the inside, because that's where they belong. "
Dachande. says, "Outside looks better though, otherwise it's like you're hitchin em to your britches."
Azure hugs Kuttas.
Kia disagrees.
Kia is slowly drifting towards removing the belt loops from his suit trousers.
Dachande. says, "Personaly I like the style that attach to belt loops."
Azure yips, "You aren't even supposed to see the suspenders."
Himmel says, "You aren't."
Kia says, "Azure is espousing the super-trad opinion, under which suspenders are rather like underwear. "
Miko chatters, "Bleah."
Himmel says, "It's very plebeian, very pedestrian, to show one's suspenders."
Azure yips, "That's why I only wear suspenders under a jacket mostly."
Himmel says, "Only a working man need take off his jacket."
Azure yips, "Though I do have a pear of clip-ons I wear with jeans if I'm doing moving."
Srass hugs Azure with a foreleg, carefully.
Azure yips, "Since I find if I'm bending and wiggling around suspenders are better than a belt."
Kia'd feel rather silly wearing his angels-and-devils suspenders if no one could see them.
Azure yips, "Ornamentation belongs on your tie :)"
Dralen meeeeeeps.
Dachande. says, "I think they're like undies, i wear fancy nice looking underwear that matches the main color of my clothes for my own pleasure, not the showing of others."
Kia does not wear a tie if he can possibly avoid it.
Azure doesn't really like 'cutesy' ties.
Srass says, "That's like wearing spiderman underoos, Kia.  Some things are better left hidden."
Azure yips, "Though someone did get me a really nice royal blue one with a random pattern of lightning bolts I'm quite fond of."
Kia disagrees! but then he's the one who's made this a thing of his.
Kia says, "WOrthy of note: Ladies love the suspenders. "
Himmel says, "Kia: do suspenders go over or under a waistcoat?"
Dachande. says, "Laides love them because they can line them over thier nipples and show all of the fun bags with out getting arrested."
Kia doesn't generally wear a three-piece, but they'd go under. This is fairly obvious, since the waistcoat extends below the waist of the pants.
Duelist growls quietly, "ClassyFox."
Azure has one three-piece and one two-piece.  Tends to wear the three piece more at night and the two piece in the day.
Kia doesn't *ever* wear a three-piece, actually. Not that it's not pretty awesome, but jesus h. He sweats enough as is.
Azure yips, "Plus the two piece is a nice light grey and I think it goes better with the bright violet and electric blue shirts."
Makyo has 3-piece from wedding.  Wears it very rarely, because yeah, sweating >:/
Himmel says, "YOu would hate my typical style, Kia, maybe."
Azure yips, "The three-piece is a dark charcoal and I generally wear a white shirt, mother of pearl cuff links, and a more conservative tie with it.,"
Kia also may or may not have Millenium Falcon cufflinks.
Azure has three pears of cuff links, one lapis, one mother of pearl, and one just stainless steel.
Kuttas says, "What are the pieces?"
Duelist naturally, when talking about suits, recommends double breasted.
Himmel says, "Though I must thank you. I've just realized a need for Braces."
You yerf, "Slacks, jacket, vest, Kuttas."
Kuttas wears jeans pretty much all the time. The only suit he owns is a military uniform.
Kia has his Millenium Falcons, his 1950s subway tokens, his 3 kopek pieces, the art deco ones he can't actually put on, and the ones made from .45 Long Colts.
Himmel combines waistcoats and dress shirt with flared jeans with frayed hems and maybe holes at the knees or under the ass.
Kuttas says, "Ah. So, in the two piece, is it slack and jacket? Or jacket and vest?"
Kuttas knows a number of people who wear jacket, vest, and jeans.
KurtMRufa's player got a suit in high school and still has that same one.
Kia isn't paying nearly enough attention to this Dr. Who.
Duelist has many suits because, well, he likes wearing 'em
Himmel does have this glorious brown suit.
Azure used to have a three piece double breasted coal black suit he adored, but it ended up being Severely Damaged due to him wearing it all the time.
Himmel says, "I hate brown clothing, I should note."
Himmel says, "Doesn't work well with my complexion."
Kia likes his suits. And... fuckity fuck.
Azure says to Himmel, "But, really, I wear way too much colour on a daily basis to be properly 'trad'."
Himmel says, "But this suit is -beautiful-. And manages to work."
Himmel chuckles at Azure.
Kia'd meant to swing by CitiShoes and pick up some stuff to apply to his horse's-ass shoes. :(
MegaWolf totally fails at fending off RL
Kia, having spent a stupid amount of money on these shoes, wants to treat them really, really well.
You yerf, "Slacks and jacket for 2-piece, yeah :o)"
Kuttas wears what he normally wears. Blue Jeans, carhartt shirt, plaid Woolrich overshirt, boots and belt.
Azure tends to go for something like, say, dark grey slacks, light grey jacket, bright violet shirt, and a nice geometric or striped tie.
Duelist should get a new suit. Hmm!
Azure yips, "And a silk square, of course."
Kia recommends MyTailor.com.
Kia says, "Best if Mr. Whatzisnuts, the owner, comes to your town, but always good. "
Kia says, "Hemrajani, that's his name. "
Duelist just goes to Caesar's Palace and buys a Dolce and Gabbana and has it fit to him.
Kia says, "Better to have a suit made-to-measure for you from scratch.  Your fabric, your choices for everything. "
Azure admits he really wants to get a proper linen suit made for summer time.
Duelist growls quietly, "Not when you change sizes like I do."
Dralen can't afford pretty clothes. "Mexx and Buffalo. Can't afford D&G or Zegna.
Kia would like a linen suit, but dunno how it'd go over. Maybe if he switches to the not fox firm.
Azure yips, "And species."
Duelist growls quietly, "Ahh, I used to go Armani,but that's so played....and then I found D&G and just really liked 'em."
Dachande. wears $15 jeans and $20 shirts, looks like a fat fuck.
Kia says, "And a... thingy. "
Kia brainfarts.
Miko chatters, "Hello, me."
Kia says, "The other summer fabric. Not madras; I don't want to look like a degenerate gambler. "
Kia says, "Seersucker. "
Duelist has linen and seersucker suits. Required out here.
Dralen says deeply, "Versace fits me to a T, but no way I can afford Versace."
Azure yips, "Seersucker?"
Kia really wants to roll into work in a seersucker, straw fedora, and spectators.
Azure yips, "I like madras."
Duelist growls quietly, "Nothing fits me. The standard drop for a US suit is 6 inches. My drop is 14."
Azure yips, "Actually my favourite thing to wear in the summer is a linnen jacket, madras shirt, and a pair of darkish brown slacks."
Kia points at MyTailor!
Darkness arrives from the foyer.
Azure yips, "White shoes and a panama."
Darkness waves.
Makyo rrf, so much for early bed.  Gulps down half a muscle-relaxant and sprawls, about bedtime.
Srass wavesw.
Kuttas waves.
Duelist has a panama hat :)
Duelist wave too
Azure has been accused of drifting straight out of 'business casual' and into 'business technicolor', though.
Kia likes madras too. His standard summer wear involves madras shorts. But he'd never do slacks or a sportcoat in it, because... again, he'd look like a degenerate railbird.
Himmel wishes he was a chick, when thinking on Fashion.
Azure yips, "Chicks don't get pockets."
Azure yips, "I just wish I were in the 19th century."
Himmel says, "Steampunk is so much easier when you're a girl, though."
Azure yips, "It is?"
Himmel nods at Azure.
Dachande. says, "So true"
Azure yips, "They have to do corsets and crap."
Azure yips, "Men get all the good clothes in steampunk."
Azure would so love to be able to get away with going to work in a frock suit.
Makyo hands out cheek-kisses, because you all are wonderful.  Will idle here, again, until disconnected for exactly the same reason.
Himmel says, "Yes, but those are far more readily available than, say, a functionally single-piece waistcoat."
Duelist growls quietly, "You are a gentleman, Azure"
Duelist growls quietly, "And, as such, you should dress appropriately."
Himmel says, "Or perhaps it's just my locale."
Azure yips, "That is true, it always annoys me how much old design clothing is made like costumeware instead of something you'd actually wear."
Himmel nods.
Duelist - http://www.gentlemansemporium.com/gentlemans.php
Himmel thanks Duelist a lot.
Azure does seriously want an opera cloak now, though, ever since he had a dream in which he was fighting a duel in one.
Kuttas hmms. He hasn't been to that site in a while.
Miko likes suits on under-25s and over-60s.
Himmel throws three weeks' worth of checks at the 'Vest' section.
Skylos arrives from the foyer.
Skylos softly barks, "woof!\"
Skylos sits.
Azure listens to some Ambient Metal.
Miko also has an outfit that he lately just wears and wears and wears and then washes and then wears again.
Azure grins at Duelist, "Well, I believe in the Nikola Tesla school of fashion.  Nothing says "I spend my days working on fantastic technical problems and trying to revolutionize the world" like a really nice suit.
Kia says, "Azure: Become Solicitor General of the United States. "
MegaWolf puppy sleeping in her box.
Azure asks Kia, "Why?"
Duelist growls quietly, "I agree, Mr TinyFox."
Kia says, "On the rare occasion that the SG goes to court, they wear morning dress. "
Kia says, "Stripey pants, frock coat and all. "
Miko chatters, "Dark gray worn and frayed bootcut jeans, black zippered and twin-breast-pocketed knit thing with shoulder thingies and horizontal grey stripes in pairs, snug short black leather jacket with hood. Black slip-on tennis shoes. They all just go super well."
Azure ooohs.
Miko doesn't have any other ensembles that fit so well so he just doesn't wear anything else any more. c.c
Darkness sits quietly on one of the couches.
Azure suspects having his background in mathematics rather than law would somewhat impede this goal.
KurtMRufa remarks, "Pants."
Azure asks Darkness, "How do you do?"
Duelist growls quietly, "Men should dress finely."
Dralen dresses like a hipster.
Kia says, "Law schools exist. "
Miko thinks really young guys in suits &c look cute, and old men in the full getup look charmingly dapper.
Kia knows this from personal experience.
Miko chatters, "Anyone in between.. eh.. look like they're in accountancy."
Miko chatters, "Unless they're going nuts with the waxed moustache and cane."
Duelist growls quietly, "Then they ain't wearing the right suit, Miko"
Kia says, "Depending on your specific educational background, you could wind up in patent prosecution, which is a really lucrative niche.  On the other hand, it won't make you SG of the US. "
Azure yips, "Yes, but I'm pissed off at patent law."
Kia says, "Well, it is sort of rubbish. "
Azure did have fun chatting with the Patent Attorney, though.
JanusFox has disconnected.
JanusFox @batbats his ISP, but, to no avail.  He wimpers as he fades out.
Miko chatters, "Couldn't you fight the other side as a patent lawyer?"
MegaWolf growls softly, "Calvin's dad was a patent attorney"
Azure yips, "he even gave us the "You don't have to like it.  You have to accept the law as it is and act rationally." speech."
Azure yips, "Which I respected quite a lot."
Darkness looks up to Azure. "I am well. How are you?"
Miko chatters, "OK, not all guys under 25 look good in the full kit. Zac Efron just looks like a giant douche when he wears a suit."
Miko image googling, aimlessly.
Azure smiles at Darkness, "I'm doing qutie well, thank you."
Dralen says deeply, "Adrien Brody looks pretty fucking hot in a sharp suit."
Kia says, "Patent prosecution is specifically the practice of applying for and getting patents with the USPTO. "
Miko chatters, "I think it's because he always looks so rumpled."
Miko chatters, "I mean, not the suit. The guy inside it."
Kia says, "It requires, because of what you have to do to practice before the USPTO, a specific educational background. "
Miko chatters, "It's the contrast."
Kia says, "Patent litigation is a different specialty, which is basically just a litigator who litigates patent cases. "
Azure aaahs.
Kia says, "Helps to have a technical background, but isn't required. "
Darkness smiles.
Miko titters at http://cs1.fashionising.com/media/suit-trends/three-piece-suit-2011.jpg
Azure can't wait until his danged patents get approves so he can point to them and say, "See?  SEE?" when he applies for jobs.
Himmel says, "Those gloves are -perfect- with that, Miko."
Duelist growls quietly, "You will lose, Azure."
Miko chatters, "I didn't even notice the gloves."
Miko chatters, "But they are indeed very rapey gloves."
Azure yips, "Lose?"
Skylos heard a series of gunshots nearby after police went buy with lots of sirens vrooming and horns.  Then there was a helicopter.  Then the helicopter went away.
Azure yips, "Lose what?"
Miko chatters, "And so go very well with the rest of the "date rapist" Halloween costume."
Duelist growls quietly, "Yep, someone with a much huger patent litigation budget will just steal your patent."
Miko scratches his head. Is this a bad suit? http://www.ahfashion.com/products_pictures/Sharcoal.jpgM.jpg
Himmel says, "I think, instead of sunglasses, he ought to have gone with a hat, either also-solid-black or also-pinstriped."
Himmel says, "I would say, yes, Miok."
Miko chatters, "Because that looks just terrible. That's like a nasty cheap supermarket suit, right?"
Duelist growls quietly, "It'd be a nicer suit if it fit him properly, Miko."
MegaWolf patents the method of soothing small blue foxes with a FoxBox
Himmel says, "Miko."
Azure yips, "Oh, I wouldn't litigate it."
Azure yips, "I'd be very put off with my employer if they tried it."
Himmel says, ":nods."
Azure yips, "And offer to testify for the defense."
Miko chatters, "It looks like it's too tight at the shoulders and too loose at the waist, yeah."
Kia isn't so sure about his fall hat. May be time to visit Pork Pie again.
Duelist growls quietly, "Bottom line, Patent is all about money. If you got the budget, you win the idea."
Azure yips, "I just like it since it's a matter of public record and I can actually show off the technical details of something I've worked on."
Miko chatters, "Right, yes, it's a $189 suit."
Darkness is enveloped in a sparkling glow as a space/time rift envelops her and she winks out of sight.
Darkness has left.
MegaWolf growls softly, "Or some European guy named Einstein steals it and loses your application."
Miko chatters, "Or Thomas Edison crosses your name out and writes his in."
Azure doesn't even think it should have been patentable.
Azure hisses at THomas Edison.
Azure yips, "The Steve Jobs of the electrical world."
Duelist growls quietly, "May 9, 2008, Tech Crunch reports MIT students demonstrating their Android apps. Winner is an app called Locale which allows a user to dynamically change their phone settings based on location. June 26, 2008 Apple files a patent app to patent 'allowing a user to dynamically change their phone settings based on location'."
Kia shakes his fist at Thomas Edison and pets his pigeons. Whom he loves. Like women.
Duelist -  http://techcrunch.com/2008/05/09/mit-students-demonstrate-their-android-applications/
Miko chatters, "I didn't realize the "size 00" trend in fashion models extended to men. All these dudes modeling for Dolce & Gabbana's suits look like they've got corsets on under there."
Himmel whiiiiiiiines: http://tinyurl.com/8jrwjqm
Duelist growls quietly, "Apple has a HUGE patent litigation budget. THat's how they innovate."
MegaWolf growls softly, "I'm going to laugh so hard when the Apple bubble finally pops"
Azure yips, "The iPhone 5 is a fairly good sign it's starting to."
Kia says, "This will make you feel better, Miko. http://worldwideinterweb.com/component/k2/item/1444-the-ultimate-runway-model-fails-compilation.html"
Mundy shows http://www.digikey.com/product-detail/en/CD14538BE/296-14074-5-ND/525847 to TIGRSKNK.
Himmel says, "Social apps are really popular."
Miko chatters, "Poor girls."
Duelist O.O
Kuttas idles.
Mundy says, "I think I'm gonna order some of these on Monday."
Duelist growls quietly, "What is that?"
Himmel says, "Multivibrater?"
Himmel says, "Vibrator, rather."
Mundy says, "Imagine the breadboard pic I showed you, shriveled up into a single IC chip, with power and LEDs connected to it."
Kia's favorites, in order, are: the one who walks off the stage, the one who falls into the pool, and the one who gets hit by the giant pendulum.
Duelist huhs.
MegaWolf gets a headache looking at digikey's website
Kia idles briefly.
Mundy says, "Cheaper and easier."
Kuttas has been saying multivibrator all along. Monostable, bistable, and astable.
Duelist growls quietly, "How is this useful to me?"
Kuttas now idles
Himmel rub Yenaears.
Duelist growls quietly, "Is true! Y3NA has been saying that!"
Mundy says, "More useful to me, because it'll be easier to work with.  But produces the same results."
Mundy says, "And you didn't go to Y3NA to make these? :)"
Duelist growls quietly, "I did! But Y3NA is a hard workin' yena and is busy!"
KurtMRufa licks its nose.
Mundy says, "Also.. You gonna be using N-Scale switch lights?"
Miko nuzzles and goes to bed. He was intending to get up five hours from now, but guesses he'll sleep in.
Miko winks out of sight in the sparkling glow of a space/time rift.
Miko has left.
Somewhere on the muck, Miko has disconnected.
Srass helps Kurt lick its nose.
Srass compares and contrasts the taste with that of Kuttas' nose.
Duelist growls quietly, "I was just gonna use LEds"
Mundy says, "Little tiny LEDs with wires running to the controller?"
Duelist growls quietly, "Sure!"
Acy sees his piglet looking at him!
Acy daaaawh!
Acy wrassles with little piglet!
Mundy needs to know stuff before building anything. ^.^;
MegaWolf hrms. Video won't run for him despite telling Noscript to "allow all" five times in a row.
Duelist growls quietly, "Let me see here"
Mundy says, "Like.. Where are these controller modules gonna be located?  At the switches, or at a central control spot."
Duelist growls quietly, "Man, wiring a train is a bitch!"
Duelist growls quietly, "CEntral control spot"
Kuttas wriggles his nose. His nose tastes like hyena and [redacted].
MegaWolf growls softly, "I should probably upgrade firefox"
Srass tastes hyena repeatedly.
MegaWolf growls softly, "I'm still on 3.latest"
Kuttas tastes more and more like hyena. He noses along Srass' gigantic panthernoggin.
Srass rumbles, and paws gently at Kuttas.
Kuttas wraps his arms around Srass' neck and clings close.
MegaWolf's still annoyed with Firefox suddenly jumping 10 numbers in a year or so
Srass hugs Kuttas close.
Mundy says, "Hmm.. Also.. How many blinken lights per switch track are we looking at?"
Duelist growls quietly, "Blink?!"
Azure yips, "Well, yeah, that was a stupid decision."
Duelist growls quietly, "They don't blink!"
Azure yips, "I blame Google."
Mundy biteys TIGRSKNK.
Mundy says, "One pair per switch?"
Kia prrs at Otello. So dramatic.
Duelist growls quietly, "I don't understand!"
Duelist growls quietly, "Hang on...."
Kia looks forward to seeing one of the Three Tenors conduct it.
Kia, pleased to have seen Placido sing in The Mysterious Island, too.
Duelist - http://tinyurl.com/8et2ff6
Mundy says, "You have two LEDs.. One indicates left-side, the other right-side."
Duelist growls quietly, "The LED determines which side is open"
Mundy says, "So these LEDs are gonna be on the 'main control'."
Mundy says, "Nothing out there in the model?"
Mundy says, "Also.. This begets another question.. Are you gonna have a control panel for the switches like that pic?"
Skylos has disconnected.
Skylos has connected.
Duelist growls quietly, "Yes"
Mundy says, "Okay."
Mundy says, "This is a critical bit of info for the enclosure of the controller. ^.^"
Somewhere on the muck, Tigerwolf has disconnected.
Himmel orgasms in his ears.
Somewhere on the muck, Tilton has connected.
Somewhere on the muck, Rollo has connected.
Dachande. says, "Ugh i hate getting that out of my ear, harder than up the nose"
Makyo hands out cheek-kisses, because you all are wonderful.  Will idle here, again, until disconnected for exactly the same reason.p #away Snoozin'
Mundy says, "Or inbetween the keys."
Kyhwana mrrp
You say, "fuck phones"
Kuttas climbs up on top of Srass and sprawls.
Mundy ponders tiny little black boxen with screw terminals all over.
Himmel snugs Makyo.
Away message and away flag are now set.
Srass reaches up and pets Kuttas, lazily.
You say, "just trying to set away :S nighty for real"
Duelist smooch Makyo!
Kuttas pets Srass back, sprawling lazily.
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
Rollo arrives from the foyer.
Rollo waves gently
Skylos softly barks, "Rollo!"
Skylos hugs otter
MegaWolf licks the not-asleep-Makyo :>
Rollo churrrs, and hugs the nice doggie
Skylos smiles and petpets the nice otter.
Kia checks on the shipping status of his lifetime supply of lube.
Kuttas kinda craves Chinese food again
Skylos softly barks, "a 55 gallon barrel of j-lube powder?"
Makyo just a paranoid fox.  Very.  REally bed now, though y'all can keep the resmooching.
Kia says, "An 8+1 pack of bad-dragon cumlube clear. "
Himmel would enjoy a bad dragon product.
Kia checks on the shipping status of his outrageous order of large silicone appliances.
Acy says, "Night kids."
Duelist o.o
Acy has disconnected.
Kia has a bad dragon product. Likes it, more or less. Not a huge fan of the knot, though.
Kuttas wonders which one.
Himmel probably wouldn't require a knot.
Kuttas pets Himmel. "Silly cat."
Himmel says, "The Dragon Toys are particularly appealing."
Himmel says, "As is the Gryphon."
Kia hmms and thinks he's going to get a fucking huge delivery of a) lube, b) huge fucking silicone toys and c) snuff on Monday.
Himmel is soft.
Skylos softly barks, "tell me of the silicon toyes"
Kia has the Faerie Dragon. http://bad-dragon.com/products/elden
Skylos but you getting new ones?
Dralen wants to get a new Bad Dragon toy, but can't afford it.
Himmel oooooooohs.
Himmel says, "The Earth Dragon looks veeeeery nice."
Kuttas shakes his head. "Ridged are not cool...
Himmel | http://bad-dragon.com/products/clayton
Kia whispers about things to Skylos. None of the rest of you need to know about his perversions.
Duelist is keen on Bad Dragon. Great business model.
Rollo has disconnected.
Kuttas says, "Oh? What's their business model?"
Kia says, "Sell perverted sex toys to perverts. "
Himmel oooooh: http://bad-dragon.com/products/cole
Duelist growls quietly, "Well, the artist draws lewd porn to get his fans all hot-n-horny"
Duelist growls quietly, "Then, all of a sudden,you can buy the dick featured in the lewd porn!"
Kuttas cackles.
Kia thinks that the lewd porn looks like everyone is made of rubber.
Duelist growls quietly, "It's a great idea."
Duelist growls quietly, "And, clearly, it works."
Duelist growls quietly, "Then you 'buy' a popular porn site and get free advertising."
Dachande. says, "Oi none of them dragon toys look like they'd be good up the ass."
Kuttas says, "They own a porn site?"
Himmel says, "For vids of people testing toys."
Himmel says, "Well. Using, not just testing."
Kuttas says, "Oh. Hmm."
Skylos softly barks, "I LOVE my dragon toy 'bruiser fusion' up the ass.  And my drippy dragon.  And my david the werewolf."
MegaWolf growls softly, "Whowhuh?"
Kia quite likes his Eldon, but again... lemur seems not to work well with knots.  Apparently he has the "made to be fucked by horses rather than dogs" gene.
Himmel is also rather enamored with that one, Skylos. And also, the liger.
Himmel says, "Bruiser and David, I mean."
MegaWolf @.@
MegaWolf stays outta this one. n.n
Kuttas says, "So, anyway."
Kuttas says, "How 'bout them Royals?"
Duelist growls quietly, "They're no good, man"
Kia supposes he needs to get himself a Reds hat.
Himmel says, "They suck."
Kia, sort of hoping for the Yanks to flame out so that he doesn't get stuck with a Reds-Yanks world series.
Skylos softly barks, "I think I can see the pattern though Kia."
Duelist growls quietly, "Oakland A's. That's the team!"
Skylos softly barks, "the less emphasized the knot the more fun it is."
Kia frinks?
Skylos softly barks, "Like I have a bad dragon 'ridgeback' original design"
Skylos softly barks, "that's FRICKING AWESOME to be fucked by"
Skylos softly barks, "Its just really hard to find somebody who will fuck me with it."
Kia says, "No, it's not that. The knot is pleasant enough, but once it's in you just feel really full... and then ou have to get it out again. And that is less fun. "
Skylos softly barks, "I even wrote a fan fiction about it."
Skylos likes to play with sliding knot in and out.
Skylos softly barks, "http://dogpawz.com/skylos/indexes/title-dragoncock.html"
Duelist sits by Kuttas. He got no idea about these toys. He just uhh....has sex. Heh.
Kia likes a bit of that feeling of pulling inside, but the knot thing is too much. Also, we are totally going to get bitched out fby someone for breaking the rating in here, right? Didn't that happen a few nights ago?
Skylos softly barks, "duelist has a partner that will have sex with him."
Kuttas says, "So, yeah. How about we spare the graphic descriptions of what you do with your toys, eh? PG-13 and all."
Skylos softly barks, "that's a nice thing to have."
Kia, psychic.
Himmel decides to save up for Clayton. Nods.
MegaWolf blinks.
Kia doesn't like Clayton. Ugly.
Kuttas says, "I'm not bitching anyone off, Kia. You can get off your horse now."
Kia was on a horse?
Kuttas nudges Duelist.
Kia thought he was on a boat.
Floid suggests the Zeta tiger, anyhey.
Kuttas says, "I kinda want chinese food."
Skylos softly barks, "clayton looks nice and ripply."
Himmel disagrees, Kia!
Duelist hms! "Do they have Chinese food up there?"
Himmel says, "No, D. It's all Whale Blubber."
Kuttas says, "Of course! As much as anywhere, anyway."
Kia says, "De gustibus, Himmel. "
Floid says, "Also, wait, wait."
Floid says, "Kia, you just ... you're into SNUFF PORN?"
Dralen says deeply, "I thought you enjoyed riding your horse, Kia :D"
Kia says, "No, no. "
Dralen says deeply, "Nono, Floid. Snuff the tobacco format."
Floid says, "That was the pun kids."
MegaWolf growls softly, "Man, anime with half serious realistically drawn characters and half cartoony emoticon/Snarf characters is just annoying to watch."
Himmel snickers.
Kia says, "https://mistersnuff.com/"
MegaWolf growls softly, "Visually annoying."
Floid says, "It was basically the worst pun ever, hence the warning shot."
Kia may or may not have a small collection of HorseMage pics, but that's beside the point.
Duelist peers at Kuttas! "I am surprised by that. Are there any places open right now? Delivery?"
Kuttas says, "Yeah, but they won't deliver out here in the sticks. I'll have to go in. The Buffet is open until 10:30"
Duelist hmms! Buffet!
Floid also scrolls up.  Do not underestimate the popularity of the iPhone 5.  Everyone at the office wants one even though they do not know why.  Fashion symbol + this year's Buick.
MegaWolf nips Floid's dingo-y parts
Duelist do like buffet!
Dralen lives in Chinatown in Toronto. Can get Chinese food until about 3am.
MegaWolf growls softly, "Dingos!"
Kuttas does, too. He eats like a hyena. c.c
Floid says, "I cannot totally bitch about the 'we ran out of other things to do so we started figuring out how to improve the voice quality' part, though."
Kia shows up at Dralen's for dim sum.
Floid says, "That'll be nice when it trickles down into cheapphones."
Kia does not like NY chinatown. It's filthy, smells bad, and is crowded. Plus, it's full of Chinamen.
Floid says, "It does have That Smell to it, whatever that is."
Kia says, "Plus, it keeps expanding. "
Kia doesn't even understand it. Chinamen shouldn't be able to afford Manhattan.
MegaWolf growls softly, "Little Italy is now Little Tokyo"
Floid says, "Culturally I think the haggling thing runs deep there."
Floid does not recall much Tokyo there, Mega.
Kia says, "Nah, Little Italy is still there, but it's basically Disneyland. "
Floid says, "LI is down to one street, like, though.  Is Puglia's still there?"
Kuttas says, "They have those little sugar-stuffed doughballs rolled in sesame seeds. They're delicious."
Kia says, "A couple blocks of red sauce restaurants. "
Dralen says deeply, "We'll go for dumplings next time, Kia."
Kuttas says, "Plus the steamed pork dumplings that remind me of mandu."
Kuttas says, "Hmm... perhaps I should go to the Korean restaurant, instead. I haven't had kimbap in forever."
Kia has occasionally wound up in Chinatown when running southwest. He's never happy about it. He's actually given up on running that direction--has realized that, while hitting USq sucks, it's like two blocks of pedestrian congestion. SoHo is block after block after block of hell.
Himmel purrpurrpurr, Kimbap.
Kia once wound up in TriBeCa when running southeast, which he almost never does. Lemur was lucky to make it back home.  The streets down there make no sense.
Kia says, "And it's not like the Village, where at least you can occasionally sight off of the Freedom Tower. "
Kia says, "No landmarks at all. Just lots of little streets going off in no direction at all. "
Kia finally found the FDR and walked home.
Dralen had good Ethiopian the other day. "I'm lucky... I live in a neighborhood with just about any kind of major cuisine you could name.
Dralen says deeply, "In under 10 minute walk."
Dralen says deeply, "Under 5 for most."
Kia has that here too.
MegaWolf growls softly, "We have chinese and seriously overpriced thai"
Kia tried to take the ex for Ethiopean once. The walk was five minutes. The wait at the restaurant was more like 30
MegaWolf growls softly, "And chain restaurants"
Kia still needs to get someone to go provide moral support for his battle with phaal.
Himmel says, "Pride goes before the Phaal."
Kuttas points at the lazing sleepers and goes all tribal, shouting, "Ki'i ki-rharg, ki'i etya stye ngyet-ngye!"
Rollo is sent home.
Rollo has left.
Khyber growls and lets the broom sweep him into a portal, but not before snapping it's handle.
Khyber has left.
Acy is sent home.
Acy has left.
JanusFox takes the hint and heads off someplace more quiet.
JanusFox has left.
MegaWolf squeek-meep Dralen
Kia wants to get on the Phaal of Fame.
MegaWolf noms on Floid, because dingo.
Somewhere on the muck, Triggur has reconnected.
Kia says, "Dingos nom on others. Mostly babbies. "
Kia says, "How are they formed, anyway? Babbies, I mean. Not dingoes. "
Himmel says, "How -is- babby formed?"
Kia wants to know how girl get pragnent.
MegaWolf pokes at Floidingo, who doesn't really seem to do much of anything at all.
Dralen smooches on Mega.
MegaWolf growls softly, "I think I should exchange him"
Kia gives Floid a pinch of snuff. Porn.
KurtMRufa teleports away.
KurtMRufa has left.
Somewhere on the muck, KurtMRufa has disconnected.
Kia says, "Benoit."
Dralen says deeply, "Balls."
Dralen says deeply, "See? It's automatic."
Kia kisses Dralen. :)
Dralen grins.
Mundy says, "Babby ate my balls."
Kia is going to introduce a coworker to Archer tomorrow.
Kia has already given her The Big Lebowski. Not to be confused with the Dude, or His Dudeness, or Duder, or El Duderino if you're not into that whole brevity thing.
Kuttas drapes over Srass.
Srass curls around and nuzzles along Kuttas.
Kia manages a 3/5 on the Composers edition of Truth or Fail.
Floid awws, his scrollback doesn't extend all the way to 'before he connected and immediately went to sleep.'
Kia hates that the vlogbrothers do not do all of the Truth or Fails. >:(
MegaWolf's fortune cookie is "The suspense is exciting. I hope it last."
Floid also had the experience of WTF Tribeca, come to think of it.
MegaWolf growls softly, "Does anyone make fortune cookies that actually tell fortunes anymore?"
Srass says, "Yeah, I see them all the time at the place I go to."
Duelist always gets cookies that say 'some damn woof will need biteys today'!
MegaWolf bop Duelist!
Kuttas idles to see why his alarm clock is going off.
Duelist growls quietly, "Pretty accurate!"
Duelist bitey MegaWoof!
Floid says, "Duelist the Poodle."
MegaWolf doesn't do anything bad but tigers and skunks bitey anyway!
MegaWolf growls softly, "Duoodle?"
Srass says, "Doodle!"
Kia pffs. 2/5 on Cats.
Duelist oh yeah!
Duelist feelin' FOXY!
MegaWolf kisses Duelist instead!
Duelist bitey MegaWoof!
Duelist growls quietly, "Now you got bitey from a fox too"
MegaWolf *smewch!*
MegaWolf growls softly, "Foxes are hot too :>"
MegaWolf nibbles all over fox ears!
Mundy says, "Maybe you should eat him, FOX."
Duelist ew!
Mundy says, "Hah"
MegaWolf flicks Mundy woof's nose
Mundy says, "Season him with dragon spoo first? ;)"
Duelist hms!
Duelist growls quietly, "Says the guy with the drum."
Kia grrrs. 3/5 on Muppets.
Mundy drops Mundy's Spooge Drum of One Hundred Gallons.
Kuttas climbs into the spooge filled drum with a thick *SCHPLUT!*
Kuttas has left.
Mundy <.<
Mundy says, "Kuttas says, "I found a penny!""
Kuttas arrives from the foyer.
Kuttas c.c
Kuttas found a penny in there. TOTALLY worth it.
Srass says, "Be sure and wash it off."
Srass says, "Or go back in and spend it. c.c"
Kuttas says, "Spend it? On what?"
Kuttas rubs on Mundy.
Duelist muhahaha!
Floid says, "You just put it in that slot at the tip of his dick and see what comes out."
Srass says, "'Spend a penny' is a British idiom for taking a piss."
Skylos softly barks, "Kind of like seeing a man about a horse"
Kuttas hmms. That sounds vaguely familiar.
Floid finds http://www.furaffinity.net/view/8840919/ for Mega.
Somewhere on the muck, Tony_Cheval has disconnected.
Duelist hah!
Dachande. tilts his head... "That buldge is off."
Dachande. says, "It's like he has a sock in there."
Paladin barks, "He needs heelpads."
Dachande. says, "That too"
Dachande. says, "Everything is good except the crotch, the extra ass cheeks, and the heels"
Srass squints.  "Extra ass cheeks?"
Kuttas says, "Probably best not to ask..."
Srass says, "Someone paid for that. o.o"
Kia'd see a man about a horse.
Kia'd also buy that for a dollar, but not *that.*
Dachande. says, "This is why you pay after you find out they look like they have a sock stuffed in their testicles."
Kia notes that if his mother was a sculptor, equestrian statues would looks slightly different.
Dachande. says, "More vag?"
Mundy says, "Here's a commission horror: http://www.furaffinity.net/view/7019725/ :)"
Dachande. says, "I swear I can read the sarcasam in post 4"
Himmel says, "Eh, there are people who would slobber over that."
Kia says, "Mom hates dogballs, so I assume she'd hate horseballs too. "
Dachande. says, "I blame my current inner monologue."
Kia says, "And equestrian statues always have horseballs. "
Srass says, "Your mom has tried dogballs?"
Dachande. says, "Of course they would have horseballs, they're a classic symbol of fertility."
Kia says, "In Russia, near St. Isaac's, there was this building... it didn't just have horseballs. It had horse sheath with plainly visible horsecock inside, complete with horse urethral process. "
Srass o.O
Dachande. says, "And lemur fingerprints? :D"
Kia wanted to take a picture, but was shy. <:)
Kia says, "Always it's a bit awkward with horse genitals. "
Dachande. says, "Ehh they are probably used to tourists from a prude country being surprised at the casual nature at which their country acceps the items that exist in reality on bodies."
Floid needs to upload merhorse dong that was down the street from the office for city art-horse-event-thing still.
Paladin ponders urethral process.
Mundy kisses Paladin!
Kia says, "Russia doesn't really have tourists, because they make it really fucking difficult. "
Kia would've also liked to have taken a picture of the Belgian mares, but... well, he took a picture of one's face. Not the other end. <:)
Kia says, "She did have a pretty face.  But one does not just take a picture of a Belgian police mare's ass. "
Kuttas has left.
Kuttas arrives from the foyer.
Dachande. licks Kuttas!
Floid frowns at being 'home' which results in being handed drafts to read at 1:35AM on a Sunday and told what he'll be doing tomorrow.
Kia thinks Floid is continuing to exemplify why families should never have businesses.
Kia says, "Perhaps somewhat less than crazy bitch I have to deal with, but. "
Dralen says deeply, "There's a good result for a commission: http://www.furaffinity.net/view/8845139/"
Kia wishes that crazy bitch was as crazy in person as she is in email. IN person, she's charming. In email, she leads to me drinking myself stupid and cutting myself.
Srass says, "That's definitely an improvement."
Kia worries that, if he gets job at not fox, crazy bitch will become a friend's responsibility. No one should have to deal with crazy bitch.
Srass is rather fond of this particular commission, too, but he forgot who tipped him off to it: http://www.furaffinity.net/view/7118610/
Kia thinks this commission is awesome. http://www.furaffinity.net/view/4172160
Duelist bedtime!
Duelist licks Kuttas!
Duelist licks Srass!
Himmel says, "Dem balls."
Srass licks Duelist!
Himmel pet Duelist.
Duelist growls quietly, "You two be 'good'! >;)"
Duelist growls quietly, "Nite all!"
Srass says, "Aw, man!"
Kuttas hugs Duelist.
Kia asks you all to remind him to take his contacts out before bed.
Kuttas says, "Who us? O.o"
Duelist nods! 'good'! Note the quotes >;)
Kuttas c.c
Duelist grins.
Duelist goes home.
Duelist has left.
Himmel will, Kia.
Srass tries to imagine lemur contacts.  They must be the size of dinner plates. o.o
Dachande. says, "It is nice seeing nuts in a size 15."
Srass says, "That's a nifty looking one, Kia, but... Man, those feet look nearly gollumesque somehow. o.o"
Somewhere on the muck, Triggur has disconnected.  (But they're still online.)
Kia felt bad for Bryn Teufel watching the Ring. That blackout contact on his eye looked really uncomfy.
Kia gives Srass two big toes up.
Srass giggles.
Kia continues to love his favorite Warren Zevon song.
Kia says, "Even as it gets ever closer to my life. "
Kuttas should probably go get food. Probably too late for Chinese.
Dachande. likes this commision, http://bit.ly/RTYhu1
Skylos winks out of sight in the sparkling glow of a space/time rift.
Skylos has left.
Dralen says deeply, "Never too late for Chinese... in my neighbourhood, at least."
Kuttas would totally encourage someone commission him if he didn't suck at drawing
Kia looks away down Second Avenue.
Kuttas says, "It closes early here. Well, not terribly early."
Kuttas says, "But too soon for me to haul ass in and eat."
Dachande. digs it because friend randomly did it for him, and added the cyan, which i kinda like.
Dachande. needs a real scan of it.
Kia peers at this and wonders if he'll have a scar.
Dachande. says, "You can rub sand in it if you want one."
Dachande. says, "Kitty sand works best, the infection helps the skin panic andd grow faster which results in the scar tissue formation."
Dachande. says, "Also the weeping puss will prolong the seperation of skin which agian, scar tissue."
Kuttas says, "Dach, you've got issues. o.o"
Floid says, "So that's how you got that nevus in the shape of Bob Dobbs."
Kia doesn't, really.
Dachande.:D
Kia says, "Just... well. Never mind. I'll spare you the crazy talk. "
Floid offers some Bactine, anyway.
Kesareya arrives from the foyer.
Kesareya pads in and flops.
Floid snugs on a Kes, tiredly.
Malkoten arrives from the foyer.
Malkoten flops.
Vetiver pats Malkoten.
Kesareya licks over Floid softly.
Floid says, "Vrrf."
Kesareya smiles and licks one of Floid's ears.
Srass strokes Malkoten.
Dralen okays. Falling asleep means bed time.
Kesareya says, "Aww, nini, draggy."
Srass hugs Dralen!
Srass says, "'Night!"
Kuttas noses Dralen. "Rest well."
Dralen smooches on Srass and Kuttas, and fuzzles all the length of Kia's tail.
Malkoten curls up around Srass trap like.
Dralen swishes his tail, and is gone.
Dralen has left.
Dachande. says, "AH well off to bed guys, ya'll take it easy."
Paladin cuddles Dachande.!
Srass says, "Same here on both counts."
Srass earscritches the lot of you.
Srass is set upon by amorphous, eyeless chartreuse anthropods of no distinct species, and vaguely tribal-looking garb.  He is quickly bound and gagged, and dragged off by his ankles, struggling and trying to curse through the gag.
Srass has left.
Himmel says, "g'nigth."
Kesareya has left.
Malken has disconnected.
Floid hrh.  Apparently he's been doing the protein-shake thing long enough that his body doesn't know what the fuck to do with a huge wad of pasta.
Lion_Cub arrives from the foyer.
Lion_Cub mehs.
Floid hm.  Or he could've easily picked up some crud from dealing with visiting (and vacuuming portions of) dog-dust house and so on today.
Floid says, "So much loose DNA flopping around."
Kuttas mehs, also.
Floid applies some Purel, then pets L_C.
Lion_Cub craps, reading about Margaras.  "That's awful."
Kuttas nods.
(p) In a page-pose to you, Lion_Cub hugs. "Ugh.  Thanks for posting the obit."
Kyhwana nods at LC x.x
Floid then pets more.
Kuttas mehs again, abruptly fighting off tears once more.
Kuttas sighs.
Lion_Cub sorries. "I didn't mean to bring it up again."
Kuttas says, "No, no worries."
Kuttas says, "I've been doing this all day. I've still got his picture open on my desktop."
Himmel squeezes Kuttas.
Malkoten snugga LC!
Malkoten rumbles, "Just so you know LC, yer not allowed to die."
Lion_Cub noses a panther.
Lion_Cub purrs, "I hope you hold me to that."
Malkoten waggles his eyebrows
Lion_Cub curls up beside panthers. "Folsom is next weekend."
MegaWolf has disconnected.
Malkoten has never been.  Far too Canadian.
Lion_Cub frowns. "I went with Andreal, once." x.x
Malkoten rearranges that so it makes more sense.  Too far, Canadian :D
Malkoten rumbles, "what's it all about?"
Lion_Cub purrs, "The leather and what not."
Kia whistles for a taxi...
Kia leaves via the quiet Taxi service.
Kia has left.
Zhorah stirs
Himmel bed.
Himmel winks out of sight in the sparkling glow of a space/time rift.
Himmel has left.
Vetiver goes home.
Vetiver has left.
Floid also would've accepted "Far.  Canadian, too."
Somewhere on the muck, Azure has disconnected.
Kuttas slips out
Kuttas has left.
Somewhere on the muck, Herefox has disconnected.
Lion_Cub winks out of sight in the sparkling glow of a space/time rift.
Lion_Cub has left.
Somewhere on the muck, Lion_Cub has disconnected.
Floid tries something sleep-related again.
Floid has disconnected.
Zeph arrives from the foyer.
Zeph rowr.
Kyhwana meow
Paladin barrrrk.
Zhorah has disconnected.
Somewhere on the muck, Tilton has disconnected.
Kareb arrives from the foyer.
Scruff arrives from the foyer.
Scruff chirps!
Zhorah is sent home.
Zhorah has left.
MegaWolf is sent home.
MegaWolf has left.
Floid is sent home.
Floid has left.
Malken raises a warding finger, and says serenly,"Do not bother, I can provide my own transportation."  He then disappears in a swirl of darkness.
Malken has left.
Scruff leeeans in against Malks
Kyhwana chirp atta Scruff
Scruff hugsaleopardtail
Paladin barks, "Spots and dots."
Scruff has those! Although some of them are more like smudges o.o
Paladin has fluff and ruff.
Paladin barks, "Though I do have a spotty dawg laying around."
Zeph mews, "Mornin' Scruffles!"
Kareb has disconnected.
Scruff chirps, "You're a snowleopard again! <3"
Zeph is! He rekatted.
Malkoten unidles
Malkoten hugsa Scruffs, could use cuddles ^.^
Malkoten thinks he's gonna head to bed now.  2 am is bed time *nods*
Malkoten winks out of sight in the sparkling glow of a space/time rift.
Malkoten has left.
Scruff sneaksouttoo
Scruff teleports away.
Scruff has left.
Somewhere on the muck, Scruff has disconnected.
Himmel arrives from the foyer.
Himmel says, "The sandman and I have had a disagreement."
Himmel whistles for a bouncer, and when it comes near, the nametag says, "Fresh," and it has dice in one ear.
Kareb is sent home.
Kareb has left.
Somewhere on the muck, Triggur has disconnected.
Zeph has disconnected.
Kyhwana lifts up the rug and pushes all the sleepers under it.. he jumps on it a few times and the rug goes flat
Zeph is sent home.
Zeph has left.
Kyhwana durp
Undine arrives from the foyer.
Himmel says, "Hey, Unds."
Himmel says, "Did you hear?"
Undine says, "What?"
Himmel says, "About Margs."
Himmel gestures toward the message board.
Kyhwana mrps at Undines
Draconis arrives from the foyer.
Draconis mwrf.
Undine says, "Thanks Himmel."
Draconis sad :(
Himmel rubs Undine.
Himmel and Draco.
Draconis nuz.
Himmel rubs Dracosnout.
Undine has connected.
Undine has disconnected.

You have been logged out due to inactivity.

% Connection to furry closed by foreign host.
\end{verbatim}
\newpage

\begin{verbatim}
% Trying to connect to furry: 74.207.243.108 8889.
% Connected to furry.
#$#mcp version: "2.1" to: "2.1"
Welcome to
              _____                 _ _ _   _    _ __   _   ,  SM
               /  '                ' ) ) ) ' )  / /  ) ' ) /
            ,-/-, . . __  __  __  , / / /   /  / /      /-<
           (_/   (_/_/ (_/ (_/ (_/ / ' (_  (__/ (__/   /   )
                                /
                               '
          The first 99 & 44/100% anthropomorphic/Furry TinyMu*

(The SM means that FurryMuck is a Service Mark of the FurryMuck Wizards)
To connect to your existing character, type "connect <name> <password>".
To receive a new character, send mail to join@furrymuck.com
To see the latest news, type "news" after connecting to a character.
To disconnect from a character, type "QUIT".
Use the WHO command to find out who is currently online.
Use the 'whereare' command to find places with active people.
Use the 'wizzes' command to see what Wizards are on line, or the 'helpstaff'
 command to see who of the help staff is on.
Use "connect guest guest" to visit FurryMUCK as a guest.
All users of FurryMuck are bound by our AUP. "NEWS AUP" to read this document.
----

Sadly, FurryMuck has lost one of its own.

S'A'Alis, May 29, 1963 -- September 5, 2012, the Large Furry Marsupial, and a
member of the L'Drey, a space-faring, fox-like species. He was never without his
'Eternally Filled Highly Caffeinated Coffee Mug of Doom'. From 1993 - 1999,
S'A'Alis hosted the servers that FurryMUCK ran on, and was a character creation
wizard 1993-2001. Condolences can be sent to his beloved wife, IceWolf:

M. Vogt, W5910 Genske Road, Black Creek, WI 54106

Life is eternal, and love is immortal,
and death is only a horizon;
and a horizon is nothing save the limit of our sight.
 -Rossiter Worthington Raymond

----
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
Makyo stretches out and yawns toothily, shaking Makyo's fur out.
Players online for whom you are watching:
Danish            Makyo             Sarusa
Done.
The next scheduled database save will be in 0 secs.
You place a strategic call to one deity or another.
Makyo disappears in a puff of complacency.
Purple Nurple Foyer(#52464RLJ)
You step in through the door and into a cramped foyer.  Advertising
posters plaster the walls and there's another door right in front
of you (east).  The door is padded purple vinyl, studded in a diamond
pattern.  This is the Purple Nurple, Furrymuck's gay/les/bi nightclub
and meeting place.  Feel free to come on in if you are straight too.. we
don't bite (unless you ask nicely ;)  There is a sign on the wall next to
the door and a notice where the computer used to be, saying that it's now
in the main room.
Players inside the Nurple:
 Danish             Singe              Draconis           Kyhwana
 Paladin            Dachande.
[Exits: <IN> to the Purple Nurple   <OUT> to Sable Street]
Contents:
PN RULES : READ THIS TO BE ABLE TO ENTER
You enter the PN
Makyo disappears in a puff of complacency.
The Purple Nurple
You are in the Purple Nurple, furry's premier gay/les/bi spot.
The room is large, a converted warehouse - the ceiling's
about fifty feet above the crowded floor.  An entire suspended
lighting grid swivels back and forth in the middle of the room,
rigged with a complex array of lights, lasers and mirrors.
The overall effect is of an alien spacecraft hovering about twenty
feet over the dance floor.  Huge projection wall-screens flicker
images of furries dancing, clips from anime movies, computer
graphics reels and old cartoons.  The music is loud, thumping
techno and house, bass thundering through the gyrating furries
on the dance floor.
To one side is a lounge area, acoustically out of the main thrust
of the speaker stacks allowing normal conversation.  A bar with
every drink known is along the wall of the lounge, and
the floor is scattered with heavy-duty beanbag chairs, funky couches,
and other assorted furnishings, all roomy enough for at least two furs.
A small staircase leads up to the Nurple Apartments.
Contents:
Danish
Fiend Plushie
Singe
Draconis
Kyhwana
Paladin
Dachande.
All complaints --> Rigel
NURPLE ADULT/PG POLICIES ****** PLEASE READ
Bulletin Board
Name                   Sex        Species     ('whospe #help' for help)
Makyo                  N/A        Anthro Arctic Foxy
Danish                 Manmoose   Manmoose
Singe[idle 11m]        Male       Anthro Fire Dragon
Draconis[asleep]       male       Daggin
Kyhwana[idle 1h]       male       Young morphic'leopard
Paladin[idle 8m]       Male       Big Blond Dingo
Dachande.[idle 21m]    Male.      Wolf.
Makyo recurl.  Just for a bit.
Kyhwana mrp, pets curled Makyos
Danish snuzzle on fox.
Somewhere on the muck, Miko has connected.
Miko arrives from the foyer.
Miko wanders in.
Paladin ruffle-snuffles Miko!
Miko pets Paladin!
Danish lows, "Hey, squirrel."
Makyo nosenoses at folks, prrf.
Miko snoofs fox in the ear and perches in an antler.
Makyo sqkyprr ^^
Makyo should probably go shower, alas.  Gotta walkadoggy one last time before a week without dogwalking.
Makyo recurl, sticks around here for a while.  In and out throughout the day.
Away message and away flag are now set.
Paladin likes to 'walk the dog'!
Draconis has connected.
Draconis whrf.
Draconis hugs Miko!
Draconis nibbles Danish!
Danish nar.
Somewhere on the muck, Tigerwolf has connected.
Somewhere on the muck, Tigerwolf has disconnected.
Undine arrives from the foyer.
Miko hugs Undine!
Undine hugs Miko!
Undine snugs Dachande.!
Danish nuzzles Undine!
Undine says, "D-ain-sorta."
Danish eyep.
Undine says, "How's it going?"
Danish is ok, still waking up.  Yourself?
Undine says, "I found two mah-hooos-ive slugs in the garden when getting rid of the ornamental plants."
Danish ooh.  Sounds like an exciting morning.
Undine has to go make lunch, has a wobble.
JanusFox arrives from the foyer.
Draconis has disconnected.
Paladin has disconnected.
Paladin yawns and curls up in a big blond ball of dingoness, putting his muzzle on his paws and his tail over his face.
Miko chatters, "Undines wobble but they don't fall down."
Miko chatters, "Unless they've had three bottles of wine."
Danish pokes Miko.  "Major Mud's Medicinal Tincture."
Cain arrives from the foyer.
Danish braq.
Undine has disconnected.
Cain Qrab
Danish nods.
Cain lean on Danish
Cain  whistles for a bouncer, and a huge gorilla steps out of nowhere, and hauls out the sleeping furries. "Time ta go, boyz.." he growls..
Undine is sent home.
Undine has left.
Draconis is sent home.
Draconis has left.
Paladin grunts when he gets woken up, pads over to the sweeper and buttpurrs, then padpads off home.
Paladin has left.
Miko chatters, "Ah, yes, of course."
Miko idles for approximately forever, or the length of time it goes to have lunch with mum.
Danish pets Cain, waves to outbound squirrel.
Kyhwana has disconnected.
Gyroe arrives from the foyer.
Gyroe growlfs!
Danish lows, "Heya."
Somewhere on the muck, Sarusa has disconnected.
Gyroe rumbles, "Rowr."
Dralen arrives from the foyer.
Dralen meeeeeeeeeeeeeeps.
Dralen leans on Gyroe.
Gyroe kneads him some droxy.
Dralen rrrrrrs and wiggles and purpurrrs.
Zeph arrives from the foyer.
Zeph rowr.
Cain pats ZephRowrs
Dralen meeeps and tailswishes at Zeph.
Gyroe licks Zeph!
Zeph licks Gyroe and Dralen some.
Gyroe to bed!
Gyroe goes home.
Gyroe has left.
JanusFox zephmews.
Zeph snugs on SpookyFox!
JanusFox licks in Zephears.
Dralen pushes Zeph over and cuddles on top of him.
Puc arrives from the foyer.
Puc mrwrfs.
Somewhere on the muck, Herefox has connected.
Cain puts Puc in a bowl of jello!
Puc o.O
Zeph, with dragonfox atop!
Puc swims through the jello, snagging a cherry on his way out ala-Pacman *nom*.
Dralen rrrrrs softly and closes his eyes and strokes at sneppid.
Cain claps
Dralen annoyed at Sandra and Woo >:(
Zeph rumbles osme.
Dralen nibbles on Zeph's ears.
Puc stretches and mrrfs.
Djirin arrives from the foyer.
Djirin has left.
Somewhere on the muck, Triggur has connected.
Somewhere on the muck, Zhorah has connected.
Zhorah arrives from the foyer.
Zhorah waves.
Zhorah sleepdrgn
Puc has disconnected.
Somewhere on the muck, Triggur has disconnected.
MegaWolf arrives from the foyer.
MegaWolf arranges Dachande and Cain for maximum pillow usage, drapes across them.
Srass arrives with a sudden echoing boom, and a musical flourish involving two dozen brass instruments, six timpani, and a crash of cymbals.  Angels sing in beautiful harmony, and sprinkle sparkling dust over him.
Srass has arrived.
Dralen meeeeps at Srass and Xane.
Srass coils around Dralen.
Dralen rrrrrs quietly.
Cain has disconnected.
Duelist arrives from the foyer.
Duelist .... uhhh
Srass licks all the usual suspects' ears.  Duelist included.
Duelist yips!
Duelist licks Srass!
Duelist is Kaiser Soze!
Srass says, "Who is Kaiser Soze?  Did he depose Kaiser Permanente?"
Duelist oh! He spelled it wrong. Keyser Soze!
Undine arrives from the foyer.
Duelist growls quietly, "He's the 'bad guy' in the movie 'The Usual Suspects'"
Undine waves!
Duelist licks Undine!
Undine licks Duelist!
Srass hugs Undine!
Undine hugs Srass!
Undine says, "Hello."
Duelist growls quietly, "Which, if you have never seen, I highly recommend."
Undine slumps on a couch. "What's going on?"
Srass says, "Just sitting here existing, at the moment."
Zeph is prettyfying his Bandcamp site that is looked at by nobody ever.
Undine's resting after stripping more wallpaper off the wall and finding a big band of steel, for no apparent reason.
MegaWolf squeek Dralen
MegaWolf growls softly, "Vhat a tweest"
Dralen rrrrrrrs.
MegaWolf licks Duelist's ears
MegaWolf snouts Undine
MegaWolf growls softly, "It's the tension band holding the entire house up"
Dralen says deeply, "It's an elastrator for the bottom half of the house."
Zeph mews, "It keeps the bad ether out."
Djirin arrives from the foyer.
Djirin boink
Dralen idles for brekkie.
Undine suspects it's for the Ether retention, as Zeph says.
Undine noses Megawolf.
MegaWolf pets Undine's parts
Srass mouths on Djirin.
Duelist growls quietly, "You sure it's steel?"
Undine says, "It's ferrous and galvanised."
Djirin gets drooled on? ew
Djirin points Srass at Undine instead
Srass drools on Undine and Djirin both.
Undine pets Srass' head, drips on Djirin.
Zeph mews, "Poor old Srass can do nothing but drool."
Undine says, "Leaky cat, does that when he's excited."
Zeph mews, "Oh, Unds, I got a really good book on abstract painting."
Danish rubs Srass' flank.
Zeph mews, "I also ordered a book on doing clever things with acrylics but they inexplicably sent me watercolour paper instead."
Undine laughs!
Srass purrs, and nuzzles Danish.
Undine says, "Beautiful."
Undine says, "What's the book?"
Undine says, "Danish, I was uttering something about you to someone you'll never meet."
Zeph mews, "'Painting Abstracts' by Rolina van Vliet, translated from Dutch."
Danish lows, "You're referring to the thing you just said to me and you're trying to make my head explode with recursion."
Danish lows, "Never again."
Djirin idles. lawn mowing awaits
Singe bobbles up the sleepers, but for how long?
Puc heads to the sweeper's home to bang their mother.
Puc has left.
Cain swears, "It's the Fuzz!" before hopping in his car and making a hasty getaway.
Cain has left.
Kyhwana jumps up and gives the sweeper a big *smooch* and bounds off home
Kyhwana has left.
Singe ding
Undine says, "Would I ever try such a thing.."
Duelist could mow his lawn. 11 blades of bermuda grass have seem to poked up thru his uhhh 'yard'. He should go remove them.
Undine dug out corms and rhizomes of various plants in his garden. Getting rid! :D Turnin the place back to bare soil.
Duelist do not allow unauthorized plant life on his property!
Undine hehs, it's a bit harder here. Plants grow a lot.
Undine says, "Did you see the state of the house, Duelist? All the boarded up windows?"
Makyo peeks on from phone. Awful client, but hi :3
MegaWolf petpets Makyo
MegaWolf growls softly, "I was going to do yard work then suddenly rain"
Miko unidles and cheekrubs on Makyo.
Makyo peeks on from phone. Awful client, but hi :3
Zhorah licks Makyonose
You say, "augh, this may be too awful..."
Zhorah licks Miko nose too.
Zhorah idle for breakfast
Miko squeeps.
Makyo nuzz at Miks and Mega and Zhorah, just watches instead
Undine hugs Srass!
Miko bought a couple of drinkies. Something that looks suspiciously like a Scandiwegian knockoff of Scrumpy Jack.
Miko chatters, "'S called "Happy Jack" and comes in "dry" or "oaky"."
Puc arrives from the foyer.
Duelist demands to see boarded up house!
Singe growls, "err ner! http://cheezburger.com/6576656384"
Duelist looks at the googler.
Undine says, "Google+, duelist. :)"
Undine says, "Just uploading."
Duelist sees Srass is making a bad decision....
Duelist growls quietly, "What, you don't want a giant window in your can, Undine?"
Srass says, "I'm crossing over to the dark side!  Aaaahahahahahaaaaa!"
Duelist growls quietly, "C'mon, get to know yer neighbors!"
Srass also hugs Undine.
Undine says, "Haa, there will be a giant window there, even bigger than the previous two. :)"
Undine strokes Srass lovingly.
Zeph mews, "Fling poop at passers-by."
Duelist growls quietly, "All glass walls in the can."
Duelist growls quietly, "That's what I would do."
Undine chuckles. "Horrible!"
Duelist growls quietly, "Make absolutely sure that no one could ever be comfortable."
Undine says, "Not the "water closet" but the "solar poop incinerator"."
Duelist growls quietly, "At least a jail cell has one solid wall."
Zeph cackles!
Srass says, "Claude's old boss actually did have a sliding glass door in the bathroom."
Duelist growls quietly, "So what are you doing here, Undine?"
Undine says, "I know, taking a small break from the shit-storm that is my current existence."
Undine says, "Having a cup of tea. Litrally it's now and times when i'm asleep or on "the can" where I stop to think."
Duelist growls quietly, "A man does some of his best thinking on the can."
Undine says, "Want any more pics, Duelist?"
Duelist growls quietly, "Well of course!"
Zeph mews, "Being able to think while asleep is an impressive ability."
Zeph mews, "Also it sounds like TIGR wants pictures of you on the loo, squish."
Dralen remeeps.
Duelist growls quietly, "Nah, that ain't my thing."
Duelist growls quietly, "I get it, some folks are into it, but...."
Undine nodnods. "I know, it has been said that there is no greater man than the thinker at-stool."
Duelist growls quietly, "I just never could."
Zeph grins, didn't think it was, just being daft.
Undine says, "Don't you think while asleep, Zeph?"
Zeph mostly has batshit-insane dreams.
Undine ahems, "I meant of the house, of course."
Makyo finds a slightly better client, cheer.
Zeph huzz, better phonefox!
Makyo wigglewiggle :3
Duelist growls quietly, "You know, your thoughts might be better than mine but I have thoughts going around in my head too about different thinkings and brain things that you can use."
Duelist growls quietly, "You guys don't always know what's best. My fuckin' thoughts have feelings of their own too sometimes."
Miko chatters, "Today's Finnishism: "To be with a wing on the ground""
Makyo's thoightsare pretty fuzzy
Srass says, "Brain things.  How do I get those?"
MegaWolf licks Duelist's brains
Undine uploads some more ppics.
Undine zzziiip!
You yerf, "Better client doesn't mean foxes can type on a phone, alas."
Miko chatters, "i.e. to be low, depressed, etc. Presumably derived from the behaviour of injured avians."
Undine says, "To have GIMS?"
Srass says, "Aww, it's a snee!"
Miko chatters, "GIMS is different."
Miko chatters, "Ooh, panorama of Randon's yard. http://t.co/PP4KKpR8"
Duelist growls quietly, "Who?"
Miko chatters, "My friend (and ex's current boyfriend) whose place I spend an inordinate amount of time at."
Duelist growls quietly, "Undine, did you remove ALL your windows?"
Undine says, "They were too small.."
Undine says, "Or didn't exist before."
Duelist growls quietly, "Too small?!"
Duelist growls quietly, "Ohh, I like that thinking."
Duelist growls quietly, "I love windows."
Undine says, "Yeah srass, a cauldron of snee."
Makyo huhs. Guy at gate with honest to goodness man-pris
MegaWolf http://skia.deviantart.com/art/Phone-Fox-175079615
Undine says, "I like light. :)"
Duelist growls quietly, "I totally misread, Miko. Of course we know Randon (or at least know of him)."
Miko chatters, "Oh right."
Duelist growls quietly, "Wow, that's such a peaceful lookin' place."
Srass says, "Foxyfluffs really *are* phone dialers! 8D"
Duelist growls quietly, "Forest and Subaru"
Miko chatters, "He occasionally complains about the neighbours."
Duelist growls quietly, "Or is that an Audi?"
Miko chatters, "'Cause, like, once or twice a week one will walk past in the road."
You yerf, "pagemail that to me, Mega?"
Duelist growls quietly, "Everything looks the same from the side nowadays"
You sense you have new mail from MegaWolf.
Miko chatters, "It's a turbo diesel Passat."
Duelist growls quietly, "See what I mean?"
Miko chatters, "Yeah, I hear ya."
MegaWolf pets the foxyo
Duelist used to be able to identify cars via profile!
You yerf, "Fanks :3"
Miko chatters, "It's nicely located. Not a long way to the lake, either, and the house comes with a boat spot for some reason."
Duelist growls quietly, "For a boat"
Undine sniffs the air. Autumn's coming and he has a house with big gaping holes. Fuuuuuuccck.
Makyo prr, prr.
Miko chatters, "It's rowboats there mostly. Kinda in the sticks."
Duelist growls quietly, "I know! Seasons are changing! It's only 99F around here nowadays."
Undine gotta go, back to the grind. "Take care all."
Duelist licks Undine!
Undine snugs Duelist!
Srass kisses Undine!
Undine says, "Be good, Skunklista."
Duelist o.o
Duelist rahter foxy today, ya know
Undine says, "Srass, for god sake, cover up."
Srass dangles at Undine!
You yerf, "Byeeee"
Miko chatters, "Not far from a city where rich people tend to have summer homes, though. Nice part of the world. Of course, he went from "casually dating" to "wanting to move in with" a guy who lives halfway across the country around the same time buying the house was finalized, so he's not *entirely* satisfied with his present homeownership.."
Undine says, "Eep!"
Srass says, "They don't make clothes my size!"
Undine says, "Miko, put that away."
Miko chatters, "It's nice out, but put it away?"
Duelist growls quietly, "Hey that reminds me."
Undine says, "Danish, for the last time.. take that out of your mouth."
Duelist growls quietly, "I haven't done that hot little finnish guy in awhile."
Undine snugs Miko!
Undine teleports away.
Undine has left.
MegaWolf nips foxy rump!
Somewhere on the muck, Herefox has disconnected.
Zhorah returns
Zhorah had biscuits
You say, "Alright. Enough of this phone business. Gonna reidle."
Makyo nuzznuzz lots of folks, curl.
Zhorah pets bigfox
Floid arrives from the foyer.
"Ar," Floid says "f."
Zhorah leans on Floid.
Zeph fuzzles on Floidingo some.
Duelist licks Zhorah!
Floid kickstand.
Floid pets notayenas.
Zeph rekatted.
Zhorah snug snlep!
Floid read that as reratted for a moment, got hopes up.
Srass noses Floid.
Puc waves a hand over his head where smoke has been beginning to build.
Floid gets secondhand Puc.
o/~ Katu tdyttyy askelista, eldmd on kuolemista o/~ Pane kdsi kdteen, ollaan hiljaa o/~ [Miko]
Duelist =^.^=
Dralen sprawwwwwwwwwwwwwwls.
Samanthia arrives from the foyer.
Samanthia slinks in.
Samanthia pets DLST.
Srass nuzzles along Samanthia.
Zeph oh wow, best photoshopping ever 10/10 < http://mutanerda.deviantart.com/art/MONTADA-321193687 >
Samanthia pets Srass up and down.
Djirin has left.
MegaWolf nibbles Floid's 2001st part.
Cain arrives from the foyer.
Cain grunt
Zeph licks on Cainwoofs some.
Cain wig-el
Floid loses hearing in one ear, thus.
Cain flees
Cain teleports away.
Cain has left.
MegaWolf has disconnected.
Zhorah has disconnected.
Floid wonders what is wrong with him re: 70F feeling freezing.  End-of-summer-syndrome, clearly.
JanusFox was thinking the same thing heh.
Puc has disconnected.
Somewhere on the muck, Azure has connected.
Djirn arrives from the foyer.
Djirn crawls all over Srass. *crawl*crawl*
Floid says, "http://www.furaffinity.net/view/8789565/"
Floid thinks Djirsrassles will appreciate that.
Djirn blink
Singe growls, "fox! http://www.topatoco.com/merchant.mvc?Screen=PROD&Store_Code=TO&Product_Code=SGR-EATED"
Srass pets all over Djirin.
JanusFox perks at shirt, needs.
Srass says, "I dunno about the cicada nipples. o.o"
JanusFox yips, "Angry ticks fire out of my nipples."
Miko chatters, "For the love of all that's holy, my anus is bleeding!"
Floid offers Miko a manpon.
JanusFox yips, "Well that's okay, even the one guy one jar guy survived without surgery."
Floid says, "Holy shit.  http://www.furaffinity.net/view/8820873/"
Zhorah has connected.
Zhorah rumbles, "I thought it was quiet"
JanusFox yips, "Man, people will hug you anywhere in a fursuit."
Floid says, "He did train first.  http://www.furaffinity.net/view/8540284/"
Kia arrives from the foyer.
Kia frinks.
Kia calls up Comrade Stalin, who shows up in his orange vest with a broom to sweep the sleepers off to their homes.
Puc heads to the sweeper's home to bang their mother.
Puc has left.
MegaWolf is sent home.
MegaWolf has left.
Djirn frunk
Duelist growls quietly, "One should really close mouf when skydiving."
Duelist growls quietly, "One never knows what'll fly up in there."
Floid demands one of these things for a pillow.  http://www.furaffinity.net/view/7700639/
Floid says, "As the comments mention, he would've had to rubber-band it shut.  Which probably would've looked silly on video."
Dralen meeeeeeeeeeps.
Duelist growls quietly, "Hah, the video is awesome"
Floid got no frash on this thing.
Duelist growls quietly, "That is really really cool."
Floid says, "I think maybe I should throw out 4 years of completely-out-of-date configuration (read: move to another ~/oldhome/, /oldetc) and just reinstall the latest DragonFly hotness."
Himmel arrives from the foyer.
Duelist growls quietly, "That's really awesome!"
Himmel obtains Danish. Uses it as a perch.
Dralen says deeply, "Haha! Cat sleep positions: http://www.buzzfeed.com/paws/awkward-cat-sleeping-positions"
Floid says, "It's a shame all my homebuild machines are un-identical tracking every AM2 chipset Radeon X200orwhatever -> 780G, or I could swap some shit out of the office and put the single-core Semprons back in those and have relatively-low-power fast-as-hell-for-home-server-use boxes."
Floid says, "I wonder if they didn't cut the ECC lines in those."
Floid wonders that, then remembers that all the ECC DIMMs he bought uselessly are DDR2.
Floid says, "It appears Lenovo paid someone to go through specific trouble to not draw those traces on the board on the Thinkwhatever tower that is the office "server"."
Himmel squeezes Floid's stuff.
Floid got no room for racks, though, and the only thing office needs is a switch to AM2 from 939 (hrrr) to deal with running Windows in a VM at faster-than-molasses speed.  It's still faster than NT on a 486, though.
Dachande. Waks up, surprirsed to find he slept in til 10.
Floid says, "Barely, but still."
Duelist growls quietly, "They got little tiny cabinets you can mount way up on a wall."
Zeph licks on Dachwuff some.
Dachande. licks on Zeph more.
Duelist growls quietly, "It'll hold a server, a switch...."
Floid says, "Economically and cosmetically it makes really little sense."
Duelist growls quietly, "Is this in your house?"
Floid should just trade crap out of the 'server' box into something homebuild with a board that consents to believe ECC exists someday.
Floid says, "Nah, law office, think bedroom-sized plus cubicle out in the floor-farm."
Duelist growls quietly, "I uhhh can't think that."
Duelist growls quietly, "I'm all about the true corporate office"
Floid says, "The real thing is, with ATX crap... let's say the worst happens and PSU fries, I have 3 spares at home plus Staples down the road."
Floid says, "If rack PSU fries, we gotta dump $300 on getting some stupid custom piece of shit FedEx'd out."
Floid says, "It really don't make sense for 'SOHO.'"
Duelist growls quietly, "Why not just cloud it?"
Duelist growls quietly, "Yeah I said it....cloud. Ugh."
Duelist growls quietly, "Or is it some goofy 'file server' thing?"
Floid says, "I'm a little tetchy about that because legal."
Duelist growls quietly, "Oh yeah, that's right."
Floid says, "Whup phone."
Huh?  (Type "help" for help.)
JanusFox is just happy not to need AT power supplies anymore.
Srass has arrived.
Srass has left.
JanusFox yips, "Had that one spare kicking around for years. People kept having them :P"
Samanthia hands Duelist: http://laspegasusunicon.com
Duelist growls quietly, "Oh for f...."
Duelist growls quietly, "At the Riviera? Haha"
Dachande. says, "Huh, wouldn't have figured the riv would be where they'd hold a bronycon."
Himmel says, "You should go, Dach."
Himmel says, "Bring a +1."
Himmel looks meaningfully at Duelist. >=3
Dachande. says, "Hahh, well they do have Tara Strong,sot hey might actually get a decent crowd."
Miko chatters, "What's the Riviera like?"
Miko chatters, "That name sounds like it's kinda cheap and trashy."
Dachande. says, "Kind of old, little small compared to some of the others on the strip but it's nice."
Miko chatters, "Ooh right."
Miko chatters, "I didn't think of the possibility it'd be a vintage name."
Dachande. says, "It's just one of the original ones."
Himmel pets Miko's ears.
Miko chatters, "From back when the Riviera as an idea had an air of sophistication, Sophia Loren and cocktails."
Dachande. says, "But unlike Cesars which was an early strip presence but just grew and grew and grew until you feel like the casino never effing ends. Riv is still pretty swank though."
Himmel says, "This next part of Black Mesa I'm about to do is freaking impossible."
Singe growls, "which part?"
Himmel says, "The Box-to-Box jumping."
Himmel is like gaaaaah.
Dachande. says, "Pretend the floor is lava."
Dachande. says, "Surely we've all traind for that since childhood."
Himmel is gonna eat lunch, first.
Himmel says, "Well, yes."
Himmel says, "But if Videogames were controlled with my own actions, I'd be even better at them."
JanusFox also fox... http://www.topatoco.com/merchant.mvc?Screen=PROD&Store_Code=TO&Product_Code=RUMB-SKATEFRIENDS&Category_Code=WELCOME
Himmel just imagines, full-body control and VR-rendering of Assassin's Creed. Any downstairs neighbors he'd have would hate him, but it'd be such fun!
Miko chatters, "Is there anywhere that looks like the 70s?"
Himmel says, "... Rural Sweden?"
Miko would love to go to a hotel/casino in Vegas that's themed to look like a hotel/casino in Vegas ca. 1965.
Zeph mews, "Tara Strong's awesome."
Zeph goes back to sleep.
Himmel lunchtiemnao.
Dachande. says, "The Golden Gate Club is like that Miko, they kind of never updated other than the machines."
JanusFox nodnods at Miko, wants that too.
Samanthia slinks out.
Samanthia teleports away.
Samanthia has left.
Zeph hugs about, sneaks to feed his mewface.
Zeph goes home.
Zeph has left.
Somewhere on the muck, Zeph has disconnected.
JanusFox wants 1971 and pink carpet.
JanusFox yips, "Actually the Florida Keys come close in some places.  But that's a different story."
Himmel wants 192X and a Jazz Club. But, of course, with all his modern comforts like video games and hair-straighteners.
Himmel says, "Well... Hair-straighteners that aren't just Irons."
Dachande. says, "They're squeezing irons."
Dachande. says, "Great for dual creesing socks."
JanusFox doesn't think Himmel wants the 1920s.
Himmel totally wants the 1920s.
Himmel says, "The Fashion, the Music."
JanusFox yips, "The racism :3"
Himmel points: Jazz Club.
Himmel would be safer than elsewhere!
Himmel says, "Of course, if I, as a musician, gained any sort of following, I'd be targetted for being an abomination."
Himmel says, "But oh, well!"
Himmel seriously, lunch.
Mundy arrives from the foyer.
Zhorah rawr some
Somewhere on the muck, Herefox has connected.
Kia has disconnected.
Mundy gooses Duelist!
Singe growls, "BOXES http://www.vgcats.com/comics/"
Mundy stares at FOX.
Zhorah rawr.
Zhorah has disconnected.
Zhorah has connected.
Zhorah eek
Zhorah clings to people
Duelist =O.O=
Somewhere on the muck, Rollo has connected.
Mundy licks Duelist!
Miko flails with a stick at nutritional information labeled "serving size: 1 serving".
Duelist licks Mundy!
Dralen has left.
Singe growls, "there's this One-A-Day brand of chewable multivitamins that instructs you to take two."
Mundy fiddles with FOX belly.
Djirn takes two Singe's a day. *nibble*
JanusFox likes gummy multivitamins, cause, gummy.
Zhorah rawr
Dachande. says, "I think One-A-Day referres to just the one dose, but really it'd be beter to have 2 a day in different intervals since you're going to piss out most of the first one by mid day."
Djirn urps
Duelist growls quietly, "I believe 'One-A-Day' is a brand name"
Djirn purrs quietly, "it is"
Singe growls, "and the not-chewable version you do take only one of"
Duelist growls quietly, "Man"
Duelist growls quietly, "So I started looking up weird and bad brand names..."
Duelist growls quietly, "And I found this: http://tinyurl.com/5wwurk"
Duelist growls quietly, "Waht the hell was wrong with us back then?"
Danish lows, "http://www.dangerouslaboratories.org/radscout.html  The rosy-cheeked lad at the bottom turned his backyard into a Superfund site as an Eagle Scout project."
Singe growls, "in shoe stores there was a popular x-ray machine for measuring feet. huge doses."
Duelist growls quietly, "Yeah, but this...."
Dachande. would like a radium watch, bets it still tics.
Duelist growls quietly, "All radium. Brush your teeth with radium toothpaste, wash it down with radium water....plug a radium suppository up your ass and wrap some around your balls....oh, and hasve a little radium chocolate for dessert."
Mundy licks Dachande.!
Dachande. taastes of hot sauce
Mundy's tongue bursts into flames.
Danish lows, "If Mundy's teeth were on fire..."
Danish unzips.
Somewhere on the muck, Rollo has disconnected.
Mundy <.<
Somewhere on the muck, Tony_Cheval has connected.
Mundy ponders a set of dentures, where all the teeth are shaped and colored like flames, and made out of a translucent material.
Djirn purrs quietly, "And have mini led's in them so they light up?"
Zhorah has disconnected.
Zhorah has connected.
Zhorah clean now
Djirn has left.
MegaWolf arrives from the foyer.
MegaWolf licks Floid
MegaWolf growls softly, "Curled curly tail"
MegaWolf http://www.puplookup.com/content/images/dog-breeder/breeder_2359_662.jpg
MegaWolf also *smewches* Duelist FOX!
Dachande. licks MegaWolf!
MegaWolf nuz nuz Dachande
Zhorah has disconnected.
Travis arrives from the foyer.
Zeph arrives from the foyer.
Zeph mewmewmews.
Kia has connected.
Travis waves
MegaWolf kisses snowmew
Zeph purrs on MegaPup some.
Zeph wiggles paws idly.
Duelist stretch out!
MegaWolf kisses Duelist 'gain too!
MegaWolf sneaks, RL
MegaWolf has disconnected.
Floid says, "Man, seriously Japanese people can be macabre."
Zeph mews, "Explain?"
Singe growls, "guro?"
Floid says, "This nice middle-aged immigrant friend-client lady is having trouble finding a decent job here after a divorce and trying to decide if she's moving back to Japan to basically linger around the nursing home where her folks are living until they're gone and it's her turn to wind up in it."
Somewhere on the muck, Azure has disconnected.
Danish lows, "I think that's the Japanese way of bringing up that she's available."
Floid says, "So... my father, being kind of a blunt sort, and somewhat agreeing with the 'enough is enough' attitude, kept leading her on with the whole 'don't want to be a burden, sometimes I just want to die, ...'"
Floid says, "Polite awkward conversation.  Stereotypical but aieesh, steer it *away* when it goes there people."
Travis winks out of sight in the sparkling glow of a space/time rift.
Travis has left.
Floid says, "Don't forget to do all that while fueling up with Ethyl, tigr."
Duelist o.o
Kia has disconnected.
Floid finds it sorta interesting how it only took about 100 years to go from 'wow, chemistry is simple!' to 'woah, we better make sure we design this shit to degrade, because the simplest stuff persists forever.'
Luperion pads in and growls!
Luperion has arrived.
Mundy cuddles Luperion!
Luperion ruffle-snuffles Mundy!
Dachande. says, "Sort of nsfw, but amusing, http://imgur.com/gF7Gs ."
Floid says, "Rainbowels."
Dachande. says, "Must be unicorn variant."
Floid freezings much.  Desires some form of medication which does not exist, at least in his vicinity.
Luperion dogs Floid to keep him warm.
Duelist growls quietly, "It's called booze"
Floid says, "Enh."
Duelist growls quietly, "Cures what ails ya"
Floid's stomach just fails to thrill at the idea.  In part because it's empty, whups.
Dachande. says, "Get some Dr. James Barttolomew Horatio's Medicating Tonic Water. It's full of 180 vegetables and 13 different animals with just enough alcohol to keep it shelf stable for years. One spoon a day keeps the rickets away."
Floid opts to try to figure it out after trying to sneak additional nap.  People are wanting him to do extremely inconvenient things and have them done already.
JanusFox wants something with 13 different animals.  Not enough of that on the market.
JanusFox also learned that dropping a small rare earth magnet on metal drill fillings makes it instantly the sharpest object known to man.
Somewhere on the muck, Sarusa has connected.
Zeph dead from cute: < http://faror1.deviantart.com/art/Shimeji-Snow-Leopard-264681891 >
Miko whoa. http://www.youtube.com/watch?v=UYEUoSQXdcE
Miko immediately hears it alleged that in parts of fFinland that plant is known as a "pries's dick".
JanusFox yips, "omg cute."
Duelist ooo, cattails!
JanusFox also hasn't seen one of these things since 1995.
Mav arrives from the foyer.
Mav wuffs.
Miko chatters, "..annnnd apparently the real name of the plant in Finnish is obscure-archaic for "wolverine's dick"."
Zeph wouldn't mind seeing Wolverine's dick.
Duelist go store!
Duelist goes home.
Duelist has left.
Mundy GWAHAHAS. http://cheezburger.com/6572261376
Puc arrives from the foyer.
Puc gruffs.
Zeph noses on Puc some.
Puc mrarfs, headbutts Zeph.
Mav wruffs gruffly, "Kittens"
Kia has connected.
Somewhere on the muck, Herefox has disconnected.
Kia has disconnected.
Kia has connected.
Kia has disconnected.
Kia has connected.
Kia frinks.
Mav mephs.
Miko strokes Kiabutt.
Somewhere on the muck, Herefox has connected.
Kia prrs at Miko and grrs at mudclient, which lee
Kia says, "keeps fucking up. "
MegaWolf has connected.
MegaWolf growls softly, "Dingo, notdingo."
MegaWolf shakes off from the shower, then curls up, muzzle on paws. z.z
Luperion woofs, "The We and the Not-We."
Mav wruffs gruffly, "Knotdingo."
Luperion woofs, "Gladly."
MegaWolf ponders a snow dingo hybrid.
Luperion gruffles, "Sneaux dingeaux?"
MegaWolf growls softly, "That too"
Luperion giggles.
MegaWolf ponders a pack of all the canids. Dingo, dhole, wild dog, Ethiopian wolf, jackals, 'yotes, etc.
Somewhere on the muck, Azure has connected.
Luperion wuuffs, "For cuddles?"
MegaWolf growls softly, "And such!"
Luperion gruffles, "Indeed."
Luperion barks, "Puppies love cuddles."
MegaWolf growls softly, "Cuddles. Yep. ,.,"
Himmel not cuddles Mega.
Luperion pants, "Knot cuddles?"
Mav wruffs gruffly, "Knots are best cuddled."
MegaWolf pleads the fifth... of vodka.
MegaWolf velcros Himmel.
Himmel yipe.
Luperion wuuffs, "To Mav!"
Mav hugs his tail.
Himmel gonna play Black Mesa for a bit.
MegaWolf curls up, gnaws on chewybone.
Kia has disconnected.
Himmel gets on his gaming goggles.
Miko chatters, "What is the purpose of the goggles?"
Himmel says, "THey... don't really do much."
Himmel says, "Yeah, now that I think about it..."
Himmel says, "The goggles?"
Himmel says, "They, uh... do"
Himmel says, "very little."
Luperion growls, "Doggles."
Luperion idles to 'walk the dog'!
Luperion growls and pads out!
Luperion has left.
Himmel says, "He means 'Masturbate.'"
Miko chatters, "You know, they'd help prevent a psychotic Rainbow Squirt den mother from plucking out your eyes."
MegaWolf growls softly, "So Black Mesa actually got released, eh?"
Himmel says, "Couple days ago, yeah."
Himmel says, "And... Maybe, Miko. But I have no idea what that is."
MegaWolf growls softly, "I'm sure it'll do okay but I wonder how much interest there is left for it."
Miko chatters, "Philistine."
Himmel says, "Maybe I shouldn't play video games."
Puc has disconnected.
Himmel says, "I really ought to read something."
Himmel says, "Like this great piece, what was it..."
Danish lows, "Have you ever said something that was 100% true but 100% irrelevant?"
Himmel says, "Bartleby and the Scrivener?"
Miko punts Himmel.
Himmel =3
Himmel says, "Problem?"
Miko chatters, "It's from Psychonauts, when the G-Men interrogate Raz. "WHAT IS THE PURPOSE OF THE GOGGLES?!""
Miko chatters, "And later the Rainbow Squirt den mother threatens to pluck out his eyes and he goes "Ah-ha! THAT is the purpose of the goggles!""
Himmel assumed Miko was going for 'The Goggles, they do Nothing!'
Danish ohhhh, I vaguely remember that.
Himmel has not played Psychonauts, though, no.
Himmel says, "But then, no one has."
Himmel says, "Hence its reputation as Best Game No One Played."
Himmel says, "2005, iirc."
Miko chatters, "Well, nobody did when it first came out."
MegaWolf tickles Himmel's insidey parts.
Himmel eek.
Miko chatters, "I bet when/if they Kickstart it they'll get $4M in the first day, though."
Himmel is not making much progress in the Play Black Mesa thing.
Miko chatters, "The sequel, I mean."
Himmel says, "Most definitely, Squiz."
Miko chatters, "A lot of people want it something fierce. Notch was all "well, I can invest $2M or so in it""
Miko chatters, ""Because I want to play it""
Himmel says, "Most expensive game ever."
MegaWolf growls softly, "Neo Geo?"
Miko chatters, "Neo Geo did not cost $2M."
MegaWolf growls softly, "Sure felt like it!"
Danish lows, "You had one?"
Miko chatters, "Of course, if he invests $2M he'll probably get a game and $2.2M for his trouble, but.."
Gyroe arrives from the foyer.
Gyroe growlfs!
Mav wof.
Danish's childhood punches MegaWolf.
Himmel is mostly playing Black Mesa for the Nerd Points, though, he admits.
Himmel says, "It's an FPS, and lord knows I hate the format."
Danish lows, "Even as a kid I knew there was no point in asking for a Neo Geo."
Himmel says, "Because Portal."
Himmel says, "And Still Alive."
MegaWolf growls softly, "Nah"
Himmel thinks he left out a line, there.
Himmel says, "'But I still want to, as a matter of gamer cred.'"
Danish lows, "That's not an FPS, Wolfenstein 3D's an FPS."
Miko peers at Danish.
Danish lows, "I can see you've played knifey-spooney before."
Kuttas arrives from the foyer.
Kuttas points at the lazing sleepers and goes all tribal, shouting, "Ki'i ki-rharg, ki'i etya stye ngyet-ngye!"
Puc heads to the sweeper's home to bang their mother.
Puc has left.
Kia is sent home.
Kia has left.
Zhorah is sent home.
Zhorah has left.
Kuttas has left.
Danish lows, "Hi K..."
Danish lows, "Hi Kimmel."
Danish hugs Kimmel.
Himmel pets Danish.
MegaWolf O.o
Rhi arrives from the foyer.
MegaWolf growls softly, "Double Dragon!"
Mav falls over, paws in the air.
Himmel says, "Half Life Vets."
Himmel says, "Tell me."
Himmel says, "How often is there ventilation duct combat?"
Rhi has disconnected.
Rhi teleports away.
Rhi has left.
Kia arrives from the foyer.
Kia frinks.
Vetiver arrives from the foyer.
Himmel says, "Hey, Kia."
Srass arrives from the foyer.
Srass nuzzles around and and things.
Kuttas arrives from the foyer.
Srass licks Kuttas' muzzle.
Kuttas licks Srass' whiskers.
Gyroe kneads on Kuttas and Srarse.
Kuttas snickers.
Srass purrs, and paws at Gyroe.
Kuttas rubs Gyrow.
Kuttas errs, Gyroe*
Srass says, "Let's put the ow in Gyrow."
Srass chews on the dragon's arse!
Kuttas pinches!
Danish lows, "Let's put the gyro in Gyroe."
Danish does this.
Kuttas spins Dragon!
Srass says, "Save some for us!"
Duelist arrives from the foyer.
Srass licks Danish and Duelist.
Kuttas licks Duelist!
Duelist =^.^=
Kuttas pinches Moose.
Duelist licks Srass!
Duelist licks Kuttas!
Danish just licks everyone and has a bunch of weird fur on his tongue.
Kuttas thinks the weird fur is probably Srass'. Almost certainly, in fact.
Srass is weird all over, so it stands to reason his fur would be weird.
Kuttas isn't weird at all. Nope, nosir, not one bit.
Danish oh, there was this one curly black hair that was 20 feet long, that was probably Srass.
Kuttas pets Srass' nose with [redacted].
Srass licks Kuttas' [redacted].
Kuttas adds a couple more [redacted] per nostril.
Srass o.O
Kuttas snickers evilly.
Srass mouths on Kuttas' entire forearm at once.
Srass slobber, drool.
Kuttas pets Panther's uvula. *tugtug*
Srass' expression gets stranger. *glurk*
Danish read that as vulva, didn't question it.  :/
Kuttas nods to Danish. Srass is -that- weird. c.c
Danish pets Srass' vuvuzela.
Kuttas says, "Don't pet it. Blow on it."
Danish t-toot... toot... *blush*
Srass *definitely* does not have one of those!  Not even in the chicken form!
Kuttas says, "What, a vuvuzela?"
Srass says, "Yeah!"
Kuttas says, "Why not?"
Kuttas says, "They're terribly annoying! :-D"
Srass says, "They're annoying!"
Kuttas inquires, "Aren't hyenas annoying, too?" He tugs some more.
Srass says, "Hyenas are flavorful. c.c"
Duelist preps for hardcore, full contact, professional BINGO!
Srass makes a strange gurgling sound.
Kuttas >.>
Danish lows, "What kinda stakes?"
Kuttas O.o
Srass says, "You'd probably better stop tugging on that.  It doubles as a delivery lever of sorts."
Kuttas peers into Srass' mouth. His voice reverberates, "What's that noise?"
Kuttas says, "Delivery level?"
Kuttas says, "Err, lever?"
Himmel says, "Kuttas."
Srass says, "Delivery lever.  Of half-digested lunch."
Himmel | http://images.4chan.org/v/src/1347829959465.jpg
Duelist growls quietly, "Let's see....it's a double action session...."
Kuttas ohs. He pets the back of Srass tongue, instead.
Himmel says, "Stolen from Tapestries."
Kuttas peers at Himmel.
Himmel was amused.
Duelist growls quietly, "1/2 the games pay $200, half pay $400, Coverall pays $1000, hotball is $2500 and the progressive is $26,913"
Kuttas has seen that image before.
Himmel says, "Oldie but goodie?"
Kuttas shrugs.
Miko fnarrrr, hotball.
Tequiua arrives from the foyer.
Tequiua waves.
Srass pets Tequiua.
Duelist growls quietly, "Boulder Station progressive bingo win pays $135,500"
Himmel says, "Total, or top-tier?"
Tequiua pets Srass.
Danish is pretty good at Bingo.
Srass says, "How do you manage to be good at Bingo?  It's a game of chance, isn't it?"
Tequiua says, "Pretty good? There is a technique for Bingo?"
Tequiua hehs at Srass.
Srass grins at Tequiua.
Duelist growls quietly, "It's ALL skill man!"
Duelist growls quietly, "Same with slot machines"
Srass says, "Gosh... that little old lady sure is good at pulling levers."
Danish lows, "There's no random element in top-tier bingo, it comes down to playing it right."
Miko chatters, "Just like the stock market!"
Srass says, "How's this possible?  You hear a number, you put a chip on the number."
Duelist growls quietly, "IT's HOW you chip that number that makes all the difference."
Duelist growls quietly, "Also, daub"
Duelist growls quietly, "Not chip"
Duelist growls quietly, "Rookie."
Srass says, "I haven't played since grade school.  Of course I'm a rookie. :-P"
Tequiua says, "Top-tier? There are tiers in Bingo?"
Kuttas wriggles on Srass distractingly. Annoying hyena is annoying!
Zeph mews, "Over here bingo is played by old women and people who are under the mistaken impression it might be fun."
Srass zerberts Kuttas' nuts.
Duelist growls quietly, "Listen...."
Kuttas murrrrs!
Srass says, "It's the same thing over here, too, Zeph."
Duelist growls quietly, "$135,000 to win."
Duelist growls quietly, "Fuck those old ladies. I'm takin' that money!"
Duelist growls quietly, "To win that $135,000 you have to coverall in 51 balls or less."
Tequiua says, "Here too, bingo is played by widows, old ladies and old dudes expecting to score with an old gal."
Srass oooohs!
Srass says, "Now I know Duelist's angle. >;)"
Duelist growls quietly, "On a super coverall progressive like that there is usually only one winner."
Scruff arrives from the foyer.
Scruff sneaks in, and up into FOXY lap
Srass pets Scruff's ears.
Scruff headrubs up at srasspaw. Mriew!
Kia has disconnected.
Vetiver snugs Scruff.
Duelist petpetpte CHTA!
Duelist growls quietly, "These guys are makin' fun of me, CHTA"
Scruff chirps, "Butbutbutbut, big FOXY!"
Scruff noses at a mapsbok paw. That one! *nosenosenose*
Scruff inspects the big FOXY. Yup, excellent creature!
Danish hugfuzzles Scruff.
Kuttas considers turning on the radio.
Scruff rears up on hindpaws, hugs 'round moosemuzz ^-^
Kuttas hasn't got any QSL cards lately
Duelist needs to put his antennas back up!
Kuttas says, "https://imo.im/fd/C/QkPpapbN9P/292225_306211372787161_1053649823_n.jpg"
Danish ha.
Duelist growls quietly, "Oooo, great pic!"
Scruff loves that pic!
Duelist needs to get ready for BINGO.
Duelist growls quietly, "Just, while y'all are pokin' fun at me....I should mention...."
Duelist growls quietly, "Since 2011, I am up $12,300 playin' bingo."
Kuttas could use $12300
Duelist growls quietly, "But that don't mean it came home with me >;)"
Srass grins.  "Cool."
Miko could use $123.
Danish huh.  Gotta make it rain sometimes.
Himmel could use $12.30
Danish could use $12.
Srass says, "No?  What'd you do with it?"
Kuttas would be on a plane in short notice if he had that.
Duelist growls quietly, "Slots, restaurants, bars....etc."
Miko could .. no, he's probably got $1.23 on the floor, total.
Srass ahs.
Duelist growls quietly, "I have a running tally of my 'casino in general' fund...."
Duelist growls quietly, "Since 2008 I'm up, like, $8"
Danish lows, "Miko, if you share your $1.23 with me I can get a pack of smokes."
Scruff chirps, "Eight bucks!"
Miko chatters, "I'll just put the change in the mail for you, yeah?"
Duelist growls quietly, "So consider that as a career."
Kuttas says, "That's $19.65 or so a day"
Danish pets, you're a dear.
Duelist growls quietly, "$8 in 4 years. So that's $2 a year."
Duelist growls quietly, "About 200 hours a year..."
Duelist growls quietly, "I make a penny an hour, gambling!"
Srass says, "I imagine you're doing better than a lot of people. :-P"
Danish lows, "Have you gotten any old lady hugs, though?  Those are more precious than money."
Duelist growls quietly, "Hell no"
Duelist growls quietly, "Those old biddies are a menace!"
Kuttas snickers.
Duelist growls quietly, "Especially around nickle slots!"
Duelist growls quietly, "Watch those old, pointy elbows, cuz they throw 'em"
Duelist growls quietly, "Anyhoo, time to BINGO! Wish me luck!"
Tequiua says, "Nickle slots? They go that low?"
Danish lows, "Luck!"
Srass says, "Good luck!"
Miko chatters, "What happens if you add the money you've spent on eating and drinking to that $8? I mean, you don't subtract lunch from your paycheck."
Tequiua says, "I though the lowest was $1 USD"
Miko chatters, "Break a leg!"
Duelist hah!
Duelist bingooooooo!
Duelist goes home.
Duelist has left.
Danish lows, "Macbeth!"
MegaWolf vaguely fends off RL
MegaWolf nosekisses Scruff, 'cuz kitten.
Kuttas had this creepy chick hitting on him hard the last two times he went to the redneck bar. The second time, he asked her, "So, you lookin' to take a randy young cowboy home to rock your world all night long?" with a suggestive grin. When she smiled and waggled her eyebrows and said, "Yes," he continued. "Me too. Any prospects?"
Kuttas says, "Err, Creepy old chick*"
Srass giggles.  "What'd she say to that?" :D
Kuttas says, "Not a word."
Srass laughs!
Tequiua says, "Brakeback mountain episode."
Kuttas says, "She just got this really weird expression and wandered off."
MegaWolf snibbles Makyo and Zeph, Floid gets tweaked.
Kuttas says, "She was also like, 4'2" and probably old enough to be my mother. It was ridiculous to start with. "
Tequiua is ok with old people sex, "They are good on bed too."
Gyroe scoots!
Gyroe goes home.
Gyroe has left.
Tequiua says, "Or so... I... em... had heard... <.< >.>"
Danish lows, "So, old, short, good to go, and you turned this down?"
Kuttas says, "Yes."
Danish pets Tequiua, we all like DILFs here.
Srass giggles, and pets Tequiua.
Tequiua says, "DILF?"
Himmel says, "Dad I'd like to Fuck."
Tequiua chuckles.
Himmel, super into'em.
Kuttas says, "I've got no problem with older women. Older women are awesome. But I don't like being hounded, and I'm not keen on casual bar hookups."
Danish growls, "Himmel, go to your room... on second thought, go to my room."
Kuttas says, "Actually, I'm no keen on casual hookups in general."
Tequiua says, "Casual hookups are good. Straight to the point."
Mundy BURP.
Himmel goes to Danish's room. Waits patiently.
Tequiua says, "Cheaper in the long run."
Danish lows, "Itty bitty baby."
MegaWolf growls softly, "Ugh, what is with websites and this Springboard video server?"
MegaWolf growls softly, "The videos won't play for me"
Miko chatters, "Itty bitty boat."
Tequiua says, "Springboard sucks!"
Himmel says, "I CAN'T BE-MEME- IT."
Scruff noses around, sneaks out!
Scruff teleports away.
Scruff has left.
MegaWolf also hates it when there's like twenty servers he has to pick from in Noscript to get anything to work at all.
Kuttas rubs PILF.
Srass mews, and nuzzles Kuttas extensively.
Kuttas snuggles all over Srass.
Danish lows, "http://i.imgur.com/kQQUy.jpg"
Srass says, "Cute."
MegaWolf growls softly, "Hah"
Zeph listens to a mixtape type thing he got sent by a fellow werewolf enthusiast called 'Wolfsongs for Wolfbros'.
Mundy says, "Hungry Like the Wolf on it? :)"
MegaWolf growls softly, "Hungry Like I Was a Teenage Werewolf Of London"
Miko mutters something about showing you what all that howl is for.
Himmel says, "Or Within Temptation's The Killing?"
Zeph mews, "Heh, first track is a cover of that, Meeks."
MegaWolf totally needs to remix a song with that title now. n.n
Kia has connected.
Floid boggles at his landlordlady re: text messages.
Danish licks Miko!
Danish lows, "You reminded me I actually really do like a song about werewolves."
Zeph mews, "One of us! One of us!"
Himmel says, "Sorry. Not The Killing."
Danish lows, "https://www.youtube.com/watch?v=j1-xRk6llh4"
Himmel says, "The Howling."
MegaWolf growls softly, "THT DNT CNFRNT ME, LNG AS I GT MY MNY NXT FRI"
Danish oh.  Really needs to read up before posting things.
MegaWolf growls softly, "Werehuahuas"
MegaWolf growls softly, "The Yipping"
Huh?  (Type "help" for help.)
Himmel says, "I would love this song if it was mixed down differently and the guy sang differently."
Zeph mews, "Man, I kinda want to share the mediafire link for this mixtape thing but I was asked not to. But it's really awesome. Dilemma."
Danish lows, "https://www.youtube.com/watch?v=s4s5bj5fZO8  There you go, Himmel."
Miko chatters, "Try a live version? https://www.youtube.com/watch?v=MxawVMQ02dc&"
Himmel says, "Well, I meant going the other way, Danish."
Miko chatters, "Actually, given the choice of which one to put on an album, I'd go with that live recording over the studio one."
Himmel says, "The Live Version is better, yes."
Miko chatters, "But then, I almost always would."
Zeph totally accidentally copypastes http://www.mediafire.com/?n2w8ufd6a3coghs
Danish lows, "https://www.youtube.com/watch?v=XSEYGsk6KTM , Himmel?"
Danish lows, "Sorry, wrong link.  https://www.youtube.com/watch?v=Uec35ppYLIc"
Miko chatters, "I like how little most of them look like members of a rock band."
Makyo mrp.
Makyo mrp from Canada.
Danish lows, "Makyo summoned by the dulcet tones of Neil Sedaka."
Danish hugs you!
(p) In a page-pose to you, Rikoshi snoof.
Zeph snugs a Makyofops, who he saw rather the likeness of on FA: < http://www.furaffinity.net/view/7700639/ >
Duelist arrives from the foyer.
Kuttas licks Duelist!
Himmel gapes at Danish.
Himmel says, "That guy is..."
Himmel says, "So..."
Himmel says, "-So- White."
Somewhere on the muck, Rikoshi has connected.
Duelist growls quietly, "oh yeah! time for hardcore championship bingo!"
Duelist licks Kuttas!
Mundy says, "Full-contact bingo? :)"
Kuttas says, "Have fun!"
You are currently marked as being away.
You page-pose, "Makyo nuzznuzz, all the way over from Canada." to Rikoshi
You have 1 mail messages waiting.  Use 'page #mail' to read.
(p) In a page-pose to you, Rikoshi thinks you smell metric.
Duelist growls quietly, "nah, full contact is for screwing"
MegaWolf gently headbutts Duelist FOX
MegaWolf (Today at 8:22:40AM) -- http://skia.deviantart.com/art/Phone-Fox-175079615
*Done*
Kuttas says, "Hide the dauber."
Kuttas snerks.
Mundy says, "Dauber dick."
Himmel says, "Dobiedick."
MegaWolf ohgodtehkyoot. http://www.furaffinity.net/view/8847494/
You are currently marked as being away.
You page-pose, "Makyo nod!  Well...mostly smells like fox.." to Rikoshi
Zeph eeeeee.
Away flag reset.
Duelist growls quietly, "sweet foxies"
You yerf, "Goodfoxes."
Danish lows, "Whole gallery is brainmelting."

----------

Ogg arrives from the foyer.
Ogg waves 'round, glumly, having just read about Margaras.
Draconis hugs the Ogg, and glums right along.
Ouroboros waves to Ogg.
Djirn rubs Draconis' belly to keep up the wrring
Makyo nuzz on Ogg.
Ogg chatters, "That's two military furs that we've lost in vehicular crashes.  Doesn't seem fair."
Floki "Hi Ogg!
Floki says, "Meep, what happened...?"
Floki says, "Reading, where...?"
Justin arrives from the foyer.
Floki reads 'read'.
Floki says, "Oh, heavens..."
Justin pounces and puppylicks! Floki
Floid has disconnected.
Floki meep!s at Justin.
Floki says, "Hi!  You got furry!"
Floki's left head mourns at Margaras.
Ogg hugs Floki!  Floki hugs the pea-green monkey warmly and scritches his spine.
Floki snugs Ogg sadly.
Makyo mmmf ._.
JanusFox work, no plays.
Justin yaps, "You think I should shave?"
JanusFox changes a few array pointers around and ends up someplace else.
JanusFox has left.
Floki says, "No!  I am far more used to furred people than bare-skinned!"
Djirn sheds on Draconis so he looks furry for Floki
Ogg chatters, "That's fuzzy logic."
Floki grins at Djirn. "Scales are not bare skin!"
Floki fuzzles Ogg.
Skylos has disconnected.
Somewhere on the muck, Tigerwolf has connected.
Miko hugs Ogg!  Ogg YEEKs in alarm and blushes a deep forest green, but does nothing to try to escape Miko's attentions.
Miko shrieks, "WHAT UP MOTHERFUCKERS HERE'S A BOMB ON Y'ALL"
Skylos is sent home.
Skylos has left.
Puc heads to the sweeper's home to bang their mother.
Puc has left.
Floid is sent home.
Floid has left.
Singe eeks!
Singe has left.
Fiend Plushie bounds after Singe.
Miko ahems. c.c
Floki says, "Hi, Miko."
Makyo o.o;
Miko chatters, "Hi, Floki."
Miko cuddles on Flokes, too.
Floki purrs on Miko a lot.
Tear has disconnected.
Miko sneaks to take his mama shopping.
Miko winks out of sight in the sparkling glow of a space/time rift.
Miko has left.
Somewhere on the muck, Miko has disconnected.
Undine licks Draconis!
Undine hugs Ogg!  Ogg YEEKs in alarm and blushes a deep forest green, but does nothing to try to escape Undine's attentions.
Justin  whistles for a bouncer, and a huge gorilla steps out of nowhere, and hauls out the sleeping furries. "Time ta go, boyz.." he growls..
Tear is sent home.
Tear has left.
Undine raises the modesty screen. ;)
Draconis growfs, "you get my mail squish? re: window stuff?"
Undine says, "I dih."
Draconis growfs, "goodo."
Gyroe sneaks!
Gyroe goes home.
Gyroe has left.
Ogg counterhugs Undine.

-----

Makyo yrp.
Kia has a listen to Who by Fire?.
Miko hugs you!
Himmel rubs Miko.
Kia says, "The live version, so it isn't tarnished by Cohen's cheap-Casio aesthetic. "
Harth says, "That sucks about Marg, first I heard about that."
Kia says, "Though he wasn't doing that on New Skin yet. "
Makyo squeeze MIKS?
Miko eek.
You say, "Argh phone ;.;"
You yerf, "Sorry..."
Miko pets Makyo and his phone.
Miko thinks about Crocu for a bit now.
Makyo leeean.  Sigh.
Azure arrives from the foyer.
Azure prowls in.
Duelist thump Footpad. "Woof, how you is, hmm?"
Footpad blinks, widens his eyes, and exhales a deep breath.  "Knocked" is about the best word for it.
Miko then thinks about Margs' music, some of which was sitting in a folder somewhere on a webserver, and trying to find that URL, and his first thought is 'ask Margs'. Stupid brain.
Footpad would have complained about the cold he's got, but suddenly it's no longer so goddamn relevant.
Makyo woke up thinking about Lynx. Has been up and down all day.
Arcturus arrives from the foyer.
Pontiac chomps on Arcturus.
Footpad oddly knows he's not really going to grieve for lynx.  Just think about him a lot for a while.
Duelist growls quietly, "I think that time has passed....enough....that we will be coming to grips with this in our own ways."
Himmel daubs at Foots's nose.
Miko puts on "So You'll Aim Toward The Sky" for the eleventh time this week.
Grynn tackle jaql.
JanusFox yips, "Poor guy.  Ah well, keep calm, carry on, and all that rubbish."
Skylos softly barks, "how many people are comfortable with death?"
JanusFox yips, "The trick is to be a jerk so you live forever."
Himmel says, "Depends on whose, Skylos."
Miko chatters, "My own death, or death in general?"
Makyo gets all sniffly in hotel bar. Classy as fuck. Idles a few.
Himmel says, "As for Margs, I'm just going to miss him."
Kia shrugs... Death comes to us all. Lemur would prefer it not come to him too soon, except for when he feels trapped, depressed and alone.
Skylos softly barks, "I'd think both, Miko.  But if yo have to choose one, I'd say that of others.  You'll have to deal with that a whole lot more times."
Skylos softly barks, "Nobody likes to feel like they don't have options."
Himmel says, "As for me, I have no problem with it happening. I hope as few people are distraught by my passing as possible, because I don't want to cause people pain."
Kia says, "As for others... And so it goes. "
Footpad is in the mood for angry music.
Kia gives Footpad some Geto Boys? They're his go to for angry music.
MegaWolf growls softly, "In the Angry Dome."
Duelist growls quietly, "Death isn't nearly as much of an issue as 'we want more' is. Face it, we want more. Taking someone away from us sucks. Yeah, it might sound selfish, but that's what it is. We want more."
Duelist growls quietly, "And now that we can't have more, well, it sucks."
Himmel nods.
JanusFox yips, "I'm really more concerned about the nature of the demise."
Miko chatters, "Well."
Miko chatters, "I was just thinking I wouldn't be so upset if Margs had.. gone somewhere. Become unavailable to me specifically."
MegaWolf growls softly, "Also the perceived unfairness of it."
JanusFox yips, "What concerns me is well... erf.  I just hope he was going fast enough."
Skylos is curious of the circumstances of the accident, but it doesn't matter in the end.
Miko chatters, "It's that there's no more Margs to be had, for anyone, anywhere."
Miko chatters, "Been trying not to think about that, Janus, thanks."
Srass has left.
Srass has arrived.
Duelist growls quietly, "Yeah...."
Duelist growls quietly, "I don't want to consider either."
Duelist growls quietly, "Cuz it ain't nice, no matter how you think about it."
Footpad finds himself protective and angry at the thought... no, fuck that.
Footpad wants more time with lynx.  Wants lynx to have more time with him.  It's not just selfish.
Himmel leans on Footpad.
Skylos huffs.
Skylos softly barks, "well.  "
Kia pets Footpad.
Somewhere on the muck, Tigerwolf has connected.
Kia oohs. There are "Mad World" piano tutorials.
TealFox arrives from the foyer.
JanusFox yips, "80s or 90s?"
Kia dunnos. Lemur's listening to a little known cover from the fabulous Red Paintings right now. Will look at the piano tuts momentarily.
Kia'd like to check the lyrics on this one. Suspects they're different.
Skylos wags.
Joe arrives from the foyer.
Skylos sniffs Joe.
Kia wonders where Joe's going with that gun in his hand.
Joe eyes Megawolf, comes over with a bottle of the good stuff.
Joe sez, "Kia, I'm going to shoot my old lady, heard she been messin' around wit anutha man!"
Joe sits across from Megawolf, waits for him to awake.
Joe waves to the small wuff and the big wuff.
Joe sits back, putting one ankle on a knee.
Footpad watches Joe with polite mistrust.  Wolves tend to be that way with strangers.
Joe is not just a stranger but strange little Footpad.
Joe peers but smiles.
Miko chatters, "Speaking of, Foots. I miss you. We should try to actually figure out a time & place."
Kia thinks looking at piano tutorials for nice songs will distract him.
Joe eyes Miko and looks away.
Skylos coldnoses Joe and tries to lean on him.
Joe pets Skylos a bit but directs him to a chair at the table he's at with Megawolf.
Joe would sniff Kiwaku but the foxy party boy is not about tonight.
Kia already has the sheet music for fucking SMB.
Joe orders a Bin 63, and Damian and Enrico spring into action, preparing it in a matter of moments and sliding it across the bar with a flirty wink.
Skylos climbs up on chair?
Joe drops Bin 63.
Joe orders a Bin 65, and Damian and Enrico spring into action, preparing it in a matter of moments and sliding it across the bar with a flirty wink.
Joe drinks a bit of Bin 65.
Makyo okay.  Back at room.
Joe eyes the Skylos and gives snax.
TealFox hugs Makyo
Skylos munches.
Makyo squeeze around Tealio.
Kia wonders if he could convince his tutor to drop To a Wild Rose in favor of Mad World.
TealFox provides comforting and soothing hugs
Joe leans on elbows on the table, wresting his chin on one fist and idly petting Skylos with the other.
Kia will get arund to Maple Leaf Rag in due time.
Skylos tries to lick in Joe's mouth.
Kia prrs quietly. Lemur supposes he's done found his instrument.
Somewhere on the muck, Vikki_Fox has connected.
Joe rather avoids tounge with Skylos, popping a pretzle into that maw. "This always happens. Megawolf has /just/ left and I'm here with a pencil and paper. He's prolly in another window watching and laughing."
Joe rolls his eyes and chuckles.
Skylos softly barks, "what are you going to do with the paper?"
Joe sez, "Write on it."
Joe peers at Skylos.
Skylos softly barks, "what are you going to write on it?"
Joe sez, "Your home address and then show up in nothing but a leather halter when your dad answers the door."
Joe ^.~
Skylos softly barks, "Hell yea."
Skylos can't wait.
Joe lauhgs.
Joe drinks a bit of Bin 65.
Weaving under the weight of an order of Bacon, >Manuel< stumbles over and gives it to Joe.  He trots back to the kitchen, panting.
Joe rips off a piece and gives it to Skylos.
Joe eats a bit of Bacon.
Skylos softly barks, "my dad: http://dogpawz.com/photos/People/dad2.jpg"
Skylos softly barks, "he had a surgery recently on his neck artery because it was clogged"
Skylos softly barks, "but there was a complication and he had a stroke."
Mundy pokes at MSMVs.. Grf.
Skylos softly barks, "He'll be staying with my brother and nephews and sister in law for a while until the doc says he can do stairs again."
Makyo curls 'gainst Tealfoxes.  Wrrf.
Joe sez, "Ironically thats not far from what I look like in RL: http://3.bp.blogspot.com/-bKbQXVNBnIc/T1z--qrC5XI/AAAAAAAAAIU/5VM9IWCOWQM/s1600/DocHD.jpg"
TealFox is good for curlling up with
Pontiac teleports away.
Pontiac has left.
Joe thinks Skylos dad did okay, he made Skylos.
Makyo prr and prr on Teal :3
Joe sez, "When did Megawolf last post here?"
Skylos heh.  "That's kind of you to say Joe.
Joe drinks a bit of Bin 65, finishing it.
Footpad likes the look of Skylos's dad.
Skylos softly barks, "my dad is a real friendly sweet guy."
Skylos softly barks, "Love him so much."
Joe sez, "You exemplify this."
Miko paws at Footpad.
Joe imagines an inverse of the Vader thing, Skylos is nice, like his father before him.
Footpad leans on Miko, and sighs thoughtfully.
Miko counterleans and closes his eyes.
TealFox snugs on Makyo. So is not liking sudden fall allergy attack...stupid texas trees
Footpad nudges Miko with his nose.  Is there a better airport to look for than 'sinki?
Joe really needs to chat with Megawolf eventually.
Dachande. says, "Wouldn't the inverse of Vader mean that his father would have been good and then his father would have been mean? Although luke was sort of a dick now that I think about it."
Skylos isn't whiney, he hopes.
Joe sez, "No, inverse of the whole deal."
Skylos softly barks, "My doggie Akando is whiney.  In fact, he just whined atm e just now."
Duelist growls quietly, "Bite that bad dog!"
Miko was looking at Tampere-Frankfurt because RyanAir is all he can afford, before having a poke at the other departure options.
Skylos softly barks, "but he's cute, and he has a flop ear."
Joe eyes his cat. "Bubba is full of love and purrs. I have this fantasy that we are both reincarnated. I was a brash priest in a hindu temple and went out for wood in the morning and he killed me as a tiger and now he's my pet in America. XD
Footpad would quite like to see Finland again.  On the other hand, he'd like Miko to meet Mischa.  So it can go either way.
Joe gets Footpad some vodka.
Joe orders a Finlandish Vodka, and Damian and Enrico spring into action, preparing it in a matter of moments and sliding it across the bar with a flirty wink.
Azure turns and runs away, disappearing in an azure-edged silver flash.
Azure has left.
TealFox has disconnected.
Arcturus hnngf
Kia notes that Helsinki airport is lovely.
Name                   Sex        Species     ('whospe #help' for help)
Joe                    Unknown    Transhuman
TealFox[asleep]        male       Arctic Vulpine
Srass[idle 9m]         herm       polymorphic chakat
Arcturus               male       Jackal
Makyo                  N/A        Anthro Arctic Foxy
Harth[idle 9m]         Male       Minotaur
Skylos[idle 2m]        male       Man-Dog
Footpad                male       grey wolf (non-morphic)
Acy                    mALE       Chow chow (chow)
Grynn                  male       Grey/Arctic Wolf
Vexus[idle 1h]         Male       Cosmic Black Fox
Vetiver[idle 24m]      Male       Gemsbok (Southern oryx)
JanusFox[idle 4m]      male       Cross Fox
Kia                    male       ringtailed lemur (lemur catta)
MegaWolf[idle 23m]     male       White Wolf 'Morph
Malkoten[idle 3h]      male       Black Panther
Himmel[idle 24m]       Male       Cat
Floid[idle 1h]         male       Dingo
Duelist[idle 2m]       Male       Skunk!
Mundy[idle 8m]         -unknown-  -unknown-
Miko[idle 2m]          o->        Nut muncher
Dachande.[idle 3m]     Male.      Wolf.
Joe hands Finlandish Vodka to Footpad.
Kia suspects it beats hell out of flying out of Pulkovo, which, when flying in, struck him as if his British Airways flight was also a time machine to 1973.
Skylos brings Akando to meet Mischa.
Miko cares little about the details. He just wants some Footles time. :)
Joe gives Footpad to Miko
Joe is not authorized to do that but tries anyway.
Miko appreciates the thought.
Skylos softly barks, "here"
Skylos softly barks, "here's the white akando, sable banshee, and me: https://picasaweb.google.com/lh/photo/rrJg5hctUS6dSzvd412HvdMTjNZETYmyPJy0liipFm0?feat=directlink"
Miko awr, doggies.
Duelist bites all those bad dogs!
Himmel misses his pup. ._.
Makyo snf.  Miss dogs.
Joe sez, "Okay, seriously, when did Megawolf come on to FM so I can meet up with him?"
Skylos softly barks, "duelist, can't you tell these are good dogs, because they are german shepherds?"
Duelist growls quietly, "Of course they are!"
Duelist growls quietly, "They can take biteys too, cuz GSD is tough dog!"
Footpad guesses Kostya is lucky he can take biteys, because he must get a lot from TIGR.
Miko wishes he had a better idea of his plans past the end of the month. It's all up in the air.
Duelist do bite Kostya! *grni*
Duelist err grin!
Duelist growls quietly, "Kostya looks like Banshee."
Skylos softly barks, "megawolf shows online, Joe."
Joe hands Bacon to MegaWolf.
Duelist - http://www.bigtiger.net/images/Kostya.jpg
Skylos softly barks, "he hasn't sent a message for 27 minutes though."
Joe orders a Meet With Joe, and Damian and Enrico spring into action, preparing it in a matter of moments and sliding it across the bar with a flirty wink.
Skylos orders a doggie blaster, and Damian and Enrico spring into action, preparing it in a matter of moments and sliding it across the bar with a flirty wink.
Skylos drinks a bit of doggie blaster.
Skylos drinks a bit of doggie blaster.
Skylos drinks a bit of doggie blaster, finishing it.
Joe hands Meet With Joe to MegaWolf.
Joe sez, "There."
Joe chuckles.
Skylos softly barks, "Akando is whining up  storm.  Better dog the walk."
Footpad wags his tail gently.  Kostya is so very, very purty.  Happy memories of dog when he was only three months old.
Srass has left.
Makyo just got dogpictures tonight.
Joe sez, "I always thought the internal email of mucks could be used for short encrypted messages, but this is different."
Srass arrives from the foyer.
Joe imagines the NSA watching the Nurple.
Joe O.O
Say version 3.11a (c)1993 by Tim (#64369)
Type 'sayhelp' for help on say. Local notify-routines now supported. Sayhelp 5
You yerf, "There we go: http://pics.lockerz.com/s/246236343 "
Makyo must hug that dog.
Mundy says, "Kostya looks almost camera shy."
Duelist growls quietly, "Awww, sweet foxy dog!"
Duelist growls quietly, "Nah, Mundy, that is suspicious dog. He is at the vet."
Mundy says, "Ah.. Gonna get stabbed with needles"
Duelist growls quietly, "He don't mind needles. He do not like the vet tech tho. The vet tech is a wuss."
Skylos winks out of sight in the sparkling glow of a space/time rift.
Skylos has left.
Kia has yet another listen to Rachele Gilmore.
Mundy wonders if he cooked this MSMV..  Hmm..
Makyo dog is okay!  He's a big thing, good for a hug or two.
Joe eyes Kia.
Joe https://www.youtube.com/watch?v=k4t2AVTtPSQ
Duelist - http://www.bigtiger.net/images/kdbw.jpg
Kia says http://youtu.be/CHp4LLnlKIg
Footpad stuffit.  Gets up, packs in a hurry to board a train.
Miko hugs Footpad!
Kia pats Footpads rump onto the train.
Miko chatters, "Seeya, dearest of wolves."
Mundy says, "Happy dog is home"
Makyo hug on Footpads.
Duelist pets-n-thumps Footpad, nicely, of course.
Footpad pokes Miko with his cold nose.  We shall discuss this further.  For now: au revoir.
Footpad has disconnected.
Duelist growls quietly, "Makyo has awesome dawg."
Joe eyes the fading Megawolf and chuckles. He gets up, pays Enrico and leaves this: https://www.youtube.com/watch?v=dXYl5NrHPb4
Joe goes home.
Joe has left.
Makyo tries to snoof his way into Miko's good favor.  "So You'll Aim Toward The Sky" came on playlist and now feels all okay.
Miko pets Makyo, who is permanently favored as it is.
Makyo's dog is okay!  Sometimes a brat!
Makyo prr and prr :o)
Miko puts on a last song for the night. Low - Lullaby.
Mundy studies the logic diagrams. Brainsplodey.
Makyo awr, more dog: http://pics.lockerz.com/s/245597378
Somewhere on the muck, Tony_Cheval has disconnected.
Himmel buries himself in Science. Ugh.
Makyo ugh wants to tussle with these paws: http://pics.lockerz.com/s/243461399
Duelist growls quietly, "Awwwww"
Duelist growls quietly, "That's such a sweet dawg."
Makyo loves that dog so much :I
Duelist growls quietly, "Good!"
Duelist growls quietly, "You should"
Djirin arrives from the foyer.
Srass noses Djirin.
Kia gives Himmel some goggles. Otherwise, Science can blind you.
Miko nuzzles about and beds.
Duelist licks Srass!
Miko winks out of sight in the sparkling glow of a space/time rift.
Miko has left.
Somewhere on the muck, Miko has disconnected.
Srass licks Duelist!
Djirin blinds Sras with science
Duelist whips out his hockey stick. He 'skates' up to a sleeper, winds up and lets a slapshot go!
TealFox spins and spins into a Teal blur and then with a loud *FOOP*, disappears!
TealFox has left.
Footpad slinks cautiously to a safer sleeping-place.
Footpad has left.
Srass bumps into things.  Including science.
Harth winks out of sight in the sparkling glow of a space/time rift.
Harth has left.
Djirin nooooooogies srass nooogyingly
Srass gropes Djirin firmly!
Mundy gooses Duelist!
Duelist O.O
Zhorah arrives from the foyer.
Zhorah rar.
Somewhere on the muck, Vikki_Fox has disconnected.
Mundy grumps and flails around in http://www.ti.com/lit/ds/symlink/cd14538b.pdf
Djirin symlinks Mundy to Srass
Djirin hmms. multivibrator
Djirin peers at Mundy
MegaWolf drops Meet With Joe.
MegaWolf drops Bacon.
Mundy's not making sex toys. >.<
Duelist chrp!
Djirin murmurs quietly, "Sureeeeeee"
MegaWolf growls softly, "Speaking of... where is Alex fox?"
Srass says, "He hasn't even signed on since April."
You yerf, "AlexP/"
Zhorah rumbles, "Foxcube?"
Makyo er.. ?
Zhorah rumbles, "Alexp is a cube"
You yerf, "He's all over twitter."
MegaWolf growls softly, "Tell foxcube to revivify!"
Makyo okies, did so :o)
Kuttas arrives from the foyer.
Srass licks Kuttas' ears.
Kuttas wriggles them
Grynn ruffles Kuttas' mane.
Kuttas licks Grynn!
Grynn wags and slurrrps hyena back.
Djirin muwahahahas
Kuttas eyes Djirin.
Djirin burp
Kia's cat seems to be developing a fondness for being where he is.
Djirin drapes atop Kia too
Srass offers Kia a cat spatula.
MegaWolf gobed before Freaky von Psycho returns.
Mundy hmms.. one-shot is not one-shotting..
MegaWolf winks out of sight in the sparkling glow of a space/time rift.
MegaWolf has left.
Kia says, "I mean, exactly where I am. So I sit up in bed, and she gets between me and the pillow. :P "
Kuttas says, "Who's Xane on about?"
Somewhere on the muck, MegaWolf has disconnected.
Mundy says, "Joe, I wager."
You yerf, "Alex, Kuttas?"
Makyo oh, right, reads up c.c
Kuttas says, "Oh, oops... I forgot something..."
Kuttas bites Mundy!
Dachande. says, "I'm thinking Joe."
Duelist licks Kuttas!
Makyo nod c.c
Kuttas shakes his head. Poor Xane.
Kuttas licks Duelist!
Zhorah rumbles, "who's joe?"
Kia says, "Joe's the guy with the gun in his hand who's going to shoot his old lady. "
Kuttas says, "I thought he was a plumber."
Kia says, "Joe's the guy with a plunger in his hand, who's going to plunge his old lady's toilet 'cause he caught her flushing things down the toilet? "
Makyo cold, tired.  Probably bedtime in a bit.
Zhorah curls around Makyo
Mundy hmms.. Eyes logic doodles.
Makyo curl within curl, steals a bit of warmth.
Zhorah is very warm
Kia listens to a song that may make him cry.
Mundy seems to have also misplaced one of his little voltage doodads..
Kia gets a tin hat and a gun and gets sent away to the war.
Makyo purr and purr and purr at Zhorah.  Fox should bed.
Duelist sneak into FOX bed!
Makyo has a big bed, for the next few nights!  King!
Duelist not sure space is all that necessary >;)
Duelist kidding! Innocent foxy >:)
Zhorah sneaks in too!
Makyo giggles, prrr :3
Djirin reduces the king to a twin.  puts Duelist atop Makyo
Makyo prrr, good and cozy and warm beds :3
Kia prrfs. o/~ For to hang tents and pegs, a man needs two legs--no more waltzing Matilda for me. o/~ That'd be the part that usually gets him all misty. :(
(p) In a page-pose to you, Judas snugz. :) How you?
Duelist might not be so innocent with Zhorah tho!
Duelist whistles....
Kia mmfs. Helps that his own history has a bit of this in it.
Zhorah <.<
You page, "Rough night. Lost a friend last week, still dealin'.  You?" to Judas.
Kia's great(?)-granddad got gassed in the Great War. Wasn't the same after.
Kia says, "So I hear. I never met him. "
(p) In a page-pose to you, Judas awrfs, an' snugs you into his lap. He gently wrapps you up in foxarms an' foxtail, resting his muzz on your shoulder. "I'm okie. Just chillin' in front of the TV.
Kia's drunk-ass grampa just invaded Sicily or whatever.
Kia says, "He's dead too, before I ever had the sense to talk to him. And so it goes. "
You page-pose, "Makyo rrmfs and leans in against you all cozylike, chills with you for a few longer, then." to Judas
(p) In a page-pose to you, Judas nuzzles ears. Anything I can do?
Kuttas leans.
Kia wishes his grandfolks could've lived long enough for him to have some sense.
You page-pose, "Makyo nuzz atcha some.  Will just be time, supposes :o)" to Judas
Himmel liens on Kuttas.
Kuttas is cat exempt.
Himmel collects his ees, anyhow.
Himmel... fees.
(p) In a page-pose to you, Judas nodnods an' jus' snuggles. Gonna go to bed?
Kuttas robs Himmel blind.
Kia wants to talk to gramma S---y and grampa S---y and granny H----s and Papa H----s. Gramma could tell him about when she was in a convent. Grampa could tell him about Sicily. Papa could tell him about all of his crazy random jobs and being on the Mississip and all. Granny could tell him... um. Something. Or other. Ok, Granny, kind of an awesome lady, but perhaps not the best historical source.
Zhorah licks Kuttas.
Kia could get at great-granny the post-mistress and general-store-...woman through her, but would rather have just talked to great-granny.
Mundy bangs head on desk.
(p) Judas pages, "Should I get ready wif pillows an' plushie? :)" to you.
Kuttas pets Zhorah's nose.
Kuttas thinks Himmel is a scaredy cat.
Srass peers at Mundy.  "You okay over there?"
Zhorah rubs nose on Kuttas.
Mundy says, "No."
Kia mmmhs. And the greats could've told me about the great-greats... *sigh* Fuck you, Mr. Death.
Himmel pffs.
Himmel says, "I'm many things."
Himmel says, "A scaredy cat is not one of them."
Duelist growls quietly, "What's up, MundyWoof?"
Grynn yawwwwns.
Mundy says, "This MSMV isn't working. It looks like I've got shit connected properly.  But.. It's not behaving."
Djirin murmurs quietly, "Pound it with a rock"
Mundy says, "That'd be real helpful."
Djirin nods!
Kia anyways. Lemur lets you talk about scaredy cats and MSMVs.
Djirin offers Kuttas for pounding instead
Himmel rubs Kia.
Himmel says, "I'd love to meet my ancestors."
Himmel says, "But all of them would think I'm an abomination."
Himmel says, "The living ones all do, anyway."
Kuttas murrs!
Kia met his grandparents. All of them loved him.
You page-pose, "Makyo rrwf, nod, definitely time for bed soon.  Needs cozy :3" to Judas
Himmel says, "One of my grandparents loved me. And one of my step-grandparents."
Himmel says, "Actually."
Kia says, "All of them died before I had the sense to actually ask them anything. "
Himmel says, "I'm not even sure how to define that relationship."
Kia says, "Fuck, I should talk to my dad about Vietnam. "
(p) In a page-pose to you, Judas gently picks you up, an' carries you over to the bed. He pulls back the sheets wif his tail, sets you on the bed, gets in himself, an' covers us both up. :)
Himmel says, "My grandmother married another man."
Kuttas wonders why, if Himmel isn't a scaredy cat, he's set !K?
Kia says, "Well, at least she didn't marry another woman? "
(p) In a page-pose to you, Judas gets all snuggly, a life-size foxplush. :)
Himmel says, "... Is that what the flag is, here?"
Kia's gramma would've married another man if she hadn't been Catholic and... well, Catholic.
Himmel says, "I thought it was kill_ok?:no ."
Kia says, "Grampa was a nasty drunk. "
Himmel's biological grandfather was a douchewad.
Cain arrives from the foyer.
Cain sits down
Makyo sneaky to bed.
There's no place like home...
There's no place like home...
There's no place like home...
You wake up back home, without your possessions.
Makyo disappears in a puff of complacency.
Apartment.(#51076RLJA)
More of a studio or loft than anything this apartment has had all separating walls removed except for those protecting the privacy of those engaging in bathroomly behaviors..  Nestled in one corner is a kitchenette type thing with an island counter for eating.  Along an opposite wall are large picture windows, at the base of which a low platform surrounding two mattresses set next to each other on the ground, creating a sort of soft spot in the floor to serve as a ginormous bed type thing, with a few comfortors and loads of pillows tossed in to complete the image.
Contents:
BUTTON: He Who's Ears Are Upon Him(#51757)
Macchi
Ranna's Tails(#58415X)
Fluffy pink ribbon for Astarael's decidedly fluffy tails
You page-pose, "Makyo sqky, purrs and gets all cozy with, then, nestling under covers.  Fox really should get to bed, 'fore it stays up much longer." to Judas
(p) In a page-pose to you, Judas turns out the light. Goodnight. :) *Zzz*
(p) In a page-pose to you, Judas *mrr*-signs you to sleep. :)
(p) Judas pages, "*sings" to you.
You page-pose, "Makyo dozes 'gainst comfortably, prr." to Judas
% Connection to furry closed.
\end{verbatim}
\newpage

\begin{ally}
Thank you.
\end{ally}
I was going to save that for September sixth.

\begin{ally}
I know.
\end{ally}
You made me cry.

\begin{ally}
I know.
\end{ally}
You hurt me.

\begin{ally}
I know. It's been seven years.
\end{ally}
Yit'gadal v'yit'kadash sh'mei raba Would that I had the faith To pray daily. Eleven months to let you go, And an amen to end the sorrow.

\begin{ally}
It's okay to not let go of some things.
\end{ally}
How? How so? How could that possibly be true? How could one possible grow as a person with not letting go of something?

\begin{ally}
It's okay to not let go of some things, and to use them to inform your growth in the future. It's okay to use grief to become a better person.
\end{ally}
I guess.

But it still hurts.

\begin{ally}
I know. We can continue.
\end{ally}
\newpage
