\noindent Back in 2011 and 2012, I started to really loathe being me.

\begin{ally}
`Started'?
\end{ally}
Well, okay, in a very specific way. I started hating the anger. I started hating the expectations. I starting hating the toxicity.

\begin{ally}
You started hating a lot more than that.
\end{ally}
I started hating my brain and my body. I started hating the coarseness of me. I started hating all my angles. I started hating my hair and my face and my genitals and my lies.

I was lying to JD. I was lying to work. I was lying to Tyson. I was lying to everyone who saw me online as a girl, and I was lying to everyone who saw me online as a boy. I was in a liminal place where I could tell no one the truth.

\begin{ally}
Not even yourself.
\end{ally}
Not yet, at least.

There were a few easy steps to take, of course. I saw a doctor who got me on meds.

\begin{ally}
Tell me about suicide.
\end{ally}
Not yet. Don't derail me for a bit. I need some breathing room after yesterday.

\begin{ally}
Tell me about Younes, then.
\end{ally}
I'm getting there.

I started taking my own meds alongside those the doctor gave me. I started the slow process of ridding myself of testosterone. I hated my body so much, I did my best to camp out up in my head, to remove at least one means of having to interact with it: sex.

\begin{ally}
Go back. Before that.
\end{ally}
Before that, I changed how I presented. I changed Makyo to be genderless. Started going by `it' pronouns. And I made Younes.

Younes was a means for me to no longer lie. Or at least knock the severity of the lies down a few notches.

Younes was like me. He looked like a guy, but had something decidedly feminine about him.

\begin{ally}
Don't be coy: he had a vagina.
\end{ally}
Well, yes, but he wasn't simply male in all his interactions. He was effeminate, without being flamey. He could be both more and less than a guy.

\begin{ally}
Let's talk about kink.
\end{ally}
Soon, soon.
\newpage

There's a few things that I did wrong, here.

\begin{ally}
Objectively?
\end{ally}
Yes. Or maybe, wrong by consensus. Wrong subjectively, and also wrong by the standards of many of those around me.

\begin{ally}
Did they feel wrong at the time?
\end{ally}
They felt shameful.

\begin{ally}
Is shame wrong?
\end{ally}
Not always. It can be an indicator, I suppose.

\begin{ally}
It's a tool. It's a tool to tell you when you're being vulnerable. In this case, vulnerable in your uncertainty.
\end{ally}
I suppose.

I handled this in a way that made me feel a lot of shame. I was uncertain about a lot.

\begin{ally}
If you had done so unabashedly, would that have made it any better?
\end{ally}
I don't know, honestly.

\begin{ally}
What were you uncertain about?
\end{ally}
I was uncertain about the approach. I was uncertain about the terminology. I was uncertain about how it made me feel. That last most of all, probably.

I approached Younes as a primarily sexual facet of myself. After all, what's the point of making a character with both a penis and a vagina, I thought, if there isn't going to be some aspect of sexuality to it?

\begin{ally}
There may be a great many points besides that.
\end{ally}
Yeah, I know that now. Uncertain, remember?

\begin{ally}
Always.
\end{ally}
So I made an altersex character that was primarily sexual in nature. that was the approach. And then I called him a `male-herm'.

\begin{ally}
Ouch.
\end{ally}
Yeah, ouch. The term does not fit so well these days. Some folks own it, and I'm happy for them, but even then, the term rankled. It took a lot of history and turned it, for a lot of folks, into a fetish. A lot of intersex folks are really unhappy with it being used. Ditto `futanari'.

It's understandable, too. Like, I've dealt with chasers. Folks who fetishize my gender, my presentation, my body.

\begin{ally}
It's understandable now.
\end{ally}
Yes. Uncertainty.

It made me feel almost right. It made me feel like I was on the edge of something. It made me feel just around the corner from a revelation. It made me doubt myself. It made me doubt my place in the world. It was both a symptom and the cause of my hatred for body.

\begin{ally}
For your body, or for yourself?
\end{ally}
Both, I suppose. It was a symptom of this growing unease, this feeling of being just a few millimeters to the left of myself. This feeling of being just slightly out of focus.

A rangefinder camera uses a ghostly yellow image overlaid atop the real image when you look through the viewfinder. When you turn the ring of the lens to focus, that ghost slowly shifts to align with the object you want to be in focus.

\begin{ally}
Your view of yourself was slowly slipping from focus. Matthew was starting to lose coherency.
\end{ally}
And Younes was one of the means of slowly dragging that back into focus.

It doesn't matter how right or wrong it was of me to use this tool. It does matter how wrong I was in the mechanics of the scenario.

\begin{ally}
You hid him. You covered him up and kept him from the world. You interacted with a completely different crowd, as Younes than you did as Makyo or Macchi. When that overlapped with Rikky, it was awkward.
\end{ally}
It was, and not because of the altersex part. We interacted that way with Makyo as altersex, too, amd that didn't feel awkward at all. It felt like cheating to engage with the world as Younes. It felt shameful.

\begin{ally}
The thing that you did wrong was to lie.
\end{ally}
\newpage

Growing up, I had a real problem with lying.

\begin{ally}
There were reasons.
\end{ally}
That doesn't mean it wasn't a problem. That doesn't make it right.

\begin{ally}
It shifts more into the gray area.
\end{ally}
Let's talk about dad later. Life began at high school, remember? We can talk about the kid who grew up to be born freshman year some other time.

\begin{ally}
The problem with lying is often the problem of secrets. The only secret that can be kept is when only one person knows it, and even then it's not guaranteed.
\end{ally}
Yes.

\begin{ally}
And you got found out.
\end{ally}
Yes.

\begin{ally}
And it cost you.
\end{ally}
Yes. It cost me friends. It cost me sanity. It made me jerk away from the path I'd started down. Made me jerk out of focus again.

\begin{ally}
Let's talk about TIASAP.
\end{ally}
Yes.
\newpage
