How can one be sexual when the act of engaging in sex is so confusing, so anxiety-inducing as to be not worth it no matter how barked up one is?

\begin{quote}
You're getting ahead of yourself. The solutions arrived before the problem made itself known.
\end{quote}

I suppose so.

My first sexual experiences took place over the phone and over text. Late night, parked in front of my computer with the cordless pinned between my cheek and shoulder, Danny and I masturbated together 1,800 miles apart. There was only the soft sounds of breathing, the quiet monosyllables, and the rushed reassurances that, yes, we were close, and then a shaky sigh from both of us.

\begin{quote}
You can still hear his voice saying two things: ``Mattie'', his pet name for you, and the sleepy, giddy kind of ``I love you'' that comes after an orgasm when you've both stayed up far too late.
\end{quote}

I only met him once. We just smoked weed together in a hotel bathroom, hung out, cuddled. Sex would be too complicated for us, by then. We had gone our different ways. We had become different people.

\begin{quote}
And by then, you'd started encountering the aforementioned problem.
\end{quote}

Yes.

Another easy solution I latched onto was erotic roleplay. TS. Typefucking. Co-authoring erotica.

I latched on and wouldn't let go. Still haven't. Beyond even myself, it shows up in my writing:

And it was there where I found love. There where I found love and lust and romance and flings. I dated. I TSed (we were, of course, too cool to use so vulgar a word as `cyber'). I set up relationships for characters in our games, and I set up relationships that transcended that, two hearts touching through only those white words on a black screen.

Merlin and Marusin, The\_Prof and rranger386, people I would dream about and likely never meet. We were all young. We were in love with each other in our own little worlds, serially and in parallel.

And while sometimes I would think about who they were beyond the screen, it was rarely for long. I was in love with Merlin the fighter who hated magic. I was in love with The\_Prof the student who desperately wanted to be a professor when he grew up, and didn't care which subject.

Sometimes I would think about who they were when we TSed, would wonder what it would be like to have their paw instead of my own around my erection, but never for long. It was easier. It was safer to not bother with it.

But our relationships were as real as any collocated flings. More so, we told ourselves, for the purity of essence that came with no flesh to get in the way.

I'm sure we all hungered for touch.

\begin{quote}
Did you?
\end{quote}

Did I what? Write bits of my life into furry fiction?

\begin{quote}
Hunger for touch.
\end{quote}

In some cases, sure. I wanted nothing more than to hold, to be held. I wanted nothing more than to experience arousal and climax with these people I loved.

\begin{quote}
And that was the problem.
\end{quote}

Yes. The problem was that I wanted to experience arousal and climax, but not really the whole sex part. Or perhaps I wanted that frictionless sex that can be accomplished in typefucking. I wanted that consequence-free, painless, perfectly-lubricated and utterly mess-less sex.

Even then, I'm not so sure.
