The problem was that I didn't really want sex. I loved the idea of it, loved reading and writing about it, loved ERP, loved consuming art, loved thinking about it, loved masturbating. I just didn't really love sex itself.

Not for lack of trying, mind. I played around with my partners, tamping down my anxiety and squeamishness in order to try and just enjoy myself, enjoy our times together. Often, I was at least reasonably successful, too. I still have fond memories of some fun romps.

\begin{quote}
What rankled?
\end{quote}

It was a few things, I think. The most obvious being the increasing dissonance between my body and my identity as `male' started to fit less and less. When having a penis seems odd and discordant, engaging with it feels unsatisfactory at best, nauseating at worst.

Another was simply the mess of it all. Water-based lube gets sticky. Condoms are finicky. Fluid-bonding is great, but then the mess is magnified. Foreskin is complicated --- a rough weekend left me scarred, the resulting phimosis making sex something of an adventure.

I think, most often, it was just that it was a lot of work. You had to set aside time. You had to negotiate. You had to have the condoms handy. You had to have the lube handy. You had to both be willing and on the same page. All perfectly doable, but whether or not it was worth it was something that seemed to vary from day to day.

\begin{quote}
And the shame.
\end{quote}

Yes, there was plenty of that. The unswerving sense that I had messed up. That I was doing something wrong. That this was all so disgusting. That this baffling act of smashing meat together was somehow a positive thing, but I just couldn't see how.

\begin{quote}
You tried to cleanse yourself of that with TIASAP. You also tried going the other way. You went to the Underground parties. You gathered around you a core group of people you trusted and played with them. You worked to extract that shame from yourself so that you could live without it.
\end{quote}

Sometimes it worked. Sometimes it was a matter of the stars aligning.

Of those fond memories I mentioned, most of them surround lazy, comfortable sex, where everything was just aligned. Giving a cozy blowjob on a couch with no time pressure. Putting my hair up with a chopstick. That Underground party with lube and condoms readily available, and us two incidentally parked near enough that getting started was no stress. Sneaky fingers slipping past elastic waistbands. Tentative touches.

\begin{quote}
Sex that you had for fun. Sex with people you were close to. Sex with no expectations.
\end{quote}

Which I suppose is how it should be, but that rarely seems to be the case. Even when JD and I had moved in together and were sexually active, it was often more stress than it was worth.

\begin{quote}
And then you gave up trying to conquer shame.
\end{quote}

Yes. And since, by that point, every sexual act I engaged with left me feeling awful, I effectively gave up on sex.
