\begin{quote}
Where did the shame come from?
\end{quote}

I'm not sure. I've got a few ideas, though.

The first is likely that, as a queer person, societal shame is just part of our lives. We're not normal, after all. The sex we have doesn't line up with the sex we \emph{should} have.

I certainly bought into that, despite all of my efforts. Homosexual stuff was fine online, of course, because it was all so idyllic and perfect. No muss, no fuss. To be confronted with just how much of a mess sex can be offline, especially between two bepenised individuals, left me feeling like somehow I was falling short of that ideal.

\begin{quote}
Perhaps that is the crux of the shame: sex should be easy, and you should be good at it, if your online sex life was anything to go by. That it isn't and that you aren't felt like an indictment.
\end{quote}

Yes. The second idea that I have is that there was that misalignment between body and mind that started in 2005 and just grew wider over time. This put that indictment in very stark terms: sex should be easy, I should be good at it, and I should be a girl, if my online sex life was anything to go by, and I was none of those things.

\begin{quote}
Has the shame lessened since transition? Since surgery?
\end{quote}

Oh, quite a bit. I still feel like I'm not very good at it, that it's not easy, but I no longer have that overwhelming sense that I'm lying to everyone I lay with.

\begin{quote}
Your other ideas?
\end{quote}

Two. The first is subtler, and more of a subset of stuff already mentioned. To be raised a boy in America in the 90s is to be raised with the competing ideas that women are people and that women are sexual objects. Having sex is a balancing act between claiming what is rightfully yours as a man and treating a woman right.

To then be gay, and especially then to bottom, is to turn every bit of that on its head. You become the sexual object. You become the person who should be treated right. You fulfill all these obligations placed on sex, but somehow manage to do so completely wrong. You fuck it all up.

\begin{quote}
The other?
\end{quote}

Getting raped just kind of messes you up.

\begin{quote}
Ah.
\end{quote}

So, let's talk about kink.
