Self harm

Self harm is a recurring theme within my life.

It takes so many forms, too. The cutting and burning, sure, but also the self-sabotage. Dropping my testosterone to zero. If approaching this in a sexual fashion was wrong, then remove the sexuality.

\begin{quote}
An obvious solution.
\end{quote}

I punished myself for what I did. If was fetishizing, if I was causing harm, then I deserved to suffer for it. I removed my sexuality from the picture. Cyproterone acetate twice a day and medroxyprogesterone every two weeks does a really good job of that.

I tell myself now that if I belive something to be true when I'm depressed as well as when I'm hypomanic, it's more likely to be right.

\begin{quote}
One of us only tells the truth, and one of us only lies.
\end{quote}

Perhaps if I still felt like I existed a few millimeters to the left of my body when sex wasn't a part of the equation, I was more likely to be right in pursuing the path of gender exploration.

I talked with JD about this, he helped me out, but I told basically no one else. I tanked my T and attempted to learn from my punishment.

\begin{quote}
Now now, what did we say about secrets?
\end{quote}

And then I let it slip on FurryMUCK, yes.

\begin{quote}
You spilled the beans.
\end{quote}

Yes. Then I admitted it. I talked about it.

\begin{quote}
You spoiled the surprise.
\end{quote}

Everyone was so confused.

\begin{quote}
Lapsus linguae.
\end{quote}

I was so ashamed.

\begin{quote}
You spoke too soon.
\end{quote}

Even my punishment was wrong.

\begin{quote}
It was the last thing Margaras heard from you.
\end{quote}

Never mind stopping myself from creating Younes, nevermind stopping myself from chemical castration; if I could go back in time, I would stop myself from saying anything for just a few more days.

\begin{quote}
He died knowing that about you.
\end{quote}

If Margaras had to die, I would that he not die with that being the last he heard from me.

\begin{quote}
You cannot take that back.
\end{quote}

If Younes, chemcast, and Margs' death are immutable, if losing my friends was inevitable, at least let me delay the hour of my mistake.

\begin{quote}
You cannot.
\end{quote}

Please.

\begin{quote}
You cannot.
\end{quote}

Oh god.

\begin{quote}
It was the last thing he heard from you.
\end{quote}

Merciful god, please take me away.

\begin{quote}
You never spoke to him again.
\end{quote}

I will close my eyes and my heart and become a stone.
