\label{selfharm:selfharm}
\index{Mental Health!self harm}
\renewcommand*{\footnoterule}{%
  \kern-3pt%
  \color[HTML]{dddddd}\hrule width 0.4\columnwidth
  \kern2.6pt}
\renewfontfamily\pagenumfont{Gentium Book Basic}[Color=DDDDDDFF]
\backgroundcolor{c[0]}[HTML]{222228}
\backgroundcolor{C[0](10000pt,10000pt)(0.6\columnsep,10000pt)}[HTML]{222228}
\backgroundcolor{c[1]}[HTML]{222228}
\backgroundcolor{C[1](0.6\columnsep,10000pt)(10000pt,10000pt)}[HTML]{222228}

\begin{paracol}{2}
\begin{leftcolumn}

\fontspec{Gentium Book Basic}[Color=DDDDDDFF,Ligatures=TeX]
\renewfontfamily\allyFont{Merriweather Sans}[Scale=0.9,Color=EEEEFFFF,Ligatures=TeX]

\noindent Self harm is a recurring theme within my life.

It takes so many forms, too. The cutting and burning, sure, but also the self-sabotage. Dropping my testosterone to zero. If approaching this in a sexual fashion was wrong, then remove the sexuality.

\begin{ally}
An obvious solution.
\end{ally}
I punished myself for what I did. If was fetishizing, if I was causing harm, then I deserved to suffer for it. I removed my sexuality from the picture. Cyproterone acetate twice a day and medroxyprogesterone every two weeks does a really good job of that.

I tell myself now that if I belive something to be true when I'm depressed as well as when I'm hypomanic, it's more likely to be right.

\begin{ally}
One of us only tells the truth, and one of us only lies.
\end{ally}
Perhaps if I still felt like I existed a few millimeters to the left of my body when sex wasn't a part of the equation, I was more likely to be right in pursuing the path of gender exploration.

I talked with JD about this, he helped me out, but I told basically no one else. I tanked my T and attempted to learn from my punishment.

\begin{ally}
Now now, what did we say about secrets?
\end{ally}
And then I let it slip on FurryMUCK, yes.

\begin{ally}
You spilled the beans.
\end{ally}
Yes. Then I admitted it. I talked about it.

\begin{ally}
You spoiled the surprise.
\end{ally}
Everyone was so confused.

\begin{ally}
Lapsus linguae.
\end{ally}
I was so ashamed.

\begin{ally}
You spoke too soon.
\end{ally}
Even my punishment was wrong.

\begin{ally}
It was the last thing Margaras heard from you.
\end{ally}
Never mind stopping myself from creating Younes, nevermind stopping myself from chemical castration; if I could go back in time, I would stop myself from saying anything for just a few more days.

\begin{ally}
He died knowing that about you.
\end{ally}
If Margaras had to die, I would that he not die with that being the last he heard from me.

\begin{ally}
You cannot take that back.
\end{ally}
If Younes, chemcast, and Margs' death are immutable, if losing my friends was inevitable, at least let me delay the hour of my mistake.

\begin{ally}
You cannot.
\end{ally}
Please.

\begin{ally}
You cannot.
\end{ally}
Oh god.

\begin{ally}
It was the last thing he heard from you.
\end{ally}
Merciful god, please take me away.

\begin{ally}
You never spoke to him again.
\end{ally}
I will close my eyes and my heart and become a stone.
\newpage
\null
\thispagestyle{empty}
\newpage

\noindent There is too much fire in me

to be described by the soldering iron's tip.

\begin{ally}
I must not fear.
\end{ally}
Were I to draw it across my skin,

it would all spill out at once.

\begin{ally}
Fear is the mind-killer.
\end{ally}
I'd melt, eaten whole by flames,

and flow into a pool of molten glass.

\begin{ally}
Fear is the little-death that brings total obliteration.
\end{ally}
Sublimation would claim me,

atoms would scatter, diffuse.

\begin{ally}
I will face my fear.
\end{ally}
I would be borne up through the clouds,

and grow lighter by the second.

\begin{ally}
I will permit it to pass over me and through me.
\end{ally}
All that energy poured to the air around me,

an imperceptible increase in temperature.

\begin{ally}
And when it has gone past I will turn the inner eye to see its path.
\end{ally}
Particle would excite particle

until I'm felt only as warmth on your face.
\newpage
\null
\vfill

\begin{ally}
Where the fear has gone there will be nothing.
\end{ally}
But even that would not be enough.

\begin{ally}
Only I will remain.
\end{ally}
\vfill
\newpage

\noindent TIASAP stands for \emph{The Ill-Advised Self-Administration Period}.

This is why.

I was unsafe about it.

I lost my sexuality for years.

I turned the need for change into punishment.

The color drained from my universe. The flavor was gone from food. I could not smell.

\begin{ally}
And when you added in a bit of estrogen, you wept at the return of sensation.
\end{ally}
I tell myself now that if I belive something to be true when I'm depressed as well as when I'm hypomanic, it's more likely to be right.

And, well.

% XXX footnote color
Now I knew it was right.\footnote{\color[HTML]{dddddd}Page \pageref{gender:gender}}

But I was unsafe, I was punishing myself, and I did it all on purpose.

\begin{ally}
Why ruin your life on accident when you can do it on purpose?
\end{ally}
\newpage
\null
\thispagestyle{empty}
\newpage

\end{leftcolumn}
\end{paracol}
\resetbackgroundcolor
\renewcommand*{\footnoterule}{\oldfootnoterule}
