Back in 2011 and 2012, I started to really loathe being me.

\begin{quote}
`Started'?
\end{quote}

Well, okay, in a very specific way. I started hating the anger. I started hating the expectations. I starting hating the toxicity.

\begin{quote}
You started hating a lot more than that.
\end{quote}

I started hating my brain and my body. I started hating the coarseness of me. I started hating all my angles. I started hating my hair and my face and my genitals and my lies.

I was lying to JD. I was lying to work. I was lying to Tyson. I was lying to everyone who saw me online as a girl, and I was lying to everyone who saw me online as a boy. I was in a liminal place where I could tell no one the truth.

\begin{quote}
Not even yourself.
\end{quote}

Not yet, at least.

There were a few easy steps to take, of course. I saw a doctor who got me on meds.

\begin{quote}
Tell me about suicide.
\end{quote}

Not yet. Don't derail me for a bit. I need some breathing room after yesterday.

\begin{quote}
Tell me about Younes, then.
\end{quote}

I'm getting there.

I started taking my own meds alongside those the doctor gave me. I started the slow process of ridding myself of testosterone. I hated my body so much, I did my best to camp out up in my head, to remove at least one means of having to interact with it: sex.

\begin{quote}
Go back. Before that.
\end{quote}

Before that, I changed how I presented. I changed Makyo to be genderless. Started going by `it' pronouns. And I made Younes.

Younes was a means for me to no longer lie. Or at least knock the severity of the lies down a few notches.

Younes was like me. He looked like a guy, but had something decidedly feminine about him.

\begin{quote}
Don't be coy: he had a vagina.
\end{quote}

Well, yes, but he wasn't simply male in all his interactions. He was effeminate, without being flamey. He could be both more and less than a guy.

\begin{quote}
Let's talk about kink.
\end{quote}

Soon, soon.
