There's a few things that I did wrong, here.

\begin{quote}
Objectively?
\end{quote}

Yes. Or maybe, wrong by consensus. Wrong subjectively, and also wrong by the standards of many of those around me.

\begin{quote}
Did they feel wrong at the time?
\end{quote}

They felt shameful.

\begin{quote}
Is shame wrong?
\end{quote}

Not always. It can be an indicator, I suppose.

\begin{quote}
It's a tool. It's a tool to tell you when you're being vulnerable. In this case, vulnerable in your uncertainty.
\end{quote}

I suppose.

I handled this in a way that made me feel a lot of shame. I was uncertain about a lot.

\begin{quote}
If you had done so unabashedly, would that have made it any better?
\end{quote}

I don't know, honestly.

\begin{quote}
What were you uncertain about?
\end{quote}

I was uncertain about the approach. I was uncertain about the terminology. I was uncertain about how it made me feel. That last most of all, probably.

I approached Younes as a primarily sexual facet of myself. After all, what's the point of making a character with both a penis and a vagina, I thought, if there isn't going to be some aspect of sexuality to it?

\begin{quote}
There may be a great many points besides that.
\end{quote}

Yeah, I know that now. Uncertain, remember?

\begin{quote}
Always.
\end{quote}

So I made an altersex character that was primarily sexual in nature. that was the approach. And then I called him a `male-herm'.

\begin{quote}
Ouch.
\end{quote}

Yeah, ouch. The term does not fit so well these days. Some folks own it, and I'm happy for them, but even then, the term rankled. It took a lot of history and turned it, for a lot of folks, into a fetish. A lot of intersex folks are really unhappy with it being used. Ditto `futanari'.

It's understandable, too. Like, I've dealt with chasers. Folks who fetishize my gender, my presentation, my body.

\begin{quote}
It's understandable now.
\end{quote}

Yes. Uncertainty.

It made me feel almost right. It made me feel like I was on the edge of something. It made me feel just around the corner from a revelation. It made me doubt myself. It made me doubt my place in the world. It was both a symptom and the cause of my hatred for body.

\begin{quote}
For your body, or for yourself?
\end{quote}

Both, I suppose. It was a symptom of this growing unease, this feeling of being just a few millimeters to the left of myself. This feeling of being just slightly out of focus.

A rangefinder camera uses a ghostly yellow image overlaid atop the real image when you look through the viewfinder. When you turn the ring of the lens to focus, that ghost slowly shifts to align with the object you want to be in focus.

\begin{quote}
Your view of yourself was slowly slipping from focus. Matthew was starting to lose coherency.
\end{quote}

And Younes was one of the means of slowly dragging that back into focus.

It doesn't matter how right or wrong it was of me to use this tool. It does matter how wrong I was in the mechanics of the scenario.

\begin{quote}
You hid him. You covered him up and kept him from the world. You interacted with a completely different crowd, as Younes than you did as Makyo or Macchi. When that overlapped with Rikky, it was awkward.
\end{quote}

It was, and not because of the altersex part. We interacted that way with Makyo as altersex, too, amd that didn't feel awkward at all. It felt like cheating to engage with the world as Younes. It felt shameful.

\begin{quote}
The thing that you did wrong was to lie.
\end{quote}
