So, if we've talked about furry and we've talked about the dress and we've talked about dad and self-harm and the yellow couch, then what is there to talk about when it comes to gender?

\begin{quote}
Talk about what happened.
\end{quote}

Are those not things that happened?

\begin{quote}
They are things that happened before. They are precursors and doormats and signs. They all point to gender. Talk about gender. Talk about what happened.
\end{quote}

Alright.

I remember laying on the couch --- that awful, awful yellow couch --- and him getting playful, and then some little movement of his touched a nerve and I started crying because of the way that brushed up against that me that wasn't in focus. It brought it to the forefront the fact that I didn't align with myself, that there was a lag in my proprioception, that I was falling behind myself.

\begin{quote}
As you said.
\end{quote}

I remember scooting back up into a sitting position, facing JD, with us sitting by the picture window in the living room. I remember words coming out in a jumble. I remember leaning heavily on similes. I remember taking lots of breaks as though I was collecting my thoughts when really I was trying to talk without my voice going all gross with tears. That horrible, bubbly, trapped-in-my-chest sound that comes with trying to talk while crying.

I remember explaining to him that I'd been spending so much time online having different parts than I actually had, that it was super jarring to have it brought into focus that that was actually not the case. I tried to say how, feeling him aroused and pressing against me, pressing between my legs, it hurt on a very emotional level that he was pressing only against my perineum and not against a vulva.

\begin{quote}
Emotional isn't the right word there. It hurt on a visceral level. On a primitive level. It hurt in the sense that you had all of the reactions to pain except for the physical sensation of pain itself. There was the panic, the need to get away, to stop whatever was happening to cause that pain.
\end{quote}

I remember saying that I was having some complicated feelings about gender, but being largely unable to explain what they were.

They were things that I could feel and not say. They were as yet ineffable. They were liminal. They had yet to surface completely.

\begin{quote}
And they were frightening. Too frightening to say.
\end{quote}

Yes, had I the words, I would not have been able to say them out of fear. Fear that they might drive JD away, but also fear that they might be true, because if they were true, I was fucked.
