\label{gender:surgery}
\index{Gender!surgery|(}
\index{Writing!samples!poetry|(}
\null
\vfill
\begin{verse}[1.01\textwidth]
  Saturday is for mechanics.\\
  Sunday is for terror.\\
  Monday is for acceptance.\\
  Tuesday is for purging.\\
  Wednesday is for anxiety.\\
  Thursday is for sleep.
\end{verse}
\vfill

\newpage

\begin{verse}[1.01\textwidth]
  It is surprisingly hard to think something real\\
  when every indication, every word, all you feel\\
  tells you that that must not be the case.\\
  There's no easy way to make yourself face\\
  that which your emotions continually deny,\\
  no matter how true you know it to be.\\*
  \vinphantom{no matter how true you know it to be.} But why\\
  must all these contradictions claim events\\
  that mean the most to us? What prevents\\
  them from taking the unimportant? The small?\\
  Is the import just to big? Can we not fit all\\
  of the thing in our heads? Are we too weak?\\
  Is the life-changing too vast to explore, to seek\\
  out every corner?

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Have you considered that your constant seeking\\
  \vin may be the problem? That your anxieties leaking\\
  \vin all over may be what's preventing you\\
  \vin from recognizing what's actually true:\\
  \vin you can do things for yourself. It's allowed.}

  It also doesn't help that there were so many delays.\\
  The scheduler losing my application, and me counting days\\
  after those who consulted after me got their dates;\\
  The mishap of the letters, and me rushing past gates\\
  and their keepers; countless thoughts of countless regrets ---\\
  regrets which hadn't yet happened --- as mom frets\\
  that maybe I will wind up hating my new body.\\
  And why not? Why not fret? Surgery! How gaudy.\\
  I fight with myself enough over how this surgery\\
  is plastic, how I'm just doing something sugary\\
  to somehow make myself somewhat more appealing.\\
  How trite. How selfish. How lame. How revealing\\
  of my bottomless shallowness.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Your saving grace being, as always, dysphoria:\\
  \vin more than any cough or cold, more than your chorea,\\
  \vin it provided you with a problem. Something fixable.\\
  \vin It gave you a tangible solution to something integral\\
  \vin that plagued you.}

  That I had something I could concrete at which to point\\
  that would be fixed by this act, I could thus annoint\\
  it as somehow more worthy, something worth doing.\\
  If I could go through some process of ungluing,\\
  excise this thing from myself I might become whole\\
  in some way never before imagined.\\*
  \vinphantom{in some way never before imagined.} Ah, but the toll.\\
  There must always some arbitrary price to pay ---\\
  Self-actualization must never be free --- and hey,\\
  Everything in society must come with a reason.\\
  To come up with letters, proof, for that season\\
  of change must serve some sort of divine end.\\
  To wait eighteen long months, to refuse to bend\\
  to others' whims\ldots{}
  \newpage

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin You got your letters, you got your date, you did it.\\
  \vin You did your labor, you did your time. They let you fidget\\
  \vin and twist in the wind. Hell, they did it to you twice.\\
  \vin Your letters only good for one year, you had to ask nice\\
  \vin for a second set.}

  Yes.\\*
  \vinphantom{Yes. } To preempt your 'why', I followed my own advice:\\
  If I feel the same when I'm depressed as I do when I feel nice,\\
  It's a thing worth doing. Eighteen months is time enough\\
  to let at least two depressive cycles call my own bluff.\\
  When they did not, when I panicked at having to reapply\\
  and still pulled through in time, well, no need to justify\\
  my actions any further. That's when it all became real.\\
  That's when I was in. That's when I could tell just by feel\\
  that I was ready for this change. I wasn't \emph{ready} ready,\\
  but I was ready enough to come off as rock steady\\
  when I called the surgeon's office. I was visibly confident,\\
  even at the pre-operative appointments, totally cognizant\\
  that I didn't deserve this.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Whether or not you deserve this is not up for debate.\\
  \vin Not because you do or don't so much as because the hand fate\\
  \vin dealt you. You had the job, you had the insurance, the means.\\
  \vin You made the call. You took the step. You passed the screens.\\
  \vin \textbf{You} did this.}
\end{verse}
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
  When I am asleep\\
  The world changes around me.\\
  In spring, I am changed.
\end{verse}
\vfill
\newpage

\begin{verse}[1.01\textwidth]
  There are so many words that could be said\\
  about the preparation for surgery, all those steps that led\\
  to that six-thirty AM call. The days of purging.\\
  The anxiety. The drive. My husband's gentle urging.\\
  That night in the Airbnb. That last shower with the Hibiclens.\\
  All that has faded. It's distored at the edge of the lens\\
  of my memory.\\*
  \vinphantom{of my memory.} No, what remains is the two hours before:\\
  the being so scared that I was reduced to the barest core.\\
  There was nothing left of me but fear, not even a name.\\
  I could still drive --- the fear was quiet and tame ---\\
  I could get us to the ambulatory surgery waiting room.\\
  But beyond that, I was a non-person. Or convict: my doom\\
  was in their hands.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Non-person? Doom? Give yourself at least some credit.\\
  \vin You still had agency. You still had a choice, could have not let it\\
  \vin happen. You say of travel that getting you there is their job:\\
  \vin you felt the same here. You crossed the doorway and let this mob\\
  \vin of nurses do theirs.}

  And that's exactly what happened. I crossed that threshold,\\
  and then there I was: a patient before a team ready to handhold.\\
  At that point, I was no longer bearing all that weight.\\
  I was able to relax and let them guide me, a piece of freight\\
  working through a system. I even had a barcode to scan.\\
  Some gabapentin. My belongings in a bag. A rundown of the plan.\\
  An IV, and a second after the first missed. Meet the surgeon,\\
  then the anaesthesiologist.\\*
  \vinphantom{then the anaesthesiologist.} I felt myself then a virgin.\\
  I was at this point being prepared for some strange sacrifice,\\
  a process of pain and cutting, of rebirth. A cut, a slice,\\
  and I would become something more\ldots{}what? Mature? More complete?\\
  Where I'd never put stock in virginity before --- so obsolete ---\\
  it fits well, now.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin It's the penetration. It's the being opened up. The breach in tegument.\\
  \vin There is change implied in the loss of virginity. Something elegant,\\
  \vin something beyond just the physical. Maybe it's maturity,\\
  \vin maybe it's a coming of age, or even some strange aspect of purity.\\
  \vin It's a one-way change}

  That no-going-back-ness grew stronger and stronger,\\
  and the minutes just seemed to go longer and longer,\\
  as I got closer and closer to the fateful moment of change.\\
  I was laid on my back. I wwas wheeled to the OR. "How strange,"\\
  I thought. "That I'll never know where this room actually is.\\
  I'm wheeled here on my back, the surgeon does his biz,\\
  and I'll wake up in post-op." To this day, I have no idea.\\
  Did all of my friends go through this? Did Katt? Did Lutea?\\
  Were we all whisked away to some dreamside room\\
  where we would be changed? Some strange, perhaps-tomb?\\
  After all, this surgery, this procedue, none of this was riskless.\\
  Would this be where we died? Would we pass here, resistless,\\
  in the depths of anaesthesia?
  \newpage

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Was that really such a worry?\\*
  \vinphantom{\vin Was that really such a worry?} I mean, I suppose it had to have been.\\
  \vin You spent all that time polishing your will. How could you begin\\
  \vin to deny the death-thoughts inherent in a nine-hour surgery?\\
  \vin That you didn't still leaves you feeling like you're living a forgery\\
  \vin of a life.}

  But then I was in. I was in that room with surprisingly green walls.\\
  The nurses dropped me off, and from down those hidden halls\\
  came surgeon, anaesthesiologist, what seemed like dozens of people.\\
  "Here, hold this over your face," someone said as a needle\\
  wandered into my IV's injection port. "It's just oxygen."\\
  My hand began to slip. Oxygen? Some sort of intoxicant?\\
  They laughed, repeated, "No no, you have to hold it up."\\
  Perhaps it was O2, but whatever was injected began to interrupt\\
  any train of thought. The jazz music they'd put on, at my request,\\
  was overwhelmed by static. My vision followed. Silence: blessed.\\
  Speed: surprising. Is this death? A rush of nothing. Is this death?\\
  Nothing.\\*
  \vinphantom{Nothing.} Nothing. Is this death?\\*
  \vinphantom{Nothing. Nothing. Is it his death?} Is this death?
  Silence, static.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vinphantom{Nothing.} Was this death?\\*
  Nothing. \phantom{Was this death?} Nothing, death? \phantom{Nothing,} nothing.\\*
  \vspace{1em}
  \vinphantom{Nothing. Was this death? Nothing, death?} Nothing,\\
  \vinphantom{Death?} Was this death?\\*
  Death? \phantom{Was this death?} Nothing.\\*
  % \vinphantom{Death? Was this Death? Nothing. There was Nothing.} Death? Nothing.\\*
  \vspace{1em}
  \vinphantom{Death? Was this death? Nothing.} There was nothing.\\
  \vspace{2em}
  Silence.\\*
  \vspace{1em}
  \vinphantom{Silence.} Static.\\*
  \vspace{3em}
  \vinphantom{Silence. Static.} Nothing.\\*
  \vspace{4em}
  \vinphantom{Silence. Static. Nothing. Death.} Death.\\*
  \vspace{3em}
  \vinphantom{Silence. Static. Nothing.} Death.\\*
  \vspace{3em}
  \vinphantom{Silence. Static. Nothing. Death. Death.} Silence.\\*
  \vspace{2em}
  \vinphantom{Silence. Static. Nothing. Death. Death. Silence.} Death.\\
  \vinphantom{Static. Static.} Silence.\\*
  \vspace{2em}
  \vinphantom{Static.} Static.\\*
  \vspace{5em}
  Static. \phantom{Static. Silence.} Static.\\*  \vspace{10em}
  \vinphantom{Static. Static. Silence. Static.} Death, static.\\*
  \vspace{11em}
  \vinphantom{Static. Static. Silence. Static. Death, Static.} Death.\\
  \vfill
  And then you woke up.}
\end{verse}
\newpage

\begin{verse}[1.01\textwidth]
I'm no good at images, only words,\\
and yet for days after surgery,\\
as anesthesia and countless\\
\vin milligrams, milliliters, millions of\\
drugs leave my system,\\
I'm lousy with visions,\\
each lousy with meaning.

I lay in bed, unable to move,\\
struggling to keep my eyes open;\\
I know that if I close them,\\
\vin I'll be lost, I'll be lost, I'll be\\
mired in waking dreams,\\
coherent visions with all the logic\\
of that paler side of consciousness.

Perhaps the veil here\\
is still too thin and vague,\\
the pool too clear, the monsters too scary\\
\vin too lean, too mean, too hungry, or\\
perhaps I was too close to death\\
to come away totally unscathed,\\
too close to completely survive.

\newpage

\vin It's as though, laying here,\\
\vin stinking of hospital,\\
\vin I'm seeing emotions play out,\\
\vin \vin Scene after scene, scene after scene,\\
\vin anxiety shown in heaps of discarded entrails,\\
\vin hope in the ceaseless ratcheting of gears,\\
\vin determination in the marching of feet.

If I were an artist, perhaps\\
I could hope to touch these images,\\
but as it is, every word falls short,\\
\vin too vague, too inexact, too tight to\\
hope to explain something so vast\\
by the very act of attempting to reproduce;\\
I can only hint from the margins.

That poetry can accomplish what prose cannot\\
in its economy of motion\\
is attractive to me, here in recovery ---\\
\vin so tired, so tired, so tired --- so\\
maybe I can hope to express the dire import\\
of these visions dancing behind closed lids,\\
or at least remind myself on rereading.

\newpage

Even now, a week out,\\
I'm starting to lose touch with the visions,\\
I can almost touch them if I squint,\\
\vin lie real still, don't move now, but\\
even then, a shadow of the substance\ldots{}\\
I'm starting to consign to memory\\
that which was probably memory to begin with.
\end{verse}
\newpage

\begin{verse}[1.01\textwidth]
  And then I woke up, and I was in the post-op recovery room.\\
  Disoriented, loopy, giggly, not yet in pain --- a small boon.\\
  There was the nurse, and there was JD. How long had he been there?\\
  After some indeterminate time, I was wheeled\ldots{}somewhere.\\
  Yet more anonymous halls. Yet more competent nurses.\\
  Language was not yet wholly available to me, no verses\\
  yet to be had, despite the heady sensation of the opiate\\
  coursing through me; only giggles, however inappropriate,\\
  every time we went over a bump or up a ramp.\\
  And then I was in my room.\\*
  \vinphantom{And then I was in my room.} Me. A bed. My IV. A lamp.\\
  Square. Spacious. A bathroom I could not yet walk to.\\
  Hourly vitals. Friendly staff wandering through to talk to.\\
  And a button in my hand.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin That button, which you were instructed to press\\
  \vin every seven minutes. A morphine drip, or dilaudid, at a guess.\\
  \vin Every seven minutes, a bit of nightmare dripped into your veins.\\
  \vin Every seven minutes, more entrails, more gears, more chains\\
  \vin coursing through your mind.}

  There was pain, too, and the drip did indeed lessen that.\\
  Still, the pain grew less, and soon I switched meds to combat\\
  that ebbing tide. Tylenol. Hydrocodone. The button was removed.\\
  Pills. Pills. Every four hours: pills. I complain, but improved\\
  nonetheless. Antibiotics. Stool softeners. Painkillers.\\
  The nurses wandering in and out became my tillers:\\
  They steered my days, steered my pain, steered my diet.\\\newpage
  We talked. We laughed. We shared private jokes in the quiet\\
  of the night over BP cuffs. They helped with bedpan duty,\\
  thankless though it was. Another patient would cry, flutey,\\
  and they'd hurry off. I remember none of their names.\\
  Every now and then, when he made it down to Portland, James\\
  would visit, perhaps spend the night.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Your laptop unweildy, you spent most of your time on your phone.\\
  \vin Even when no one was there, you were never quite alone.\\
  \vin Hours on Taps. Hours on Telegram. Five long days on your back,\\
  \vin and you, a side sleeper! Anything and everything to distract\\
  \vin from that fact.}

  It wasn't all monotony. The surgeon came in to check on me.\\
  They removed my dressing, and then my packing, setting me free,\\
  stepwise, from confinement. The last day was the biggest of all:\\
  The packing, catheter, and drains were removed. I tried to crawl\\
  from bed, found myself on the verge of collapse. I showered\\
  and saw my body changed. They measured my urine. Nurses glowered\\
  at how little. They threatened to put the catheter back.\\
  Embarrassed, I defecated, then tried again. Now on track,\\
  I was finally discharged. It was then that I finally saw,\\
  from my wheelchair, the hitherto only hinted at hall\\
  outside my door. It was somehow still unreal to me.\\
  Or perhaps I was simply to eager to finally be free\\
  from the room.
  \newpage

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Undiluted sunlight while you waited on JD to get the car\\
  \vin hurt your eyes. You could still barely stand, afraid to jar\\
  \vin your new body in your dizziness. Almost more overwhelming\\
  \vin than the hours before the surgery was you helming\\
  \vin your dissociating self.}

  All the way to the B\&B, crossing that street, getting settled,\\
  I was nothing. I was not myself. I was soft, bepetaled.\\
  I was new. I was raw. Cliché, sure, but I was a flower\\
  newly sprouted. Under anaesthesia, I ceased to tower\\
  over the earth and instead became one with it. Or my dream\\
  finally became reality and I had become a tree, the theme\\
  of growth omnipresent within me. It was too much, too much.\\
  So I slept. I waited for Robin to join me, just to clutch\\
  at things familiar. Something to anchor past me to the present.\\
  I had become a tree, had grown, and sure, it was pleasant,\\
  but all the same, I still needed something to keep me grounded.\\
  I needed to not be completely unmoored, to not be unbounded.\\
  But it was done.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin It was done. It was complete. You'd started taking action,\\
  \vin and kept on taking steps until you were there, beyond abstraction.\\
  \vin This was concrete. This was real. This was true. \textbf{You} were true.\\
  \vin You weren't false before, but all the same, now that you were new,\\
  \vin you were more true now}
\end{verse}
\newpage

\null
\vfill
\begin{verse}[1.01\textwidth]
It is two hundred miles between what I expect and what I want.\\
Two hundred long strides that seem impassible from one direction,\\
\vin and from the other a day's short drive.

It is nine and a half hours between question and answer.\\
A half hour of jazz, nine hours of sleep, a scant second of perspective,\\
\vin and I can only traverse in one direction

It is eleven inches between who I was and who I am.\\
Ten of those inches are pain, the eleventh is numb,\\
\vin There's pleasure to be had in there, I'm promised.

It is twelve years between what I want and what I get:\\
Ten years of remembering who I will become, two years running,\\
\vin Eight days dreaming.
\end{verse}
\vfill
\newpage

\begin{verse}[1.01\textwidth]
  What can I say of healing? Of life after change?\\
  I got used to it, bit by bit. I slowly learned my range,\\
  the extent of my new body. Proprioception caught up immediately,\\
  and there were no phantom sensations, and the immediacy\\
  was startling at first, but I got used to it, to my new form.\\
  Over the next weeks and months, I slowly learned my new norm.\\
  I learned by regaining feeling. I learned with every muscular flex.\\
  I learned by dilating. I learned by masturbating. I learned by sex.\\
  While I refused to let my happiness hinge on such a thing,\\
  a part of me hoped it'd make me more comfortable get in the swing\\
  of sex, and while it helped, I still was still largely okay without.\\
  My body was still my own. Whole and entire. My life played out,\\
  and I became more myself.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin This isn't going how you pictured it, this bit of writing.\\
  \vin You were going to talk more about healing, about fighting\\
  \vin for permission to change, about your \$76,000 bill.\\
  \vin And here you talk of trees and growth. Did you not get your fill?\\
  \vin Do you still need this outlet?}

  Apparently.\\*
  \vinphantom{Apparently.} Apparently I still need to revel in the newness.\\
  Apparently, what I need out of this project isn't the trueness\\
  of the concrete. We should really have expected nothing less.\\
  This is a project to dig for truth, a project to confess.\\
  It is not a project for describing stitches stabbing me in the clit.\\
  It is not for telling about each successive dilator testing the fit\\
  of my new depths. Could I have gone into that? Yes. Perhaps.\\\newpage
  Perhaps I still will. Later. For now, I still need to run laps,\\
  to circle around some dark core and discern its edges.\\
  Perhaps if I know that shape, if I peek over enough hedges,\\
  I'll somehow know myself better. I don't know. It feels unlikely.\\
  Maybe there is no knowing the self. Still, I have to try, rightly\\
  or not.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin Fair enough. Still, at some point, discuss the concrete.\\
  \vin So many have asked you to, and perhaps you'd feel complete.\\
  \vin Perhaps that, too, would be of use to you. Not everything demands\\
  \vin such thorough introspection. Not everything fits in the wetlands\\
  \vin of your subconscious}

  Of course not. I know this. \emph{You} know I know this.\\
  I'm not deflecting, just focusing on this part of the abyss.\\
  The concrete aspects are for writing with clarity,\\
  not with verse. They're for writing with the sincerity\\
  borne of experience, so that perhaps others can benefit.\\
  Of this, only I need benefit. There is an etiquette\\
  to writing for others. Here, there is only an ally.\\
  This is for me and you. Your role is to hear my lie,\\
  to call it out, to force me to correct myself, my words.\\
  My role is to keep on writing, be it about surgery or birds,\\
  and to learn from our discussions. To learn? To suffer?\\
  Perhaps more the latter. To hurt, and grow tougher\\
  by hurting.
  \newpage

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin You have been called on that, yes, writing to suffer.\\
  \vin And it's not wrong. You sit at your laptop and fill the buffer\\
  \vin with sentences and lines and paragraphs of memories and pain.\\
  \vin Do you really grow tougher? Is it masochisim, or do you gain\\
  \vin real insight from this?}

  I think I do. It's therapeutic to try and understand myself better.\\
  is it not? With every paragraph and line and word and letter,\\
  I think I reduce the borders of that abyss. Or if not reduce,\\
  I spraypaint a red line five feet from them, so that I can deduce\\
  my roughest edges. I'm often say that it's easy to discern boundaries\\
  by crossing them. I've crossed them here, with you. Foundries\\
  of thought and emotion are within me, ceaselessly toiling.\\
  I want to tour them all. I want to see them boiling.\\
  I feel them. I house them. I smell them and taste them.\\
  I just also want to understand them. There's no chaste hem\\
  to the subconscious, so I have to map it, map these crude sources.\\
  Then I can experience thisness --- I hope --- when buffeted by forces\\
  internal.

  {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX]
  \vin If you say so, I suppose. Do you think it'll work, though?\\
  \vin Aren't such works unknowable by definition? They grow,\\
  \vin they wane. You can sense them by their effects and emissions,\\
  \vin but isn't seeing them, truly seeing, knowing their positions,\\
  \vin reserved for dreams?}
\end{verse}
\newpage

\begin{verse}[1.01\textwidth]
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
My mind\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
Nothing\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I am not who I was

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
My name\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
The word\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I am called who I am

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
My looks\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
The light\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I am seen as I am

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
My chemistry\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
The substance\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
My form is my own
\newpage

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
My body\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
The knife\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I am shaped how I am

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
Nothing\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
I was accepted\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I accepted myself

\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What have you changed?}\\
Everything\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What changed you?}\\
Everything\\
\vin {\fontspec{Merriweather Sans Italic}[Scale=0.9,Color=444444FF,Ligatures=TeX] What became of it?}\\
I became who I am
\end{verse}
\newpage

\null
\vfill
\begin{ally}
  Why verse?
\end{ally}
Surgery was, by far, the hardest thing I've ever done in my life.

\begin{ally}
  So?
\end{ally}
Why should this section then be easy to write?
\vfill
\index{Writing!samples!poetry|)}
\index{Gender!surgery|)}
\newpage
