% background: '#333a18'
% color: '#cdc'
% quote: '#efe'
Somewhere around 2014, a friend of mine went mad.

\begin{ally}
That's a bit dramatic, isn't it?
\end{ally}
I really don't know how else to put the sensation of someone's reality not meshing with yours. The closest I can come is the feeling of shock and betrayal that I felt the first (and only) time I experienced an earthquake.

\begin{ally}
Do you feel that your friend betrayed you?
\end{ally}
Not intentionally.

\begin{ally}
Can betrayal be anything but?
\end{ally}
Did the earth intend betray me? Almost certainly not. Is it even capable of such?

\begin{ally}
And yet you feel it did.
\end{ally}
I have trust issues.

\begin{ally}
Well, yes.
\end{ally}
I trust that some parts of the world around me are static, inert. Or that they move so slowly as to be indistinguishable from such. That's balanced by just how much everything else moves.

This static thing suddenly became something else. A gentle side-to-side motion became a more rapid wobble, lasting perhaps ten to fifteen seconds before fading quickly to stillness once more. In that time, I'd leaped from bed and dashed into the hallway, confused. I was just in the process of calling the dogs when it stopped.

JD simply mumbled "Earthy-quake?" and fell back asleep.

Three minutes later came a small aftershock, lasting no more than five seconds.

\begin{ally}
You raced to post it on Twitter, Mastodon, and Telegram, and fill out the I-Felt-It report like a good little Millennial.
\end{ally}
I have a type. I'll own that.

Getting that call in 2014, hearing those words that spoke of a different reality. It was an earthquake.

And\ldots{}

\newpage

% background: '#333a18'
% color: '#cdc'
% quote: '#efe'

Somewhere around 2018, a friend of mine went mad.

\begin{ally}
Same one?
\end{ally}
Same one.

\begin{ally}
Let's talk about mania.
\end{ally}
Let's talk about \emph{my} mania.

\begin{ally}
How long are your cycles?
\end{ally}
Three to five months.

\begin{quotation}
    It was toward the tail end of high school that I began to get plagued with depression and mood swings.

I was a healthy collie. All the romance of a noble lineage had gone to my parents' heads, and there was simply no reason one of my standing should ever feel bad. Sure, the family had come on hard times financially, and Idaho had been an inexpensive refuge for us. Flyover state or no, we could keep our large house and happy lives. How could any dog be sad?

And yet I was. I was in spades. I would swing down for a few months, life slowly losing its color, until I'd feel nothing except an ache behind my sternum, eating only mechanically, and only when reminded.

Then it would pass. It would be dinner and I'd realize that I was actually \emph{really} enjoying the curried chicken. I'd realize that it had been days since I'd thought about falling asleep and not waking up. I'd have energy.

I'd have a bit too much energy.

Mom would shrug and mumble something about boys. "Men in this family, always so moody. You'll grow out of it."

I mostly kept it to myself. When I did share it with friends online, it was to commiserate in the "Parents, eh? What do they know?" style that never goes out of fashion among teenagers.

Still, as awful as it was, I learned the rhythm of it. I'd spend a month or so feeling terrible, three months feeling pretty good, and then a month feeling great.

Not just great, \emph{better} than great.

I'd spend all of my allowance in a week. I'd sleep three, four hours a night. I'd write page after page of backstory for my role-playing characters. I'd scribble ideas as fast as they came to me and still not be fast enough.

I still have a folder of those ideas. They're illegible, unnerving.

And then, over the course of a week at most, I'd be back underwater once more.

Depression is a strange thing.

I tried at several points to capture some sense of it in words, but nothing ever quite fit. Whenever I did, I found myself using a lot of ellipses just to fill in, textually, my fumbling for words with enough meaning. I came up with stuff like, "I dunno. My brain just isn't all me. Like\ldots{}It's something else. It's there and exerts influence on me life, but it spends an inordinate about of time trying to destroy me."

Or poetry. I tried to throw that at depression, too, but it just came out sounding stilted and weird. I'd wind up talking about fire a lot. Fire and birds, for some reason.

Which was nonsense, really, but each in such a way that seemed to cover at least one small corner of depression.

Depression is big. It's vast and terrible and empty. Completely empty, and there you are, in the middle of it, feeling bad about nothing.

There's just no sense to it. No sense in trying to describe nothing. A ‘nothing' which is also nonsensical.

And yet I keep trying.

All these words\ldots{}
\end{quotation}

\begin{ally}
Which came first, the lilac-scented words on bipolar disorder, or the furry fiction?
\end{ally}
Does it matter?

\begin{ally}
I suppose not, but humor me.
\end{ally}
The bit about words first. Then the bit about the dog.

\begin{ally}
Let's talk about mania.
\end{ally}
Again, hypomania. That's usually what I wind up in.

\begin{ally}
Let's talk about mania.
\end{ally}
Okay.

\newpage

% background: "#283a26"
% color: '#cdc'
% quote: '#efe'

On two occasions, the world has slid away from me.

\begin{ally}
What does madness feel like from within?
\end{ally}
Oh, not madness. PNESes.

\begin{ally}
Lewd.
\end{ally}
I wince every time I say or type it. Even spelling it out still sounds crass.

\begin{ally}
Let's talk about mania.
\end{ally}
I'm working up to it.

On two occasions, the world has slid away from me. My perception shrinks. Tunnel vision, yes, but just all of perception. My ears fill with static. My skin becomes fantastically sensitive. My vision narrows to the size of a quarter held at arm's length.

My muscles stopped working.

I fell.

\begin{ally}
JD thought it was the alcohol at first.
\end{ally}
Was it not? I was drunk.

\begin{ally}
It may have been, and yet you collapsed in the bathroom months later. You were wedged between the wall, the toilet, and the bathtub. You shook and shook and shook.
\end{ally}
JD came home and held me while I shook. I was sober, and it happened again. I sobbed and said that over and over again. I was sober and it happened again.

I'm sorry for coming at this sideways. You're good at taking this in different directions than intended.

\begin{ally}
You're good at taking this in different directions than intended.
\end{ally}
Great.

\begin{ally}
I'm glad you showed the fortitude to tell me no, though.
\end{ally}
Careful, lady. Pride's a sin.

Having experienced it from the outside, and having experienced the world sliding away from beneath me, there is some similarity between the two.

And\ldots{}

\newpage

% background: "#082a16"
% color: '#bcb'
% quote: '#ded'

Let's talk about mania.

\begin{ally}
Finally.
\end{ally}
There's this rush.

This wild-nights-wild-nights rush.

There's this lack of foresight.

There's this thinking of the goal instead of the path.

There's this tinny scent to the air. There's this burning, burning sensation, burning. There's this pleasant static.

And\ldots{}

\newpage

% background: "#082010"
% color: '#aba'
% quote: '#cdc'

\begin{ally}
And?
\end{ally}
And were I to catch fire, the flames would feel like silk against my skin, against freshly-shaven skin.

\begin{ally}
And?
\end{ally}
And I feel like, were I to draw a blade along my limbs, to trace each long bone, each carpal, each tarsal, it would feel like ice, and the blood that came with would be my semen, and I would give birth to whole worlds through my flesh.

\begin{ally}
And?
\end{ally}
And if I stop, I'll surely die.

\begin{ally}
And?
\end{ally}
\newpage

% background: "#001a06"
% color: '#aba'
% quote: '#cdc'

I'm hypomanic now.

\begin{ally}
You're hypomanic now.
\end{ally}
It's not because of this.

\begin{ally}
It's not because of me.
\end{ally}
This is part of hypomania, but this is not because of it.

\begin{ally}
I am part of hypomania, but I am not because of it.
\end{ally}
I'm sorry.

\begin{ally}
I'm sorry.
\end{ally}
Let's go back, please.
\newpage
