\label{jay}
\renewcommand*{\footnoterule}{%
  \kern-3pt%
  \color[HTML]{222288}\hrule width 0.4\columnwidth
  \kern2.6pt}
\fontspec{Gentium Book Basic}[Color=222288FF,Ligatures=TeX]
\renewfontfamily\allyFont{Merriweather Sans}[Scale=0.9,Color=4444AAFF,Ligatures=TeX]
\noindent Mom and Jay got married when I was in elementary school. Fourth grade, maybe? It's a bit hazy.

\begin{ally}
Life began in high school, remember?
\end{ally}
Life began when I came out, I suppose. Or maybe when I ran away. Life began when I started to assert ownership over it.

\begin{ally}
Who owned it before?
\end{ally}
I thought my dad did. My dad and Jay, and they let my mom borrow me.

\begin{ally}
What did you own.
\end{ally}
Many gifts. A few hobbies. Later, an internet connection.
\newpage

\noindent Jay was a photographer. An artist. A true, honest, dyed-in-the-wool artist.

\begin{ally}
You looked up to him. Part of you wanted to be him. He could run a photography business funded by his day job of being a newspaper photographer. You thought of him when you changed your major to music.
\end{ally}
Did I? I was terrified of him.

\begin{ally}
Are they so different? `Awe', as a word, is not always a positive one.
\end{ally}
He took a picture of his son from a prior marriage that I still remember. Zach was shirtless, covered in mud that had started to dry and crack. He was looking down and to the left. He was holding something\ldots{}a sunflower, maybe? He had ram horns. The colors were muted\ldots{}was it black and white? Or was it just the mud?

I think I wanted to be that. Not Zach, necessarily. but I wanted to be that picture. I wanted to be a son that was loved like that. I wanted to be something as magical as that felt.

\begin{ally}
You also wanted to be the Phantom from Phantom of the Opera. Raoul was the bad guy, and you danced with your `Christine', Sarah Trowbridge, after school in front of your parents on the balance beam.
\end{ally}
I desperately craved being an artist. I drew endlessly. I played the saxophone, and sometimes I even liked it. I wrote music. My first song in third or fourth grade.

Maybe I did look up to him. He pulled it off.

\begin{ally}
Until he didn't.
\end{ally}
Right. When my mom told me to get in touch with him a decade and a half after the divorce, he owned a feed store down the block from me.

He left The Rocky Mountain News as lead photographer or something to pursue a job in 3D art. He bought Bryce 3D. He brought Lightwave. He spent a year learning Lightwave, and when the next version came out, he bought that and said it would take time to learn.

By that point, mom had been supporting all of us --- herself, him, me, my step-brother and two step-sisters --- for a year. She confided in me later that she had lost half a million dollars by the end of the relationship.

I didn't remember that folly. I majored in music and thought, ``Ah, yes, I can get a job doing library music or teaching choir while I work on my compositions'' but forgot how lucky he was when I met him.

\begin{ally}
You remembered and raced to teach yourself programming.
\end{ally}
\emph{You} remembered, maybe. I'd like to think of myself as a bit of a dreamer, even still.

\begin{ally}
Thus you, 1:19 AM on a Tuesday, gritting your teeth and trying not to write about mania.
\end{ally}
\newpage

\noindent Our punishment --- my step-siblings and I --- was time-out. Jay had an old church pew rescued from some church in New Mexico that he'd painted a grayish sky blue. ``Go sit on the bench,'' he'd tell us. ``Half an hour.''

\begin{ally}
You measured it with your fingers. You'd judge the width of the plank you sat on by pinching it. Three inches? Four? You'd lay your length on it and count how many Matts it took from one end to another.
\end{ally}
It was a perfect punishment. My dad lamented once that he couldn't send me to my room as a punishment because I'd happily sit in there for hours on end.

\begin{ally}
You'd be away from him. That's a reward.
\end{ally}
I hadn't thought of it that way.

The bench, though, was perfect. It faced a dining table,\footnote{\color[HTML]{222288}A dream: \emph{I am moving through the house, and suddenly a flood of brightly colored scorpions starts to pile in through the doors and windows. They're bright and plastic like Creepy Crawlers, but I know they'll be deadly. I have to hide under the dining room table. There is a flash, and then I'm riding on the table like a raft, but I have to be careful, as it is as if it's on a fulcrum and if I row or punt too hard, it will flip over, burying me in scorpions.}} and across from that, the computer which was kept powered off. No reading. No talking. No moving from the bench. If more than one of us were in trouble at the same time, no looking at each other; we sat on opposite ends.

When he started taking up martial arts, he brought Zach and I with him. He thought\ldots{}well, I don't know what he thought. That it would make us men? That it would teach us to defend ourselves?

In the end, it turned into its own means of punishment. He'd grapple with us. He'd grab me by the front of my shirt and slam me into the cabinets. It was just play, right? Just studying up for the next session, right?

\begin{ally}
Maybe he wanted to hit you from the start. Maybe that's why he got into karate.
\end{ally}
I think part of him did, yeah. I think part of him would rather our punishments would make him feel better at the same time. It took me a while to think of it that way, though. It took me a while to think of it as abuse.

\begin{ally}
It took you no longer being afraid of him. It took you telling your mom that, no, you wouldn't go see him at his feed store in Loveland. It took you until then to think of it as anything other than you not being man enough.
\end{ally}
I'm still afraid of him. Maybe it just took me admitting that.
\newpage

\noindent When I came out, I did so by leaving a book of stories from gay youth on top of my mom's reading pile right before taking the bus down to visit my dad for the night. She called me after dinner and asked me if the book meant what she thought it did.

\begin{ally}
Did you ever tell --- really tell, with words and everything --- any of your family you were gay? Or trans?
\end{ally}
Twice. It was awful.

She must have told him at some point. Within a week, he told my mom I had to tell Zach that I was gay, too. He left the house on a run and made my mom stand in the kitchen with me to make me say, ``Zach, I'm gay.''

He just said, ``Oh, okay'', and kept pouring his Kix.

\begin{ally}
And then he stopped talking to you.
\end{ally}
Beside the point.

After I came out, Jay changed. He got mean--

\begin{ally}
``Got'', she says.
\end{ally}
Do you fear him, then?

\begin{ally}
Mu.
\end{ally}
Fair enough.

He got mean. That's when he got physical. That's when his anger got hot.

He started reading my emails. He found some reply notifications to some posts on a forum, where kids were talking about puberty. As kids do, there was some dick-size comparing. He read that aloud in front of my mom and mocked me for my answer. I had said seven inches. It was generous, sure, but keep in mind, I was way underweight at the time--

\begin{ally}
And him rather overweight.
\end{ally}
--and the skinnier you are, the less padding you have around the base of your penis.

\begin{ally}
We're getting off topic.
\end{ally}
Are we? I was starting to own my body. I was starting to find things that I felt I could feel proud about. I was starting to form relationships. Puberty was in full swing and I was realizing that there were people my age like me who would find me attractive.

And he took that and he humiliated me for it.

\begin{ally}
Let's talk about kink.
\end{ally}
Let's fucking not.
\newpage

\noindent My mom and I got in the habit of going to the dog part after work. We'd pick up Hank, our golden lad, and Chelsea, our Phyllis-Diller-slash-Yoda mutt, and drive across town to a field dedicated to letting dogs frolic with each other.

We'd play with other dogs. We'd through tennis ball after slobbery tennis ball. We got to know the other owners, mostly as ``oh, you're Sandy's owner''.

\begin{ally}
Or ``oh, you're Zephyr's owner''. You stole your own dog's name from some random aussie shepherd at the dog park.
\end{ally}
It was a meaningful period of my life. Is there some reason that wouldn't make a big impact on me?

\begin{ally}
It was Zephyr or Samuel. Even you knew what you wanted. You had him already named in your mind.
\end{ally}
And mom and I would talk. We'd walk the perimeter or, on hot days, sit at the lone picnic table under the lone tree and talk.

I was sitting on the table itself, feet on the bench, and she was sitting next to me, when she said, ``I think I'm going to get divorced from Jay. Is it alright if I use his reaction to you coming out as the reason?''

\begin{ally}
And you thought, ``I must be the luckiest boy in the world, being able to say that I knew my parents' divorce was your fault.''
\end{ally}
She told me how much money she had lost, and how he had changed even before I came out. I think that's when I realized that she might be a friend as well as a mother.

\begin{ally}
Gag.
\end{ally}
I know. I tried typing that eight different ways, and no matter what, it sounds like a Care Bears thing or whatever.

\begin{ally}
Back to the lilac-scented word, please.
\end{ally}
Gladly.
\newpage

\noindent Between when the divorce was decided and when we were supposed to move out to the townhouse my mom had purchased, mom adopted a dog. Helen had clearly been feral rather than a surrender, because she was impossible. She didn't know how to act around dogs. She didn't know how to act around people. She didn't know how to act indoors. She didn't know how to act outside.

\begin{ally}
She didn't know how to act around you, so you hid from her.
\end{ally}
She didn't know how to act around Jay, either, to be fair. One night, three days before we were supposed to move out, mom was sleeping on the couch downstairs, and Jay came down from the master bedroom to have the last word in one argument or another, and Helen raced up to greet him, nailing him right in the nuts with her paw.

Do you laugh?

\begin{ally}
Not my department.
\end{ally}
It took my mom and I a while to laugh about that. It's the type of story that usually gets a laugh, right? Nut-shots?

\begin{ally}
Hollywood decrees it must be so.
\end{ally}
Maybe my mom smiled when she woke me to tell me we had to move out immediately. It was Sunday. We moved all we could to the townhouse in my mom's Honda Civic and slept on newly-purchased air mattresses. Mine kept going flat.

\begin{ally}
Your mom would soon learn that she had rheumatoid arthritis. You complained to her about that in the morning, and she stayed quiet about how much pain she must have been in.
\end{ally}
The next day at school was nigh intolerable.

\begin{ally}
And yet you felt free.
\end{ally}
And yet I felt free.
\newpage
\renewcommand*{\footnoterule}{\oldfootnoterule}
