\noindent A friend asked Maddy: what is the importance of tension?

Maddy said: I don't know

The friend looked sad and went away.

When the friend came back, they asked: what is the importance of tension?

Maddy said: I know-

But the friend cut her off angrily and left in a huff.

Later, the friend asked Maddy: what is the importance of tension?

Maddy said: I know: I don't know

Then they sat and chatted over a cup of tea.
\newpage

\noindent A friend asked Maddy: why do you drink tea?

Maddy said: I like it. It's tasty, it makes me feel good.

The friend said: well that's dumb.

Maddy went and drank tea.

The friend asked: why do you drink tea?

Maddy said: I don't know.

The friend said: well that's dumb.

Maddy went and drank tea.

The friend asked: why do you drink tea?

Maddy said: I like it. It's tasty, it makes me feel good.

The friend laughed and clapped delightedly, and said: perfect

Then sat to drink tea with Maddy.
\newpage

\noindent A friend asked Maddy: why are you coating yourself with grease?

Maddy said: so that when I run through a field, no dirt will stick to me, and I won't get poked by thorns.

Maddy ran through the field, and wound up covered in dirt and scratches.

The friend said: better to not run.
\newpage

Maddy built a sand castle and it was washed away.

The first friend was sad about the sand castle for Maddy, and said: better to not build the sand castle and risk further sorrow.

The second friend said this was good, because Maddy saw adversity and built the castle anyway.

The third said this was good because Maddy was able to acknowledge the castle and let it pass.

A fourth said: better to have never built the castle. The sand is itself, the wave is itself, and Maddy remains.

The fifth was helping build a bigger, better sand castle.
\newpage

\noindent A friend asked Maddy: why are you nailing boards together?

Maddy said: I'm building a house to live in.

When the friend came back later, there was an awkward jumble of sticks nailed together on the ground. They said: well that was dumb.

Some time later, the friend visited Maddy and asked: why are you frowning?

Maddy said: I paid someone to build me a house, but it's round, upside down, and a mile to the east of where it should be.

The friend shrugged and said: well that was dumb

Some time later, the friend visited Maddy and found her reading on the front porch of a cozy home. They said: did you build this?

Maddy said: no, but I did my part.

The friend laughed and sat down next to Maddy to read with her.
\newpage

\begin{ally}
Are you having fun?
\end{ally}
Yes.

\begin{ally}
You know that I'm not the friend, right?
\end{ally}
I do.

\begin{ally}
Carry on.
\end{ally}
No, I'm finished for now.
\newpage
