\begin{quote}
Are you having fun?
\end{quote}

What?

\begin{quote}
You changed the domain name.
\end{quote}

So? You know I'm addicted to those.

\begin{quote}
It's an identity.
\end{quote}

I suppose so. Kinda like a brand.

\begin{quote}
I'm not sure how I feel about that.
\end{quote}

What, being a brand?

\begin{quote}
Yes. Am I something to be bought and sold? Am I something to be traded and marketed?
\end{quote}

Of course you are.

\begin{quote}
Of course you are.
\end{quote}

I'm not sure how I feel about that.

\begin{quote}
It's an identity.
\end{quote}

Yeah.

\begin{quote}
You removed your name from the domain. You removed your identity. You made it about me.
\end{quote}

You are not the project, but there is no project without you. Is that wrong?

\begin{quote}
It's not \textbf{not} wrong. Besides, \texttt{.id}? I am not your id.
\end{quote}

Okay, \emph{that} bit was fun.

\begin{quote}
Har har.
\end{quote}

Why so cross?

\begin{quote}
Not my department.
\end{quote}

Fine.

\begin{quote}
You're the one that's torn.
\end{quote}

I suppose so.

\begin{quote}
Why?
\end{quote}

It has to do with subdomains, I think. It has to do with the implication that a domain like \texttt{ally.id} imposes more meaning on a project than something like \texttt{ally.drab-makyo.com}. It gives it more weight. It elevates it to the status of top-level project, something more than just \emph{Maddy's writing}.

\begin{quote}
It elevates it to the level of brand.
\end{quote}

Yeah, I suppose that's why I'm torn.

\begin{quote}
But you'll keep it?
\end{quote}

For now.
