How did I get here?

\begin{quote}
Start from the beginning.
\end{quote}

Which beginning?

\begin{quote}
Madison's beginning. For this, I don't think you need to go any further back for any reason other than to confirm what you already know. Or perhaps just a bit before. Start with the insurance company.
\end{quote}

What, working with Kevin?

\begin{quote}
Yes. Start from there.
\end{quote}

In 2011, I graduated --- or, well, left --- university and jumped straight into a job doing software for a subsidiary of a subsidiary of a company that made software for health insurance companies. I had a whole weekend off.

It was thrilling, in a away, to be seen as competent at something. It was nice to be able to drive to an office, sit down at a computer, type away for a few hours, drive home, and then see money in my bank account after the fact, knowing that I had done something that was useful.

\begin{quote}
Were you not doing anything useful before? You were working, you were at school. You were getting paid.
\end{quote}

I was. But even when I looked at that money in my bank account, I couldn't then count it out and say, ``Ah, yes, this was earned creating something.'' Work was spent living on the edge of failure, trying to push it back just one step further. That's the curse of IT.

\begin{quote}
And school? You were creating something there.
\end{quote}

And paying a pretty penny for the privilege to do so.

\begin{quote}
Right.
\end{quote}

But this was something new, I was given a list of things that they wanted to be able to do and given basically total freedom to pull that off. I was put in front of their raw materials and, when I showed them progressively more and more refined creations, they all stood back and applauded, and I could bow and say that I had created something for them.

\begin{quote}
And then?
\end{quote}

And then\ldots{}well, I don't know. And then the tasks got smaller and smaller, and the clients grumpier and grumpier about more and more inconsequential things. They needed twice as many new features done in half the time and could we work the weekends?

At some point that must have changed, but it all changed so gradually as to not be noticeable.

\begin{quote}
And then you started to see how capitalism worked, perhaps? That you weren't doing this because it was fun or because you were good at it, even if it was and you might have been, but because you had to.
\end{quote}

I think that may be getting a bit ahead of the game, but in a way, I suppose so. I started to see that it was very easy to use up all of one's spell slots. I started to see just what purpose free time had in one's life. I started to talk about work-life balance and to schedule vacation time that wasn't simply holidays and to dream about the office.
