\begin{quote}
At what point would you say you burned out?
\end{quote}

That's one of those surprisingly difficult questions. I can't point to a day or week when things went bad, nor even a month. At some point, I just looked around me, at my office and my coworkers and my job and said, ``I hate all of this.''

I spent a lot of time trying to fix it. I spent a lot of time changing little bits about my day or my desk or my tasks, and there was just not much that could put a dent into that mixture of loathing and anxiety that surrounded my day.

\begin{quote}
And eventually, you just dumped the whole thing in favor of something else.
\end{quote}

Yes.

\begin{quote}
Did it work?
\end{quote}

Oh, definitely. I jumped at the opportunity to stop working for an insurance company that just happened to need some software and to start working for a software company with a name that folks knew making products that I believed in.

Moving to Canonical came on such a whim, too. I met up with John Wright --- such a nice man --- at Mayor of Old Town and we talked over pints about the good and the bad of our respective jobs.

``I've been thinking about applying at Canonical,'' he said, twisting his glass between his hands. ``I'm not unhappy at where I am, I'm just\ldots{}not happy either.''

I nodded, and made silent note to check out their postings later that night.

\begin{quote}
Did you wind up stealing John's idea?
\end{quote}

Oh, totally. I apologized to him after the fact, too, for taking his idea and actually winding up with the job. He laughed and said that he didn't think he'd be able to work from home anyway.

\begin{quote}
Whereas that saved you.
\end{quote}

Yes.

In a way.

For a while.
