I could very easily get into talking about the ins and outs of working at Canonical and in software, but I don't think that's the point.

\begin{quote}
No, it's not.
\end{quote}

No.~The point is that, slowly, quietly, without me even noticing, I started hating what I do for a living. It snuck up on me once more. I once more found myself in a paralyzing mixture of anxiety and dread and anger. Every minute spent in front of my editor was spent filled with anger and frustration at not being able to work, and every minute spent away from it was spent dreading the next time I'd have to go back, fretting over how little I had gotten done.

I spent day after day on branches that should have been small and yet somehow, inexplicably, seemed insurmountable. Coworkers and bosses got upset at me. I did all I could to keep interested and invested in the company.

\begin{quote}
Even as you drifted your separate ways? Canonical stopped doing things that were relevant to you before you even moved to Seattle. They started focusing on things you didn't believe in. They laid off dozens of your coworkers. They started courting Microsoft.
\end{quote}

Sure, I suppose. There's no doubt that Canonical was changing. They were certainly not blameless in me losing my interest and investment in them.

\begin{quote}
And from what JC says, you would hate them now.
\end{quote}

I would, yes.

\begin{quote}
And yet here you speak only of yourself. Only of your failures.
\end{quote}

Is this not a selfish project? I think that it's fair to just talk about how I feel when I talk about burnout.

\begin{quote}
Burnout does not happen in a vacuum.
\end{quote}

I hardly believe that the things that Canonical was doing were so new as to be causing my burnout. They were doing as tech companies do. They were doing everything they could to maintain the same amount of velocity they had at the beginnings of projects later on. They were trying to change with the times while remaining exactly the same.

Perhaps it was just the honeymoon period finally coming to an end.
