Matthew was pretty keen on Perl at the start. Something about all the delicious punctuation, all the built-in obfuscation was appealing. Something about how you could write an incantastion that was difficult to read unless you had the proper knowledge tickled him.

\begin{quote}
He wasn't very good at it.
\end{quote}

Well, no. He was pretty terrible at it. He uploaded some samples to Perl Monks and mostly got yelled at. From then on, he developed alone, with little to no communication about what he was doing with anyone who might be able to help.

\begin{quote}
A solipsistic software engineer? Color me surprised.
\end{quote}

Right.

Perl filled high school. Dumb scripts to walk a directory (despite a module already existing in CPAN). A guestbook. A forum. A terrible website.

\begin{quote}
Was it that bad?
\end{quote}

\href{https://web.archive.org/web/20050202100148/http://ranna.babylonia.flatirons.org/}{RF!P}? Oh yes.

\begin{quote}
At least you can see the dull adherence to monochromatic web design started early on.
\end{quote}

Listen. Color is hard.

Either way. There was a brief PHP phase toward the end of high school, and then it was off to university and John Wright teaching him about Python and Django, and he was lost.

It made it so easy to start projects.

\begin{quote}
Too easy.
\end{quote}

Yes. They littered his computer, his \href{https://github.com/makyo-old/}{git repositories}. Started and abandoned, sometimes even before any code was written. There exist more than one project which is simply a skeleton of a Django application with a name. No code. No documents. No info.

\begin{quote}
No motivation.
\end{quote}

Or maybe only the false motivation that comes along with hypomania.
