At some point in late 2005, I got my first job in computers--

\begin{quote}
Well, hold on. What about that summer job at Rational?
\end{quote}

That was before birth, remember. That happened to someone else. That happened somewhere else.

\begin{quote}
You have nothing to say about your mom getting you a job testing software with one of her friends? You have nothing to say about learning the boredom of menial tasks? You have nothing to say about the time you found a rendering bug in Java, some part of the windowing system, but you couldn't file it because the bug was that characters from the PuTTY screen showing your MUCK connection showed through, scattershot? You have nothing to say about bagel mornings, about the breakfast burritos you still think about, about stopping at the hot dog cart on the way home and getting to know Mikey, who sold them, about the countless jokes you shared about how awful ketchup was on a hot dog?
\end{quote}

Clearly you do.

\begin{quote}
You thought it was great at first. No restaurant work for your first job, but something in computers. Something you could be proud of. That pride your dad taught you. Then you learned about what goes into a QA tester's job. Then you learned about how boring computers could actually be. Then you learned how to resent them for how much of a mistake they were in the first place.
\end{quote}

Bit harsh, but true enough.

\begin{quote}
``Computers were a mistake'', right? That's how you put it?
\end{quote}

Yes.

\begin{quote}
So you got your first job in computers shortly after you were born --- don't try to tell me it wasn't. It was the summer after your Freshman year. Your metaphor won't always hold up.
\end{quote}

\ldots{}Ah. Right.

\begin{quote}
And then you never got a summer job again until university. You kept looking, but there was little for you to do that would hold your interest if computers were so spoiled for you. You applied at coffee shops. You applied at Blockbuster. You applied at the YMCA.
\end{quote}

And every summer, I disappointed my mom further.
