Somewhere around 2018, a friend of mine went mad.

\begin{quote}
Same one?
\end{quote}

Same one.

\begin{quote}
Let's talk about mania.
\end{quote}

Let's talk about \emph{my} mania.

\begin{quote}
How long are your cycles?
\end{quote}

Three to five months.

It was toward the tail end of high school that I began to get plagued with depression and mood swings.

I was a healthy collie. All the romance of a noble lineage had gone to my parents' heads, and there was simply no reason one of my standing should ever feel bad. Sure, the family had come on hard times financially, and Idaho had been an inexpensive refuge for us. Flyover state or no, we could keep our large house and happy lives. How could any dog be sad?

And yet I was. I was in spades. I would swing down for a few months, life slowly losing its color, until I'd feel nothing except an ache behind my sternum, eating only mechanically, and only when reminded.

Then it would pass. It would be dinner and I'd realize that I was actually really enjoying the curried chicken. I'd realize that it had been days since I'd thought about falling asleep and not waking up. I'd have energy.

I'd have a bit too much energy.

Mom would shrug and mumble something about boys. ``Men in this family, always so moody. You'll grow out of it.''

I mostly kept it to myself. When I did share it with friends online, it was to commiserate in the ``Parents, eh? What do they know?'' style that never goes out of fashion among teenagers.

Still, as awful as it was, I learned the rhythm of it. I'd spend a month or so feeling terrible, three months feeling pretty good, and then a month feeling great.

Not just great, better than great.

I'd spend all of my allowance in a week. I'd sleep three, four hours a night. I'd write page after page of backstory for my role-playing characters. I'd scribble ideas as fast as they came to me and still not be fast enough.

I still have a folder of those ideas. They're illegible, unnerving.

And then, over the course of a week at most, I'd be back underwater once more.

Depression is a strange thing.

I tried at several points to capture some sense of it in words, but nothing ever quite fit. Whenever I did, I found myself using a lot of ellipses just to fill in, textually, my fumbling for words with enough meaning. I came up with stuff like, ``I dunno. My brain just isn't all me. Like\ldots{}It's something else. It's there and exerts influence on me life, but it spends an inordinate about of time trying to destroy me.''

Or poetry. I tried to throw that at depression, too, but it just came out sounding stilted and weird. I'd wind up talking about fire a lot. Fire and birds, for some reason.

Which was nonsense, really, but each in such a way that seemed to cover at least one small corner of depression.

Depression is big. It's vast and terrible and empty. Completely empty, and there you are, in the middle of it, feeling bad about nothing.

There's just no sense to it. No sense in trying to describe nothing. A `nothing' which is also nonsensical.

And yet I keep trying.

All these words\ldots{}

\begin{quote}
Which came first, the lilac-scented words on bipolar disorder, or the furry fiction?
\end{quote}

Does it matter?

\begin{quote}
I suppose not, but humor me.
\end{quote}

The bit about words first. Then the bit about the dog.

\begin{quote}
Let's talk about mania.
\end{quote}

Again, hypomania. That's usually what I wind up in.

\begin{quote}
Let's talk about mania.
\end{quote}

Okay.
