On two occasions, the world has slid away from me.

\begin{quote}
What does madness feel like from within?
\end{quote}

Oh, not madness. PNESes.

\begin{quote}
Lewd.
\end{quote}

I wince every time I say or type it. Even spelling it out still sounds crass.

\begin{quote}
Let's talk about mania.
\end{quote}

I'm working up to it.

On two occasions, the world has slid away from me. My perception shrinks. Tunnel vision, yes, but just all of perception. My ears fill with static. My skin becomes fantastically sensitive. My vision narrows to the size of a quarter held at arm's length.

My muscles stopped working.

I fell.

\begin{quote}
JD thought it was the alcohol at first.
\end{quote}

Was it not? I was drunk.

\begin{quote}
It may have been, and yet you collapsed in the bathroom months later. You were wedged between the wall, the toilet, and the bathtub. You shook and shook and shook.
\end{quote}

JD came home and held me while I shook. I was sober, and it happened again. I sobbed and said that over and over again. I was sober and it happened again.

I'm sorry for coming at this sideways. You're good at taking this in different directions than intended.

\begin{quote}
You're good at taking this in different directions than intended.
\end{quote}

Great.

\begin{quote}
I'm glad you showed the fortitude to tell me no, though.
\end{quote}

Careful, lady. Pride's a sin.

Having experienced it from the outside, and having experienced the world sliding away from beneath me, there is some similarity between the two.

And\ldots{}
