I did not fall into music of my own accord, my dad bought me a saxophone.

\begin{quote}
As his dad bought him before you.
\end{quote}

He wanted us to be alike in so many ways.

\begin{quote}
But you already knew that.
\end{quote}

He got me a saxophone and he and my mom pooled resourses to get me lessons.

\begin{quote}
And showed you to all his friends.
\end{quote}

I played at his Christmas parties. I played at his neighbor's Christmas parties.

\begin{quote}
Once, he was going to show you off to his friends at a barbeque, and you got so anxious and upset that you bent the octave key out of shape. You could only produce squeaks. You said it was an accident.
\end{quote}

I did it to get out of playing for the party, and instead it got me in trouble for being careless.

\begin{quote}
You were anything but. You were very careful. You acted with intent.
\end{quote}

I kept playing. Sometimes it was fun, sometimes it wasn't.

\begin{quote}
Once, you told your mom you weren't sure why she or your dad bothered with you learning to play the saxophone when all life was meaningless, anyway.
\end{quote}

How old was I, then? Ten? Eleven?

\begin{quote}
Dad made you apologize to her. I don't think either knew what to do with a nihilistic preteen.
\end{quote}

But it worked, in a roundabout way. I wound up in music. I wound up playing the saxophone and even sometimes enjoying it. I moved from that to the oboe.

And not just playing. I listened to tapes until they wore out. I made mixtapes of my dad's music after he taught me how to program his six-disc CD changer. After that, it was mix CDs, which I'd listen to on the bright yellow Sport Discman I carried everywhere. I fell asleep with headphones on more than once.

Music held --- continues to hold --- this sense of mystery about it. It worked on some level below spoken language, understandable without being text, affecting emotions without the cadence of words.

\begin{quote}
So why'd you quit?
\end{quote}

I can't just say ``computers'' and beg off, here, can I?

\begin{quote}
Nope.
\end{quote}
