Jay was a photographer. An artist. A true, honest, dyed-in-the-wool artist.

\begin{quote}
You looked up to him. Part of you wanted to be him. He could run a photography business funded by his day job of being a newspaper photographer. You thought of him when you changed your major to music.
\end{quote}

Did I? I was terrified of him.

\begin{quote}
Are they so different? `Awe', as a word, is not always a positive one.
\end{quote}

He took a picture of his son from a prior marriage that I still remember. Zach was shirtless, covered in mud that had started to dry and crack. He was looking down and to the left. He was holding something\ldots{}a sunflower, maybe? He had ram horns. The colors were muted\ldots{}was it black and white? Or was it just the mud?

I think I wanted to be that. Not Zach, necessarily. but I wanted to be that picture. I wanted to be a son that was loved like that. I wanted to be something as magical as that felt.

\begin{quote}
You also wanted to be the Phantom from Phantom of the Opera. Raoul was the bad guy, and you danced with your `Christine', Sarah Trowbridge, after school in front of your parents on the balance beam.
\end{quote}

I desperately craved being an artist. I drew endlessly. I played the saxophone, and sometimes I even liked it. I wrote music. My first song in third or fourth grade.

Maybe I did look up to him. He pulled it off.

\begin{quote}
Until he didn't.
\end{quote}

Right. When my mom told me to get in touch with him a decade and a half after the divorce, he owned a feed store down the block from me.

He left The Rocky Mountain News as lead photographer or something to pursue a job in 3D art. He bought Bryce 3D. He brought Lightwave. He spent a year learning Lightwave, and when the next version came out, he bought that and said it would take time to learn.

By that point, mom had been supporting all of us --- herself, him, me, my step-brother and two step-sisters --- for a year. She confided in me later that she had lost half a million dollars by the end of the relationship.

I didn't remember that folly. I majored in music and thought, ``Ah, yes, I can get a job doing library music or teaching choir while I work on my compositions'' but forgot how lucky he was when I met him.

\begin{quote}
You remembered and raced to teach yourself programming.
\end{quote}

\emph{You} remembered, maybe. I'd like to think of myself as a bit of a dreamer, even still.

\begin{quote}
Thus you, 1:19 AM on a Tuesday, gritting your teeth and trying not to write about mania.
\end{quote}
