When I came out, I did so by leaving a book of stories from gay youth on top of my mom's reading pile right before taking the bus down to visit my dad for the night. She called me after dinner and asked me if the book meant what she thought it did.

\begin{quote}
Did you ever tell --- really tell, with words and everything --- any of your family you were gay? Or trans?
\end{quote}

Twice. It was awful.

She must have told him at some point. Within a week, he told my mom I had to tell Zach that I was gay, too. He left the house on a run and made my mom stand in the kitchen with me to make me say, ``Zach, I'm gay.''

He just said, ``Oh, okay'', and kept pouring his Kix.

\begin{quote}
And then he stopped talking to you.
\end{quote}

Beside the point.

After I came out, Jay changed. He got mean--

\begin{quote}
``Got'', she says.
\end{quote}

Do you fear him, then?

\begin{quote}
Mu.
\end{quote}

Fair enough.

He got mean. That's when he got physical. That's when his anger got hot.

He started reading my emails. He found some reply notifications to some posts on a forum, where kids were talking about puberty. As kids do, there was some dick-size comparing. He read that aloud in front of my mom and mocked me for my answer. I had said seven inches. It was generous, sure, but keep in mind, I was way underweight at the time--

\begin{quote}
And him rather overweight.
\end{quote}

--and the skinnier you are, the less padding you have around the base of your penis.

\begin{quote}
We're getting off topic.
\end{quote}

Are we? I was starting to own my body. I was starting to find things that I felt I could feel proud about. I was starting to form relationships. Puberty was in full swing and I was realizing that there were people my age like me who would find me attractive.

And he took that and he humiliated me for it.

\begin{quote}
Let's talk about kink.
\end{quote}

Let's fucking not.
