My mom and I got in the habit of going to the dog part after work. We'd pick up Hank, our golden lad, and Chelsea, our Phyllis-Diller-slash-Yoda mutt, and drive across town to a field dedicated to letting dogs frolic with each other.

We'd play with other dogs. We'd through tennis ball after slobbery tennis ball. We got to know the other owners, mostly as ``oh, you're Sandy's owner''.

\begin{quote}
Or ``oh, you're Zephyr's owner''. You stole your own dog's name from some random aussie shepherd at the dog park.
\end{quote}

It was a meaningful period of my life. Is there some reason that wouldn't make a big impact on me?

\begin{quote}
It was Zephyr or Samuel. Even you knew what you wanted. You had him already named in your mind.
\end{quote}

And mom and I would talk. We'd walk the perimeter or, on hot days, sit at the lone picnic table under the lone tree and talk.

I was sitting on the table itself, feet on the bench, and she was sitting next to me, when she said, ``I think I'm going to get divorced from Jay. Is it alright if I use his reaction to you coming out as the reason?''

\begin{quote}
And you thought, ``I must be the luckiest boy in the world, being able to say that I knew my parents' divorce was your fault.''
\end{quote}

She told me how much money she had lost, and how he had changed even before I came out. I think that's when I realized that she might be a friend as well as a mother.

\begin{quote}
Gag.
\end{quote}

I know. I tried typing that eight different ways, and no matter what, it sounds like a Care Bears thing or whatever.

\begin{quote}
Back to the lilac-scented word, please.
\end{quote}

Gladly.
