Between when the divorce was decided and when we were supposed to move out to the townhouse my mom had purchased, mom adopted a dog. Helen had clearly been feral rather than a surrender, because she was impossible. She didn't know how to act around dogs. She didn't know how to act around people. She didn't know how to act indoors. She didn't know how to act outside.

\begin{quote}
She didn't know how to act around you, so you hid from her.
\end{quote}

She didn't know how to act around Jay, either, to be fair. One night, three days before we were supposed to move out, mom was sleeping on the couch downstairs, and Jay came down from the master bedroom to have the last word in one argument or another, and Helen raced up to greet him, nailing him right in the nuts with her paw.

Do you laugh?

\begin{quote}
Not my department.
\end{quote}

It took my mom and I a while to laugh about that. It's the type of story that usually gets a laugh, right? Nut-shots?

\begin{quote}
Hollywood decrees it must be so.
\end{quote}

Maybe my mom smiled when she woke me to tell me we had to move out immediately. It was Sunday. We moved all we could to the townhouse in my mom's Honda Civic and slept on newly-purchased air mattresses. Mine kept going flat.

\begin{quote}
Your mom would soon learn that she had rheumatoid arthritis. You complained to her about that in the morning, and she stayed quiet about how much pain she must have been in.
\end{quote}

The next day at school was nigh intolerable.

\begin{quote}
And yet you felt free.
\end{quote}

And yet I felt free.
