\begin{quote}
Carry on, then.
\end{quote}

The problem with abuse is that it robs you of time. If you have to cut out a portion of your past in order to live with yourself, suddenly that whole period of your life is something you miss out on entirely.

It might not hit you until later the full impact of that statement, of course, but we live all these different parts of our lives for a reason. Miss out on childhood, and suddenly you're a person who came into being out of nothingness at eighteen or whatever. Miss out on something, and you're a person missing all the context of a full life. You're a person who can't engage with those who do manage to lead a full life because you have no shared context.

\begin{quote}
Compile that with rape, and you wind up with hangups.
\end{quote}

Yes.

Let's pile being gender non-conforming, as well, and suddenly puberty is something that happens to other people. It's not yours. It's not something that ever happened, and it takes on this nearly magical significance. You learn about puberty from YA, from whimsical, whispered accounts from friends.

To want to reclaim that, take part in something so revered in society is natural. Or maybe just recast what you \emph{did} experience as something positive would be nice, right? Maybe even try to live a healthy life with what you've got by engaging with with your experiences, trying to understand them as you go.

\begin{quote}
And so here you are, some part of you intensely refocused on living the puberty you never had. Here you are roleplaying as a puberty-stricken girl after how poorly being a puberty-stricken boy treated you. Here you are, an only child who only had step-siblings for eight years or so living out fantasies of incest online.
\end{quote}

You can see where the shame might come from.

I understand the stated reasons for ageplay and such being frowned upon in society (I certainly hear about it often enough), don't get me wrong. This is a topic I would never engage with outside of consenting roleplay between adult players.

\begin{quote}
It's not risqué unless it comes with a disclaimer.
\end{quote}

But the sheer, overwhelming ire and disgust surrounding absolutely anything to do with it is enough to give even someone who prides themselves on openness pause.

Twitter and Mastodon, glorious platforms that they are, necessitates a separate identity. Not enough to feel torn in two, you have to \emph{actually} be torn in two. When I bitch about being `canceled' this is why. My life would be utterly destroyed were I public about trying to be healthy with it.

\begin{quote}
Thus encrypting this section.
\end{quote}

Thus encrypting this section.

It's something I've talked to a grand total of two people about. An additional two know about it, and one other suspects but politely doesn't engage. It's something I actively keep secret from at least one member of my immediate polycule. I have little desire to change that.

\begin{quote}
`Little.'
\end{quote}

Hush.

Anyway, as this project is built for such, I'm just trying to put this in words for myself, for us, to remember where I'm coming from.

For those of you who can't read it, I'm sorry. I've encrypted my apology, because to apologize to you would tip my hand, and my life would be over.
