\begin{quote}
You seem to be working ever close to some platonic perfection of what means to be Maddy.
\end{quote}

Yeah, this is one of those things where I seem to have looped all the way around from being proud of a work to being vaguely ashamed of it.

\begin{quote}
It's not bad, it's just very Maddy. Intensely Maddy. Catastrophically Maddy.
\end{quote}

Right.

So for those who are keeping track of all the goofy ergodic shit I do with my friend here--

\begin{quote}
Ally, not friend.
\end{quote}

Right. So for those who are keeping track, so far we have had:

\begin{itemize}
\tightlist
\item
  A site map generated using GraphViz
\item
  Flashing GIFs of art of my fursoñas faces pinned to the page by their third eyes.
\item
  A guided meditation session accompanied by disjointed noise music which grows in intensity as the text corrupts.
\item
  A foxy face peering over a wall thinking grawlix at you.
\item
  A somewhat magical sigil that spins.
\end{itemize}

It's time to take that one step further, so the next section is told through git commits for the source code for this site.

\begin{quote}
When do we get an ARG? And I'm still waiting on transclusion, by the way.
\end{quote}

Give it time.

\hypertarget{new-content}{%
\subsection{New content}\label{new-content}}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/makyo/ally.drab-makyo.com/pull/4}{Software}
\end{itemize}

\hypertarget{updated-content}{%
\subsection{Updated content}\label{updated-content}}

\begin{itemize}
\tightlist
\item
  \href{/18}{Ally 18}
\end{itemize}
